### 2015-09-12 docs/CDC 2015/final version/conclusion.tex
added CDC paper

% !TEX root = platooning.tex
\section{Conclusions and Future Work}
We considered single-file platoons of UAVs modeled by hybrid systems traveling along air highways. Using HJ reachability, we proposed liveness controllers and wrapped a safety controller around them to ensure no collision can occur from a single safety breach. Additional safety breaches can be handled by multiple altitude ranges in the airspace. Our simulations show that by putting vehicles into single-file platoons, the likelihood of having multiple safety breaches is low, and conflicts involving a single malfunctioning UAV or intruder can be resolved in a single altitude level.

### 2015-09-12 docs/CDC 2015/final version/formulation.tex
added CDC paper

% !TEX root = platooning.tex
\section{Problem Formulation \label{sec:formulation}}
\subsection{Vehicle Dynamics}
Consider a UAV whose dynamics are given by
\begin{equation}
\dot{x} = f(x,u)
\end{equation}

\noindent where $x\in\mathbb{R}^n$ represents the state, and $u\in\mathbb{R}^{n_u}$ represents the control action. In this paper, we will assume that each vehicle has the following simple model of a quadrotor:

\begin{equation} \label{eq:dyn}
\begin{aligned}
\dot{p}_x &= v_x, \qquad \dot{p}_y = v_y  \\
\dot{v}_x &= u_x, \qquad \dot{v}_y = u_y, \qquad |u_x|,|u_y| \le u_\text{max}
\end{aligned}
\end{equation}

\noindent where the state (at a fixed altitude) $x=(p_x, v_x, p_y, v_y)\in\mathbb{R}^4$ represents the quadrotor's position in the $x$-direction, its velocity in the $x$-direction, and its position and velocity in the $y$-direction, respectively. For convenience, we will denote the position and velocity $p=(p_x, p_y),v=(v_x,v_y)$, respectively. We will consider a group of $N$ quadrotors $Q_i, i=1\ldots,N$.

In general, the problem of collision avoidance among $N$ vehicles cannot be tractably solved using traditional dynamic programming approaches because the computation complexity of these approaches scales exponentially with the number of vehicles. Thus, in our present work, we will consider the situation where $N$ quadrotors form a platoon. The structure imposed by the platoon enables us to analyze the liveness and safety of the quadrotors in a tractable manner.

\subsection{Relative Dynamics and Augmented Relative Dynamics}
Besides Equation \eqref{eq:dyn}, we will also consider the relative dynamics between two quadrotors $Q_i,Q_j$. These dynamics can be obtained by defining the relative variables

\begin{equation} \label{eq:rel_var}
\begin{aligned}
p_{x,r} &= p_{x,i} - p_{x,j}, \qquad p_{y,r} = p_{y,i} - p_{y,j}\\
v_{x,r} &= v_{x,i} - v_{x,j}, \qquad v_{y,r} = v_{y,i} - v_{y,j}
\end{aligned}
\end{equation}

We treat $Q_i$ as Player 1, the evader who wishes to avoid collision, and we treat $Q_j$ as Player 2, the pursuer, or disturbance, that wishes to cause a collision. In terms of the relative variables given in \eqref{eq:rel_var}, we have

\begin{equation}
\begin{aligned}
\dot{p}_{x,r}& = v_{x,r}, &\dot{p}_{y,r} &= v_{y,r} \\
\dot{v}_{x,r}& = u_{x,i} - u_{x,j}, &\dot{v}_{y,r} &= u_{y,i} - u_{y,j}\\
\end{aligned}
\end{equation}

We also augment \eqref{eq:rel_var} with the velocity of $Q_i$ to impose a velocity limit when performing the avoidance maneuver.

\begin{equation} \label{eq:rel_dyn_aug}
\begin{aligned}
\dot{p}_{x,r} &= v_{x,r}, &\dot{p}_{y,r} &= v_{y,r} \\
\dot{v}_{x,r} &= u_{x,i} - u_{x,j}, &\dot{v}_{y,r}&= u_{y,i} - u_{y,j}\\
\dot{v}_{x,i} &= u_{x,i}, &\dot{v}_{y,i} &= u_{y,i} \\
\end{aligned}
\end{equation}

\subsection{Quadrotors in a Platoon\label{subsec:platoon_def}}
We consider a platoon of quadrotors to be a group of $M$ quadrotors $Q_{P_1}, \ldots, Q_{P_M}$ in a single-file formation. Not all of the $N$ quadrotors need to be in a platoon: $\{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$. $Q_{P_1}$ is the leader of the platoon, and $Q_{P_2},\ldots,Q_{P_M}$ are the followers. We will assume that the quadrotors in a platoon travel along an air highway, which is defined by as a path inside a pre-defined altitude range. The quadrotors maintain a separation distance of $b$. In order to allow for close proximity of the quadrotors and the ability to resolve multiple simultaneous safety breaches, we assume that in the event of a malfunction, a quadrotor will be able to exit the altitude range of the highway within a duration of $t_\text{internal}=1.5$. Such a requirement may be implemented practically as an emergency landing procedure to which the quadrotors revert when a malfunction is detected. Each quadrotor must be capable of performing a number of essential cooperative maneuvers. In this paper, we consider the following: 
\begin{itemize}
\item safely merging onto an air highway;
\item safely joining a platoon;
\item reacting to a malfunctioning vehicle in the platoon;
\item reacting to an intruder vehicle;
\item following the highway, a curve defined in space at constant altitude, at a specified speed;
\item maintaining a constant relative position and velocity with the leader of a platoon.
\end{itemize}

\subsection{Vehicles as Hybrid Systems}
A UAV in general may be in a number of modes of operations, depending on whether it is part of a platoon, and in the affirmative case, whether it is a leader or a follower. Therefore, it is natural to model quadrotors as hybrid systems \cite{Lygeros98,Lygeros12}. In this paper, we restrict the available maneuvers of each quadrotor depending on the mode. We assume that each quadrotor in the airspace has the following modes:

\begin{itemize}
\item Free: Vehicle not in a platoon. Available maneuvers: merge onto a highway, join a platoon on a highway.
\item Leader: Leader of platoon (could be by itself). Available maneuvers: travel along the highway at a pre-specified speed, merge current platoon with a platoon in front, leave the highway.
\item Follower: Vehicle following the platoon leader. Available maneuvers: follow a platoon, create a new platoon.
\item Faulty: Malfunctioned vehicle in a platoon: reverts to default behavior and descends after a duration of $t_\text{internal}$.
\end{itemize}

The available maneuvers and associated mode transitions are shown in Figure \ref{fig:vehicleModes}.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{"fig/vehicleModes"}
	\caption{Hybrid modes for vehicles in platoons.}
	\label{fig:vehicleModes}
\end{figure}

\subsection{Objectives}
Using the previously-mentioned modeling assumptions, we would like to address the following questions:

\begin{enumerate}
\item How do vehicles form platoons?
\item How can the safety of the vehicles be ensured during normal operation and when there is a malfunctioning vehicle within the platoon?
\item How can the platoon respond to intruders such as unresponsive UAVs, birds, or other aerial objects?
\end{enumerate}

The answers to these questions can be broken down into the maneuvers listed in Section \ref{subsec:platoon_def}. In general, the control strategies of each quadrotor have a liveness component, which specifies a set of states towards which the quadrotor aims to reach, and a safety component, which specifies a set of states that it must avoid. In this paper, we address both the liveness and safety component using reachability analysis.

### 2015-09-12 docs/CDC 2015/final version/introduction.tex
added CDC paper

% !TEX root = platooning.tex
\section{Introduction}
Unmanned aerial vehicle (UAV) systems have in the past been mainly used for military operations \cite{Tice91}. Recently, however, there has been an immense surge of interest in using UAVs for civil applications through projects such as Amazon Prime Air and Google Project Wing \cite{PrimeAir,ProjectWing,Debusk10}. As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone. This would equate to thousands of vehicles simultaneously in the air. As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) of the United States are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13}.

Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving a small number of vehicles \cite{Fisac15,Chen14,Ding08}. These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states. Reachability is powerful because it can be used for synthesizing both controllers that steer the system towards a goal (liveness controllers), and controllers that steer the system away from danger (safety controllers). Furthermore, HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems. The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ Partial Differential Equation (PDE) \cite{LSToolbox,Osher02,Sethian96}. However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles. This makes the computation intractable for large numbers of vehicles.

A considerable body of work has been done on the platooning of vehicles \cite{Kavathekar11}. For example, \cite{McMahon90} investigated the feasibility of vehicle platooning in terms of tracking errors in the presence of disturbances, taking into account complex nonlinear dynamics of each vehicle.  \cite{Hedrick92} explored several control techniques for performing various platoon maneuvers such as lane changes, merge procedures, and split procedures. In \cite{Lygeros98}, the authors modeled vehicles in platoons as hybrid systems, synthesized safety controllers, and analyzed throughput. Finally, reachability analysis was used in \cite{Alam11} to analyze a platoon of two trucks in order to minimize drag by minimizing the following distance while maintaining collision avoidance safety guarantees.

Previous analysis of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles. %In the context of HJ reachability, putting vehicles into platoons is desirable because of the additional structure that platoons impose on its members. With additional structure, pairwise safety guarantees of vehicles can be more easily translated into safety guarantees of all the vehicles in the platoon. 
In this paper, we attempt to reconciliate this trade-off by assuming a single-file platoon, which provides structure that allows pairwise safety guarantees from HJ reachability to translate to safety guarantees for the whole platoon. We first propose a hybrid systems model of UAVs in platoons to capture this structure. Then, we show how HJ reachability can be used to synthesize \textit{liveness controllers} that enable vehicles to reach a set of desired states, and wrap \textit{safety controllers} around the liveness controllers to prevent dangerous configurations such as collisions. Finally, we show simulation results of quadrotors forming a platoon, a platoon responding to a malfunctioning member, and a platoon responding to an outside intruder to illustrate the behavior of vehicles in these scenarios and demonstrate the guarantees provided by HJ reachability.

%Motivation:
%\begin{itemize}
%\item Applications of UAVs, potential numbeurs
%\item Importance of safety guarantees
%\item Computation complexity
%\end{itemize}
%
%Related work:
%\begin{itemize}
%\item Platooning references: lack of (?) safety guarantees
%\begin{itemize}\item\textcolor{blue}{Mention PATH papers \& Lygeros thesis}\end{itemize}
%\item HJI, safety guarantees, limited by dimensionality
%\end{itemize}
%
%Summary of results
%\begin{itemize}
%\item Hybrid systems model of vehicles
%\item Reachability guarantees wrapped around existing methods
%\item Reachability offers flexibility in terms of design
%\item Illustrative platoon functions
%\end{itemize}

### 2015-09-12 docs/CDC 2015/final version/platooning.tex
added CDC paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
\documentclass[letterpaper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage{amsmath}    % need for sub equations
\usepackage{amsfonts}
\usepackage{graphicx}   % need for figures
\usepackage{subcaption}
\usepackage{epsfig} 
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{cancel}
\usepackage{amssymb}
\usepackage{color}
%\usepackage{my_macros}
\usepackage[ruled,vlined,titlenotnumbered]{algorithm2e}

\title{\LARGE \bf
Safe Platooning of Unmanned Aerial Vehicles via Reachability}

\author{Mo Chen, Qie Hu, Casey Mackin, Jaime F. Fisac, and Claire J. Tomlin
\thanks{This work has been supported in part by NSF under CPS:ActionWebs (CNS-931843), by ONR under the HUNT (N0014-08-0696) and SMARTS (N00014-09-1-1051) MURIs and by grant N00014-12-1-0609, by AFOSR under the CHASE MURI (FA9550-10-1-0567). The research of M. Chen has received funding from the ``NSERC PGS-D'' Program. The research of J.F. Fisac has received funding from the ``la Caixa" Foundation.}
\thanks{All authors are with the Department of Electrical Engineering and Computer Sciences, University of California, Berkeley. \{mochen72,qiehu,cmackin,jfisac,tomlin\}@berkeley.edu}
}

\begin{document}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%
\begin{abstract}
Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, firefighting, and fast disaster response. As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met. Hamilton-Jacobi (HJ) reachability is a powerful framework for providing conditions under which these requirements can be met, and for synthesizing the optimal controller for meeting them. However, due to the curse of dimensionality, HJ reachability is only tractable for a small number of vehicles if their set of maneuvers is unrestricted. In this paper, we define a platoon to be a group of UAVs in a single-file formation. We model each vehicle as a hybrid system with modes corresponding to its role in the platoon, and specify the set of allowed maneuvers in each mode to make the analysis tractable. We propose several liveness controllers based on HJ reachability, and wrap a safety controller, also based on HJ reachability, around the liveness controllers. For a single altitude range, our approach guarantees safety for one safety breach; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges. We demonstrate the satisfaction of liveness and safety requirements through simulations of three common scenarios.
\end{abstract}

\input{introduction.tex}
% Introduction (1p)
%% Motivation
%% Related work
%% Summary of results

\input{formulation.tex}
% Problem formulation (1.5p)
%% A number of quadrotors forming a platoon in a single file
%% Platoon definition and functions

\input{solution.tex}
% Solution methodology (1.5-2p)
%% Hybrid model of vehicles
%% Reachability
%% Functions of platoons: following, joining, splitting

% \input{analysis.tex}
%% Information pattern, stability (0.5p)

\input{results.tex}
% Numerical Simuations (1-1.5p)
%% 1: normal operation: form platoon by joining --> just follow --> 1 quadrotor leaves
%% - Mo
%% 2: vehicles already in platoon, one of them goes rogue
%% - Casey
%% 3: vehicles in platoon, intruder vehicle
%% - Qie
%% 4: vehicles in platoon, another vehicle joining, one vehicle in platoon goes rogue
%%
%% followPlatoon - Jaime

\input{conclusion.tex}

% Conclusion (0.5p)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\addtolength{\textheight}{1cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

 \bibliographystyle{IEEEtran}
 \bibliography{references}
\end{document}

### 2015-09-12 docs/CDC 2015/final version/results.tex
added CDC paper

% !TEX root = platooning.tex
\section{Scenario Case Study \label{sec:scenarios}}
In this section, we consider several situations that quadrotors in a platoon on an air highway may commonly encounter, and show via simulations the behaviors that emerge from the controllers we defined in Sections \ref{sec:liveness} and \ref{sec:safety}.

\subsection{Forming a Platoon}
We first consider the scenario in which some quadrotors are trying to merge onto an initially unoccupied highway. In order to do this, each quadrotor first checks for safety with respect to the other quadrotors, and uses the safety controller if necessary, according to Section \ref{sec:safety}. Otherwise, the quadrotor uses the liveness controller described in Section \ref{sec:liveness}.

For the simulation example, the highway is specified by the line $p_y = 0.5p_x$, the point of entry on the highway is chosen to be $(\bar{p}_x, \bar{p}_y) = (4,2)$, and the target velocity is such that the quadrotors travel at a speed $\bar{v}=3$ along the direction of the highway. This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{subsec:highway_merge}.

The first quadrotor that completes merging onto the empty highway creates a platoon and becomes its leader, while subsequent quadrotors form a platoon behind the leader in a pre-specified order according to the process described in Section \ref{subsec:platoon_merge}. Here, we choose $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $b$ behind the last quadrotor in the platoon, and $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$. This gives us the target set $\mathcal{L}_P$.

Figures \ref{fig:normal2} and \ref{fig:normal5} show the simulation results. Since the liveness reachable sets are in 4D and the safety reachable sets are in 6D, we compute and plot their 2D slices based on the quadrotors' velocities and relative velocities.

Figure \ref{fig:normal2} illustrates the use of liveness and safety reachable sets using just two quadrotors to reduce visual clutter. The first quadrotor $Q_1$ (red disk) first travels in a straight line towards the highway merging point $\bar{x}$ (red circle) at $t=1.5$, because it is not yet in the liveness reachable set for merging onto the highway (red dotted boundary). When it is within the liveness reachable set boundary at $t=2.8$, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$. During the entire time, the $Q_1$ checks whether it may collide with $Q_2$ within a time horizon of $t_\text{external}$; we chose $t_\text{external}=3>t_\text{internal}$.

After $Q_1$ has reached $\bar{x}_H$, it forms a platoon, becomes the platoon leader, and continues to travel along the highway. $Q_2$ (blue disk), at $t=7$, begins joining the platoon behind $Q_1$, by moving towards the target $\bar{x}_P$ relative to the position of $Q_1$. When $Q_2$ moves inside the liveness reachable set boundary for joining the platoon (blue dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target whenever it is outside the safety reachable set (blue dashed boundary).

Figure \ref{fig:normal5} shows the behavior of all 5 quadrotors which eventually form a platoon and travel along the highway together. The liveness controllers allow the quadrotors to optimally and smoothly enter the highway and join platoons, while the safety controllers prevent collisions from occurring.

\begin{figure}
	\centering
	\includegraphics[width=0.35\textwidth]{"fig/normal2"}
	\caption{Reachable sets used to merge onto a highway to form a platoon (top subplots) and to join a platoon on the highway (bottom subplots).}
	\label{fig:normal2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.35\textwidth]{"fig/normal5"}
	\caption{Five quadrotors merging onto a highway.}
	\label{fig:normal5}
\end{figure}

\subsection{Malfunctioning Vehicle in Platoon}
We now consider a scenario where a quadrotor in a platoon of five malfunctions while the platoon is traveling along a highway. To best demonstrate the behavior of the other quadrotors in the platoon, this simulation assumes that $Q_{P_3}$, the middle quadrotor, malfunctions and reverses direction. When this happens, all of the other quadrotors in the platoon begin checking safety against it. In addition, $Q_{P_3}$ is removed from the platoon, causing the other quadrotors to treat it as an intruder.  Trailing quadrotors must leave the highway to avoid colliding with the faulty quadrotor.

Figure \ref{fig:faulty2} shows the platoon of quadrotors, $Q_i,i = 1,...,5$ with $P_i = i$, traveling along the highway. At $t=0, Q_3$ malfunctions and begins to track the highway in reverse. Once $Q_3$ malfunctions, it is removed from the platoon and treated as an intruder. The platoon is then restructured with the faulty quadrotor removed ($Q_{P_i} = Q_{i+1}$ for $i=3,4$). After avoiding $Q_3$, the trailing quadrotors $Q_4$ and $Q_5$ accelerate to reach their new platoon positions. $Q_1$ and $Q_2$ are unaffected by the malfunctioning quadrotor.

Figure \ref{fig:faulty2} also shows the safe reachable set of $Q_4$ with respect to $Q_3$ (green dashed line), and the safe reachable set of $Q_5$ with respect to $Q_4$ and $Q_3$ (purple dashed lines).

At $t=1,Q_4$ applies the safe controller to avoid entering the safe reachable set with respect to $Q_3$. During $Q_4$'s avoidance maneuver, $Q_5$ simply follows $Q_4$, and does not come across any safety breaches, as shown by the $t=1$ and $t=2.1$ subplots. The safety breach ends soon after, and by $t=4.5$, $Q_4$ begins merging back onto the highway, followed by $Q_5$, in order to continue to follow the platoon. In this particular case, the safety breach is resolved even without any altitude change.

%\begin{figure}
%	\center
%		\includegraphics[width=0.45\textwidth]{fig/faultyNoRsets}
%		\caption{A quadrotor in the platoon becomes faulty. The rest of the platoon safely avoids the quadrotor and continues normal operation as a platoon once the faulty quadrotor has been cleared.}
%		\label{fig:faulty1}
%\end{figure}

\begin{figure}
	\center
		\includegraphics[width=0.4\textwidth]{fig/faultyRsets}
		\caption{Reachable sets used by trailing quadrotors to avoid colliding with the faulty quadrotor.}
		\label{fig:faulty2}
\end{figure}

\subsection{Intruder Vehicle}
We now consider the scenario in which a platoon of quadrotors encounters an intruder vehicle. To avoid collision, each quadrotor checks for safety with respect to the intruder and any quadrotor in front and behind in the platoon. If necessary, each quadrotor switches to using the safety controller.

Figure \ref{fig:intruder1} shows the simulation result. At $t=0$, a platoon of 4 quadrotors, $Q_{P_i},i=1,\ldots,4$ with $P_i = i$, travel along the highway. An intruder vehicle $Q_0$ (red disk) starts from position $(40,30)$ and heads toward bottom-left of the grid.

The platoon leader $Q_{P_1}$'s (black disk) safety is unaffected by the intruder. Followers $Q_{P_2}$ (blue disk), $Q_{P_3}$ (green disk) and $Q_{P_4}$ (pink disk), on the other hand, must use the safety controller in order to avoid collision with the intruder ($t=3.3,6.2$). This causes their paths to deviate off the highway. Once each quadrotor is safe relative to the intruder, they rejoin the original platoon ($t=12.4$). Figure \ref{fig:intruder2} illustrates the use of safety reachable sets in this scenario using only $Q_{P_2}$ as an example. The safety reachable sets of $Q_{P_2}$ with respect to the intruder $Q_0$, $Q_{P_1}$ and $Q_{P_3}$ (red, black, green dashed lines) are shown. %With respect to $Q_0$, $Q_{P_2}$'s safety is considered to be breached if $V_S(-t_\text{external},x_{P_2}-x_0) \le 0$. To avoid possible collision with the intruder, $Q_{P_2}$ must remain outside the safety reachable set with respect to the intruder. The same applies to collision avoidance with $Q_{P_1}$ and $Q_{P_3}$. %\textcolor{red}{\sout{Note that safety reachable sets with $Q_{P_1}$ and $Q_{P_3}$ are much smaller than that with the intruder. This is because under normal conditions, vehicles in the same platoon have near-zero relative velocity. For this reason, they may only check possible collisions within the next 1.5 seconds, instead of 3 seconds for vehicles outside of the platoon. This allows vehicles to travel closer together within a platoon and thus increasing throughput on the air highway.}} \textcolor{blue}{The 1.5 seconds is because we made the assumption that malfunctioning vehicles will change altitude within 1.5 seconds.}

Initially, $Q_{P_2}$ ($P_2=2$) is a follower and is outside all 3 safety reachable sets. At time $t=0.6$, $Q_2$ comes to the boundary of the safety set with respect to the intruder and therefore must apply the safety control law to avoid potential future collision. Thus it splits the original platoon and becomes the leader of a new platoon consisting of itself, $Q_3$ and $Q_4$. $Q_2$ keeps using the safety controller until it is safe with respect to the intruder again at $t=3$. After $t=3$, $Q_2$ is safe to use the liveness controller again to merge back onto the highway and join the original platoon as a follower. Note that during the entire time, $Q_2$ maintains safety against the intruder, $Q_1$ and $Q_3$ by always staying outside of all three safety reachable sets.

\begin{figure}
	\centering
	\includegraphics[width=0.35\textwidth]{"fig/Intruder1"}
	\caption{Reaction of a platoon of 4 quadrotors on a highway to an intruder.}
	\label{fig:intruder1}
\end{figure}

\begin{figure}
	\centering
		\includegraphics[width=0.35\textwidth]{"fig/intruder2"}
	\caption{Reachable sets used by quadrotor $Q_2$ to avoid collision with respect to the intruder and quadrotors $Q_1$ and $Q_3$ in front and behind it respectively.}
	\label{fig:intruder2}
\end{figure}

### 2015-09-12 docs/CDC 2015/final version/solution.tex
added CDC paper

% !TEX root = platooning.tex
\section{Hamilton-Jacobi Reachability  \label{sec:HJI}}
\subsection{General Framework}
Consider a differential game between two players described by the system
\begin{equation} \label{eq:dyn}
\dot{x} = f(x, u_1, u_2), \text{for almost every }t\in [-T,0]
\end{equation}

\noindent where $x\in\mathbb{R}^n$ is the system state, $u_1\in \mathcal{U}_1$ is the control of Player 1, and $u_2\in\mathcal{U}_2$ is the control of Player 2. We assume $f:\mathbb{R}^n\times \mathcal{U}_1 \times \mathcal{U}_2 \rightarrow \mathbb{R}^n$ is uniformly continuous, bounded, and Lipschitz continuous in $x$ for fixed $u_1,u_2$, and the control functions $u_1(\cdot)\in\mathbb{U}_1,u_2(\cdot)\in\mathbb{U}_2$ are drawn from the set of measurable functions. Player 2 is allowed to use nonanticipative strategies \cite{Evans84,Varaiya67} $\gamma$, defined by

\begin{equation}
\begin{aligned}
\gamma &\in \Gamma := \{\mathcal{N}: \mathbb{U}_1 \rightarrow \mathbb{U}_2 \mid  u_1(r) = \hat{u}_1(r) \\
&\text{for almost every } r\in[t,s] \Rightarrow \mathcal{N}[u_1](r) \\
&= \mathcal{N}[\hat{u}_1](r) \text{ for almost every } r\in[t,s]\}
\end{aligned}
\end{equation}

In our differential game, the goal of Player 2 is to drive the system into some target set $\mathcal{L}$, and the goal of Player 1 is to drive the system away from it. The set $\mathcal{L}$ is represented as the zero sublevel set of a bounded, Lipschitz continuous function $l:\mathbb{R}^n\rightarrow\mathbb{R}$. We call $l(\cdot)$ the \textit{implicit surface function} representing the set $\mathcal L: \mathcal{L}=\{x\in\mathbb{R}^n \mid l(x)\le 0\}$.

Given the dynamics \eqref{eq:dyn} and the target set $\mathcal{L}$, we would like to compute the backwards reachable set, $\mathcal{V}(t)$:

\begin{equation}
\begin{aligned}
\mathcal{V}(t) &:= \{x\in\mathbb{R}^n \mid \exists \gamma\in\Gamma \text{ such that } \forall u_1(\cdot)\in\mathbb{U}_1, \\
&\exists s \in [t,0], \xi_f(s; t, x, u_1(\cdot), \gamma[u_1](\cdot)) \in \mathcal{L} \}
\end{aligned}
\end{equation}
where $\xi_f$ is the trajectory of the system satisfying initial conditions $\xi_f(t; x, t, u_1(\cdot), u_2(\cdot))=x$ and the following differential equation almost everywhere on $[-t, 0]$
\begin{equation}
\begin{aligned}
\frac{d}{ds}&\xi_f(s; x, t, u_1(\cdot), u_2(\cdot)) \\
&= f(\xi_f(s; x, t, u_1(\cdot), u_2(\cdot)), u_1(s), u_2(s))
\end{aligned}
\end{equation}

For this paper, we use the HJ formulation in \cite{Mitchell05}, which has shown that the backwards reachable set $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:

\begin{equation} \label{eq:HJIPDE}
\begin{aligned}
D_t &V +\min \{0, \max_{u_1\in\mathcal{U}_1} \min_{u_2\in\mathcal{U}_2} D_x V \cdot f(x,u_1,u_2) \} = 0, \\
&V(0,x) = l(x)
\end{aligned}
\end{equation}

\noindent from which we obtain $\mathcal{V}(t) = \{x\in\mathbb{R}^n \mid V(t,x)\le 0\}$. From the solution $V(t,x)$, we can also obtain the optimal controls for both players via the following:

\begin{equation} \label{eq:HJI_ctrl_syn}
\begin{aligned}
u_1^*(t,x) &= \arg \max_{u_1\in\mathcal{U}_1} \min_{u_2\in\mathcal U_2} D_x V(t,x) \cdot f(x,u_1,u_2)\\
u_2^*(t,x) &= \arg \min_{u_2\in\mathcal{U}_2} D_x V(t,x) \cdot f(x,u_1^*,u_2)
\end{aligned}
\end{equation}

In the special case where there is only one player (player 2 does not exist), we obtain an optimal control problem for a system with dynamics

\begin{equation} \label{eq:dyn_d}
\dot{x} = f(x, u), t\in [-T,0], u\in\mathcal U.
\end{equation}

The reachable set in this case would be given by the Hamilton-Jacobi-Bellman (HJB) PDE

\begin{equation} \label{eq:HJBPDE}
\begin{aligned}
D_t V(t,x) + \min \{0, \min_{u\in\mathcal{U}} D_x V(t,x) \cdot f(x,u)\} &= 0 \\
V(0,x) = l(x)&
\end{aligned}
\end{equation}

\noindent where the optimal control is given by

\begin{equation} \label{eq:HJB_ctrl_syn}
u^*(t,x) = \arg \min_{u\in\mathcal{U}} D_x V(t,x) \cdot f(x,u)
\end{equation}

For our application, we will use a several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real time 4D reachable set computations and tractable 6D reachable set computations.

\section{Liveness Controllers \label{sec:liveness}}
\subsection{Merging onto a Highway \label{subsec:highway_merge}}
We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity along the highway. Thus, a quadrotor would aim to drive the system \eqref{eq:dyn} to a state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set

\begin{equation}
\begin{aligned}
\mathcal{L}_H = \{x: |p_x-\bar{p}_x|\le r_{p_x}, |v_x-\bar{v}_x|\le r_{v_x}, \\
|p_y - \bar{p}_y| \le r_{p_y}, |v_y - \bar{v}_y|\le r_{v_y} \}.
\end{aligned}
\end{equation}

In this reachability problem, $\mathcal{L}_H$ is the target set, represented by the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE to be solved. The solution we obtain, $V_H(t,x)$, is the implicit surface function representing the reachable set $\mathcal V_H(t)$; $V_H(-T,x)\le 0$, then, specifies the reachable set $\mathcal{V}_H(T)$, the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$. This gives the algorithm for merging onto the highway:

\begin{enumerate}
\item Move towards $\bar{x}_H$ in a straight line until $V_H(-T,x)\le 0$. This heuristic works well in practice. 
\item Apply the optimal control extracted from $V_H(-T,x)$ according to \eqref{eq:HJB_ctrl_syn} until $\mathcal{L}_H$ is reached.
\end{enumerate}

\subsection{Merging into a Platoon \label{subsec:platoon_merge}}
We again pose the merging of a quadrotor into a platoon on an air highway as a reachability problem. Here, we would like quadrotor $Q_i$ to merge onto the highway and follow another quadrotor $Q_j$ in a platoon. Thus, we would like to drive the system given by \eqref{eq:rel_dyn_aug} to a specific $\bar{x}_P = (\bar{p}_{x,r}, \bar{v}_{x,r}, \bar{p}_{y,r}, \bar{v}_{y,r})$, or a small range of relative states defined by the set

\begin{equation}
\begin{aligned}
\mathcal{L}_P = \{x: |p_{x,r}-\bar{p}_{x,r}|\le r_{p_x}, |v_{x,r}-\bar{v}_{x,r}|\le r_{v_x}, \\
|p_{y,r} - \bar{p}_{y,r}| \le r_{p_y}, |v_{y,r} - \bar{v}_{y,r}|\le r_{v_y} \}
\end{aligned}
\end{equation}

The target set $\mathcal{L}_P$ is represented by the implicit surface function $l_P(x)$, which specifies the terminal condition of the HJI PDE \eqref{eq:HJIPDE}. The zero sublevel set of the solution to \eqref{eq:HJIPDE}, $V_P(-T,x)$, gives us the set of relative states from which $Q_i$ can reach the target and join the platoon following $Q_j$ within a duration of $T$. We assume that $Q_j$ moves along the highway at constant speed, so that $u_j(t)$ = 0. The following is a suitable algorithm for a quadrotor merging onto a highway and joining a platoon to follow $Q_j$:

\begin{enumerate}
\item Move towards $\bar{x}_P$ in a straight line until $V_P(-T,x)\le 0$.
\item Apply the optimal control extracted from $V_P(-T,x)$ according to \eqref{eq:HJI_ctrl_syn} until $\mathcal{L}_P$ is reached.
\end{enumerate}

\subsection{Other Quadrotor Maneuvers}
For the simpler maneuvers of traveling along a highway and following a platoon, we resort to simpler controllers described below.

\subsubsection{Traveling along a highway} \label{sec:travel_hwy}
We use a model-predictive controller (MPC) for traveling along a highway at a pre-specified speed. Here, a leader quadrotor tracks a constant-altitude path, defined as a curve $\bar{p}(s)$ parametrized by $s\in[0,1]$ in $p=(p_x, p_y)$ space (position space), while maintaining a velocity $\bar{v}(s)$ that corresponds to constant speed in the direction of the highway.

\subsubsection{Following a Platoon} \label{sec:follow_platoon}
Follower vehicles use a feedback control law tracking a nominal position and velocity in the platoon, with an additional feed-forward term given by the leader's acceleration input.

The $i$-th member of the platoon, $Q_{P_i}$, is expected to track a relative position in the platoon $r^i = (r_x^i,r_y^i)$ with respect to the leader's position $p_{P_1}$, and the leader's velocity $v_{P_1}$ at all times. The resulting control law has the form:
\begin{equation}\label{eq:follow}
u^i(t) = k_p \big[p_{P_1}(t) + r^i(t) - p^i(t) \big] + k_v\big[v_{P_1}(t) - v^i(t)\big] + u_{P_1}(t)
\end{equation}
for some $k_p,k_v>0$. A simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
\begin{equation}\label{eq:nominal_pos}
r^i(t) = - (i-1) b \frac{v_{P_1}}{\|v_{P_1}\|_2}
\end{equation}
where $b$ is the spacing between vehicles along the platoon. and $\frac{v_{P_1}}{\|v_{P_1}\|_2}$ is the platoon leader's direction of travel.

\section{Safety Controllers \label{sec:safety}}
\subsection{Wrapping Reachability Around Existing Controllers}
A quadrotor can use a liveness controller when it is not in any danger of collision with other quadrotors or obstacles. If the quadrotor could potentially be involved in a collision within the next short period of time, it must switch to a safety controller. In this section, we will demonstrate how HJ reachability can be used to both detect imminent danger and synthesize a controller that guarantees safety within a specified time horizon. For our safety analysis, we will use the model in Equation \eqref{eq:rel_dyn_aug}.

We begin by defining the target set $\mathcal{L}_S$, which characterizes configurations in relative coordinates for which quadrotors $Q_i,Q_j$ are considered to be in collision:

\begin{equation}
\begin{aligned}
\mathcal{L}_S = \{x: &|p_{x,r}|, |p_{y,r}|\le d \vee |v_{x,i}| \ge v_\text{max} \vee |v_{y,i}| \ge v_\text{max} \}
\end{aligned}
\end{equation}

With this definition, $Q_i$ is considered to be unsafe if $Q_i$ and $Q_j$ are within a distance $d$ in both $x$- and $y$-directions simultaneously, or if $Q_i$ has exceeded some maximum speed $v_\text{max}$ in either $x$- or $y$-direction. For illustration purposes, we choose $d=2$ meters, and $v_\text{max}= 5$ m/s.

We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJI PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition. As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the reachable set $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst case control. To avoid collisions, $Q_i$ must apply the safety controller according to \eqref{eq:HJI_ctrl_syn} on the boundary of the reachable set in order to avoid going into the reachable set. The following algorithm wraps our safety controller around liveness controllers:

\begin{enumerate}
\item For a specified time horizon $t$, evaluate$V_S(-t,x_i-x_j)$ for all $j\in \mathcal{Q}(i)$.

$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against. We discuss $\mathcal{Q}(i)$ in Section \ref{subsec:safety_guarantees}.

\item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:

If $\exists j\in \mathcal{Q}(i),V_S(-t,x_i-x_j)\le 0$, then $Q_i,Q_j$ are in potential conflict, and $Q_i$ must use a safety controller; otherwise $Q_i$ uses a liveness controller.
\end{enumerate}

\subsection{Platoon Safety Guarantees \label{subsec:safety_guarantees}}
Under normal operations in a single platoon, each follower quadrotor $Q_{P_i},i>1$ checks whether it is in the safety reachable set with respect to $Q_{P_{i-1}}$ and $Q_{P_{i+1}}$. So $\mathcal{Q}(i) = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$. Assuming there are no nearby quadrotors outside of the platoon, the platoon leader $Q_{P_1}$ checks safety against $Q_{P_2}$, and the platoon trailer $Q_{P_N}$ checks safety against $Q_{P_{N-1}}$. So $\mathcal{Q}(P_1)=\{P_2\}, \mathcal{Q}(P_N)=\{P_{N-1}\}$. No pair of quadrotors should be in an unsafe configuration if the liveness controllers are well-designed. Occasionally, a quadrotor $Q_k$ may behave unexpectedly due to faults, which may lead to an unsafe configuration.

With our choice of $\mathcal{Q}(i)$ and the assumption that the platoon is in a single-file formation, some quadrotor $Q_i$ would get into an unsafe configuration with $Q_k$, where $Q_k$ is likely to be the quadrotor in front or behind of $Q_i$. In this case, a ``safety breach" occurs. Our synthesis of the safety controller guarantees that between every pair of quadrotors $Q_i,Q_k$, as long as $V_S(-t,x_i- x_k)>0$, $\exists u_i$ to keep $Q_i$ from colliding with $Q_k$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $Q_k$. Therefore, as long as the number of ``safety breaches" is at most one, $Q_i$ can simply use the optimal control to avoid $Q_k$ and avoid collision for the time horizon of $t$. Since quadrotors in platoons are able to exit the current altitude range within a duration of $t_\text{internal}$, if we choose $t=t_\text{internal}$, the safety breach would always end before any collision can occur.

Within a duration of $t_\text{internal}$, there is a small chance that additional safety breaches may occur. However, as long as the total number of safety breaches does not exceed the number of affected quadrotors, collision avoidance of all the quadrotors can be guaranteed for the duration $t_\text{internal}$. However, as our simulation results show, putting quadrotors in single-file platoons makes the likelihood of multiple safety breaches low during a quadrotor malfunction and during the presence of one intruder vehicle.

In the event that multiple safety breaches occur for some of the quadrotors due to a malfunctioning quadrotor within the platoon or an intruding quadrotor outside of the platoon, those quadrotors with more than one safety breach still have the option of exiting the highway altitude range in order to avoid collisions. Every extra altitude range reduces the number of simultaneous safety breaches by $1$, so $K$ simultaneous safety breaches can be resolved using $K-1$ different altitude ranges.

Given that quadrotors within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons. By treating each platoon as a single unit, we reduce the number of individual quadrotors that need to check for safety against each other, reducing overall computation burden.

### 2015-09-12 code/platoon/@platoon/createLQR.m

@@ -1,9 +1,7 @@
-function K= createLobj(obj)
-
+function K= createLQR(obj)
 %creates an lqr controller for the quadrotor to follow the path
 % obj is the quadrotor object, and obj.A and obj.B describe the dynamics of
 % the linear dynamics of the quadrotor
 
-
-K=lqr(obj.A,obj.B,diag([1 2 1 2]),eye(2)*.01);
+K = lqr(obj.A, obj.B, diag([1 2 1 2]), eye(2)*.01);
 end

### 2015-09-21 docs/CDC 2015/final version/formulation.tex
no message

@@
 \noindent where $x\in\mathbb{R}^n$ represents the state, and $u\in\mathbb{R}^{n_u}$ represents the control action.
-In this paper, we will assume that each vehicle has the following simple model of a quadrotor:
+In this paper, we will assume that each vehicle has a simple kinematics model of a quadrotor:
 
@@
 
-\noindent where the state (at a fixed altitude) $x=(p_x, v_x, p_y, v_y)\in\mathbb{R}^4$ represents the quadrotor's position in the $x$-direction, its velocity in the $x$-direction, and its position and velocity in the $y$-direction, respectively.
+\noindent where the state (at a fixed altitude) $x=(p_x, v_x, p_y, v_y)\in\mathbb{R}^4$ represents the quadrotor's position in the $x$ direction, its velocity in the $x$ direction, and its position and velocity in the $y$ direction, respectively.
 For convenience, we will denote the position and velocity $p=(p_x, p_y),v=(v_x,v_y)$, respectively.
@@
 \subsection{Relative Dynamics and Augmented Relative Dynamics}
-Besides Equation \eqref{eq:dyn}, we will also consider the relative dynamics between two quadrotors $Q_i,Q_j$. These dynamics can be obtained by defining the relative variables
+Besides \eqref{eq:dyn}, we will also consider the relative dynamics between two quadrotors $Q_i,Q_j$. These dynamics can be obtained by defining the relative variables
 
@@
 A UAV in general may be in a number of modes of operations, depending on whether it is part of a platoon, and in the affirmative case, whether it is a leader or a follower.
-Therefore, it is natural to model quadrotors as hybrid systems \cite{Lygeros98,Lygeros12}.
+Therefore, it is natural to model vehicles as hybrid systems \cite{Lygeros98,Lygeros12}.
 In this paper, we restrict the available maneuvers of each quadrotor depending on the mode.
@@
 \begin{enumerate}
-\item How do vehicles form platoons?
+\item How can vehicles effectively form platoons?
 \item How can the safety of the vehicles be ensured during normal operation and when there is a malfunctioning vehicle within the platoon?
@@
 The answers to these questions can be broken down into the maneuvers listed in Section \ref{subsec:platoon_def}.
-In general, the control strategies of each quadrotor have a liveness component, which specifies a set of states towards which the quadrotor aims to reach, and a safety component, which specifies a set of states that it must avoid.
+In general, the control strategies of each vehicle have a liveness component, which specifies a set of states towards which the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.
 In this paper, we address both the liveness and safety component using reachability analysis.

### 2015-09-21 docs/CDC 2015/final version/introduction.tex
no message

@@
 Recently, however, there has been an immense surge of interest in using UAVs for civil applications through projects such as Amazon Prime Air and Google Project Wing \cite{PrimeAir,ProjectWing,Debusk10}.
-As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone.
-This would equate to thousands of vehicles simultaneously in the air.
-As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) of the United States are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13}.
+As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Space Administration (NASA) of the United States are also investigating air traffic control for autonomous vehicles to prevent collisions among potentially numerous UAVs \cite{FAA13}.
 
-Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving a small number of vehicles \cite{Fisac15,Chen14,Ding08}.
-These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
+Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving a small number of vehicles \cite{Fisac15,Chen14,Ding08}.
+These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the backwards reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
 Reachability is powerful because it can be used for synthesizing both controllers that steer the system towards a goal (liveness controllers), and controllers that steer the system away from danger (safety controllers).
-Furthermore, HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems.
-The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ Partial Differential Equation (PDE) \cite{LSToolbox,Osher02,Sethian96}.
+Furthermore, HJ formulations are flexible in terms of system dynamics, enabling the analysis of nonlinear systems.
+The power and success of HJ reachability analysis in previous applications is evident, especially since numerical tools are readily available to solve the associated HJ Partial Differential Equation (PDE) \cite{LSToolbox,Osher02,Sethian96}.
 However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles.
@@
 In \cite{Lygeros98}, the authors modeled vehicles in platoons as hybrid systems, synthesized safety controllers, and analyzed throughput.
-Finally, reachability analysis was used in \cite{Alam11} to analyze a platoon of two trucks in order to minimize drag by minimizing the following distance while maintaining collision avoidance safety guarantees.
+Finally, reachability analysis was used in \cite{Alam11} to analyze a platoon of two trucks in order to reduce drag by minimizing the following distance while maintaining collision avoidance safety guarantees.
 
-Previous analysis of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
+Previous analyses of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
 %In the context of HJ reachability, putting vehicles into platoons is desirable because of the additional structure that platoons impose on its members.

### 2015-09-21 docs/CDC 2015/final version/platooning.tex
no message

@@
 \author{Mo Chen, Qie Hu, Casey Mackin, Jaime F. Fisac, and Claire J. Tomlin
-\thanks{This work has been supported in part by NSF under CPS:ActionWebs (CNS-931843), by ONR under the HUNT (N0014-08-0696) and SMARTS (N00014-09-1-1051) MURIs and by grant N00014-12-1-0609, by AFOSR under the CHASE MURI (FA9550-10-1-0567).
+\thanks{This work is supported in part by NSF under CPS:ActionWebs (CNS-0931843) and CPS:FORCES (CNS1239166), by NASA under grants NNX12AR18A and UCSCMCA-14-022 (UARC), by ONR under grants N00014-12-1-0609, N000141310341 (Embedded Humans MURI), and MIT\_5710002646 (SMARTS MURI), and by AFOSR under grants UPenn-FA9550-10-1-0567 (CHASE MURI) and the SURE project.
 The research of M.

### 2015-09-21 docs/CDC 2015/final version/solution.tex
no message

@@
 The set $\mathcal{L}$ is represented as the zero sublevel set of a bounded, Lipschitz continuous function $l:\mathbb{R}^n\rightarrow\mathbb{R}$.
-We call $l(\cdot)$ the \textit{implicit surface function} representing the set $\mathcal L: \mathcal{L}=\{x\in\mathbb{R}^n \mid l(x)\le 0\}$.
+We call $l(\cdot)$ the \textit{implicit surface function} representing the set $\mathcal{L}=\{x\in\mathbb{R}^n \mid l(x)\le 0\}$.
 
@@
 \end{equation}
-where $\xi_f$ is the trajectory of the system satisfying initial conditions $\xi_f(t; x, t, u_1(\cdot), u_2(\cdot))=x$ and the following differential equation almost everywhere on $[-t, 0]$
+where $\xi_f$ is the trajectory of the system satisfying initial conditions $\xi_f(t; x, t, u_1(\cdot), u_2(\cdot))=x$ and the following differential equation almost everywhere on $[-t, 0]$:
 \begin{equation}
@@
 
-In the special case where there is only one player (player 2 does not exist), we obtain an optimal control problem for a system with dynamics
+In the special case where there is only one player (Player 2 does not exist), we obtain an optimal control problem for a system with dynamics
 
@@
 We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity along the highway.
-Thus, a quadrotor would aim to drive the system \eqref{eq:dyn} to a state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
+Thus, a vehicle would aim to drive the system \eqref{eq:dyn} to a state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
 
@@
 \begin{enumerate}
-\item Move towards $\bar{x}_H$ in a straight line until $V_H(-T,x)\le 0$. This heuristic works well in practice. 
+\item Move towards $\bar{x}_H$ in a straight line until $V_H(-T,x)\le 0$. This simple controller is chosen heuristically.
 \item Apply the optimal control extracted from $V_H(-T,x)$ according to \eqref{eq:HJB_ctrl_syn} until $\mathcal{L}_H$ is reached.
@@
 \subsection{Merging into a Platoon \label{subsec:platoon_merge}}
-We again pose the merging of a quadrotor into a platoon on an air highway as a reachability problem.
-Here, we would like quadrotor $Q_i$ to merge onto the highway and follow another quadrotor $Q_j$ in a platoon.
+We again pose the merging of a vehicle into a platoon on an air highway as a reachability problem.
+Here, we would like quadrotor $Q_i$ to merge onto the highway and follow another vehicle $Q_j$ in a platoon.
 Thus, we would like to drive the system given by \eqref{eq:rel_dyn_aug} to a specific $\bar{x}_P = (\bar{p}_{x,r}, \bar{v}_{x,r}, \bar{p}_{y,r}, \bar{v}_{y,r})$, or a small range of relative states defined by the set
@@
 We assume that $Q_j$ moves along the highway at constant speed, so that $u_j(t)$ = 0.
-The following is a suitable algorithm for a quadrotor merging onto a highway and joining a platoon to follow $Q_j$:
+The following is a suitable algorithm for a vehicle merging onto a highway and joining a platoon to follow $Q_j$:
 
@@
 In this section, we will demonstrate how HJ reachability can be used to both detect imminent danger and synthesize a controller that guarantees safety within a specified time horizon.
-For our safety analysis, we will use the model in Equation \eqref{eq:rel_dyn_aug}.
+For our safety analysis, we will use the model in \eqref{eq:rel_dyn_aug}.
 
-We begin by defining the target set $\mathcal{L}_S$, which characterizes configurations in relative coordinates for which quadrotors $Q_i,Q_j$ are considered to be in collision:
+We begin by defining the target set $\mathcal{L}_S$, which characterizes configurations in relative coordinates for which vehicles $Q_i,Q_j$ are considered to be in collision:
 
@@
 
-With this definition, $Q_i$ is considered to be unsafe if $Q_i$ and $Q_j$ are within a distance $d$ in both $x$- and $y$-directions simultaneously, or if $Q_i$ has exceeded some maximum speed $v_\text{max}$ in either $x$- or $y$-direction.
+With this definition, $Q_i$ is considered to be unsafe if $Q_i$ and $Q_j$ are within a distance $d$ in both $x$ and $y$ directions simultaneously, or if $Q_i$ has exceeded some maximum speed $v_\text{max}$ in either $x$ or $y$ direction.
 For illustration purposes, we choose $d=2$ meters, and $v_\text{max}= 5$ m/s.
@@
 Our synthesis of the safety controller guarantees that between every pair of quadrotors $Q_i,Q_k$, as long as $V_S(-t,x_i- x_k)>0$, $\exists u_i$ to keep $Q_i$ from colliding with $Q_k$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $Q_k$.
-Therefore, as long as the number of ``safety breaches" is at most one, $Q_i$ can simply use the optimal control to avoid $Q_k$ and avoid collision for the time horizon of $t$.
-Since quadrotors in platoons are able to exit the current altitude range within a duration of $t_\text{internal}$, if we choose $t=t_\text{internal}$, the safety breach would always end before any collision can occur.
+Therefore, as long as the number of ``safety breaches" is at most one, $Q_i$ can simply use the optimal control $u_i$ to avoid collision with $Q_k$ for the time horizon of $t$.
+Since by assumption, vehicles in platoons are able to exit the current altitude range within a duration of $t_\text{internal}$, if we choose $t=t_\text{internal}$, the safety breach would always end before any collision can occur.
 

### 2015-10-08 docs/AIAA 2015/high_eikon.tex
no message

% !TEX root = main.tex
\subsection{The Eikonal Equation -- Cost-Minimizing Path}

### 2015-10-08 docs/AIAA 2015/high_form.tex
no message

% !TEX root = main.tex
\section{Air Highways}
\subsection{Problem Formulation}
We consider air highways to be line segments of constant altitude over a region. On the highway, a number of platoons may be present. The concept of platoons will be proposed in Section \ref{sec:platooning}. For now, denote the line segments $\hw(s), s\in[0,1]$. In a horizontal plane of fixed altitude, the end points of the line segment are given by $x_0 = \hw(0)$ and $y_0\hw(1)$. We assign a speed of travel $v_\hw$ and specify the direction of travel to be the direction from $\hw(0)$ to $\hw(1)$, denoted using a unit vector $\hwd = \frac{\hw(1) - \hw(0)}{\lVert\hw(1) - \hw(0)\rVert_2}$.

Air highways not only provide structure to make the analysis of a large number of vehicles tractable, but also allow vehicles reach their destinations. Thus, given a origin-destination pair (eg. two cities), air highways must connect the two points while potentially satisfying other criteria. We call this the ``air highway placement problem'', and propose to address it in the following way:

\begin{enumerate}
\item Establish a cost map over a region of space. This cost map represents the aggregate cost of placing air highways over any point in space. The costs of placing air highways may include interference with commercial air spaces, cost of accidents, noise pollution, etc., and can be designed by government regulation bodies.
\item Compute the cost-minimizing path from an origin to multiple destinations. 
\item Convert the cost-minimizing path into a sequence of air highways. The endpoints of the resulting air highways can be thought of as waypoints in the airspace.
\end{enumerate}

### 2015-10-08 docs/AIAA 2015/high_sim.tex
no message

% !TEX root = main.tex
\subsection{Results}
To illustrate our air highway placement proposal, we used the San Francisco Bay Area as an example, and classified each point on the map into three different region. Each region has an associated cost, reflecting the desirability of flying a vehicle over an area in the region. In general, these costs can be arbitrary and determined by government regulation agencies. For illustration purposes, we assumed the following categories and costs:

\begin{itemize}
\item Region around airports: $\cost{airports}=b$,
\item Cities: $\cost{cities}=1$,
\item Water: $\cost{water}=b^{-2}$,
\item Other: $\cost{other}=b^{-1}$.
\end{itemize}

This assumption assigns costs in descending order to the categories ``region around airports'', ``cities'', ``water'', and ``other''. Flying a UAV in each category is more costly by a factor of $b$ compared to the next most important category. The factor $b$ is a tuning parameter that we adjusted to vary the relative importance of the different categories, and we used $b=4$ in the figures below.

Fig. \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function. The region enclosed by the black boundary represent ``regoin around airports'', which have the highest cost. The dark blue, yellow, and light blue regions represent the ``cities'', the ``water'', and the ``other''' categories, respectively. We assumed that the origin corresponds to the city ``Concord'', and chose a number of other major cities as destinations.

A couple of important observations can be made here. First, the cost-minimizing paths to the various destinations in general overlap, and only split up when they are very close to entering their destination cities. This is intuitively desirable because the number of air highways is kept low. In addition, the cost of flying in the airspace according to the cost map is minimized. Secondly, the spacing of the contours, which correspond to level curves of the value function, have a spacing corresponding to the cost map. This provides insight into the placement of air highways to destinations that were not illustrated.

\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{"fig/airHighway_results"}
	\caption{Cost-minimizing paths computed by the Fast Marching Method based on the assumed cost map of the San Francisco Bay Area}
	\label{fig:airHighway_results}
\end{figure}

### 2015-10-08 docs/AIAA 2015/main.tex
no message

\documentclass[letterpaper]{AIAA}

\newcommand{\hw}{\mathbb{H}}
\newcommand{\hwd}{\hat{d}}
\newcommand{\cost}[1]{c_\text{#1}}

\begin{document}

\title{Guaranteeing Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}

\author{Mo Chen\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.}}
\affiliation{Business or Academic Affiliation 1, City, State, Zip Code}
\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
\affiliation{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
\affiliation{Business or Academic Affiliation 2, City, State, Zip Code}

\begin{abstract}
\end{abstract}

\maketitle

\section*{Nomenclature}
(Nomenclature entries should have the units identified)\\
\noindent\begin{tabular}{@{}lcl@{}}
\textit{x}  &=& System state \\
\end{tabular} \\

\input{introduction.tex}
\input{high_form.tex}
\input{high_eikon.tex}
\input{high_sim.tex}
\input{plat_form.tex}
\input{plat_reach.tex}
\input{plat_intra.tex}
\input{plat_inter.tex}
\input{plat_safety.tex}
\input{plat_sim.tex}
\input{conclusions.tex}

\section*{Appendix}

\section*{Acknowledgments}
This work is supported in part by NSF under CPS:ActionWebs (CNS-0931843) and CPS:FORCES (CNS1239166), by NASA under grants NNX12AR18A and UCSCMCA-14-022 (UARC), by ONR under grants N00014-12-1-0609, N000141310341 (Embedded Humans MURI), and MIT\_5710002646 (SMARTS MURI), and by AFOSR under grants UPenn-FA9550-10-1-0567 (CHASE MURI) and the SURE project.

\section*{References}

\begin{thebibliography}{}
\bibitem{1} Vatistas, G. H., Lin, S., and Kwok, C. K., ``Reverse Flow Radius in Vortex Chambers,'' \textit{AIAA Journal}, Vol. 24, No. 11, 1986, pp. 1872, 1873. doi: 10.2514/3.13046
\bibitem{2} Dornheim, M. A., ``Planetary Flight Surge Faces Budget Realities,'' \textit{Aviation Week and Space Technology}, Vol. 145, No. 24, 9 Dec. 1996, pp. 44--46.
\bibitem{3} Terster, W., ``NASA Considers Switch to Delta 2,'' \textit{Space News}, Vol. 8, No. 2, 13--19 Jan. 1997, pp. 1, 18.
\bibitem{4} Peyret, R., and Taylor, T. D., \textit{Computational Methods in Fluid Flow}, 2$^{{\rm nd}}$ ed., Springer-Verlag, New York, 1983, Chaps. 7, 14.
\bibitem{5} Oates, G. C. (ed.), \textit{Aerothermodynamics of Gas Turbine and Rocket Propulsion}, AIAA Education Series, AIAA, New York, 1984, pp. 19, 136.
\bibitem{6} Volpe, R., ``Techniques for Collision Prevention, Impact Stability, and Force Control by Space Manipulators,'' \textit{Teleoperation and Robotics in Space}, edited by S. B. Skaar and C. F. Ruoff, Progress in Astronautics and Aeronautics, AIAA, Washington, DC, 1994, pp. 175--212.
\bibitem{7} Thompson, C. M., ``Spacecraft Thermal Control, Design, and Operation,'' \textit{AIAA Guidance, Navigation, and Control Conference}, CP849, Vol. 1, AIAA, Washington, DC, 1989, pp. 103--115
\bibitem{8} Chi, Y. (ed.), \textit{Fluid Mechanics Proceedings}, NASA SP-255, 1993.
\bibitem{9} Morris, J. D., ``Convective Heat Transfer in Radially Rotating Ducts,'' \textit{Proceedings of the Annual Heat Transfer Conference}, edited by B. Corbell, Vol. 1, Inst. of Mechanical Engineering, New York, 1992, pp. 227--234.
\bibitem{10} Chapman, G. T., and Tobak, M., ``Nonlinear Problems in Flight Dynamics,'' NASA TM-85940, 1984.
\bibitem{11} Steger, J. L., Jr., Nietubicz, C. J., and Heavey, J. E., ``A General Curvilinear Grid Generation Program for Projectile Configurations,'' U.S. Army Ballistic Research Lab., Rept. ARBRL-MR03142, Aberdeen Proving Ground, MD, Oct. 1981.
\bibitem{12} Tseng, K., ``Nonlinear Green's Function Method for Transonic Potential Flow,'' Ph.D. Dissertation, Aeronautics and Astronautics Dept., Boston Univ., Cambridge, MA, 1983.
\bibitem{13} Richard, J. C., and Fralick, G. C., ``Use of Drag Probe in Supersonic Flow,'' \textit{AIAA Meeting Papers on Disc} [CD-ROM], Vol. 1, No. 2, AIAA, Reston, VA, 1996.
\bibitem{14} Atkins, C. P., and Scantelbury, J. D., ``The Activity Coefficient of Sodium Chloride in a Simulated Pore Solution Environment,'' \textit{Journal of Corrosion Science and Engineering} [online journal], Vol. 1, No. 1, Paper 2, URL: \url{http://www.cp/umist.ac.uk/JCSE/vol1/vol1.html} [cited 13 April 1998].
\bibitem{15} Vickers, A., ``10-110 mm/hr Hypodermic Gravity Design A,'' \textit{Rainfall Simulation Database} [online database], URL: \url{http://www.geog.le.ac.uk/bgrg/lab.htm} [cited 15 March 1998].
\bibitem{16} TAPP, Thermochemical and Physical Properties, Software Package, Ver. 1.0, E. S. Microware, Hamilton, OH, 1992.
\bibitem{17} Scherrer, R., Overholster, D., and Watson, K., Lockheed Corp., Burbank, CA, U.S. Patent Application for a ``Vehicle,'' Docket No. P-01-1532, filed 11 Feb. 1979.
\bibitem{18} Doe, J., ``Title of Paper,'' \textit{Name of Journal} (to be published).
\bibitem{19} Doe, J., ``Title of Chapter,'' \textit{Name of Book}, edited by\ldots , Publisher's name and location (to be published).
\bibitem{20} Doe, J., ``Title of Work,'' Name of Archive, Univ. (or organization), City, State, Year (unpublished).
\end{thebibliography}
\end{document}

### 2015-10-08 docs/AIAA 2015/plat_form.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/formulation.tex
@@
-% !TEX root = platooning.tex
-\section{Problem Formulation \label{sec:formulation}}
-\subsection{Vehicle Dynamics}
+% !TEX root = main.tex
+\section{Unmanned Aerial Vehicle Platooning \label{sec:platooning}}
+\subsection{Problem Formulation}
+\subsubsection{Vehicle Dynamics}
 Consider a UAV whose dynamics are given by
@@
 
-\noindent where the state (at a fixed altitude) $x=(p_x, v_x, p_y, v_y)\in\mathbb{R}^4$ represents the quadrotor's position in the $x$-direction, its velocity in the $x$-direction, and its position and velocity in the $y$-direction, respectively.
+\noindent where the state $x=(p_x, v_x, p_y, v_y)\in\mathbb{R}^4$ represents the quadrotor's position in the $x$-direction, its velocity in the $x$-direction, and its position and velocity in the $y$-direction, respectively.
 For convenience, we will denote the position and velocity $p=(p_x, p_y),v=(v_x,v_y)$, respectively.
@@
 In general, the problem of collision avoidance among $N$ vehicles cannot be tractably solved using traditional dynamic programming approaches because the computation complexity of these approaches scales exponentially with the number of vehicles.
-Thus, in our present work, we will consider the situation where $N$ quadrotors form a platoon.
-The structure imposed by the platoon enables us to analyze the liveness and safety of the quadrotors in a tractable manner.
+Thus, in our present work, we will consider the situation where UAVs travel on air highways in platoons, defined in the following secions.
+The structure imposed by air highways and the platoon enables us to analyze the liveness and safety of the vehicles in a tractable manner.
 
-\subsection{Relative Dynamics and Augmented Relative Dynamics}
-Besides Equation \eqref{eq:dyn}, we will also consider the relative dynamics between two quadrotors $Q_i,Q_j$. These dynamics can be obtained by defining the relative variables
-
-\begin{equation} \label{eq:rel_var}
-\begin{aligned}
-p_{x,r} &= p_{x,i} - p_{x,j}, \qquad p_{y,r} = p_{y,i} - p_{y,j}\\
-v_{x,r} &= v_{x,i} - v_{x,j}, \qquad v_{y,r} = v_{y,i} - v_{y,j}
-\end{aligned}
-\end{equation}
-
-We treat $Q_i$ as Player 1, the evader who wishes to avoid collision, and we treat $Q_j$ as Player 2, the pursuer, or disturbance, that wishes to cause a collision.
-In terms of the relative variables given in \eqref{eq:rel_var}, we have
-
-\begin{equation}
-\begin{aligned}
-\dot{p}_{x,r}& = v_{x,r}, &\dot{p}_{y,r} &= v_{y,r} \\
-\dot{v}_{x,r}& = u_{x,i} - u_{x,j}, &\dot{v}_{y,r} &= u_{y,i} - u_{y,j}\\
-\end{aligned}
-\end{equation}
-
-We also augment \eqref{eq:rel_var} with the velocity of $Q_i$ to impose a velocity limit when performing the avoidance maneuver.
-
-\begin{equation} \label{eq:rel_dyn_aug}
-\begin{aligned}
-\dot{p}_{x,r} &= v_{x,r}, &\dot{p}_{y,r} &= v_{y,r} \\
-\dot{v}_{x,r} &= u_{x,i} - u_{x,j}, &\dot{v}_{y,r}&= u_{y,i} - u_{y,j}\\
-\dot{v}_{x,i} &= u_{x,i}, &\dot{v}_{y,i} &= u_{y,i} \\
-\end{aligned}
-\end{equation}
-
-\subsection{Quadrotors in a Platoon\label{subsec:platoon_def}}
+\subsubsection{Vehicles in a Platoon\label{subsec:platoon_def}}
 We consider a platoon of quadrotors to be a group of $M$ quadrotors $Q_{P_1}, \ldots, Q_{P_M}$ in a single-file formation.
@@
 Such a requirement may be implemented practically as an emergency landing procedure to which the quadrotors revert when a malfunction is detected.
-Each quadrotor must be capable of performing a number of essential cooperative maneuvers.
-In this paper, we consider the following:
+
+As part of a platoon, each quadrotor must be capable of performing a number of essential cooperative maneuvers. In this paper, we consider the following: 
 \begin{itemize}
@@
 
-\subsection{Vehicles as Hybrid Systems}
+\subsubsection{Vehicles as Hybrid Systems}
 A UAV in general may be in a number of modes of operations, depending on whether it is part of a platoon, and in the affirmative case, whether it is a leader or a follower.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/vehicleModes"}
+	\includegraphics[width=0.45\textwidth]{"fig/vehicleModes"}
 	\caption{Hybrid modes for vehicles in platoons.}
@@
 
-\subsection{Objectives}
+\subsubsection{Objectives}
 Using the previously-mentioned modeling assumptions, we would like to address the following questions:

### 2015-10-08 code/airHighway/bayAreaMap.m

@@ -114,7 +114,7 @@ contour(g2.xs{2}, g2.xs{1}, obs, [0 0], 'k-', 'linewidth', 2)
 
 axis(g.axis)
 axis square
-title('Bay Area Map, Shortest Paths')
+title('Bay Area Map, Cost-Minimizing Paths')
 
 % Shortest paths on top of speed profile and value function
 subplot(1,2,2)
@@ -132,7 +132,7 @@ contour(g2.xs{2}, g2.xs{1}, obs, [0 0], 'k-', 'linewidth', 2)
 
 axis(g.axis)
 axis square
-title('Speed Profile, Shortest Paths, Value Function')
+title('Cost Map, Cost-Minimizing Paths, Value Function')
 
 % Figure window size
 f2.Position(3:4) = [1043 420];

### 2015-10-08 code/airHighway/path2hws_test.m

@@ -10,14 +10,6 @@ g.bdry = @addGhostExtrapolate;
 g2 = g;
 g = processGrid(g);
 
-% ----- Load path -----
-load('bay_area_raw_paths')
-
-i = randi(length(spath));
-raw_path = spath{i};
-
-% Compute indices
-pts = path2hws(raw_path);
 
 % ----- Load images -----
 % Image indices
@@ -27,13 +19,23 @@ imInd2 = 850:1500;
 % Picture of Bay Area with city labels
 dots = imread('bayAreaLabels.png');
 dots = dots(imInd1, imInd2, :);
-
 g2.N = size(dots,1);
 g2 = processGrid(g2);
 
-% ----- Plot -----
 figure;
 image(g2.vs{1}, g2.vs{2},dots); hold on
-plot(raw_path(2,:), raw_path(1,:), 'b-')
-plot(pts(2,:), pts(1,:), 'ro-')
-axis square
+
+% ----- Load path -----
+load('bay_area_raw_paths')
+
+for i = 1:length(spath)
+  raw_path = spath{i};
+  
+  % Compute indices
+  pts = path2hws(raw_path);
+  
+  % ----- Plot -----
+  plot(raw_path(2,:), raw_path(1,:), 'r-');
+  plot(pts(2,:), pts(1,:), 'bo-')
+  axis square
+end

### 2015-10-13 docs/AIAA 2015/high_sim.tex
updated air highways section

@@
 
+\subsubsection{Cost-Minimizing Paths}
 Fig.
@@
 Secondly, the spacing of the contours, which correspond to level curves of the value function, have a spacing corresponding to the cost map.
-This provides insight into the placement of air highways to destinations that were not illustrated.
+This provides insight into the placement of air highways to destinations that were not shown in this example.
 
@@
 \end{figure}
+
+Fig. \ref{fig:airHighway_sparse} shows the result of converting the cost-minimizing paths to a small number of waypoints. The left subfigure shows
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.75\textwidth]{"fig/airHighway_sparse"}
+	\caption{Results of conversion from cost-minimizing paths to highway way points.}
+	\label{fig:airHighway_sparse}
+\end{figure}

### 2015-10-13 docs/AIAA 2015/high_waypoints.tex
updated air highways section

% !TEX root = main.tex
\subsection{From Paths to Waypoints}
Each of the cost-minimizing paths computed from the solution to the Eikonal equation consists of a set of points which are close to adjacent points. To sparsify this set of points to obtain a collection of waypoints, $\mathcal{W}_i$, which are also endpoints of air highways, we first add the destination point to the collection and note the path's heading. Next, we add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$. This process is repeated along the entire path. Finally, we add the origin points to the collection. We create a collection of these points for all the cost-minimizing paths.

If there is a large change in heading within a small section of the cost-minimizing path, then the collection $\mathcal{W}$ may contain several points which are close together. In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable); thus, many points in $\{\mathcal{W}_i\}_{i=1}^N$ may be very close together, cluttering the airspace with too many waypoints. We propose to sparsify the waypoints by clustering the points in $\{\mathcal{W}_i\}_{i=1}^N$. Each cluster contains points that are within a certain distance to the closest point in the cluster, and all points in each cluster are replaced with a single point located at the centroid of the cluster.

### 2015-10-13 code/airHighway/bayAreaWaypoints.m

@@ -1,0 +1,69 @@
+clear all;
+close all;
+
+addpath('..')
+
+% ----- Grid -----
+g.dim = 2;
+g.min = -1;
+g.max = 1;
+g.N = 201;
+g.bdry = @addGhostExtrapolate;
+g2 = g;
+g = processGrid(g);
+
+
+% ----- Load images -----
+% Image indices
+imInd1 = 150:800;
+imInd2 = 850:1500;
+
+% Picture of Bay Area with city labels
+dots = imread('bayAreaLabels.png');
+dots = dots(imInd1, imInd2, :);
+g2.N = size(dots,1);
+g2 = processGrid(g2);
+
+f = figure;
+subplot(1,2,2)
+image(g2.vs{1}, g2.vs{2},dots); hold on
+axis square
+
+subplot(1,2,1)
+image(g2.vs{1}, g2.vs{2},dots,'visible','off'); hold on
+axis square
+
+
+% ----- Load path -----
+load('bay_area_raw_paths')
+
+% Plot initial way points
+pts = cell(length(spath),1);
+colors = lines(length(spath));
+for i = 1:length(spath)
+  raw_path = spath{i};
+  
+  % Compute indices
+  pts{i} = path2hws(raw_path);
+  
+  % ----- Plot -----
+  subplot(1,2,1)
+  plot(pts{i}(2,:), pts{i}(1,:), '.:', 'color', colors(i,:))
+  axis square
+end
+
+% ----- Sparsify -----
+threshold = 0.025;
+sparse_pts = sparsify_paths(pts, threshold);
+for i = 1:length(sparse_pts)
+  subplot(1,2,2)
+  plot(sparse_pts{i}(2,:), sparse_pts{i}(1,:), 'x-', ...
+    'color', colors(i,:), 'linewidth', 2)
+  
+  subplot(1,2,1)
+  plot(sparse_pts{i}(2,:), sparse_pts{i}(1,:), 'x-', ...
+    'color', colors(i,:))
+end
+
+% Figure window size
+f.Position(3:4) = [1043 420];

### 2015-10-16 docs/AIAA 2015/high_waypoints.tex
no message

@@
 \subsection{From Paths to Waypoints}
-Each of the cost-minimizing paths computed from the solution to the Eikonal equation consists of a set of points which are close to adjacent points.
-To sparsify this set of points to obtain a collection of waypoints, $\mathcal{W}_i$, which are also endpoints of air highways, we first add the destination point to the collection and note the path's heading.
+Each of the cost-minimizing paths $\hpath_{ij}$ computed from the solution to the Eikonal equation consists of a set of points which are close to adjacent points.
+To sparsify this set of points to obtain a collection of waypoints, $\wpt_{ij}$, which are also endpoints of air highways, we first add the destination point to the collection and note the path's heading.
 Next, we add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$.
@@
 
-If there is a large change in heading within a small section of the cost-minimizing path, then the collection $\mathcal{W}$ may contain several points which are close together.
-In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable); thus, many points in $\{\mathcal{W}_i\}_{i=1}^N$ may be very close together, cluttering the airspace with too many waypoints.
-We propose to sparsify the waypoints by clustering the points in $\{\mathcal{W}_i\}_{i=1}^N$.
+If there is a large change in heading within a small section of the cost-minimizing path, then the collections $\wpt_{ij}$ may contain many points which are close together.
+In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), also cluttering the airspace with too many waypoints.
+We propose to sparsify the waypoints by clustering the points in $\wpt_{ij}$.
 Each cluster contains points that are within a certain distance to the closest point in the cluster, and all points in each cluster are replaced with a single point located at the centroid of the cluster.

### 2015-11-30 docs/AIAA 2015/main.tex
updated air highways section
no message
New template for platoon paper journal version

@@
-\documentclass[letterpaper]{AIAA}
+\documentclass[journal]{aiaa-pretty}
 
@@
 \newcommand{\cost}[1]{c_\text{#1}}
+\newcommand{\hpath}{\mathcal{P}}
+\newcommand{\wpt}{\mathcal{W}}
 
-\begin{document}
+\author{Mo Chen}
 
@@
 
-\author{Mo Chen\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.}}
-\affiliation{Business or Academic Affiliation 1, City, State, Zip Code}
-\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
-\affiliation{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
-\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
-\affiliation{Business or Academic Affiliation 2, City, State, Zip Code}
+\abstract{Abstract.}
 
-\begin{abstract}
-\end{abstract}
+\begin{document}
 
@@
 \input{high_eikon.tex}
+\input{high_waypoints.tex}
 \input{high_sim.tex}

### 2015-12-04 code/airHighway/tests/sparsify_paths_test.m
New Node super class to facilitate printing info, change highway simulation

@@ -24,12 +24,11 @@ dots = dots(imInd1, imInd2, :);
 g2.N = size(dots,1);
 g2 = processGrid(g2);
 
-figure;
-subplot(1,2,1)
+f1 = figure;
 image(g2.vs{1}, g2.vs{2},dots); hold on
 axis square
 
-subplot(1,2,2)
+f2 = figure;
 image(g2.vs{1}, g2.vs{2},dots,'visible','off'); hold on
 axis square
 
@@ -47,7 +46,7 @@ for i = 1:length(spath)
   pts{i} = path2hws(raw_path);
   
   % ----- Plot -----
-  subplot(1,2,2)
+  figure(f2)
   plot(pts{i}(2,:), pts{i}(1,:), '.:', 'color', colors(i,:))
   axis square
 end
@@ -55,11 +54,11 @@ end
 % ----- Sparsify -----
 sparse_pts = sparsify_paths(pts);
 for i = 1:length(sparse_pts)
-  subplot(1,2,1)
+  figure(f1)
   plot(sparse_pts{i}(2,:), sparse_pts{i}(1,:), 'x-', ...
     'color', colors(i,:), 'linewidth', 2)
   
-  subplot(1,2,2)
+  figure(f2)
   plot(sparse_pts{i}(2,:), sparse_pts{i}(1,:), 'x-', ...
     'color', colors(i,:))
 end

### 2015-12-04 code/platoon/@Node/Node.m

@@ -1,3 +1,13 @@
 classdef Node < handle
+  % Node class: superclass of TFM, Highway, Platoon, and Vehicle
+  % Used only for printing information
+  %
+  % The airspace can organized into a tree structure, where the TFM is the
+  % root with Highway objects as children. Each Highway object has Platoon
+  % objects as children, and each Platoon object has Vehicle objects as
+  % children. All vehicles which are part of a platoon would be part of
+  % this tree.
   
+  % No explicit constructor; use the constructor of TFM, Highway, Platoon,
+  % or Vehicle to instantiate a Node
 end

### 2015-12-04 code/platoon/@Node/getChildren.m

@@ -1,6 +1,8 @@
 function children = getChildren(obj)
 % getChildren(obj)
 % method of Node class
+%
+% Returns the children of a node
 
 if isa(obj, 'TFM')
   children = obj.hws;
@@ -20,7 +22,7 @@ elseif isa(obj, 'Vehicle')
   children = {};
   
 else
-  error('Unknown elements in printing queue!')
+  error('Unknown Node type!')
   
 end
 

### 2015-12-04 code/platoon/@Node/printBreadthFirst.m

@@ -1,4 +1,9 @@
 function printBreadthFirst(obj)
+% printBreadthFirst(obj)
+% method of the Node class
+%
+% Prints the entire subtree with the current object as root, breadth first
+
 queue = {obj};
 
 while ~isempty(queue)

### 2015-12-04 code/platoon/@Node/printInfo.m

@@ -1,10 +1,12 @@
 function printInfo(obj)
 % printInfo(obj)
 % Method of Node class
+%
+% Prints information about the current node
 
 if isa(obj, 'TFM')
-  %% ====================================================================
-  disp('TFM Info:')
+  %% =========================== TFM ====================================
+  disp('===== TFM Info =====')
   disp(['  Highway speed = ' num2str(obj.hw_speed)])
   disp(['  Intra-platoon separation distance = ' num2str(obj.ipsd)])
   disp(['  Number of registered vehicles = ' num2str(length(obj.aas))]);
@@ -12,21 +14,23 @@ if isa(obj, 'TFM')
   disp(['  Target threshold time = ' num2str(obj.ttt)]);
   disp(['  Reachable set threshold time = ' num2str(obj.rtt)]);
   disp(['  Period of zero order hold = ' num2str(obj.dt)]);
+  disp('====================')
   
 elseif isa(obj, 'Highway')
-  %% ====================================================================
-  disp('Highway Info:')
-disp(['  width = ' num2str(obj.width)])
-
-pla_str = '  Platoons:';
-for i = 1:length(obj.ps)
-  pla_str = [pla_str ' ' num2str(obj.ps{i}.ID)];
-end
-disp(pla_str)
-
+  %% ============================ Highway ===============================
+  disp('===== Highway Info =====')
+  disp(['  width = ' num2str(obj.width)])
+  
+  pla_str = '  Platoons:';
+  for i = 1:length(obj.ps)
+    pla_str = [pla_str ' ' num2str(obj.ps{i}.ID)];
+  end
+  disp(pla_str)
+  disp('========================')
+  
 elseif isa(obj, 'Platoon')
-  %% ====================================================================
-  disp('Platoon Info:')
+  %% ======================= Platoon ====================================
+  disp('===== Platoon Info =====')
   disp(['  ID = ' num2str(obj.ID)])
   
   veh_str = '  Vehicles:';
@@ -41,10 +45,11 @@ elseif isa(obj, 'Platoon')
   disp(['  n = ' num2str(obj.n)])
   disp(['  FP ID = ' num2str(obj.FP.ID)])
   disp(['  BP ID = ' num2str(obj.BP.ID)])
+  disp('========================')
   
 elseif isa(obj, 'Vehicle')
-  %% ====================================================================
-  disp('Vehicle Info:')
[…]

### 2015-12-04 code/platoon/@Node/printPreOrder.m

@@ -1,6 +1,9 @@
 function printPreOrder(obj)
 % printPreOrder(obj)
 % Method of Node class
+%
+% Prints the subtree with the current node as the root, depth first,
+% preorder traversal (root first, then children, recursively)
 
 obj.printInfo;
 children = obj.getChildren;

### 2015-12-04 code/platoon/@Platoon/Platoon.m

@@ -20,6 +20,9 @@ classdef Platoon < Node
     %       attempting to occupy the slot by joining platoon
     slotStatus
     
+    % List of vehicles joining the platoon
+    joiners
+    
     % handle to the highway the platoon is on
     hw
     
@@ -77,6 +80,7 @@ classdef Platoon < Node
       obj.vehicles{1} = leader;
       obj.slotStatus = zeros(nmax, 1);
       obj.slotStatus(1) = 1;
+      obj.joiners = cell(obj.nmax, 1);
       
       % Set vehicle mode to leader
       obj.vehicles{1}.q = 'Leader';

### 2015-12-04 code/platoon/@Platoon/addJoiner.m

@@ -1,0 +1,29 @@
+function idx = addJoiner(obj, veh)
+% idx = addJoiner(obj, veh)
+% method of Platoon class
+
+%% Update vehicle's old target platoon if needed
+if ~isempty(veh.pJoin)
+  prev_idx = veh.pJoin.findJoiner(veh);
+  veh.pJoin.removeJoiner(prev_idx);
+end
+veh.pJoin = obj;
+
+%% Update vehicle's old platoon if needed
+if ~isempty(veh.p)
+  veh.p.removeVehicle(veh.idx);
+end
+
+%% Get first available position in new platoon
+idx = obj.getFirstEmptySlot;
+
+if isempty(idx)
+  idx = [];
+  warning('No available slots for joining!')
+  return
+end
+
+%% Update joiner list and slot status in new platoon
+obj.slotStatus(idx) = -1;
+obj.joiners{idx} = veh;
+end

### 2015-12-04 code/platoon/@Platoon/findJoiner.m

@@ -1,0 +1,15 @@
+function idx = findJoiner(obj, veh)
+% idx = findJoiner(obj, veh)
+% method of Platoon class
+%
+% Returns the index of a joiner if found; otherwise returns empty
+
+idx = [];
+for i = 1:length(obj.joiners)
+  if veh == obj.joiners{i}
+    idx = i;
+    return
+  end
+end
+
+end

### 2015-12-04 code/platoon/@Platoon/removeJoiner.m

@@ -1,0 +1,12 @@
+function removeJoiner(obj, idx)
+% removeJoiner(obj, idx)
+% method of Platoon class
+%
+% Removes a joiner from the joiners list
+
+% Free up the slot
+obj.slotStatus(idx) = 0;
+obj.joiners{idx}.pJoin = [];
+obj.joiners{idx} = [];
+
+end

### 2015-12-04 code/platoon/@Platoon/removeVehicle.m

@@ -1,75 +1,87 @@
 function removeVehicle(obj, idx)
-% function u = removeVehicle(obj, vehicle)
+% function removeVehicle(obj, idx)
 %
 % Remove vehicle from platoon
 %
-% Inputs: obj     - platoon object
-%         vehicle - vehicle to be removed
+% Inputs: obj - platoon object
+%         idx - index of vehicle to be removed
 %
 % Qie Hu, 2015-07-01
 % Modified: Mo Chen, 2015-11-19
 
+vehToRemove = obj.vehicles{idx};
+
 %% Removing the last vehicle of the platoon
 if obj.n == 1
   % Update vehicle properties
-  obj.vehicles{idx}.q = 'Free';
-  obj.vehicles{idx}.FQ = [];
-  obj.vehicles{idx}.BQ = [];
-  obj.vehicles{idx}.idx = [];
+  vehToRemove.q = 'Free';
+  vehToRemove.FQ = [];
+  vehToRemove.BQ = [];
+  vehToRemove.idx = [];
 
   % Remove pointers to this platoon and delete
-  obj.vehicles{idx}.p = [];
+  vehToRemove.p = [];
   obj.hw.removePlatoon(obj.idx);
   delete obj;
   return
 end
 
 %% Removing a follower
-if strcmp(obj.vehicles{idx}.q, 'Follower')
-  % Update vehicle properties
-  obj.vehicles{idx}.q = 'Free';
-  obj.vehicles{idx}.FQ = [];
-  obj.vehicles{idx}.BQ = [];
-  obj.vehicles{idx}.idx = [];
-  
+if strcmp(vehToRemove.q, 'Follower')
   % If there are no vehicles behind, then make the front vehicle point to
   % itself. Otherwise, there is a vehicle behind this one. In this case, 
   % point vehicle in front to vehicle behind, and vice versa
-  if isempty(obj.vehicles{idx}.BQ)
-    obj.vehicles{idx}.FQ.BQ = obj.vehicles{idx}.FQ;
-  else
-    obj.vehicles{idx}.FQ.BQ = obj.vehicles{idx}.BQ;
-    obj.vehicles{idx}.BQ.FQ = obj.vehicles{idx}.FQ;
+  vehToRemove.FQ.BQ = vehToRemove.BQ;
+  if ~isempty(vehToRemove.BQ)
[…]

### 2015-12-04 code/platoon/@Quadrotor/followPlatoon.m

@@ -21,7 +21,10 @@ end
 idx = obj.p.getFirstEmptySlot;
 if idx < obj.idx
   obj.p.slotStatus(obj.idx) = 0;
+  obj.p.vehicles{obj.idx} = [];
+  
   obj.p.slotStatus(idx) = 1;
+  obj.p.vehicles{idx} = obj;
   obj.idx = idx;
 end
 

### 2015-12-04 code/platoon/@Quadrotor/joinPlatoon.m

@@ -4,6 +4,6 @@ function u = joinPlatoon(obj, platoon, tfm)
 %
 % Requests the control signal to join a platoon from the tfm
 
-u = tfm.joinPlatoon(obj, platoon, tfm);
+u = tfm.joinPlatoon(obj, platoon);
 
 end

### 2015-12-04 code/platoon/@TFM/TFM.m

@@ -1,5 +1,9 @@
 classdef TFM < Node
   % Traffic flow manager
+  % Checks safety of all vehicles
+  % Stores necessary reachable sets for safety and liveness
+  % Stores global constants in the air space
+  
   properties
     % Highways
     hws = {};

### 2015-12-04 code/platoon/@TFM/joinPlatoon.m

@@ -1,15 +1,28 @@
-function u = joinPlatoon(obj, veh, platoon, tfm)
+function u = joinPlatoon(obj, veh, platoon)
 % u = joinPlatoon(obj, platoon)
 % method of TFM class
+%
+% Tells the vehicle veh how to join the platoon
+%
+% Inputs: obj     - tfm object
+%         veh     - the vehicle joining the platoon
+%         platoon - the platoon
+% Output: u       - control signal for joining platoon
+%
+% Mo Chen, 2015-11-22
 
-if ~strcmp(veh.q, 'Free') && ~strcmp(veh.q, 'Leader')
-  error('Vehicle must be ''Free'' or ''Leader''!')
-end
+% if ~strcmp(veh.q, 'Free') && ~strcmp(veh.q, 'Leader')
+%   error('Vehicle must be ''Free'' or ''Leader''!')
+% end
 
 veh.tfm_status = 'busy';
 
-% Get first available slot
-idx = platoon.getFirstEmptySlot;
+% Check to see if the vehicle's target platoon is already set to this
+% platoon. If not, set this platoon to the target platoon for the vehicle
+idx = platoon.findJoiner(veh);
+if isempty(idx)
+  idx = platoon.addJoiner(veh);
+end
 
 % Compute phantom position
 pPh_rel = platoon.phantomPosition(obj.ipsd, idx);
@@ -20,11 +33,12 @@ u = getToRelpos(obj, veh, platoon.vehicles{1}, pPh_rel);
 % After merging, update properties
 if isempty(u)
   veh.tfm_status = 'idle';
+  platoon.removeJoiner(idx);
   
   % If vehicle is free, we're done
   if strcmp(veh.q, 'Free')
     platoon.insertVehicle(veh, idx);
-    u = veh.followPlatoon(tfm); % Needs to be after vehicle is a follower
+    u = veh.followPlatoon(obj); % Needs to be after vehicle is a follower
     return
   end
   
@@ -36,6 +50,6 @@ if isempty(u)
       idx = idx + 1;
     end
   end
-  u = veh.followPlatoon(tfm); % Needs to be after vehicle is a follower
+  u = veh.followPlatoon(obj); % Needs to be after vehicle is a follower
 end
 end

### 2015-12-04 code/platoon/@Vehicle/Vehicle.m

@@ -26,10 +26,10 @@ classdef Vehicle < Node
     %% Platoon-related properties
     p           % Pointer to platoon
     idx         % Vehicle index in platoon (determines phantom position)
-    FQ                 % Pointer to quadrotor in front (self if leader)
-    BQ                 % Pointer to quadrotor behind (self if tail)
+    FQ          % Pointer to quadrotor in front (self if leader)
+    BQ          % Pointer to quadrotor behind (self if tail)
     
-    pJoin   % platoon that vehicle is trying to join
+    pJoin       % platoon that vehicle is trying to join
     
     %% Figure handles
     hpxpy           % Position

### 2015-12-04 code/platoon/simulateChangeHighway.m

@@ -1,0 +1,130 @@
+function simulateChangeHighway()
+% simulateFormPlatoon()
+%
+% Simulates 5 quadrotors forming a single platoon on a highway
+
+%% TFM
+tfm = TFM;
+tfm.computeRS('qr_rel_target_V');
+tfm.computeRS('qr_abs_target_V');
+tfm.computeRS('qr_qr_safe_V');
+
+%% Highways
+theta1 = 2*pi*rand;
+theta2 = theta1 + 45*pi/180;
+hw_length = 200;
+z0b = hw_length*[-1 0];
+z1b = hw_length*[1 0];
+
+% Highway 1
+z0 = rotate2D(z0b, theta1);
+z1 = rotate2D(z1b, theta1);
+hw1 = Highway(z0, z1, tfm.hw_speed);
+tfm.addHighway(hw1);
+
+% Highway 2
+z0 = rotate2D(z0b, theta2);
+z1 = rotate2D(z1b, theta2);
+hw2 = Highway(z0, z1, tfm.hw_speed);
+tfm.addHighway(hw2);
+
+% plot
+figure;
+hw1.lpPlot;
+hold on
+hw2.lpPlot;
+hold on
+
+%% Quadrotors
+% Platoon 1 (4 vehicles)
+x0 = -10*tfm.ipsd;
+xs = x0 + 3*tfm.ipsd: -tfm.ipsd: x0;
+ys = zeros(size(xs));
+xs_ys = rotate2D([xs; ys], theta1);
+xs = xs_ys(1,:);
+ys = xs_ys(2,:);
+for j = 1:length(xs)
+  q = Quadrotor([xs(j) 0 ys(j) 0]);
+  tfm.regVehicle(q);
+  if j == 1
+    p1 = Platoon(q, hw1, tfm);
+  else
+    p1.insertVehicle(q, j);
+  end
+end
+
+% Platoon 2 (3 vehicles)
+x0 = -5*tfm.ipsd;
+xs = x0 + 2*tfm.ipsd: -tfm.ipsd: x0;
+ys = zeros(size(xs));
+xs_ys = rotate2D([xs; ys], theta2);
+xs = xs_ys(1,:);
+ys = xs_ys(2,:);
+for j = 1:length(xs)
+  q = Quadrotor([xs(j) 0 ys(j) 0]);
+  tfm.regVehicle(q);
+  if j == 1
+    p2 = Platoon(q, hw2, tfm);
+  else
[…]

### 2015-12-04 code/platoon/simulateFormPlatoon.m

@@ -24,7 +24,7 @@ hw.lpPlot;
 hold on
 
 %% Quadrotors
-xs = 0:25:100;
+xs = 100:-25:0;
 ys = sign(rand(size(xs))-0.5).*(125 - xs);
 xs_ys = rotate2D([xs; ys], theta);
 xs = xs_ys(1,:);
@@ -63,6 +63,7 @@ for i = 1:length(t)
 
 end
 
+tfm.printBreadthFirst;
 
 end
 

### 2015-12-04 code/platoon/tests/printing_tests.m

@@ -1,6 +1,15 @@
 function printing_tests()
 % printing_tests()
 % Tests functions that print information of nodes
+%
+%      TFM
+%     /     \
+%   hw1     hw2
+%   /          \
+%  p1          p2
+% /  \        /  \
+% q1  q3     q2  pl1
+%
 
 addpath('..')
 tfm = TFM;

### 2015-12-16 code/platoon/@Highway/printPreOrder.m
Completed simulations for forming platoon (showing reachable sets), changing highway, and responding to intruder. Also changed reachable set computation for quadrotor against quadrotors

@@ -1,9 +1,0 @@
-function printPreOrder(obj)
-% printPreOrder(obj)
-% method of Highway class
-
-obj.printInfo;
-for i = 1:length(obj.ps)
-  obj.ps{i}.printPreOrder;
-end
-end

### 2015-12-16 code/platoon/@TFM/checkAASafety.m

@@ -1,4 +1,4 @@
-function [safe, uSafe] = checkAASafety(obj)
+function [safe, uSafe, safe_val] = checkAASafety(obj)
 % function [safe, uSafe] = checkAASafety(obj)
 %
 % Checks the safety of every active agent with respect to all other active
@@ -16,16 +16,20 @@ function [safe, uSafe] = checkAASafety(obj)
 % different agents
 safe = ones(length(obj.aas));
 uSafe = cell(length(obj.aas), 1);
+safe_val = 10*ones(length(obj.aas));
 
 % Go through every pair of agents and return safety indicator and control
 for i = 1:length(obj.aas)
   uSafei = cell(1, length(obj.aas));
 
-  % Free vehicles check safety against all other free vehicles and leaders
+  % Free vehicles check safety against 
+  %   all other free vehicles
+  %   all leaders
   if strcmp(obj.aas{i}.q, 'Free')
     for j = 1:length(obj.aas)
-      if strcmp(obj.aas{j}.q, 'Free') || strcmp(obj.aas{j}.q, 'Leader')
-        [safe(i,j), uSafei{j}] = obj.checkPWSafety(i, j);
+      if strcmp(obj.aas{j}.q, 'Free') || ...
+          strcmp(obj.aas{j}.q, 'Leader') 
+        [safe(i,j), uSafei{j}, safe_val(i,j)] = obj.checkPWSafety(i, j);
       end
     end
   end
@@ -36,16 +40,20 @@ for i = 1:length(obj.aas)
     for j = 1:length(obj.aas)
       if obj.aas{j} == obj.aas{i}.BQ || strcmp(obj.aas{j}.q, 'Free') ...
           || strcmp(obj.aas{j}.q, 'Leader')
-        [safe(i,j), uSafei{j}] = obj.checkPWSafety(i, j);
+        [safe(i,j), uSafei{j}, safe_val(i,j)] = obj.checkPWSafety(i, j);
       end
     end
   end
 
-  % Followers check safety against vehicles in front and behind
+  % Followers check safety against 
+  %   Vehicle in the same platoon that is in front
+  %   Vehicle in the same platoon that is behind
+  %   'Free' vehicles (for CDC 2015 paper)
   if strcmp(obj.aas{i}.q, 'Follower')
     for j = 1:length(obj.aas)
[…]

### 2015-12-16 code/platoon/@TFM/checkPWSafety.m

@@ -1,4 +1,4 @@
-function [safe, uSafe] = checkPWSafety(obj, i, j)
+function [safe, uSafe, safe_val] = checkPWSafety(obj, i, j)
 % function checkPWSafety(obj, i, j)
 %          (check pairwise safety)
 %
@@ -6,18 +6,20 @@ function [safe, uSafe] = checkPWSafety(obj, i, j)
 % gives a safety-preserving input if necessary
 %
 % Inputs:  obj - tfm object
-%          i   - index of agent for whom safety is checked
-%          j   - index of agent against whom safety is checked
+%          i   - index of agent for whom safety is checked (evader)
+%          j   - index of agent against whom safety is checked (pursuer)
 % Outputs: safe - boolean specifying whether agent i is safe with respect
 %                 to agent j
 %          uSafe - safety-preserving input (empty if not needed)
 %
 % Mo Chen, 2015-11-04
+% Modified: Mo Chen, 2015-12-13
 
 % Vehicle is safe with respect to itself
 if isempty(obj.aas{j}) || obj.aas{i} == obj.aas{j}
   safe = 1;
   uSafe = [];
+  safe_val = 10;
   return
 end
 
@@ -26,7 +28,7 @@ switch(class(obj.aas{i}))
     %% agent i is a quadrotor
     switch(class(obj.aas{j}))
       case 'Quadrotor'
-        [safe, uSafe] = checkPWSafety_qr_qr(obj.qr_qr_safe_V, ...
+        [safe, uSafe, safe_val] = checkPWSafety_qr_qr(obj.qr_qr_safe_V, ...
           obj.safetyTime, obj.aas{i}, obj.aas{j});
         
       otherwise
@@ -38,7 +40,7 @@ switch(class(obj.aas{i}))
     %% agent i is a Plane
     switch(class(obj.aas{j}))
       case 'Plane'
-        [safe, uSafe] = checkPWSafety_pl_pl(obj.pl_pl_safe_V, ...
+        [safe, uSafe, safe_val] = checkPWSafety_pl_pl(obj.pl_pl_safe_V, ...
           obj.aas{i}, obj.aas{j});
         
       otherwise
@@ -48,7 +50,7 @@ switch(class(obj.aas{i}))
[…]

### 2015-12-16 code/platoon/@Vehicle/Vehicle.m

@@ -42,7 +42,8 @@ classdef Vehicle < Node
     hpvhist = cell(2,1);
     
     h_abs_target_V     % for getting to an absolute target
-    h_safe_V % Safety sets
+    h_rel_target_V     % for getting to a relative target
+    h_safe_V           % Safety sets
 
   end % end properties
 

### 2015-12-16 code/platoon/@Vehicle/plot_abs_target_V.m

@@ -13,21 +13,16 @@ if numel(level) == 1
   level = [level level];
 end
 
-% Project reachable set to 2D
-[g2D, data2D] = proj2D(abs_target_V.g, abs_target_V.data, [0 1 0 1], ...
-  rotate2D(obj.getVelocity, -target_heading));
-
-% translation and rotation
-gRot = rotateGrid(g2D, target_heading);
-gFinal = shiftGrid(gRot, target_position);
+[g2D, data2D] = get_target_V_plotData(obj, abs_target_V, ...
+  target_position, target_heading);
 
 % Plot result
 if isempty(obj.h_abs_target_V)
-  [~, obj.h_abs_target_V] = contour(gFinal.xs{1}, gFinal.xs{2}, data2D, ...
-    level, 'linestyle', ':', 'linewidth', 2);
+  [~, obj.h_abs_target_V] = contour(g2D.xs{1}, g2D.xs{2}, data2D, ...
+    level, 'linestyle', ':', 'linewidth', 2, 'color', obj.hpxpy.Color);
 else
-  obj.h_abs_target_V.XData = gFinal.xs{1};
-  obj.h_abs_target_V.YData = gFinal.xs{2};
+  obj.h_abs_target_V.XData = g2D.xs{1};
+  obj.h_abs_target_V.YData = g2D.xs{2};
   obj.h_abs_target_V.ZData = data2D;
   obj.h_abs_target_V.Visible = 'on';
 end

### 2015-12-16 code/platoon/@Vehicle/plot_safe_V.m

@@ -19,11 +19,11 @@ if numel(level) == 1
 end
 
 shift = other.getPosition;
-theta = other.getHeading;
+theta = obj.getHeading;
 
 % Project reachable set to 2D
 [g2D, data2D] = proj2D(safe_V.g, safe_V.data, [0 1 0 1], ...
-  rotate2D(obj.getVelocity, -theta));
+  rotate2D(obj.getVelocity - other.getVelocity, -theta));
 
 % translation and rotation
 gRot = rotateGrid(g2D, theta);
@@ -32,7 +32,7 @@ gFinal = shiftGrid(gRot, shift);
 % Plot result
 if isempty(obj.h_safe_V)
   [~, obj.h_safe_V] = contour(gFinal.xs{1}, gFinal.xs{2}, data2D, ...
-    level, 'linestyle', ':', 'linewidth', 2, 'color', other.hpxpy.Color);
+    level, 'linestyle', '--', 'linewidth', 2, 'color', obj.hpxpy.Color);
 else
   obj.h_safe_V.XData = gFinal.xs{1};
   obj.h_safe_V.YData = gFinal.xs{2};

### 2015-12-16 code/platoon/@Vehicle/unplotPosition.m

@@ -2,12 +2,12 @@ function unplotPosition(obj)
 % function unplotPosition(obj)
 % Unplot the current state and the trajectory of obj
 %
-%
 % Qie Hu, 2015-03-20
 
 if ~isempty(obj.hpxpyhist)
     set(obj.hpxpyhist, 'Visible','off');
 end
+
 if ~isempty(obj.hpxpy)
     set(obj.hpxpy, 'Visible','off');
 end

### 2015-12-16 code/platoon/@Vehicle/unplotSafeV.m

@@ -1,27 +1,0 @@
-function unplotSafeV(obj, others)
-% function unplotSafeV(obj, others)
-%
-% Unplot safe region around others that obj must stay out of in order to
-% be safe.
-%
-% Inputs: obj    - this quadrotor
-%         others - list of quadrotors for which reachable set plots should
-%                  be turned off
-%
-% Qie Hu, 2015-07-25
-% Modified: Mo Chen, 2015-10-20
-
-% Check input
-others = checkVehiclesList(others, 'quadrotor');
-
-% Go through vehicles list and compare with list of plotted vehicles. 
-% Turn off plots for matching vehicles
-for i = 1:length(others)
-  for j = 1:length(obj.safeV_vehicles)
-    if isequal(others{i}, obj.safeV_vehicles{j})
-      obj.hsafeV{j}.Visible = 'off';
-    end
-  end
-end
-
-end

### 2015-12-16 code/platoon/@Vehicle/unplot_safe_V.m

@@ -1,0 +1,12 @@
+function unplot_safe_V(obj)
+% function unplotSafeV(obj, others)
+%
+% Unplot safe region around others that obj must stay out of in order to
+% be safe.
+%
+% Qie Hu, 2015-07-25
+% Modified: Mo Chen, 2015-12-13
+
+obj.h_safe_V.Visible = 'off';
+
+end

### 2015-12-16 code/platoon/RS_core/quad_quad_collision_2D.m

@@ -1,20 +1,20 @@
 function [data, g, tau] = quad_quad_collision_2D(d, speed, visualize)
-% function [dataC, g2D, tau] = quad2Dcollision(d, visualize)
+% function [data, g2D, tau] = quad2Dcollision(d, speed, visualize)
 %
 % Computes collision reachable set for 4D relative quadrotor dynamics by
 % first computing 2D reachable sets in each axis and the reconstructing the
 % 4D reachable set
 %
 % The relative coordinate dynamics in each axis is
+% \dot x_r = v_r (= ve - vp)
+% \dot v_r = ue - up
 %
-% \dot x_r = v_r (= v1 - v2)
-% \dot v_r = u1 - u2
-%
-% where input u2 trying to avoid the target and
-%       input u1 trying to hit the target.
+% where input up trying to hit the target and
+%       input ue trying to avoid the target.
+%       
 %
 % Inputs:
-%   d         - separation distance (default = 2)
+%   d         - separation distance (default = 5)
 %   visualize - whether to visualize the 2D reachable set (default = 1)
 %
 % Outputs:
@@ -60,10 +60,10 @@ dissType = 'global';
 
 %---------------------------------------------------------------------------
 % Problem Parameters.
-u1Max = 3;
-u1Min = -3;
-u2Max = 3;
-u2Min = -3;
+upMax = 3;
+upMin = -3;
+ueMax = 3;
+ueMin = -3;
 
 %---------------------------------------------------------------------------
 % Approximately how many grid cells?
@@ -88,10 +88,10 @@ schemeData.hamFunc = @HamFunc;
 schemeData.partialFunc = @PartialFunc;
 
 % The Hamiltonian and partial functions need problem parameters.
-schemeData.u1Max = u1Max;
-schemeData.u1Min = u1Min;
-schemeData.u2Max = u2Max;
-schemeData.u2Min = u2Min;
+schemeData.upMax = upMax;
+schemeData.upMin = upMin;
+schemeData.ueMax = ueMax;
+schemeData.ueMin = ueMin;
 
 %---------------------------------------------------------------------------
 % Choose degree of dissipation.
[…]

### 2015-12-16 code/platoon/simulateFormPlatoon.m

@@ -1,90 +1,0 @@
-function simulateFormPlatoon()
-% simulateFormPlatoon()
-%
-% Simulates 5 quadrotors forming a single platoon on a highway
-
-%% TFM
-tfm = TFM;
-tfm.computeRS('qr_rel_target_V');
-tfm.computeRS('qr_abs_target_V');
-tfm.computeRS('qr_qr_safe_V');
-
-%% Highway
-theta = 2*pi*rand;
-hw_length = 500;
-z0 = [0 0];
-z1 = hw_length*[1 0];
-z1 = rotate2D(z1, theta);
-hw = Highway(z0, z1, tfm.hw_speed);
-tfm.addHighway(hw);
-
-% plot
-figure;
-hw.lpPlot;
-hold on
-
-%% Quadrotors
-xs = 100:-25:0;
-ys = sign(rand(size(xs))-0.5).*(125 - xs);
-xs_ys = rotate2D([xs; ys], theta);
-xs = xs_ys(1,:);
-ys = xs_ys(2,:);
-for j = 1:length(xs)
-  tfm.regVehicle(Quadrotor([xs(j) 0 ys(j) 0]));
-  tfm.aas{j}.plotPosition;
-end
-title('t=0')
-drawnow
-
-%% Target entry points
-tep = rotate2D([150 0], theta);
-
-%% Integration
-tMax = 30;
-t = 0:tfm.dt:tMax;
-
-u = cell(size(tfm.aas));
-for i = 1:length(t)
-  [safe, uSafe] = tfm.checkAASafety;
-  
-  for j = 1:length(tfm.aas)
-    if safe(j)
-      u{j} = controlLogic(tfm, tfm.aas{j}, tep);
-
-    else
-      u{j} = uSafe{j};
-    end
-    
-    tfm.aas{j}.updateState(u{j}, tfm.dt);
-    tfm.aas{j}.plotPosition;
-  end
-  title(['t=' num2str(t(i))])
-  drawnow
-
-end
-
-tfm.printBreadthFirst;
-
-end
-
-function u = controlLogic(tfm, veh, tep)
-% If no platoon has been formed, then try to go on the highway to form one
-if isempty(tfm.hws{1}.ps)
-  u = veh.goOnHighway(tfm.hws{1}, tep, tfm);
-  return
-end
-
-if strcmp(veh.q, 'Leader')
-  u = veh.followPath(tfm.hws{1});
-  return
-end
-
[…]

### 2015-12-16 code/platoon/simulations/simulateChangeHighway.m

@@ -1,7 +1,13 @@
-function simulateChangeHighway()
+function simulateChangeHighway(save_figures)
 % simulateFormPlatoon()
 %
 % Simulates 5 quadrotors forming a single platoon on a highway
+
+addpath('..')
+
+if nargin < 1
+  save_figures = false;
+end
 
 %% TFM
 tfm = TFM;
@@ -77,6 +83,16 @@ title('t=0')
 axis square
 drawnow
 
+if save_figures
+  fig_dir = [fileparts(mfilename('fullpath')) '/' mfilename '_figs'];
+  if ~exist(fig_dir, 'dir')
+    cmd = ['mkdir -p ' fig_dir];
+    system(cmd)
+  end
+  export_fig([fig_dir '/0'], '-png', '-m2')
+end
+
+
 %% Integration
 tMax = 23;
 t = 0:tfm.dt:tMax;
@@ -99,6 +115,9 @@ for i = 1:length(t)
   title(['t=' num2str(t(i))])
   drawnow
 
+  if save_figures
+    export_fig([fig_dir '/' num2str(i)], '-png', '-m2')
+  end
 end
 
 tfm.printBreadthFirst;

### 2015-12-16 code/platoon/simulations/simulateFormPlatoon.m

@@ -1,0 +1,132 @@
+function simulateFormPlatoon(save_figures)
+% simulateFormPlatoon()
+%
+% Simulates 5 quadrotors forming a single platoon on a highway
+
+addpath('..')
+
+if nargin < 1
+  save_figures = false;
+end
+
+%% TFM
+tfm = TFM;
+tfm.computeRS('qr_rel_target_V');
+tfm.computeRS('qr_abs_target_V');
+tfm.computeRS('qr_qr_safe_V');
+
+%% Highway
+theta = 2*pi*rand;
+hw_length = 350;
+z0 = [0 0];
+z1 = hw_length*[1 0];
+z1 = rotate2D(z1, theta);
+hw = Highway(z0, z1, tfm.hw_speed);
+tfm.addHighway(hw);
+
+% plot
+f = figure;
+
+hw.lpPlot;
+hold on
+f.Children.FontSize = 16;
+
+%% Quadrotors
+xs = 100:-25:0;
+ys = sign(rand(size(xs))-0.5).*(125 - xs);
+xs_ys = rotate2D([xs; ys], theta);
+xs = xs_ys(1,:);
+ys = xs_ys(2,:);
+for j = 1:length(xs)
+  tfm.regVehicle(Quadrotor([xs(j) 0 ys(j) 0]));
+  tfm.aas{j}.plotPosition;
+end
+
+title('t=0', 'FontSize', 16)
+drawnow
+
+if save_figures
+  fig_dir = [fileparts(mfilename('fullpath')) '/' mfilename '_figs'];
+  if ~exist(fig_dir, 'dir')
+    cmd = ['mkdir -p ' fig_dir];
+    system(cmd)
+  end
+  export_fig([fig_dir '/0'], '-png', '-m2')
+end
+
+%% Target entry point
+tep = rotate2D([150 0], theta);
+
+%% Integration
+tMax = 23;
+t = 0:tfm.dt:tMax;
+
+u = cell(size(tfm.aas));
+for i = 1:length(t)
+  [safe, uSafe] = tfm.checkAASafety;
+  
+  for j = 1:length(tfm.aas)
+    if safe(j)
+      u{j} = controlLogic(tfm, tfm.aas{j}, tep);
+
+    else
+      u{j} = uSafe{j};
+    end
+    
+    tfm.aas{j}.updateState(u{j}, tfm.dt);
+    tfm.aas{j}.plotPosition;
+  end
+  title(['t=' num2str(t(i))])
+  drawnow
+  
[…]

### 2015-12-16 code/platoon/simulations/simulateIntruder.m

@@ -1,0 +1,126 @@
+function simulateIntruder(save_figures)
+% simulateFormPlatoon()
+%
+% Simulates 5 quadrotors forming a single platoon on a highway
+
+addpath('..')
+
+if nargin < 1
+  save_figures = false;
+end
+
+%% TFM
+tfm = TFM;
+tfm.computeRS('qr_rel_target_V');
+tfm.computeRS('qr_abs_target_V');
+tfm.computeRS('qr_qr_safe_V');
+tfm.ipsd = 10;
+%% Highways
+theta = 2*pi*rand;
+hw_length = 300;
+z0 = hw_length*[-0.1 0];
+z1 = hw_length*[1 0];
+
+% Highway 1
+z0 = rotate2D(z0, theta);
+z1 = rotate2D(z1, theta);
+hw = Highway(z0, z1, tfm.hw_speed);
+tfm.addHighway(hw);
+
+% plot
+figure;
+hw.lpPlot;
+hold on
+
+%% Quadrotors
+% Platoon 1 (4 vehicles)
+x0 = 0;
+xs = x0: -tfm.ipsd: x0 - 3*tfm.ipsd;
+ys = zeros(size(xs));
+xs_ys = rotate2D([xs; ys], theta);
+xs = xs_ys(1,:);
+ys = xs_ys(2,:);
+vq = [10 0];
+vq = rotate2D(vq, theta);
+for j = 1:length(xs)
+  q = Quadrotor([xs(j) vq(1) ys(j) vq(2)]);
+  tfm.regVehicle(q);
+  if j == 1
+    p = Platoon(q, hw, tfm);
+  else
+    p.insertVehicle(q, j);
+  end
+end
+
+% Intruder
+pin = [250 50];
+vin = [10 0];
+vin = rotate2D(vin, 9*pi/8);
+pin = rotate2D(pin, theta);
+vin = rotate2D(vin, theta);
+intruder = Quadrotor([pin(1) vin(1) pin(2) vin(2)]);
+tfm.regVehicle(intruder);
+
+for j = 1:length(tfm.aas)
+  tfm.aas{j}.plotPosition;
+end
+title('t=0')
+axis equal
+drawnow
+
+if save_figures
+  fig_dir = [fileparts(mfilename('fullpath')) '/' mfilename '_figs'];
+  if ~exist(fig_dir, 'dir')
+    cmd = ['mkdir -p ' fig_dir];
+    system(cmd)
+  end
[…]

### 2015-12-16 code/platoon/tests/checkPWSafety_qr_qr_test.m

@@ -6,25 +6,27 @@ addpath('../RS_core')
 tfm = TFM;
 tfm.computeRS('qr_qr_safe_V');
 
-N = 10;
+N = 5;
 for i = 1:N
-  checkPWSafety_qr_qr_single(tfm)
+  checkPWSafety_qr_qr_single(tfm, i, N)
 end
 
 end
 
-function checkPWSafety_qr_qr_single(tfm)
-
-theta = 2*pi*rand;
+function checkPWSafety_qr_qr_single(tfm, i, N)
+disp(['Trial ' num2str(i)])
+theta1 = 2*pi*rand;
+theta2 = theta1 + 2*pi * i/(N+1);
 dist2 = 50;
-p1 = -rotate2D([dist2 0], theta) + rand(1,2);
-p2 = rotate2D([dist2 0], theta);
-v1 = rotate2D([10 0], theta);
+p1 = rotate2D([dist2 0], theta1) + rand(1,2);
+p2 = rotate2D([dist2 0], theta2);
+v1 = -rotate2D([10 0], theta1);
+v2 = -rotate2D([10 0], theta2);
 
 % Add quadrotors to TFM
 tfm.aas = {};
 tfm.regVehicle(Quadrotor([p1(1) v1(1) p1(2) v1(2)]));
-tfm.regVehicle(Quadrotor([p2(1) -v1(1) p2(2) -v1(2)]));
+tfm.regVehicle(Quadrotor([p2(1) v2(1) p2(2) v2(2)]));
 
 % Plot initial setup
 figure;
@@ -37,12 +39,12 @@ ylim([-dist2 dist2])
 axis square
 
 % Integration parameters
-tMax = 15;
+tMax = 10;
 t = 0:tfm.dt:tMax;
 
 % Integrate
 for i = 1:length(t)
-  [safe, uSafe] = tfm.checkAASafety;
+  [safe, uSafe, safe_val] = tfm.checkAASafety;
 
   for j = 1:length(tfm.aas)
     if safe(j)
@@ -51,13 +53,25 @@ for i = 1:length(t)
       u = uSafe{j};
     end
     
+    if j == 2
+      u = [0; 0];
+    end
+    
     tfm.aas{j}.updateState(u, tfm.dt);
     tfm.aas{j}.plotPosition;
     
-    % Plot safety reachable set for the other vehicle
[…]

### 2015-12-16 code/platoon/tests/getToPose_test.m

@@ -70,7 +70,7 @@ end
 hold on
 
 % Plot initial setup
-level = tfm.rtt/2; % Level of the value function to show
+level = tfm.rtt; % Level of the value function to show
 %% Main plot showing position and reachable set in position space
 tfm.aas{1}.plotPosition('b');
 tfm.aas{1}.plot_abs_target_V( ...

### 2015-12-16 code/platoon/tests/getToRelpos_test.m

@@ -62,6 +62,10 @@ for j = 1:length(tfm.aas)
   hold on
 end
 
+level = tfm.rtt;
+follower.plot_rel_target_V(tfm.qr_rel_target_V, ...
+  leader.getPosition, leader.getHeading, level)
+
 % Plot path of leader
 tMax = 30;
 x0 = leader_init_pos(1);
@@ -102,6 +106,10 @@ for i = 1:length(t)
     tfm.aas{j}.plotPosition;
   end
   
+
+  follower.plot_rel_target_V(tfm.qr_rel_target_V, ...
+  leader.getPosition, leader.getHeading, level)
+
   abs_pos = leader.getPosition + relpos;
   ha.XData = abs_pos(1);
   ha.YData = abs_pos(2);  

### 2015-12-16 docs/AIAA 2015/high_eikon.tex
no message

@@
 \subsection{The Eikonal Equation -- Cost-Minimizing Path}
+Consider the cost map $\cmap(\pos_x, \pos_y)$ which captures the cost incurred for UAVs flying over the position $\pos = (\pos_x, \pos_y)$.
+Potential costs include fuel, noise pollution, and damage due to accidents.
+A position with high cost indicates that the position is undesirable for UAVs to fly over.
+For example, highly populated areas or the region around airports may be assigned high costs, while unpopulated areas may be assigned a low cost.
+
+Given the cost map $\cmap(\pos_x, \pos_y)$, suppose a UAV flies from an origin point $p^o = (\pos_x^o, \pos_y^o)$ to a destination point $p^d = (\pos_x^d, \pos_y^d)$ along some path $\ppath(s)$ parametrizes by the parameters $s$.
+Let $\ppath(s_0) = p^o$ denote the origin, and $\ppath(s_1) = p^d$ denote the destination.
+All intermediate $s$ values denote the intermediate positions of the path, i.e.
+$\ppath(s) = \pos(s) = (\pos_x(s), \pos_y(s))$.
+
+Along the entire path $\ppath(s)$, the cumulative cost $\ccost(\ppath)$ is incurred. Define $\ccost$ as follows:
+
+\begin{equation}
+\ccost(\ppath) = \int_{s_0}^{s_1} \cmap(\ppath(s)) ds
+\end{equation}
+
+The problem of finding the cost-minimizing path is finding the path such that the above cost is minimized.
+More generally, given an origin point $p^o$, we would like to compute the function $\ocost$ representing optimal cumulative cost for any destination point $\pos$:
+
+\begin{equation}
+\begin{aligned}
+\ocost(\pos_x, \pos_y) &= \min_{\ppath(\cdot)} \ccost(\ppath) \\
+&= \min_{\ppath(\cdot)} \int_{s_0}^{s_1} \cmap(\ppath(s)) ds
+\end{aligned}
+\end{equation}
+
+The solution to the Eikonal equation \eqref{eq:eikonal} precisely computes the function $\ocost$ given the cost map $\cmap$. Once $V$ is found, the path $\ppath$ can be obtained via gradient descent.
+
+\begin{equation}
+\label{eq:eikonal}
+\cmap(\pos)|\nabla \ocost(\pos)| = 1
+\end{equation}
+
+\eqref{eq:eikonal} can be efficiently computed numerically using the fast marching method \cite{}

### 2015-12-16 docs/AIAA 2015/main.tex
no message

--- 2015-10-08 docs/AIAA 2015/main.tex
@@
 
+\newcommand{\pos}{p}
+\newcommand{\vel}{v}
 \newcommand{\hw}{\mathbb{H}}
@@
 \newcommand{\cost}[1]{c_\text{#1}}
-
-\begin{document}
+\newcommand{\hpath}{\mathcal{P}}
+\newcommand{\wpt}{\mathcal{W}}
+\newcommand{\cmap}{c}
+\newcommand{\ccost}{C}
+\newcommand{\ppath}{\mathbb{P}}
+\newcommand{\ocost}{V}
 
@@
 \begin{thebibliography}{}
-\bibitem{1} Vatistas, G. H., Lin, S., and Kwok, C. K., ``Reverse Flow Radius in Vortex Chambers,'' \textit{AIAA Journal}, Vol. 24, No. 11, 1986, pp. 1872, 1873. doi: 10.2514/3.13046
-\bibitem{2} Dornheim, M. A., ``Planetary Flight Surge Faces Budget Realities,'' \textit{Aviation Week and Space Technology}, Vol. 145, No. 24, 9 Dec. 1996, pp. 44--46.
-\bibitem{3} Terster, W., ``NASA Considers Switch to Delta 2,'' \textit{Space News}, Vol. 8, No. 2, 13--19 Jan. 1997, pp. 1, 18.
-\bibitem{4} Peyret, R., and Taylor, T. D., \textit{Computational Methods in Fluid Flow}, 2$^{{\rm nd}}$ ed., Springer-Verlag, New York, 1983, Chaps. 7, 14.
-\bibitem{5} Oates, G. C. (ed.), \textit{Aerothermodynamics of Gas Turbine and Rocket Propulsion}, AIAA Education Series, AIAA, New York, 1984, pp. 19, 136.
-\bibitem{6} Volpe, R., ``Techniques for Collision Prevention, Impact Stability, and Force Control by Space Manipulators,'' \textit{Teleoperation and Robotics in Space}, edited by S.
-B.
-Skaar and C.
-F.
-Ruoff, Progress in Astronautics and Aeronautics, AIAA, Washington, DC, 1994, pp.
-175--212.
-\bibitem{7} Thompson, C. M., ``Spacecraft Thermal Control, Design, and Operation,'' \textit{AIAA Guidance, Navigation, and Control Conference}, CP849, Vol. 1, AIAA, Washington, DC, 1989, pp. 103--115
-\bibitem{8} Chi, Y. (ed.), \textit{Fluid Mechanics Proceedings}, NASA SP-255, 1993.
-\bibitem{9} Morris, J.
-D., ``Convective Heat Transfer in Radially Rotating Ducts,'' \textit{Proceedings of the Annual Heat Transfer Conference}, edited by B.
-Corbell, Vol.
-1, Inst.
-of Mechanical Engineering, New York, 1992, pp.
-227--234.
-\bibitem{10} Chapman, G. T., and Tobak, M., ``Nonlinear Problems in Flight Dynamics,'' NASA TM-85940, 1984.
-\bibitem{11} Steger, J.
-L., Jr., Nietubicz, C.
-J., and Heavey, J.
-E., ``A General Curvilinear Grid Generation Program for Projectile Configurations,'' U.S.
-Army Ballistic Research Lab., Rept.
-ARBRL-MR03142, Aberdeen Proving Ground, MD, Oct.
-1981.
-\bibitem{12} Tseng, K., ``Nonlinear Green's Function Method for Transonic Potential Flow,'' Ph.D. Dissertation, Aeronautics and Astronautics Dept., Boston Univ., Cambridge, MA, 1983.
-\bibitem{13} Richard, J. C., and Fralick, G. C., ``Use of Drag Probe in Supersonic Flow,'' \textit{AIAA Meeting Papers on Disc} [CD-ROM], Vol. 1, No. 2, AIAA, Reston, VA, 1996.
-\bibitem{14} Atkins, C.
-P., and Scantelbury, J.
-D., ``The Activity Coefficient of Sodium Chloride in a Simulated Pore Solution Environment,'' \textit{Journal of Corrosion Science and Engineering} [online journal], Vol.
-1, No.
-1, Paper 2, URL: \url{http://www.cp/umist.ac.uk/JCSE/vol1/vol1.html} [cited 13 April 1998].
-\bibitem{15} Vickers, A., ``10-110 mm/hr Hypodermic Gravity Design A,'' \textit{Rainfall Simulation Database} [online database], URL: \url{http://www.geog.le.ac.uk/bgrg/lab.htm} [cited 15 March 1998].
-\bibitem{16} TAPP, Thermochemical and Physical Properties, Software Package, Ver. 1.0, E. S. Microware, Hamilton, OH, 1992.
-\bibitem{17} Scherrer, R., Overholster, D., and Watson, K., Lockheed Corp., Burbank, CA, U.S. Patent Application for a ``Vehicle,'' Docket No. P-01-1532, filed 11 Feb. 1979.
-\bibitem{18} Doe, J., ``Title of Paper,'' \textit{Name of Journal} (to be published).
-\bibitem{19} Doe, J., ``Title of Chapter,'' \textit{Name of Book}, edited by\ldots , Publisher's name and location (to be published).
-\bibitem{20} Doe, J., ``Title of Work,'' Name of Archive, Univ. (or organization), City, State, Year (unpublished).
+\bibitem{1} J.
+A.
+Sethian , ``A fast marching level set method for monotonically advancing fronts,'' \textit{Proceedings of the National Academy of Sciences of the United States of America}, Vol.
+93, 1996, pp.
+1591-1595
+
 \end{thebibliography}

### 2015-12-16 docs/AIAA 2015/plat_form.tex
no message

@@
 \begin{aligned}
-\dot{p}_x &= v_x, \qquad \dot{p}_y = v_y  \\
-\dot{v}_x &= u_x, \qquad \dot{v}_y = u_y, \qquad |u_x|,|u_y| \le u_\text{max}
+\dot{\pos}_x &= \vel_x, \qquad \dot{\pos}_y = \vel_y  \\
+\dot{\vel}_x &= u_x, \qquad \dot{\vel}_y = u_y, \qquad |u_x|,|u_y| \le u_\text{max}
 \end{aligned}
@@
 
-\noindent where the state $x=(p_x, v_x, p_y, v_y)\in\mathbb{R}^4$ represents the quadrotor's position in the $x$-direction, its velocity in the $x$-direction, and its position and velocity in the $y$-direction, respectively.
-For convenience, we will denote the position and velocity $p=(p_x, p_y),v=(v_x,v_y)$, respectively.
+\noindent where the state $x=(\pos_x, \vel_x, \pos_y, \vel_y)\in\mathbb{R}^4$ represents the quadrotor's position in the $x$-direction, its velocity in the $x$-direction, and its position and velocity in the $y$-direction, respectively.
+For convenience, we will denote the position and velocity $\pos=(\pos_x, \pos_y),\vel=(\vel_x,\vel_y)$, respectively.
 We will consider a group of $N$ quadrotors $Q_i, i=1\ldots,N$.

### 2015-12-16 code/platoon/@Plane4/Plane4.m

@@ -88,20 +88,5 @@ classdef Plane4 < Vehicle
       end
     end
 
-    function plotSafeV(obj, others, safeV, t)
-      % function plotSafeV(obj, others, safeV, t)
-      %
-      % Plots the safe region around others that obj must stay out of in order to
-      % be safe.
-      %
-      % Inputs: obj   - this plane
-      %         other - other plane
-      %         safeV - Reachable set
-      %         t     - time horizon
-      %
-      % TODO: implement this function
-      % Mahesh Vashishtha, 2015-12-3
-      others = checkVehiclesList(others, 'plane');
-    end
   end % end methods
 end % end classdef

### 2015-12-16 code/platoon/legacy/simulateIntruder.m

@@ -1,0 +1,350 @@
+function simulateIntruder(from_checkpoint, save_graphics, output_directory, visualize_vehicle_on)
+% function simulateIntruder(from_checkpoint, save_graphics, output_directory)
+%
+% Simulates Simulates a platoon behavior with intruder.
+%
+% Inputs:  from_checkpoint  - whether to load previous checkpoint
+%          save_graphics    - whether to export graphics (for making an
+%                            animation)
+%          output_directory - for graphics export
+%                             - requires export_fig package
+%                             - don't include a "/" at the end
+%
+% Author: Qie Hu, 2015-07-14
+
+% Default input parameters
+if nargin<1
+  from_checkpoint = false;
+end
+
+if nargin<2
+  save_graphics = false;
+end
+
+if nargin<3
+  output_directory = 'saved_graphics';
+end
+
+if nargin<4
+  visualize_vehicle_on = false;
+end
+
+cvx_quiet true % Shuts cvx up if using MPC controller in followPath
+warning('off','all')
+
+% Checkpoint directory and file
+check_point_dir = 'checkpoints';
+check_point = [check_point_dir '/' mfilename '.mat'];
+
+%% Initialization
+if from_checkpoint
+  disp('Loading from last checkpoint')
+  load(check_point)
+  
+else
+  % Make directory if needed
+  system(['mkdir ' check_point_dir]);
+  
+  tEnd = 10;                 % End of simulation time
+  dt = 0.1;                 % Sampling time
+  t = 0:dt:tEnd;            % Time horizon
+  tSteps = 5;               % MPC horizon in followPath
+  gridSize = 50;
+  v = 3;                  % Target highway speed
+  d = 2;                  % Safe separation distance
+  
+  % Get reachability information
+  [reachInfo, safeV] = generateReachInfo();
+  
+  
+  % ===== Create highway here =====
+  z1 = [0 0];
+  z2 = [gridSize gridSize];
+  hw = highway(z1, z2, v);
+  
+  % ===== Create intruder here =====
[…]

### 2015-12-16 code/platoon/legacy/simulateIntruder2.m

@@ -1,0 +1,369 @@
+function simulateIntruder2(from_checkpoint, save_graphics, output_directory, visualize_vehicle_on)
+% function simulateIntruder(from_checkpoint, save_graphics, output_directory)
+%
+% Simulates Simulates a platoon behavior with intruder.
+%
+% Inputs:  from_checkpoint  - whether to load previous checkpoint
+%          save_graphics    - whether to export graphics (for making an
+%                            animation)
+%          output_directory - for graphics export
+%                             - requires export_fig package
+%                             - don't include a "/" at the end
+%
+% Author: Qie Hu, 2015-07-25
+
+% Default input parameters
+if nargin<1
+    from_checkpoint = false;
+end
+
+if nargin<2
+    save_graphics = false;
+end
+
+if nargin<3
+    output_directory = 'saved_graphics';
+end
+
+if nargin<4
+    visualize_vehicle_on= false;
+end
+    
+
+cvx_quiet true % Shuts cvx up if using MPC controller in followPath
+warning('off','all')
+
+% Checkpoint directory and file
+check_point_dir = 'checkpoints';
+check_point = [check_point_dir '/' mfilename '.mat'];
+
+%% Initialization
+if from_checkpoint
+    disp('Loading from last checkpoint')
+    load(check_point)
+    
+else
+    % Make directory if needed
+    system(['mkdir ' check_point_dir]);
+    
+    tEnd = 8;                 % End of simulation time
+    dt = 0.1;                 % Sampling time
+    t = 0:dt:tEnd;            % Time horizon
+    tSteps = 5;               % MPC horizon in followPath
+    gridSize = 50;
+    v = 3;                  % Target highway speed
+    d = 2;                  % Safe separation distance
+    
+    % Get reachability information
+    [reachInfo, safeV] = generateReachInfo();
+    
+    
+    % ===== Create highway here =====
+    z1 = [0 0];
+    z2 = [gridSize gridSize];
+    hw = highway(z1, z2, v);
+    
+    % ===== Create intruder here =====
+    qiX0 = [25;17];       % Initial position
+    qiXt = [-5;17];       % Final position
[…]

### 2015-12-16 code/platoon/legacy/simulateIntruderTest.m

@@ -1,0 +1,117 @@
+function simulateIntruder()
+
+cvx_quiet true
+
+
+tEnd = 20;                  % End of simulation time
+dt = 0.1;                   % Sampling time
+numQ = 6;                  % Number of quadrotors in platoon
+tFollow = 2;                % Follow time between quadrotors inside platoon
+gridSize = 60;             % Size of grid
+
+
+% Get reachability information
+[reachInfo, safeV] = generateReachInfo();
+
+% intruding quadrotor
+intruderX0 = [35;20];       % Initial position
+intruderXt = [0;gridSize];       % Final position
+Intruder = quadrotor(0, dt, [intruderX0(1);-3;intruderX0(2);3]);
+
+
+% Define paths
+highwayPath = @(s)rpath(s,[0;gridSize/2],[gridSize;gridSize/2]);
+intruderPath = @(s)rpath(s,intruderX0,intruderXt);
+
+
+% put some quadrotors in a horizontal line and create a platoon
+quadrotors = cell({});
+quadrotors{1} = quadrotor(1, dt, [25;4;gridSize/2;0], reachInfo);
+platoons{1} = quadrotors{1}.newPlatoon(numQ, tFollow); 
+for i = 2:numQ
+    quadrotors{i} = quadrotor(i, dt, [0;4;0;0], reachInfo);
+    quadrotors{i}.joinPlatoon(platoons{1});
+    quadrotors{i}.x(quadrotors{i}.pdim) = quadrotors{i}.phantomPosition(highwayPath);
+    quadrotors{i}.xhist(:,1) = quadrotors{i}.x;
+end
+
+
+tNow = 0;
+tSteps = 5;
+
+% plotQuadrotors
+valSafe = zeros(numQ);
+fig = figure; %hts = cell(1,numQ); hps = cell(1,numQ);
+drawHighway(fig,highwayPath,gridSize,'black');
+for i = 1:numQ
+    [hts{i}, hps{i}] = drawQuadrotor(fig,[],[],quadrotors{i});
+end
+[hti, hpi] = drawQuadrotor(fig,[],[],Intruder);
+
+% quadrotors{i}.plotSafeV(Intruder,'r', quadrotors{i}.tauExt);
+axis([0,gridSize, 0, gridSize]);
+title(sprintf('t = %.1f',tNow));
+drawnow;
+
+while tNow < tEnd
+    
+    
+    % For each quadrotor in platoon check if it's safe against Intruder
+    for i = 1:length(quadrotors)
[…]

### 2015-12-16 code/platoon/legacy/simulateIntruder_orig.m

@@ -1,0 +1,279 @@
+% Simulates a platoon behavior with intruder
+
+clear; close all;
+
+
+cvx_quiet true
+warning('off','all')
+
+tEnd = 7;                                % End of simulation time
+dt = 0.1;                                   % Sampling time
+t = 0:dt:tEnd;                              % Time horizon
+tSteps = 5;                                 % MPC horizon in followPath
+
+gridSize = 70;
+v = 3.5;                                    % Target highway speed
+
+% Get reachability information
+[reachInfo, safeV] = generateReachInfo();
+
+
+% Highway
+z1 = [0 0];
+z2 = [gridSize gridSize];
+hw = highway(z1, z2, v);
+
+% intruding quadrotor
+qiX0 = [40;30];       % Initial position
+qiXt = [10;20];       % Final position
+qi = quadrotor(0, dt, [qiX0(1);-4;qiX0(2);-2], reachInfo);
+qiPath = highway(qiX0, qiXt, v);
+
+
+% create a platoon of quadrotors on the highway
+leaderPos = [23;23];
+leaderVel = [4;4];
+Nqr = 4;
+p = popPlatoon(hw, leaderPos, leaderVel, Nqr, 1);
+
+qr = [];
+for j = 1:Nqr
+    qr = [qr,p.vehicle(j)];
+end
+
+u = zeros(2,Nqr);
+
+
+% % Set up video writer
+% writerObj = VideoWriter(sprintf('Intruder1.mp4'),'MPEG-4');    % Create object for writing video
+% writerObj.FrameRate = 10;                   % Number of frames / sec
+% open(writerObj);                            % Start videoWriter
+
+% Set up plotting
+f1 = figure;                                    % Normal version
+f2 = figure;                                    % Snapshots
+
+% Figure 1
+figure(f1)
+hw.hwPlot; hold on
+
+colors = lines(Nqr);
+for j = 1:Nqr
+    qr(j).plotPosition(colors(j,:,:));
+end
+qi.plotPosition('red');                   % Intruder in red
+
+xlabel('x');    ylabel('y');
+
+ds = hw.ds;
+vx = v*ds(1);
+vy = v*ds(2);
+
+title(sprintf('t = %.01d',t(1)));
+axis([0, gridSize, 0, gridSize]); %axis equal;
+
+% Set up variables for plotting snap shots
+tplot = [0 3.3 6.2];
+spC = 2;
+spR = 2;
+plotnum = 0;
+
+
+% % Record videos
+% ax = f1.CurrentAxes;
[…]

### 2015-12-16 code/platoon/simulateIntruder.m

@@ -1,350 +1,112 @@
-function simulateIntruder(from_checkpoint, save_graphics, output_directory, visualize_vehicle_on)
-% function simulateIntruder(from_checkpoint, save_graphics, output_directory)
+function simulateIntruder()
+% simulateFormPlatoon()
 %
-% Simulates Simulates a platoon behavior with intruder.
-%
-% Inputs:  from_checkpoint  - whether to load previous checkpoint
-%          save_graphics    - whether to export graphics (for making an
-%                            animation)
-%          output_directory - for graphics export
-%                             - requires export_fig package
-%                             - don't include a "/" at the end
-%
-% Author: Qie Hu, 2015-07-14
+% Simulates 5 quadrotors forming a single platoon on a highway
 
-% Default input parameters
-if nargin<1
-  from_checkpoint = false;
+%% TFM
+tfm = TFM;
+tfm.computeRS('qr_qr_safe_V');
+
+%% Highways
+theta = 2*pi*rand;
+hw_length = 300;
+z0b = hw_length*[-0.25 0];
+z1b = hw_length*[1 0];
+
+% Highway 1
+z0 = rotate2D(z0b, theta);
+z1 = rotate2D(z1b, theta);
+hw = Highway(z0, z1, tfm.hw_speed);
+tfm.addHighway(hw);
+
+% plot
+figure;
+hw.lpPlot;
+hold on
+
+%% Quadrotors
+% Platoon 1 (4 vehicles)
+x0 = 0;
+xs = x0 + 3*tfm.ipsd: -tfm.ipsd: x0;
+ys = zeros(size(xs));
+xs_ys = rotate2D([xs; ys], theta);
+xs = xs_ys(1,:);
+ys = xs_ys(2,:);
+
+v = rotate2D([10 0], theta);
+for j = 1:length(xs)
+  q = Quadrotor([xs(j) v(1) ys(j) v(2)]);
+  tfm.regVehicle(q);
+  if j == 1
+    p1 = Platoon(q, hw, tfm);
+  else
+    p1.insertVehicle(q, j);
+  end
 end
 
-if nargin<2
-  save_graphics = false;
+% Intruder
+ih = pi/4 + 6*pi/4*rand; % initial heading of intruder
+mp = [50 0]; % meeting point between intruder and platoon
+ip = mp - mp(1)*[cos(ih) sin(ih)]; % initial position
[…]

### 2015-12-16 code/platoon/simulateIntruder2.m

@@ -1,369 +1,0 @@
-function simulateIntruder2(from_checkpoint, save_graphics, output_directory, visualize_vehicle_on)
-% function simulateIntruder(from_checkpoint, save_graphics, output_directory)
-%
-% Simulates Simulates a platoon behavior with intruder.
-%
-% Inputs:  from_checkpoint  - whether to load previous checkpoint
-%          save_graphics    - whether to export graphics (for making an
-%                            animation)
-%          output_directory - for graphics export
-%                             - requires export_fig package
-%                             - don't include a "/" at the end
-%
-% Author: Qie Hu, 2015-07-25
-
-% Default input parameters
-if nargin<1
-    from_checkpoint = false;
-end
-
-if nargin<2
-    save_graphics = false;
-end
-
-if nargin<3
-    output_directory = 'saved_graphics';
-end
-
-if nargin<4
-    visualize_vehicle_on= false;
-end
-    
-
-cvx_quiet true % Shuts cvx up if using MPC controller in followPath
-warning('off','all')
-
-% Checkpoint directory and file
-check_point_dir = 'checkpoints';
-check_point = [check_point_dir '/' mfilename '.mat'];
-
-%% Initialization
-if from_checkpoint
-    disp('Loading from last checkpoint')
-    load(check_point)
-    
-else
-    % Make directory if needed
-    system(['mkdir ' check_point_dir]);
-    
-    tEnd = 8;                 % End of simulation time
-    dt = 0.1;                 % Sampling time
-    t = 0:dt:tEnd;            % Time horizon
-    tSteps = 5;               % MPC horizon in followPath
-    gridSize = 50;
-    v = 3;                  % Target highway speed
-    d = 2;                  % Safe separation distance
-    
-    % Get reachability information
-    [reachInfo, safeV] = generateReachInfo();
-    
-    
-    % ===== Create highway here =====
-    z1 = [0 0];
-    z2 = [gridSize gridSize];
-    hw = highway(z1, z2, v);
-    
-    % ===== Create intruder here =====
-    qiX0 = [25;17];       % Initial position
-    qiXt = [-5;17];       % Final position
[…]

### 2015-12-16 code/platoon/simulateIntruderTest.m

@@ -1,117 +1,0 @@
-function simulateIntruder()
-
-cvx_quiet true
-
-
-tEnd = 20;                  % End of simulation time
-dt = 0.1;                   % Sampling time
-numQ = 6;                  % Number of quadrotors in platoon
-tFollow = 2;                % Follow time between quadrotors inside platoon
-gridSize = 60;             % Size of grid
-
-
-% Get reachability information
-[reachInfo, safeV] = generateReachInfo();
-
-% intruding quadrotor
-intruderX0 = [35;20];       % Initial position
-intruderXt = [0;gridSize];       % Final position
-Intruder = quadrotor(0, dt, [intruderX0(1);-3;intruderX0(2);3]);
-
-
-% Define paths
-highwayPath = @(s)rpath(s,[0;gridSize/2],[gridSize;gridSize/2]);
-intruderPath = @(s)rpath(s,intruderX0,intruderXt);
-
-
-% put some quadrotors in a horizontal line and create a platoon
-quadrotors = cell({});
-quadrotors{1} = quadrotor(1, dt, [25;4;gridSize/2;0], reachInfo);
-platoons{1} = quadrotors{1}.newPlatoon(numQ, tFollow); 
-for i = 2:numQ
-    quadrotors{i} = quadrotor(i, dt, [0;4;0;0], reachInfo);
-    quadrotors{i}.joinPlatoon(platoons{1});
-    quadrotors{i}.x(quadrotors{i}.pdim) = quadrotors{i}.phantomPosition(highwayPath);
-    quadrotors{i}.xhist(:,1) = quadrotors{i}.x;
-end
-
-
-tNow = 0;
-tSteps = 5;
-
-% plotQuadrotors
-valSafe = zeros(numQ);
-fig = figure; %hts = cell(1,numQ); hps = cell(1,numQ);
-drawHighway(fig,highwayPath,gridSize,'black');
-for i = 1:numQ
-    [hts{i}, hps{i}] = drawQuadrotor(fig,[],[],quadrotors{i});
-end
-[hti, hpi] = drawQuadrotor(fig,[],[],Intruder);
-
-% quadrotors{i}.plotSafeV(Intruder,'r', quadrotors{i}.tauExt);
-axis([0,gridSize, 0, gridSize]);
-title(sprintf('t = %.1f',tNow));
-drawnow;
-
-while tNow < tEnd
-    
-    
-    % For each quadrotor in platoon check if it's safe against Intruder
-    for i = 1:length(quadrotors)
[…]

### 2015-12-16 code/platoon/simulateIntruder_orig.m

@@ -1,279 +1,0 @@
-% Simulates a platoon behavior with intruder
-
-clear; close all;
-
-
-cvx_quiet true
-warning('off','all')
-
-tEnd = 7;                                % End of simulation time
-dt = 0.1;                                   % Sampling time
-t = 0:dt:tEnd;                              % Time horizon
-tSteps = 5;                                 % MPC horizon in followPath
-
-gridSize = 70;
-v = 3.5;                                    % Target highway speed
-
-% Get reachability information
-[reachInfo, safeV] = generateReachInfo();
-
-
-% Highway
-z1 = [0 0];
-z2 = [gridSize gridSize];
-hw = highway(z1, z2, v);
-
-% intruding quadrotor
-qiX0 = [40;30];       % Initial position
-qiXt = [10;20];       % Final position
-qi = quadrotor(0, dt, [qiX0(1);-4;qiX0(2);-2], reachInfo);
-qiPath = highway(qiX0, qiXt, v);
-
-
-% create a platoon of quadrotors on the highway
-leaderPos = [23;23];
-leaderVel = [4;4];
-Nqr = 4;
-p = popPlatoon(hw, leaderPos, leaderVel, Nqr, 1);
-
-qr = [];
-for j = 1:Nqr
-    qr = [qr,p.vehicle(j)];
-end
-
-u = zeros(2,Nqr);
-
-
-% % Set up video writer
-% writerObj = VideoWriter(sprintf('Intruder1.mp4'),'MPEG-4');    % Create object for writing video
-% writerObj.FrameRate = 10;                   % Number of frames / sec
-% open(writerObj);                            % Start videoWriter
-
-% Set up plotting
-f1 = figure;                                    % Normal version
-f2 = figure;                                    % Snapshots
-
-% Figure 1
-figure(f1)
-hw.hwPlot; hold on
-
-colors = lines(Nqr);
-for j = 1:Nqr
-    qr(j).plotPosition(colors(j,:,:));
-end
-qi.plotPosition('red');                   % Intruder in red
-
-xlabel('x');    ylabel('y');
-
-ds = hw.ds;
-vx = v*ds(1);
-vy = v*ds(2);
-
-title(sprintf('t = %.01d',t(1)));
-axis([0, gridSize, 0, gridSize]); %axis equal;
-
-% Set up variables for plotting snap shots
-tplot = [0 3.3 6.2];
-spC = 2;
-spR = 2;
-plotnum = 0;
-
-
-% % Record videos
-% ax = f1.CurrentAxes;
[…]

### 2016-01-20 code/platoon/simulations/simulateChangeHighway.m
Added capability to save figures in simulation code

@@ -1,4 +1,4 @@
-function simulateChangeHighway(save_figures)
+function simulateChangeHighway(save_figures, fig_formats)
 % simulateFormPlatoon()
 %
 % Simulates 5 quadrotors forming a single platoon on a highway
@@ -7,6 +7,10 @@ addpath('..')
 
 if nargin < 1
   save_figures = false;
+end
+
+if nargin < 2
+  fig_formats = {'png'};
 end
 
 %% TFM
@@ -35,8 +39,9 @@ hw2 = Highway(z0, z1, tfm.hw_speed);
 tfm.addHighway(hw2);
 
 % plot
-figure;
+f = figure;
 hw1.lpPlot;
+f.Children.FontSize = 16;
 hold on
 hw2.lpPlot;
 hold on
@@ -79,17 +84,31 @@ end
 for j = 1:length(tfm.aas)
   tfm.aas{j}.plotPosition;
 end
-title('t=0')
+title('t=0', 'FontSize', 16)
 axis square
 drawnow
 
+% Save initial figure
 if save_figures
   fig_dir = [fileparts(mfilename('fullpath')) '/' mfilename '_figs'];
   if ~exist(fig_dir, 'dir')
     cmd = ['mkdir -p ' fig_dir];
     system(cmd)
   end
-  export_fig([fig_dir '/0'], '-png', '-m2')
+  
+  for ii = 1:length(fig_formats)
+    if strcmp(fig_formats{ii}, 'png')
+      export_fig([fig_dir '/0'], '-png', '-m2', '-transparent')
+    end
+    
+    if strcmp(fig_formats{ii}, 'pdf')
+      export_fig([fig_dir '/0'], '-pdf', '-m2', '-transparent')
+    end
+    
+    if strcmp(fig_formats{ii}, 'fig')
+      savefig([fig_dir '/0.fig']);
+    end
+  end
 end
 
 
@@ -99,6 +118,7 @@ t = 0:tfm.dt:tMax;
 
 u = cell(size(tfm.aas));
 for i = 1:length(t)
+  % Simulate
   [safe, uSafe] = tfm.checkAASafety;
   
   for j = 1:length(tfm.aas)
@@ -115,8 +135,21 @@ for i = 1:length(t)
   title(['t=' num2str(t(i))])
   drawnow
 
+  % Save figures
   if save_figures
-    export_fig([fig_dir '/' num2str(i)], '-png', '-m2')
+    for ii = 1:length(fig_formats)
[…]

### 2016-01-20 code/platoon/simulations/simulateFormPlatoon.m

@@ -1,4 +1,4 @@
-function simulateFormPlatoon(save_figures)
+function simulateFormPlatoon(save_figures, fig_formats)
 % simulateFormPlatoon()
 %
 % Simulates 5 quadrotors forming a single platoon on a highway
@@ -7,6 +7,10 @@ addpath('..')
 
 if nargin < 1
   save_figures = false;
+end
+
+if nargin < 2
+  fig_formats = {'png'};
 end
 
 %% TFM
@@ -45,13 +49,27 @@ end
 title('t=0', 'FontSize', 16)
 drawnow
 
+% Save initial figure
 if save_figures
   fig_dir = [fileparts(mfilename('fullpath')) '/' mfilename '_figs'];
   if ~exist(fig_dir, 'dir')
     cmd = ['mkdir -p ' fig_dir];
     system(cmd)
   end
-  export_fig([fig_dir '/0'], '-png', '-m2')
+  
+  for ii = 1:length(fig_formats)
+    if strcmp(fig_formats{ii}, 'png')
+      export_fig([fig_dir '/0'], '-png', '-m2', '-transparent')
+    end
+    
+    if strcmp(fig_formats{ii}, 'pdf')
+      export_fig([fig_dir '/0'], '-pdf', '-m2', '-transparent')
+    end
+    
+    if strcmp(fig_formats{ii}, 'fig')
+      savefig([fig_dir '/0.fig']);
+    end
+  end
 end
 
 %% Target entry point
@@ -79,8 +97,21 @@ for i = 1:length(t)
   title(['t=' num2str(t(i))])
   drawnow
   
+  % Save figures
   if save_figures
-    export_fig([fig_dir '/' num2str(i)], '-png', '-m2')
+    for ii = 1:length(fig_formats)
+      if strcmp(fig_formats{ii}, 'png')
+        export_fig([fig_dir '/' num2str(i)], '-png', '-m2', '-transparent')
+      end
+
+      if strcmp(fig_formats{ii}, 'pdf')
+        export_fig([fig_dir '/' num2str(i)], '-pdf', '-m2', '-transparent')
+      end
+
+      if strcmp(fig_formats{ii}, 'fig')
+        savefig([fig_dir '/' num2str(i) '.fig']);
+      end
+    end
   end
 end
 

### 2016-01-20 code/platoon/simulations/simulateIntruder.m

@@ -1,4 +1,4 @@
-function simulateIntruder(save_figures)
+function simulateIntruder(save_figures, fig_formats)
 % simulateFormPlatoon()
 %
 % Simulates 5 quadrotors forming a single platoon on a highway
@@ -7,6 +7,10 @@ addpath('..')
 
 if nargin < 1
   save_figures = false;
+end
+
+if nargin < 2
+  fig_formats = {'png'};
 end
 
 %% TFM
@@ -74,7 +78,20 @@ if save_figures
     cmd = ['mkdir -p ' fig_dir];
     system(cmd)
   end
-  export_fig([fig_dir '/0'], '-png', '-m2')
+  
+  for ii = 1:length(fig_formats)
+    if strcmp(fig_formats{ii}, 'png')
+      export_fig([fig_dir '/0'], '-png', '-m2', '-transparent')
+    end
+    
+    if strcmp(fig_formats{ii}, 'pdf')
+      export_fig([fig_dir '/0'], '-pdf', '-m2', '-transparent')
+    end
+    
+    if strcmp(fig_formats{ii}, 'fig')
+      savefig([fig_dir '/0.fig']);
+    end
+  end
 end
 
 
@@ -103,7 +120,19 @@ for i = 1:length(t)
   drawnow
 
   if save_figures
-    export_fig([fig_dir '/' num2str(i)], '-png', '-m2')
+    for ii = 1:length(fig_formats)
+      if strcmp(fig_formats{ii}, 'png')
+        export_fig([fig_dir '/' num2str(i)], '-png', '-m2', '-transparent')
+      end
+
+      if strcmp(fig_formats{ii}, 'pdf')
+        export_fig([fig_dir '/' num2str(i)], '-pdf', '-m2', '-transparent')
+      end
+
+      if strcmp(fig_formats{ii}, 'fig')
+        savefig([fig_dir '/' num2str(i) '.fig']);
+      end
+    end
   end
 end
 

### 2016-01-20 docs/AIAA 2016/Template/journalstemp.tex
no message

\documentclass{AIAA}

\begin{document}

\title{Preparation of Papers for AIAA Technical Journals}

\author{First A. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B. Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
\affiliation{Business or Academic Affiliation 1, City, State, Zip Code}
\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
\affiliation{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
\affiliation{Business or Academic Affiliation 2, City, State, Zip Code}

\begin{abstract}
These instructions give you guidelines for preparing papers for AIAA Technical Journals. Use this document as a template if you are using Microsoft Word 2001 or later for Windows, or Word X or later for Mac OS X. Otherwise, use this document as an instruction set. If you previously prepared an AIAA Conference Paper using the Papers Template, you may submit your journal paper in that format with one exception: after you have entered all of your text and figures into the table, be sure to double space your paper before submitting it to WriteTrack$\texttrademark $. Carefully follow the journal paper submission process in Sec. II of this document. Keep in mind that the electronic file you submit will be formatted further at AIAA. This first paragraph is formatted in the abstract style. Abstracts are required \textit{only} for regular, full-length papers. Be sure to define all symbols used in the abstract, and do not cite references in this section. The footnote on the first page should list the Job Title and AIAA Member Grade (if applicable) for each author.
\end{abstract}

\maketitle

\section*{Nomenclature}
(Nomenclature entries should have the units identified)\\
\noindent\begin{tabular}{@{}lcl@{}}
\textit{A}  &=& amplitude of oscillation \\
\textit{a   }&=&    cylinder diameter \\
\textit{C}$_{p}$&=& pressure coefficient \\
\textit{Cx} &=& force coefficient in the \textit{x} direction \\
\textit{Cy} &=& force coefficient in the \textit{y} direction \\
c   &=& chord \\
d\textit{t} &=& time step \\
\textit{Fx} &=& \textit{X} component of the resultant pressure force acting on the vehicle \\
\textit{Fy} &=& \textit{Y} component of the resultant pressure force acting on the vehicle \\
\textit{f, g}   &=& generic functions \\
\textit{h}  &=& height \\
\textit{i}  &=& time index during navigation \\
\textit{j}  &=& waypoint index \\
\textit{K}  &=& trailing-edge (TE) nondimensional angular deflection rate
\end{tabular} \\

\section{Introduction}
THIS document is a template for Microsoft Word 2001 or later. If you are reading a hard-copy or .pdf version of this document, download the electronic file, Journalstemp.dot, from \url{http://www.aiaa.org/content.cfm?pageid=167} and use it to prepare your manuscript.

Authors using Microsoft Word will first need to save the Journalstemp.dot file in the ``Templates'' directory of their hard drive. To do so, simply open the Journalstemp.dot file and then click ``File>Save As:'' to save the template. [Note: Windows users will need to indicate ``Save as Type>Document Template (*.dot)'' when asked in the dialogue box; Mac users should save the file in the ``My Templates'' directory.] To create a new document using this template, use the command ''File>New>From Template'' (Windows) or ``File>Project Gallery>My Templates'' (Mac). The new document that opens will be titled ``Papers\_Template.doc.'' To create your formatted manuscript, type your own text over sections of Journalstemp.doc, or cut and paste from another document and then use the available markup styles. Note that special formatting such as subscripts, superscripts, and italics may be lost when you copy your text into the template. See Sec. IV for more detailed formatting guidelines.

\section{Procedure for Paper Submission}
All manuscripts are to be submitted online at \url{http://www.writetrack.net.} Select ``Submit to AIAA Technical Journals,'' and then click ``Start New.'' Once you enter your e-mail address, you will receive an e-mail message containing your tracking number and password. This information will allow you to track your manuscript's status, update submission data, upload your manuscript and subsequent revisions, and communicate with the editors, through your Author Status Page, at any time during the publication process.

After entering all required submission data, you must use the ``Upload Manuscript'' feature of the Author Status Page to upload your submission. Remember that your document must be in single-column, double-spaced format (as this template) before you upload it. Please be sure that the name of the file you upload for processing is short and simple (i.e., ``msc12345.doc'') with no spaces, tildes, symbols, or other special characters. Authors are encouraged to upload .pdf files, which are less likely to have conversion errors on upload. If the file being uploaded is in Microsoft Word, the document must be based on the Word default styles. (The AIAA Journals Template is based on those styles.) Failure to meet these requirements could result in a processing error that would require you to re-upload your manuscript. Once you have uploaded your manuscript, please inspect the file for accuracy. This step is required to complete your submission. If you experience difficulties with the upload and/or conversion of your manuscript, please contact AIAA WriteTrack Support (WriteTrackSupport@writetrack.net) for additional assistance.
\textit{Attention Asian Authors: If you are uploading a .pdf or PostScript file, please remove Asian fonts from your fil}e\textit{,} \textit{under File>Properties}.

\section{General Guidelines}
The following section outlines general (nonformatting) guidelines to follow. These guidelines are applicable to all authors and include information on the policies and practices relevant to the publication of your manuscript.

\subsection{Publication by AIAA}
Your manuscript cannot be published by AIAA if
\begin{enumerate}
\item[1)]The work is classified or has not been cleared for public release.

\item[2)]The work contains copyright-infringing material.

\item[3)]The work has been published or is currently under consideration for publication or presentation elsewhere. (Exception: Papers presented at AIAA conferences \textit{may} be submitted to AIAA journals for possible publication.)
\end{enumerate}

You will be asked to provide the publication or presentation history of your paper (or any similar paper) if it has \textit{ever} been submitted for publication or presentation previously. Include the name of the publication, dates, review history, final disposition of manuscript, etc.

\subsection{Copyright}
Before AIAA can publish any paper, the copyright information must be completed on WriteTrack. Failure to complete the form correctly could result in your paper not being published. You must select one copyright assignment statement (select A, B, C, or D). Read the copyright statements carefully. Because you will be completing this form online, you do not need to fill out a hard-copy form. Do not include a copyright statement anywhere on your paper. The correct statement will be included automatically at the time of processing. (If your paper was presented at an AIAA Conference, then the copyright statement chosen for the Journal Paper should be the same as for your Conference Paper.)

\subsection{Publication Charges, Reprints, and Color Artwork}
AIAA charges a voluntary publication charge of \$875 for Full-Length Papers, \$375 for Technical/Engineering Notes, \$575 for Design Forum Papers, and \$275 for Technical Comments submissions. One hundred reprints are provided to authors who pay the voluntary charge. Authors whose manuscripts contain color figures are \textit{required} to pay 50\% of the publication charge, in addition to a flat production rate of \$1200 and \$75 for each color figure. Contact the Journals staff if you have questions.

\section{Detailed Formatting Instructions}
The styles and formats for the AIAA Journals Template have been incorporated into the structure of this document. If you are using Microsoft Word, please use this template to prepare your manuscript. If you are reading a hard-copy or .pdf version of this document, please download the electronic template file, Journalstemp.dot, from \url{http://www.aiaa.org/content.cfm?pageid=167}.

If you are using the Journalstemp.dot file to prepare your manuscript, you can simply type your own text over sections of this document, or cut and paste from another document and use the available markup styles. If you choose to cut and paste, select the text from your original Word document and choose Edit>Copy. (Do not select your title and author information, since the document spacing may be affected. It is a simple task to reenter your title and author information in the template.) Open the Journals Template. Place your cursor in the text area of the template and select Edit>Paste Special. When the Paste Special box opens, choose ``unformatted text.'' Please note that special formatting (e.g., subscripts, superscripts, italics) may be lost when you copy your text into the template.

To apply the AIAA Journals formatting, use the Formatting Toolbar at the top of your Word window. Click on the top left arrow to open the Font menu, and then click on the arrow to the right of the Style menu to see a list of formats, including Heading 1, Heading 2, Text, etc. (for example, the style at this point in the document is ``Text''); all the styles you will need to format your document are available in the menu. Highlight a heading or section of text that you want to designate with a certain style, and then select the appropriate style name from the menu. The style will automatically adjust your fonts and line spacing. Repeat this process to apply formatting to all elements of your paper. \textit{Do not change the font sizes, line spacing, or margins. Do not hyphenate your document.} Use italics for emphasis; do not underline.

Use the ``Page Layout'' feature from the ``View'' menu bar (View>Page Layout) to see the most accurate representation of how your final paper will appear. Once formatting is complete, be sure to double space all sections of your manuscript.

\subsection{Document Text}
The default font for the AIAA Journals Template is Times New Roman, 10-point size. In the electronic template, use the ``Text'' style from the pull-down menu to format all primary text for your manuscript. The first line of every paragraph should be indented, and all lines should be double-spaced. Default margins are 1 in. on all sides. In the electronic version of this template, all margins and other formatting are preset. There should be no additional (blank) lines between paragraphs.
\textit{NOTE:} If you are using the electronic template to format your manuscript, the required spacing and formatting will be applied automatically, simply by using the appropriate style designation from the pull-down menu.

\subsection{Headings}
Format the title of your paper in bold, 18-point type, with capital and lower-case letters, and center it at the top of the page. The names of the authors, business or academic affiliation, city, and state/province follow on separate lines below the title. The names of authors with the same affiliation can be listed on the same line above their collective affiliation information. Author names are centered, and affiliations are centered and in italic type. The affiliation line for each author includes that author's city, state, and zip/postal code (or city, province, zip/postal code and country, as appropriate). The first footnote (bottom of first page) contains the job title and department name, street address/mail stop, and AIAA member grade for each author.

Major headings in the template (``Heading 1'' in the template style list) are bold 11-point font and centered. Please omit section numbers before all headings unless you refer frequently to different sections. Use Roman numerals for major headings if they must be numbered.

Subheadings (``Heading 2'' in the template style list) are bold, flush left, and either unnumbered or identified with capital letters if necessary for cross-referencing sections within the paper.

Sub-subheadings (``Heading 3'' in the template style list) are italic, flush left, and either unnumbered or numbered with Arabic numerals (1, 2, 3, etc.) if necessary for cross-referencing sections within the paper.

\subsection{Abstract}
An abstract appears at the beginning of Full-Length Papers. (Survey and Design Forum Papers, History of Key Technologies Papers, invited lectures, and Technical/Engineering Notes do not include abstracts.) The abstract is one paragraph (not an introduction) and complete in itself (no reference numbers). It should indicate subjects dealt with in the paper and state the objectives of the investigation. Newly observed facts and conclusions of the experiment or argument discussed in the paper must be stated in summary form; readers should not have to read the paper to understand the abstract. Format the abstract bold, indented 3 picas (1/2 in.) on each side, and separated from the rest of the document by two blank lines.

\subsection{Nomenclature}
Papers with many symbols should have a nomenclature that defines all symbols with units, inserted between the abstract and the introduction. If one is used, it must contain all the symbology used in the manuscript, and the definitions should not be repeated in the text. In all cases, identify the symbols used if they are not widely recognized in the profession. Define acronyms in the text, not in the nomenclature.

\subsection{Biographies}
Survey Papers and some Full-Length Papers include author biographies. These biographies are one paragraph each and should use the abstract formatting style.

\subsection{Footnotes and References}
Footnotes, where they appear, are placed above the 1-in. margin at the bottom of the page. To insert footnotes into the template, use the Insert>Footnote feature from the main menu as necessary. Footnotes are formatted automatically in the template, but, if another medium is used, they should appear as superscript symbols in the following sequence: *, $\dag $, $\ddag $, \S , \P , **, $\dag \dag $, $\ddag \ddag $, \S \S , etc.

List and number all references at the end of the paper. Corresponding bracketed numbers are used to cite references in the text \cite{1}, including citations that are an integral part of the sentence (e.g., ``It is shown in \cite{2} that\ldots '') or follow a mathematical expression: ``\textit{A}$^{2}$ + \textit{B} = \textit{C} (Ref. \cite{3}).'' For multiple citations, separate reference numbers with commas \cite{4,5}, or use a dash to show a range \cite{6,7,8}. Reference citations in the text should be in numerical order.

In the reference list, give all authors' names; do not use ``et al\textit{.}'' unless there are six authors or more. Papers that have not been published should be cited as ``unpublished''; papers that have been submitted or accepted for publication should be cited as ``submitted for publication.'' Private communications and personal Web sites should appear as footnotes rather than in the reference list.

References should be cited according to the standard publication reference style. (For examples, see the ``References'' section of this template.) Never edit titles in references to conform to AIAA style of spellings, abbreviations, etc. Names and locations of publishers should be listed; month and year should be included for reports and papers. For papers published in translation journals, please give the English citation first, followed by the original foreign language citation.

\subsection{Figures and Tables}
Insert tables and figures within your document; they may be either scattered throughout the text or grouped all together at the end of the file. Use the Table drop-down menu to create your tables; do not insert your figures in text boxes. Figures should have no background, borders, or outlines. In the electronic template, use the ``Figure'' style from the pull-down formatting menu to type caption text. You may also insert the caption by going to the Insert menu and choosing Caption. Make sure the label is ``Fig.,'' and type your caption text in the box provided. Captions are bold with a single tab (no hyphen or other character) between the figure number and figure description. See the Table~\ref{tab:table1} example for table style and column alignment. If you wish to center tables that do not fill the width of the page, simply highlight and ``grab'' the entire table to move it into proper position.

\begin{table}
\caption{\label{tab:table1} Transitions selected for thermometry}
\begin{ruledtabular}
\begin{tabular}{lcccccc}
& Transition& & \multicolumn{2}{c}{}\\\cline{2-2}
Line& $\nu \prime\prime $& & \textit{J}$\prime\prime $& Frequency, cm$^{-1}$& \textit{FJ}, cm$^{-1}$& \textit{G}$\nu $, cm$^{-1}$\\\hline
a& 0& P$_{12}$& 2.5& 44069.416& 73.58& 948.66\\
b& 1& R$_{2}$& 2.5& 42229.348& 73.41& 2824.76\\
c& 2& R$_{21}$& 805& 40562.179& 71.37& 4672.68\\
d& 0& R$_{2}$& 23.5& 42516.527& 1045.85& 948.76\\
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{figure}
\caption{Magnetization as a function of applied fields.}
\end{figure}

Place figure captions below all figures. If your figure has multiple parts, include the labels ``a),'' ``b),'' etc., below and to the left of each part, above the figure caption. Please verify that the figures and tables you mention in the text actually exist. When citing a figure in the text, use the abbreviation ``Fig.'' except at the beginning of a sentence. Do not abbreviate ``Table.'' Number each different type of illustration (i.e., figures and tables) sequentially with relation to other illustrations of the same type.
Figure labels must be legible after reduction to column width (preferably 7--9 points after reduction).

\subsection{Equations}
Equations are numbered consecutively, with equation numbers in parentheses flush right, as in Eq. (1). Insert a blank line both above and below the equation. First use the equation editor to create the equation. If you are using Microsoft Word, use either the Microsoft Equation Editor or the MathType add-on (\url{http://www.mathtype.com}) for equations in your paper, use the function (Insert>Object>Create New>Microsoft Equation \textit{or} MathType Equation) to insert it into the document. Please note that ``Float over text'' should \textit{not} be selected. To insert the equation into the document, do the following:
\begin{enumerate}
\item[1)]  Select the ``Equation'' style from the pull-down formatting menu, and hit ``tab'' once.
\item[2)]  Insert the equation, and hit ``tab'' again.
\item[3)]  Enter the equation number in parentheses.
\end{enumerate}

A sample equation is included here, formatted using the preceding instructions:
\begin{equation}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0 (\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}
Be sure that symbols in your equation are defined in the Nomenclature or immediately following the equation. Also define abbreviations and acronyms the first time they are used in the main text. (Very common abbreviations such as AIAA and NASA, do not have to be defined.)

\subsection{General Grammar and Preferred Usage}
Use only one space after periods or colons. Hyphenate complex modifiers: ``zero-field-cooled magnetization.'' Insert a zero before decimal points: ``0.25,'' not ``.25.'' Use ``cm$^{2}$,'' not ``cc.''

A parenthetical statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within parenthesis.) Use American, not English, spellings (e.g., ``color,'' not ``colour''). The serial comma is preferred: ``A, B, and C'' instead of ``A, B and C.''

Be aware of the different meanings of the homophones ``affect'' (usually a verb) and ``effect'' (usually a noun), ``complement'' and ``compliment,'' ``discreet'' and ``discrete,'' ``principal'' (e.g., ``principal investigator'') and ``principle'' (e.g., ``principle of measurement''). Do not confuse ``imply'' and ``infer.''

\section{Conclusion}
Although a conclusion may review the main points of the paper, it must not replicate the abstract. A conclusion might elaborate on the importance of the work or suggest applications and extensions. Do not cite references in the conclusion. Note that the conclusion section is the last section of the paper to be numbered. The appendix (if present), acknowledgment, and references are listed without numbers.

\section*{Appendix}

An Appendix, if needed, appears before the acknowledgments.

\section*{Acknowledgments}
An Acknowledgments section, if used, immediately precedes the References. Sponsorship and financial support acknowledgments should be included here.

\section*{References}

\begin{thebibliography}{}
\bibitem{1} Vatistas, G. H., Lin, S., and Kwok, C. K., ``Reverse Flow Radius in Vortex Chambers,'' \textit{AIAA Journal}, Vol. 24, No. 11, 1986, pp. 1872, 1873. doi: 10.2514/3.13046
\bibitem{2} Dornheim, M. A., ``Planetary Flight Surge Faces Budget Realities,'' \textit{Aviation Week and Space Technology}, Vol. 145, No. 24, 9 Dec. 1996, pp. 44--46.
\bibitem{3} Terster, W., ``NASA Considers Switch to Delta 2,'' \textit{Space News}, Vol. 8, No. 2, 13--19 Jan. 1997, pp. 1, 18.
\bibitem{4} Peyret, R., and Taylor, T. D., \textit{Computational Methods in Fluid Flow}, 2$^{{\rm nd}}$ ed., Springer-Verlag, New York, 1983, Chaps. 7, 14.
\bibitem{5} Oates, G. C. (ed.), \textit{Aerothermodynamics of Gas Turbine and Rocket Propulsion}, AIAA Education Series, AIAA, New York, 1984, pp. 19, 136.
\bibitem{6} Volpe, R., ``Techniques for Collision Prevention, Impact Stability, and Force Control by Space Manipulators,'' \textit{Teleoperation and Robotics in Space}, edited by S. B. Skaar and C. F. Ruoff, Progress in Astronautics and Aeronautics, AIAA, Washington, DC, 1994, pp. 175--212.
\bibitem{7} Thompson, C. M., ``Spacecraft Thermal Control, Design, and Operation,'' \textit{AIAA Guidance, Navigation, and Control Conference}, CP849, Vol. 1, AIAA, Washington, DC, 1989, pp. 103--115
\bibitem{8} Chi, Y. (ed.), \textit{Fluid Mechanics Proceedings}, NASA SP-255, 1993.
\bibitem{9} Morris, J. D., ``Convective Heat Transfer in Radially Rotating Ducts,'' \textit{Proceedings of the Annual Heat Transfer Conference}, edited by B. Corbell, Vol. 1, Inst. of Mechanical Engineering, New York, 1992, pp. 227--234.
\bibitem{10} Chapman, G. T., and Tobak, M., ``Nonlinear Problems in Flight Dynamics,'' NASA TM-85940, 1984.
\bibitem{11} Steger, J. L., Jr., Nietubicz, C. J., and Heavey, J. E., ``A General Curvilinear Grid Generation Program for Projectile Configurations,'' U.S. Army Ballistic Research Lab., Rept. ARBRL-MR03142, Aberdeen Proving Ground, MD, Oct. 1981.
\bibitem{12} Tseng, K., ``Nonlinear Green's Function Method for Transonic Potential Flow,'' Ph.D. Dissertation, Aeronautics and Astronautics Dept., Boston Univ., Cambridge, MA, 1983.
\bibitem{13} Richard, J. C., and Fralick, G. C., ``Use of Drag Probe in Supersonic Flow,'' \textit{AIAA Meeting Papers on Disc} [CD-ROM], Vol. 1, No. 2, AIAA, Reston, VA, 1996.
\bibitem{14} Atkins, C. P., and Scantelbury, J. D., ``The Activity Coefficient of Sodium Chloride in a Simulated Pore Solution Environment,'' \textit{Journal of Corrosion Science and Engineering} [online journal], Vol. 1, No. 1, Paper 2, URL: \url{http://www.cp/umist.ac.uk/JCSE/vol1/vol1.html} [cited 13 April 1998].
\bibitem{15} Vickers, A., ``10-110 mm/hr Hypodermic Gravity Design A,'' \textit{Rainfall Simulation Database} [online database], URL: \url{http://www.geog.le.ac.uk/bgrg/lab.htm} [cited 15 March 1998].
\bibitem{16} TAPP, Thermochemical and Physical Properties, Software Package, Ver. 1.0, E. S. Microware, Hamilton, OH, 1992.
\bibitem{17} Scherrer, R., Overholster, D., and Watson, K., Lockheed Corp., Burbank, CA, U.S. Patent Application for a ``Vehicle,'' Docket No. P-01-1532, filed 11 Feb. 1979.
\bibitem{18} Doe, J., ``Title of Paper,'' \textit{Name of Journal} (to be published).
\bibitem{19} Doe, J., ``Title of Chapter,'' \textit{Name of Book}, edited by\ldots , Publisher's name and location (to be published).
\bibitem{20} Doe, J., ``Title of Work,'' Name of Archive, Univ. (or organization), City, State, Year (unpublished).
\end{thebibliography}
\end{document}

### 2016-01-20 docs/AIAA 2016/conclusions.tex
no message

% !TEX root = main.tex
\section{Conclusions}
We considered single-file platoons of UAVs modeled by hybrid systems traveling along air highways. Using HJ reachability, we proposed liveness controllers for merging onto highways and merging into existing platoons, and wrapped a safety controller around liveness controllers to ensure no collision between the UAVs can occur. Under the assumption that faulty vehicles can descend after a pre-specified duration, our safety controller guarantees that no collisions will occur in a single altitude level as long as at most one safety breach occurs for each vehicle in the platoon. Additional safety breaches can be handled by multiple altitude ranges in the airspace. Our simulations show that by putting vehicles into single-file platoons, the likelihood of having multiple safety breaches is low, and conflicts involving a single malfunctioning UAV or intruder can be resolved in a single altitude level.

Immediate future work includes exploring different vehicle models, investigating algorithms for resolving multiple safety breaches within the same altitude, and more broadly related problems such as airspace structure and air highway placement.

### 2016-01-20 docs/AIAA 2016/high_eikon.tex
no message

% !TEX root = main.tex
\subsection{The Eikonal Equation -- Cost-Minimizing Path}
Let $s_0, s_1\in \mathbb{R}$, and let $\ppath: [s_0, s_1] \rightarrow \mathbb{R}^2$ be a path starting from an origin point $\pos^o = \ppath(s_0)$ and ending at a destination point $\pos^d = \ppath(s_1)$. Note that the sequence $\hws_N$ in \eqref{eq:ahpp} is a piece-wise affine example of a path $\ppath(s), s\in[s_0, s_1]$; however, a path $\ppath$ that is not piece-wise affine cannot be written as a sequence of highways $\hws_N$.

More concretely, suppose a UAV flies from an origin point $p^o$ to a destination point $p^d$ along some path $\ppath(s)$ parametrizes by the parameters $s$. Then, $\ppath(s_0) = p^o$ would denote the origin, and $\ppath(s_1) = p^d$ would denote the destination. All intermediate $s$ values denote the intermediate positions of the path, i.e. $\ppath(s) = \pos(s) = (\pos_x(s), \pos_y(s))$.

Consider the cost map $\cmap(\pos_x, \pos_y)$ which captures the cost incurred for UAVs flying over the position $\pos = (\pos_x, \pos_y)$. Along the entire path $\ppath(s)$, the cumulative cost $\ccost(\ppath)$ is incurred. Define $\ccost$ as follows:

\begin{equation}
\ccost(\ppath) = \int_{s_0}^{s_1} \cmap(\ppath(s)) ds
\end{equation}

The problem of finding the cost-minimizing path is finding the path such that the above cost is minimized. More generally, given an origin point $p^o$, we would like to compute the function $\ocost$ representing optimal cumulative cost for any destination point $\pos$:

\begin{equation}
\label{eq:rahpp} % relaxed air highway placement problem
\begin{aligned}
\ocost(\pos^d) &= \min_{\ppath(\cdot)} \ccost(\ppath) \\
&= \min_{\ppath(\cdot)} \int_{s_0}^{s_1} \cmap(\ppath(s)) ds
\end{aligned}
\end{equation}

It is well known \cite{} that the solution to the Eikonal equation \eqref{eq:eikonal} precisely computes the function $\ocost(\pos^d)$ given the cost map $\cmap$. Note that a single function characterizes the minimum cost from an origin $\pos^o$ to any destination $\pos^d$. Once $\ocost$ is found, the optimal path $\ppath$ between $\pos^o$ and $\pos^d$ can be obtained via gradient descent.

\begin{equation}
\label{eq:eikonal}
\begin{aligned}
\cmap(\pos)|\nabla \ocost(\pos)| &= 1 \\
\ocost(\pos^o) &= 0
\end{aligned}
\end{equation}

\eqref{eq:eikonal} can be efficiently computed numerically using the fast marching method \cite{}.

Note that \eqref{eq:rahpp} can be viewed as a relaxation of the air highway placement problem defined in \eqref{eq:ahpp}. Unlike \eqref{eq:ahpp}, the relaxation \eqref{eq:rahpp} can be quickly solved using currently available numerical tools. Thus, we first solve \eqref{eq:rahpp}, and then post-process the solution to \eqref{eq:rahpp} to obtain an approximation to \eqref{eq:ahpp}.

Given a single origin point $\pos^o$, the optimal cumulative cost function $\ocost(p)$ can be computed. Suppose $M$ different destination points $\pos^d_i,i=1,\ldots,M$ are chosen. Then, $M$ different optimal paths $\ppath_i,i=1,\ldots,M$ are obtained from $\ocost$.

### 2016-01-20 docs/AIAA 2016/high_form.tex
no message

% !TEX root = main.tex
\section{Air Highways}
Air highways are virtual highways in the airspace on which a number of UAV platoons may be present. UAVs seek to arrive at some desired destination starting from their origin by traveling along a sequence of air highways. Air highways are intended to be the common pathways for many UAV platoons, whose members may have different origins and destinations. By routing platoons of UAVs onto a few common pathways, the air space becomes more tractable to analyze and intuitive to monitor. The concept of platoons will be proposed in Section \ref{sec:platooning}; for now, we will focus on air highways.

Let an air highway be denoted by the function $\hw: [0, 1] \rightarrow \mathbb{R}^2$. Such a highway lies in a horizontal plane of fixed altitude, with start and end points given by $\hw(0)\in\mathbb{R}^2$ and $\hw(1)\in\mathbb{R}^2$ respectively. For simplicity, we assume that the highway segment is a straight line segment, and the parameter $s$ indicates the position in some fixed altitude as follows: $\hw(s) = \hw(0) + s(\hw(1) - \hw(0))$. To each highway, we assign a speed of travel $v_\hw$ and specify the direction of travel to be the direction from $\hw(0)$ to $\hw(1)$, denoted using a unit vector $\hwd = \frac{\hw(1) - \hw(0)}{\lVert\hw(1) - \hw(0)\rVert_2}$.

Air highways must not only provide structure to make the analysis of a large number of vehicles tractable, but also allow vehicles reach their destinations while minimizing any relevant costs to the vehicles and to the surrounding regions. Thus, given a origin-destination pair (eg. two cities), air highways must connect the two points while potentially satisfying other criteria. We now define the air highway placement problem, and propose a simple and fast way to approximate its solution.

\subsection{The Air Highway Placement Problem}
Consider a map $\cmap:\mathbb{R}^2 \rightarrow \mathbb{R}$ which defines the cost $\cmap(\pos)$ incurred when a UAV flies over the position $\pos=(\pos_x,\pos_y)\in\mathbb{R}^2$. Given any $\pos$, a large value of $\cmap(\pos)$ indicates that the position $\pos$ is costly or undesirable for a UAV to fly over. Locations with a high cost could be In general, the cost map $\cmap(\cdot)$ may be used to model cost of interference with commercial air spaces, cost of accidents, cost of noise pollution, etc., and can be designed by government regulation bodies.

Let $\pos^o$ denote an origin point and $\pos^d$ denote a destination point. Consider a sequence of highways $\hws_N = {\hw_1, \hw_2, \ldots, \hw_N}$ that satisfies the following:

\begin{equation}
\label{eq:hw_seq}
\begin{aligned}
\hw_1(0) &= \pos^o \\
\hw_i(1) &= \hw_{i+1}(0), i = 0, 1, \ldots, N-1 \\
\hw_N(1) &= \pos^d \\
\end{aligned}
\end{equation}

The interpretation of the above conditions is that the start point of first highway is the origin, the end point of a highway is the end point of the next highway, and the end point of last highway is the destination. The highways $\hw_1,\ldots,\hw_N$ form a sequence of waypoints for a UAV starting at the origin $\pos^o$ to reach its destination $\pos^d$.

Given only the origin point $\pos^o$ and destination point $\pos^d$, there are an infinite number of choices for a sequence of highways that satisfy \eqref{eq:hw_seq}. However, if one takes into account the cost of flying over any position $\pos$ using the cost map $\cmap(\cdot)$, we arrive at the air highway placement problem:

\begin{equation}
\label{eq:ahpp} % air highway placement problem
\begin{aligned}
& \min_{\hws_N, N} \sum_{i=1}^N \int_0^1 \cmap(\hw_i(s)) ds \\
& \text{subject to \eqref{eq:hw_seq}} 
\end{aligned}
\end{equation}

In other words, we consider air highways to be line segments of constant altitude over a region, and UAV platoons travel on these air highways to get from some origin to some destination. Any UAV flying on a highway over some position $\pos$ incurs a cost of $\cmap(\pos)$, so that the total cost of flying from the origin to the destination is given by \eqref{eq:ahpp}. The air highway placement problem minimizes the cumulative cost of flying from some origin $p^o$ to some destination $p^d$ along the sequence of highways $\hws_N$.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{"fig/highway_illustration"}
	\caption{Highway illustration}
	\label{fig:hw_ill}
\end{figure}

### 2016-01-20 docs/AIAA 2016/high_waypoints.tex
no message

--- 2015-10-16 docs/AIAA 2015/high_waypoints.tex
@@
 \subsection{From Paths to Waypoints}
-Each of the cost-minimizing paths $\hpath_{ij}$ computed from the solution to the Eikonal equation consists of a set of points which are close to adjacent points.
-To sparsify this set of points to obtain a collection of waypoints, $\wpt_{ij}$, which are also endpoints of air highways, we first add the destination point to the collection and note the path's heading.
+Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a continuous set of points.
+Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexes by the corresponding path.
+
+For each path $\ppath_i$, we would like to sparsify the points on the path to obtain a collection of waypoints, $\wpt_{i,j}, j = 1,\ldots, N_i+1$, which are the end points of the highways:
+
+\begin{equation}
+\begin{aligned}
+\hw^i_j(0) &= \wpt_{i,j}, \\
+\hw^i_j(1) &= \wpt_{i,j+1}, \\
+j &= 1,\ldots,N_i
+\end{aligned}
+\end{equation}
+
+ we sparsify this set of points to obtain a collection of waypoints, $\wpt$, which are also endpoints of air highways, we first add the destination point to the collection and note the path's heading.
 Next, we add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$.

### 2016-01-20 docs/AIAA 2016/introduction.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/introduction.tex
@@
-% !TEX root = platooning.tex
+% !TEX root = main.tex
 \section{Introduction}
 Unmanned aerial vehicle (UAV) systems have in the past been mainly used for military operations \cite{Tice91}.
-Recently, however, there has been an immense surge of interest in using UAVs for civil applications through projects such as Amazon Prime Air and Google Project Wing \cite{PrimeAir,ProjectWing,Debusk10}.
+Recently, however, there has been an immense surge of interest in using UAVs for civil applications.
+Through projects such as Amazon Prime Air and Google Project Wing, companies are looking to send UAVs into the airspace to deliver packages \cite{PrimeAir,ProjectWing}.
 As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone.
@@
 As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) of the United States are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13}.
+Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to firefight in areas that are difficult to reach but require prompt response \cite{Debusk10}.
 
@@
 These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
-Reachability is powerful because it can be used for synthesizing both controllers that steer the system towards a goal (liveness controllers), and controllers that steer the system away from danger (safety controllers).
-Furthermore, HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems.
+Reachability is a powerful tool because reachable sets can be used for synthesizing both controllers that steer the system towards a set of goal states (liveness controllers), and controllers that steer the system away from a set of unsafe states (safety controllers).
+Furthermore, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems.
 The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ Partial Differential Equation (PDE) \cite{LSToolbox,Osher02,Sethian96}.
@@
 We first propose a hybrid systems model of UAVs in platoons to capture this structure.
-Then, we show how HJ reachability can be used to synthesize \textit{liveness controllers} that enable vehicles to reach a set of desired states, and wrap \textit{safety controllers} around the liveness controllers to prevent dangerous configurations such as collisions.
+Then, we show how HJ reachability can be used to synthesize \textit{liveness controllers} that enable vehicles to reach a set of desired states, and wrap \textit{safety controllers} around the liveness controllers in order to prevent dangerous configurations such as collisions.
 Finally, we show simulation results of quadrotors forming a platoon, a platoon responding to a malfunctioning member, and a platoon responding to an outside intruder to illustrate the behavior of vehicles in these scenarios and demonstrate the guarantees provided by HJ reachability.

### 2016-01-20 docs/AIAA 2016/main.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/platooning.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
+\documentclass[journal]{aiaa-pretty}
 
-%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
-                                                          % if you need a4paper
-\documentclass[letterpaper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
+\newcommand{\pos}{p} % position
+\newcommand{\vel}{v} % velocity
+\newcommand{\hw}{\mathbb{H}} % a single highway
+\newcommand{\hws}{\mathbb{S}} % a sequence of highways
+\newcommand{\hwd}{\hat{d}}
+\newcommand{\cost}[1]{c_\text{#1}}
+\newcommand{\wpt}{\mathcal{W}}
+\newcommand{\cmap}{c}
+\newcommand{\ccost}{C}
+\newcommand{\ppath}{\mathbb{P}}
+\newcommand{\ocost}{V}
 
-\IEEEoverridecommandlockouts                              % This command is only
-                                                          % needed if you want to
-                                                          % use the \thanks command
-\overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
+\author{Mo Chen}
+\title{Guaranteeing Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}
 
-\usepackage{amsmath}    % need for sub equations
-\usepackage{amsfonts}
-\usepackage{graphicx}   % need for figures
-\usepackage{subcaption}
-\usepackage{epsfig} 
-\usepackage{color}
-\usepackage[normalem]{ulem}
-\usepackage{cancel}
-\usepackage{amssymb}
-\usepackage{color}
-%\usepackage{my_macros}
-\usepackage[ruled,vlined,titlenotnumbered]{algorithm2e}
-
-\title{\LARGE \bf
-Safe Platooning of Unmanned Aerial Vehicles via Reachability}
-
-\author{Mo Chen, Qie Hu, Casey Mackin, Jaime F. Fisac, and Claire J. Tomlin
-\thanks{This work has been supported in part by NSF under CPS:ActionWebs (CNS-931843), by ONR under the HUNT (N0014-08-0696) and SMARTS (N00014-09-1-1051) MURIs and by grant N00014-12-1-0609, by AFOSR under the CHASE MURI (FA9550-10-1-0567).
-The research of M.
-Chen has received funding from the ``NSERC PGS-D'' Program.
-The research of J.F.
-Fisac has received funding from the ``la Caixa" Foundation.}
-\thanks{All authors are with the Department of Electrical Engineering and Computer Sciences, University of California, Berkeley. \{mochen72,qiehu,cmackin,jfisac,tomlin\}@berkeley.edu}
-}
-
-\begin{document}
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%
-\begin{abstract}
-Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, firefighting, and fast disaster response.
+\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, firefighting, and fast disaster response.
 As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met.
@@
 For a single altitude range, our approach guarantees safety for one safety breach; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.
-We demonstrate the satisfaction of liveness and safety requirements through simulations of three common scenarios.
-\end{abstract}
+We demonstrate the satisfaction of liveness and safety requirements through simulations of three common scenarios.}
+
+\begin{document}
+
+\maketitle
+
+\section*{Nomenclature}
+(Nomenclature entries should have the units identified)\\
+\noindent\begin{tabular}{@{}lcl@{}}
+$x$ &=& System state \\
+$\pos=(\pos_x, \pos_y)$ &$=$& Horizontal position \\
+$\vel=(\vel_x, \vel_y)$ &$=$& Horizontal velocity
+\end{tabular} \\
 
 \input{introduction.tex}
-% Introduction (1p)
-%% Motivation
-%% Related work
-%% Summary of results
+\input{high_form.tex}
+\input{high_eikon.tex}
+\input{high_waypoints.tex}
+\input{high_sim.tex}
+\input{plat_form.tex}
+\input{plat_reach.tex}
+\input{plat_intra.tex}
+\input{plat_inter.tex}
+\input{plat_safety.tex}
+\input{plat_sim.tex}
+\input{conclusions.tex}
 
-\input{formulation.tex}
-% Problem formulation (1.5p)
-%% A number of quadrotors forming a platoon in a single file
-%% Platoon definition and functions
+\section*{Appendix}
 
-\input{solution.tex}
-% Solution methodology (1.5-2p)
-%% Hybrid model of vehicles
-%% Reachability
-%% Functions of platoons: following, joining, splitting
+\section*{Acknowledgments}
+This work is supported in part by NSF under CPS:ActionWebs (CNS-0931843) and CPS:FORCES (CNS1239166), by NASA under grants NNX12AR18A and UCSCMCA-14-022 (UARC), by ONR under grants N00014-12-1-0609, N000141310341 (Embedded Humans MURI), and MIT\_5710002646 (SMARTS MURI), and by AFOSR under grants UPenn-FA9550-10-1-0567 (CHASE MURI) and the SURE project.
 
-% \input{analysis.tex}
-%% Information pattern, stability (0.5p)
-
-\input{results.tex}
-% Numerical Simuations (1-1.5p)
-%% 1: normal operation: form platoon by joining --> just follow --> 1 quadrotor leaves
-%% - Mo
-%% 2: vehicles already in platoon, one of them goes rogue
-%% - Casey
-%% 3: vehicles in platoon, intruder vehicle
-%% - Qie
-%% 4: vehicles in platoon, another vehicle joining, one vehicle in platoon goes rogue
-%%
-%% followPlatoon - Jaime
-
-\input{conclusion.tex}
-
-% Conclusion (0.5p)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\addtolength{\textheight}{1cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
- \bibliographystyle{IEEEtran}
 \bibliography{references}

### 2016-01-20 docs/AIAA 2016/plat_form.tex
no message

--- 2015-12-16 docs/AIAA 2015/plat_form.tex
@@
 \begin{aligned}
-\dot{\pos}_x &= \vel_x, \qquad \dot{\pos}_y = \vel_y  \\
-\dot{\vel}_x &= u_x, \qquad \dot{\vel}_y = u_y, \qquad |u_x|,|u_y| \le u_\text{max}
+\dot{\pos}_x &= \vel_x \\
+\dot{\pos}_y &= \vel_y  \\
+\dot{\vel}_x &= u_x \\
+\dot{\vel}_y &= u_y \\
+|u_x|,|u_y| &\le u_\text{max}
 \end{aligned}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{"fig/vehicleModes"}
+	\includegraphics[width=0.5\textwidth]{"fig/vehicleModes"}
 	\caption{Hybrid modes for vehicles in platoons.}
@@
 The answers to these questions can be broken down into the maneuvers listed in Section \ref{subsec:platoon_def}.
-In general, the control strategies of each quadrotor have a liveness component, which specifies a set of states towards which the quadrotor aims to reach, and a safety component, which specifies a set of states that it must avoid.
-In this paper, we address both the liveness and safety component using reachability analysis.
+In general, the control strategies of each vehicle have a liveness component, which specifies a set of states towards which the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.
+Together, the liveness and safety controllers guarantee the success and safety of a vehicle in the airspace making any desired mode transition.
+In this paper, these guarantees are provided using reachability analysis.

### 2016-01-20 docs/AIAA 2016/plat_intra.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/solution.tex
@@
-% !TEX root = platooning.tex
-\section{Hamilton-Jacobi Reachability  \label{sec:HJI}}
-\subsection{General Framework}
-Consider a differential game between two players described by the system
-\begin{equation} \label{eq:dyn}
-\dot{x} = f(x, u_1, u_2), \text{for almost every }t\in [-T,0]
-\end{equation}
-
-\noindent where $x\in\mathbb{R}^n$ is the system state, $u_1\in \mathcal{U}_1$ is the control of Player 1, and $u_2\in\mathcal{U}_2$ is the control of Player 2.
-We assume $f:\mathbb{R}^n\times \mathcal{U}_1 \times \mathcal{U}_2 \rightarrow \mathbb{R}^n$ is uniformly continuous, bounded, and Lipschitz continuous in $x$ for fixed $u_1,u_2$, and the control functions $u_1(\cdot)\in\mathbb{U}_1,u_2(\cdot)\in\mathbb{U}_2$ are drawn from the set of measurable functions.
-Player 2 is allowed to use nonanticipative strategies \cite{Evans84,Varaiya67} $\gamma$, defined by
-
-\begin{equation}
-\begin{aligned}
-\gamma &\in \Gamma := \{\mathcal{N}: \mathbb{U}_1 \rightarrow \mathbb{U}_2 \mid  u_1(r) = \hat{u}_1(r) \\
-&\text{for almost every } r\in[t,s] \Rightarrow \mathcal{N}[u_1](r) \\
-&= \mathcal{N}[\hat{u}_1](r) \text{ for almost every } r\in[t,s]\}
-\end{aligned}
-\end{equation}
-
-In our differential game, the goal of Player 2 is to drive the system into some target set $\mathcal{L}$, and the goal of Player 1 is to drive the system away from it.
-The set $\mathcal{L}$ is represented as the zero sublevel set of a bounded, Lipschitz continuous function $l:\mathbb{R}^n\rightarrow\mathbb{R}$.
-We call $l(\cdot)$ the \textit{implicit surface function} representing the set $\mathcal L: \mathcal{L}=\{x\in\mathbb{R}^n \mid l(x)\le 0\}$.
-
-Given the dynamics \eqref{eq:dyn} and the target set $\mathcal{L}$, we would like to compute the backwards reachable set, $\mathcal{V}(t)$:
-
-\begin{equation}
-\begin{aligned}
-\mathcal{V}(t) &:= \{x\in\mathbb{R}^n \mid \exists \gamma\in\Gamma \text{ such that } \forall u_1(\cdot)\in\mathbb{U}_1, \\
-&\exists s \in [t,0], \xi_f(s; t, x, u_1(\cdot), \gamma[u_1](\cdot)) \in \mathcal{L} \}
-\end{aligned}
-\end{equation}
-where $\xi_f$ is the trajectory of the system satisfying initial conditions $\xi_f(t; x, t, u_1(\cdot), u_2(\cdot))=x$ and the following differential equation almost everywhere on $[-t, 0]$
-\begin{equation}
-\begin{aligned}
-\frac{d}{ds}&\xi_f(s; x, t, u_1(\cdot), u_2(\cdot)) \\
-&= f(\xi_f(s; x, t, u_1(\cdot), u_2(\cdot)), u_1(s), u_2(s))
-\end{aligned}
-\end{equation}
-
-For this paper, we use the HJ formulation in \cite{Mitchell05}, which has shown that the backwards reachable set $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
-
-\begin{equation} \label{eq:HJIPDE}
-\begin{aligned}
-D_t &V +\min \{0, \max_{u_1\in\mathcal{U}_1} \min_{u_2\in\mathcal{U}_2} D_x V \cdot f(x,u_1,u_2) \} = 0, \\
-&V(0,x) = l(x)
-\end{aligned}
-\end{equation}
-
-\noindent from which we obtain $\mathcal{V}(t) = \{x\in\mathbb{R}^n \mid V(t,x)\le 0\}$. From the solution $V(t,x)$, we can also obtain the optimal controls for both players via the following:
-
-\begin{equation} \label{eq:HJI_ctrl_syn}
-\begin{aligned}
-u_1^*(t,x) &= \arg \max_{u_1\in\mathcal{U}_1} \min_{u_2\in\mathcal U_2} D_x V(t,x) \cdot f(x,u_1,u_2)\\
-u_2^*(t,x) &= \arg \min_{u_2\in\mathcal{U}_2} D_x V(t,x) \cdot f(x,u_1^*,u_2)
-\end{aligned}
-\end{equation}
-
-In the special case where there is only one player (player 2 does not exist), we obtain an optimal control problem for a system with dynamics
-
-\begin{equation} \label{eq:dyn_d}
-\dot{x} = f(x, u), t\in [-T,0], u\in\mathcal U.
-\end{equation}
-
-The reachable set in this case would be given by the Hamilton-Jacobi-Bellman (HJB) PDE
-
-\begin{equation} \label{eq:HJBPDE}
-\begin{aligned}
-D_t V(t,x) + \min \{0, \min_{u\in\mathcal{U}} D_x V(t,x) \cdot f(x,u)\} &= 0 \\
-V(0,x) = l(x)&
-\end{aligned}
-\end{equation}
-
-\noindent where the optimal control is given by
-
-\begin{equation} \label{eq:HJB_ctrl_syn}
-u^*(t,x) = \arg \min_{u\in\mathcal{U}} D_x V(t,x) \cdot f(x,u)
-\end{equation}
-
-For our application, we will use a several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real time 4D reachable set computations and tractable 6D reachable set computations.
-
-\section{Liveness Controllers \label{sec:liveness}}
-\subsection{Merging onto a Highway \label{subsec:highway_merge}}
-We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity along the highway.
-Thus, a quadrotor would aim to drive the system \eqref{eq:dyn} to a state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
+% !TEX root = main.tex
+\subsection{Intra-Platoon Controllers}
+\subsubsection{Merging onto a Highway \label{subsec:highway_merge}}
+We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity whose magnitude (the speed) is given by the highway specification, and whose direction is along the highway.
+Thus, for a quadrotor, the objective would be to drive the system in \eqref{eq:dyn} to a specific state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
 
@@
 
-In this reachability problem, $\mathcal{L}_H$ is the target set, represented by the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE to be solved.
+In this reachability problem, $\mathcal{L}_H$ is the target set, represented by the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE that we need to solve.
 The solution we obtain, $V_H(t,x)$, is the implicit surface function representing the reachable set $\mathcal V_H(t)$; $V_H(-T,x)\le 0$, then, specifies the reachable set $\mathcal{V}_H(T)$, the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.
@@
 \begin{enumerate}
-\item Move towards $\bar{x}_H$ in a straight line until $V_H(-T,x)\le 0$. This heuristic works well in practice. 
+\item Move towards $\bar{x}_H$ in a straight line, with some velocity, until $V_H(-T,x)\le 0$.
 \item Apply the optimal control extracted from $V_H(-T,x)$ according to \eqref{eq:HJB_ctrl_syn} until $\mathcal{L}_H$ is reached.
@@
 
-\subsection{Merging into a Platoon \label{subsec:platoon_merge}}
+\subsubsection{Merging into a Platoon \label{subsec:platoon_merge}}
 We again pose the merging of a quadrotor into a platoon on an air highway as a reachability problem.
@@
 \begin{enumerate}
-\item Move towards $\bar{x}_P$ in a straight line until $V_P(-T,x)\le 0$.
+\item Move towards $\bar{x}_P$ in a straight line, with some velocity, until $V_P(-T,x)\le 0$.
 \item Apply the optimal control extracted from $V_P(-T,x)$ according to \eqref{eq:HJI_ctrl_syn} until $\mathcal{L}_P$ is reached.
@@
 
-\subsection{Other Quadrotor Maneuvers}
+\subsubsection{Other Quadrotor Maneuvers}
+Reachability was used in Sections \ref{subsec:highway_merge} and \ref{subsec:platoon_merge} for the relatively complex maneuvers.
 For the simpler maneuvers of traveling along a highway and following a platoon, we resort to simpler controllers described below.
@@
 \subsubsection{Traveling along a highway} \label{sec:travel_hwy}
-We use a model-predictive controller (MPC) for traveling along a highway at a pre-specified speed.
-Here, a leader quadrotor tracks a constant-altitude path, defined as a curve $\bar{p}(s)$ parametrized by $s\in[0,1]$ in $p=(p_x, p_y)$ space (position space), while maintaining a velocity $\bar{v}(s)$ that corresponds to constant speed in the direction of the highway.
+We use a model-predictive controller (MPC) for traveling along a highway; this controller allows the leader to travel along a highway at a pre-specified speed.
+Here, the goal is for a leader quadrotor to track a constant-altitude path, defined as a curve $\bar{p}(s)$ parametrized by $s\in[0,1]$ in $p=(p_x, p_y)$ space (position space), while maintaining a velocity $\bar{v}(s)$ that corresponds to constant speed in the direction of the highway.
+Assuming that the initial position on the highway, $s_0=s(t_0)$ is specified, such a controller can be obtained from the following optimization problem over the time horizon $[t_0, t_1]$:
+
+\begin{equation}
+\begin{aligned}
+\text{minimize } & \int_{t_0}^{t_1} \big\{\| p(t)-\bar{p}(s(t)) \|_2 + \\ 
+&\qquad \| v(t) - \bar{v}(s(t)) \|_2 + 1-s \big\} dt \\
+\text{subject to } & \dot{x} = f(x,u) \text{ where } f \text{ is given in \eqref{eq:dyn}} \\
+& |u_x|, |u_y| \le u_\text{max}, |v_x|, |v_y| \le v_\text{max} \\
+& s(t_0) = s_0, \dot{s} \ge 0
+\end{aligned}
+\end{equation}
+
+If we discretize time, and assume that $\bar{p}(\cdot)$ is linear, then the above optimization is convex, and can be quickly solved.
 
 \subsubsection{Following a Platoon} \label{sec:follow_platoon}
-Follower vehicles use a feedback control law tracking a nominal position and velocity in the platoon, with an additional feed-forward term given by the leader's acceleration input.
+Follower vehicles use a feedback control law tracking a nominal position and velocity in the platoon, with an additional feed-forward term given by the leader's acceleration input; here, for simplicity, we assume perfect communication between the leader and the follower vehicles.
+This following law enables smooth vehicle trajectories in the relative platoon frame, while allowing the platoon as a whole to perform agile maneuvers by transmitting the leader's acceleration command $u_{P_1}(t)$ to all vehicles.
 
@@
 \end{equation}
-for some $k_p,k_v>0$. A simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
+for some $k_p,k_v>0$.
+The leader can modify the nominal position of vehicles in the platoon, for example to command the formation to turn.
+In particular, a simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
 \begin{equation}\label{eq:nominal_pos}
@@
 
-\section{Safety Controllers \label{sec:safety}}
-\subsection{Wrapping Reachability Around Existing Controllers}
+\subsection{Safety Controllers \label{sec:safety}}
+\subsubsection{Wrapping Reachability Around Existing Controllers}
 A quadrotor can use a liveness controller when it is not in any danger of collision with other quadrotors or obstacles.
@@
 \end{enumerate}
-
-\subsection{Platoon Safety Guarantees \label{subsec:safety_guarantees}}
-Under normal operations in a single platoon, each follower quadrotor $Q_{P_i},i>1$ checks whether it is in the safety reachable set with respect to $Q_{P_{i-1}}$ and $Q_{P_{i+1}}$.
-So $\mathcal{Q}(i) = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$.
-Assuming there are no nearby quadrotors outside of the platoon, the platoon leader $Q_{P_1}$ checks safety against $Q_{P_2}$, and the platoon trailer $Q_{P_N}$ checks safety against $Q_{P_{N-1}}$.
-So $\mathcal{Q}(P_1)=\{P_2\}, \mathcal{Q}(P_N)=\{P_{N-1}\}$.
-No pair of quadrotors should be in an unsafe configuration if the liveness controllers are well-designed.
-Occasionally, a quadrotor $Q_k$ may behave unexpectedly due to faults, which may lead to an unsafe configuration.
-
-With our choice of $\mathcal{Q}(i)$ and the assumption that the platoon is in a single-file formation, some quadrotor $Q_i$ would get into an unsafe configuration with $Q_k$, where $Q_k$ is likely to be the quadrotor in front or behind of $Q_i$.
-In this case, a ``safety breach" occurs.
-Our synthesis of the safety controller guarantees that between every pair of quadrotors $Q_i,Q_k$, as long as $V_S(-t,x_i- x_k)>0$, $\exists u_i$ to keep $Q_i$ from colliding with $Q_k$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $Q_k$.
-Therefore, as long as the number of ``safety breaches" is at most one, $Q_i$ can simply use the optimal control to avoid $Q_k$ and avoid collision for the time horizon of $t$.
-Since quadrotors in platoons are able to exit the current altitude range within a duration of $t_\text{internal}$, if we choose $t=t_\text{internal}$, the safety breach would always end before any collision can occur.
-
-Within a duration of $t_\text{internal}$, there is a small chance that additional safety breaches may occur.
-However, as long as the total number of safety breaches does not exceed the number of affected quadrotors, collision avoidance of all the quadrotors can be guaranteed for the duration $t_\text{internal}$.
-However, as our simulation results show, putting quadrotors in single-file platoons makes the likelihood of multiple safety breaches low during a quadrotor malfunction and during the presence of one intruder vehicle.
-
-In the event that multiple safety breaches occur for some of the quadrotors due to a malfunctioning quadrotor within the platoon or an intruding quadrotor outside of the platoon, those quadrotors with more than one safety breach still have the option of exiting the highway altitude range in order to avoid collisions.
-Every extra altitude range reduces the number of simultaneous safety breaches by $1$, so $K$ simultaneous safety breaches can be resolved using $K-1$ different altitude ranges.
-
-Given that quadrotors within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons.
-By treating each platoon as a single unit, we reduce the number of individual quadrotors that need to check for safety against each other, reducing overall computation burden.

### 2016-01-20 docs/AIAA 2016/plat_reach.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/solution.tex
@@
-% !TEX root = platooning.tex
-\section{Hamilton-Jacobi Reachability  \label{sec:HJI}}
-\subsection{General Framework}
+% !TEX root = main.tex
+\subsection{Hamilton-Jacobi Reachability}
+\subsubsection{General Framework}
 Consider a differential game between two players described by the system
@@
 \noindent where $x\in\mathbb{R}^n$ is the system state, $u_1\in \mathcal{U}_1$ is the control of Player 1, and $u_2\in\mathcal{U}_2$ is the control of Player 2.
-We assume $f:\mathbb{R}^n\times \mathcal{U}_1 \times \mathcal{U}_2 \rightarrow \mathbb{R}^n$ is uniformly continuous, bounded, and Lipschitz continuous in $x$ for fixed $u_1,u_2$, and the control functions $u_1(\cdot)\in\mathbb{U}_1,u_2(\cdot)\in\mathbb{U}_2$ are drawn from the set of measurable functions.
+We assume $f:\mathbb{R}^n\times \mathcal{U}_1 \times \mathcal{U}_2 \rightarrow \mathbb{R}^n$ is uniformly continuous, bounded, and Lipschitz continuous in $x$ for fixed $u_1,u_2$, and the control functions $u_1(\cdot)\in\mathbb{U}_1,u_2(\cdot)\in\mathbb{U}_2$ are drawn from the set of measurable functions\footnote{
+A function $f:X\to Y$ between two measurable spaces $(X,\Sigma_X)$ and $(Y,\Sigma_Y)$ is said to be measurable if the preimage of a measurable set in $Y$ is a measurable set in $X$, that is: $\forall V\in\Sigma_Y, f^{-1}(V)\in\Sigma_X$, with $\Sigma_X,\Sigma_Y$ $\sigma$-algebras on $X$,$Y$.}.
 Player 2 is allowed to use nonanticipative strategies \cite{Evans84,Varaiya67} $\gamma$, defined by
@@
 \begin{aligned}
-\mathcal{V}(t) &:= \{x\in\mathbb{R}^n \mid \exists \gamma\in\Gamma \text{ such that } \forall u_1(\cdot)\in\mathbb{U}_1, \\
+\mathcal{V}(t) &:= \{x\in\mathbb{R}^n \mid \exists \gamma\in\Gamma \text{ such that} \forall u_1(\cdot)\in\mathbb{U}_1, \\
 &\exists s \in [t,0], \xi_f(s; t, x, u_1(\cdot), \gamma[u_1](\cdot)) \in \mathcal{L} \}
@@
 
-For this paper, we use the HJ formulation in \cite{Mitchell05}, which has shown that the backwards reachable set $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
+Many methods involving solving HJ PDEs \cite{Mitchell05} and HJ variational inequalities (VI) \cite{Bokanowski10,Barron89,Fisac15} have been developed for computing the reachable set.
+These HJ PDEs and HJ VIs can be solved using well-established numerical methods.
+For this paper, we use the formulation in \cite{Mitchell05}, which has shown that the backwards reachable set $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
 
@@
 \begin{aligned}
-D_t &V +\min \{0, \max_{u_1\in\mathcal{U}_1} \min_{u_2\in\mathcal{U}_2} D_x V \cdot f(x,u_1,u_2) \} = 0, \\
+D_t &V(t,x) + \\
+&\min \{0, \max_{u_1\in\mathcal{U}_1} \min_{u_2\in\mathcal{U}_2} D_x V(t,x) \cdot f(x,u_1,u_2) \} = 0, \\
 &V(0,x) = l(x)
@@
 \end{equation}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{"fig/RSExample"}
+	\caption{Illustration of a target set, reachable set, and their implicit surface functions.}
+	\label{fig:RSExample}
+\end{figure}
 
@@
 
-In the special case where there is only one player (player 2 does not exist), we obtain an optimal control problem for a system with dynamics
+In the special case where there is only one player, we obtain an optimal control problem for a system with dynamics
 
@@
 
-\section{Liveness Controllers \label{sec:liveness}}
-\subsection{Merging onto a Highway \label{subsec:highway_merge}}
-We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity along the highway.
-Thus, a quadrotor would aim to drive the system \eqref{eq:dyn} to a state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
+\subsubsection{Relative Dynamics and Augmented Relative Dynamics}
+Besides Equation \eqref{eq:dyn}, we will also consider the relative dynamics between two quadrotors $Q_i,Q_j$. These dynamics can be obtained by defining the relative variables
+
+\begin{equation} \label{eq:rel_var}
+\begin{aligned}
+p_{x,r} &= p_{x,i} - p_{x,j} \\
+p_{y,r} &= p_{y,i} - p_{y,j}\\
+v_{x,r} &= v_{x,i} - v_{x,j}\\
+v_{y,r} &= v_{y,i} - v_{y,j}
+\end{aligned}
+\end{equation}
+
+We treat $Q_i$ as Player 1, the evader who wishes to avoid collision, and we treat $Q_j$ as Player 2, the pursuer, or disturbance, that wishes to cause a collision.
+In terms of the relative variables given in \eqref{eq:rel_var}, we have
 
@@
 \begin{aligned}
-\mathcal{L}_H = \{x: |p_x-\bar{p}_x|\le r_{p_x}, |v_x-\bar{v}_x|\le r_{v_x}, \\
-|p_y - \bar{p}_y| \le r_{p_y}, |v_y - \bar{v}_y|\le r_{v_y} \}.
+\dot{p}_{x,r} &= v_{x,r} \\
+\dot{p}_{y,r} &= v_{y,r} \\
+\dot{v}_{x,r} &= u_{x,i} - u_{x,j} \\
+\dot{v}_{y,r} &= u_{y,i} - u_{y,j}
 \end{aligned}
@@
 
-In this reachability problem, $\mathcal{L}_H$ is the target set, represented by the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE to be solved.
-The solution we obtain, $V_H(t,x)$, is the implicit surface function representing the reachable set $\mathcal V_H(t)$; $V_H(-T,x)\le 0$, then, specifies the reachable set $\mathcal{V}_H(T)$, the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.
-This gives the algorithm for merging onto the highway:
+\begin{figure}
+	\centering
+	\includegraphics[width=0.25\textwidth]{"fig/rel_coords"}
+	\caption{Relative coordinates}
+	\label{fig:rel_coords}
+\end{figure}
 
-\begin{enumerate}
-\item Move towards $\bar{x}_H$ in a straight line until $V_H(-T,x)\le 0$. This heuristic works well in practice. 
-\item Apply the optimal control extracted from $V_H(-T,x)$ according to \eqref{eq:HJB_ctrl_syn} until $\mathcal{L}_H$ is reached.
-\end{enumerate}
+We also augment \eqref{eq:rel_var} with the velocity of $Q_i$, given in \eqref{eq:rel_dyn_aug}, to impose a velocity limit on the quadrotor.
 
-\subsection{Merging into a Platoon \label{subsec:platoon_merge}}
-We again pose the merging of a quadrotor into a platoon on an air highway as a reachability problem.
-Here, we would like quadrotor $Q_i$ to merge onto the highway and follow another quadrotor $Q_j$ in a platoon.
-Thus, we would like to drive the system given by \eqref{eq:rel_dyn_aug} to a specific $\bar{x}_P = (\bar{p}_{x,r}, \bar{v}_{x,r}, \bar{p}_{y,r}, \bar{v}_{y,r})$, or a small range of relative states defined by the set
-
-\begin{equation}
+\begin{equation} \label{eq:rel_dyn_aug}
 \begin{aligned}
-\mathcal{L}_P = \{x: |p_{x,r}-\bar{p}_{x,r}|\le r_{p_x}, |v_{x,r}-\bar{v}_{x,r}|\le r_{v_x}, \\
-|p_{y,r} - \bar{p}_{y,r}| \le r_{p_y}, |v_{y,r} - \bar{v}_{y,r}|\le r_{v_y} \}
+\dot{p}_{x,r} &= v_{x,r} \\
+\dot{p}_{y,r} &= v_{y,r} \\
+\dot{v}_{x,r} &= u_{x,i} - u_{x,j} \\
+\dot{v}_{y,r} &= u_{y,i} - u_{y,j} \\
+\dot{v}_{x,i} &= u_{x,i} \\
+\dot{v}_{y,i} &= u_{y,i}
 \end{aligned}
 \end{equation}
-
-The target set $\mathcal{L}_P$ is represented by the implicit surface function $l_P(x)$, which specifies the terminal condition of the HJI PDE \eqref{eq:HJIPDE}.
-The zero sublevel set of the solution to \eqref{eq:HJIPDE}, $V_P(-T,x)$, gives us the set of relative states from which $Q_i$ can reach the target and join the platoon following $Q_j$ within a duration of $T$.
-We assume that $Q_j$ moves along the highway at constant speed, so that $u_j(t)$ = 0.
-The following is a suitable algorithm for a quadrotor merging onto a highway and joining a platoon to follow $Q_j$:
-
-\begin{enumerate}
-\item Move towards $\bar{x}_P$ in a straight line until $V_P(-T,x)\le 0$.
-\item Apply the optimal control extracted from $V_P(-T,x)$ according to \eqref{eq:HJI_ctrl_syn} until $\mathcal{L}_P$ is reached.
-\end{enumerate}
-
-\subsection{Other Quadrotor Maneuvers}
-For the simpler maneuvers of traveling along a highway and following a platoon, we resort to simpler controllers described below.
-
-\subsubsection{Traveling along a highway} \label{sec:travel_hwy}
-We use a model-predictive controller (MPC) for traveling along a highway at a pre-specified speed.
-Here, a leader quadrotor tracks a constant-altitude path, defined as a curve $\bar{p}(s)$ parametrized by $s\in[0,1]$ in $p=(p_x, p_y)$ space (position space), while maintaining a velocity $\bar{v}(s)$ that corresponds to constant speed in the direction of the highway.
-
-\subsubsection{Following a Platoon} \label{sec:follow_platoon}
-Follower vehicles use a feedback control law tracking a nominal position and velocity in the platoon, with an additional feed-forward term given by the leader's acceleration input.
-
-The $i$-th member of the platoon, $Q_{P_i}$, is expected to track a relative position in the platoon $r^i = (r_x^i,r_y^i)$ with respect to the leader's position $p_{P_1}$, and the leader's velocity $v_{P_1}$ at all times.
-The resulting control law has the form:
-\begin{equation}\label{eq:follow}
-u^i(t) = k_p \big[p_{P_1}(t) + r^i(t) - p^i(t) \big] + k_v\big[v_{P_1}(t) - v^i(t)\big] + u_{P_1}(t)
-\end{equation}
-for some $k_p,k_v>0$. A simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
-\begin{equation}\label{eq:nominal_pos}
-r^i(t) = - (i-1) b \frac{v_{P_1}}{\|v_{P_1}\|_2}
-\end{equation}
-where $b$ is the spacing between vehicles along the platoon. and $\frac{v_{P_1}}{\|v_{P_1}\|_2}$ is the platoon leader's direction of travel.
-
-\section{Safety Controllers \label{sec:safety}}
-\subsection{Wrapping Reachability Around Existing Controllers}
-A quadrotor can use a liveness controller when it is not in any danger of collision with other quadrotors or obstacles.
-If the quadrotor could potentially be involved in a collision within the next short period of time, it must switch to a safety controller.
-In this section, we will demonstrate how HJ reachability can be used to both detect imminent danger and synthesize a controller that guarantees safety within a specified time horizon.
-For our safety analysis, we will use the model in Equation \eqref{eq:rel_dyn_aug}.
-
-We begin by defining the target set $\mathcal{L}_S$, which characterizes configurations in relative coordinates for which quadrotors $Q_i,Q_j$ are considered to be in collision:
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}_S = \{x: &|p_{x,r}|, |p_{y,r}|\le d \vee |v_{x,i}| \ge v_\text{max} \vee |v_{y,i}| \ge v_\text{max} \}
-\end{aligned}
-\end{equation}
-
-With this definition, $Q_i$ is considered to be unsafe if $Q_i$ and $Q_j$ are within a distance $d$ in both $x$- and $y$-directions simultaneously, or if $Q_i$ has exceeded some maximum speed $v_\text{max}$ in either $x$- or $y$-direction.
-For illustration purposes, we choose $d=2$ meters, and $v_\text{max}= 5$ m/s.
-
-We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJI PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition.
-As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the reachable set $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst case control.
-To avoid collisions, $Q_i$ must apply the safety controller according to \eqref{eq:HJI_ctrl_syn} on the boundary of the reachable set in order to avoid going into the reachable set.
-The following algorithm wraps our safety controller around liveness controllers:
-
-\begin{enumerate}
-\item For a specified time horizon $t$, evaluate$V_S(-t,x_i-x_j)$ for all $j\in \mathcal{Q}(i)$.
-
-$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against. We discuss $\mathcal{Q}(i)$ in Section \ref{subsec:safety_guarantees}.
-
-\item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:
-
-If $\exists j\in \mathcal{Q}(i),V_S(-t,x_i-x_j)\le 0$, then $Q_i,Q_j$ are in potential conflict, and $Q_i$ must use a safety controller; otherwise $Q_i$ uses a liveness controller.
-\end{enumerate}
-
-\subsection{Platoon Safety Guarantees \label{subsec:safety_guarantees}}
-Under normal operations in a single platoon, each follower quadrotor $Q_{P_i},i>1$ checks whether it is in the safety reachable set with respect to $Q_{P_{i-1}}$ and $Q_{P_{i+1}}$.
-So $\mathcal{Q}(i) = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$.
-Assuming there are no nearby quadrotors outside of the platoon, the platoon leader $Q_{P_1}$ checks safety against $Q_{P_2}$, and the platoon trailer $Q_{P_N}$ checks safety against $Q_{P_{N-1}}$.
-So $\mathcal{Q}(P_1)=\{P_2\}, \mathcal{Q}(P_N)=\{P_{N-1}\}$.
-No pair of quadrotors should be in an unsafe configuration if the liveness controllers are well-designed.
-Occasionally, a quadrotor $Q_k$ may behave unexpectedly due to faults, which may lead to an unsafe configuration.
-
-With our choice of $\mathcal{Q}(i)$ and the assumption that the platoon is in a single-file formation, some quadrotor $Q_i$ would get into an unsafe configuration with $Q_k$, where $Q_k$ is likely to be the quadrotor in front or behind of $Q_i$.
-In this case, a ``safety breach" occurs.
-Our synthesis of the safety controller guarantees that between every pair of quadrotors $Q_i,Q_k$, as long as $V_S(-t,x_i- x_k)>0$, $\exists u_i$ to keep $Q_i$ from colliding with $Q_k$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $Q_k$.
-Therefore, as long as the number of ``safety breaches" is at most one, $Q_i$ can simply use the optimal control to avoid $Q_k$ and avoid collision for the time horizon of $t$.
-Since quadrotors in platoons are able to exit the current altitude range within a duration of $t_\text{internal}$, if we choose $t=t_\text{internal}$, the safety breach would always end before any collision can occur.
-
-Within a duration of $t_\text{internal}$, there is a small chance that additional safety breaches may occur.
-However, as long as the total number of safety breaches does not exceed the number of affected quadrotors, collision avoidance of all the quadrotors can be guaranteed for the duration $t_\text{internal}$.
-However, as our simulation results show, putting quadrotors in single-file platoons makes the likelihood of multiple safety breaches low during a quadrotor malfunction and during the presence of one intruder vehicle.
-
-In the event that multiple safety breaches occur for some of the quadrotors due to a malfunctioning quadrotor within the platoon or an intruding quadrotor outside of the platoon, those quadrotors with more than one safety breach still have the option of exiting the highway altitude range in order to avoid collisions.
-Every extra altitude range reduces the number of simultaneous safety breaches by $1$, so $K$ simultaneous safety breaches can be resolved using $K-1$ different altitude ranges.
-
-Given that quadrotors within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons.
-By treating each platoon as a single unit, we reduce the number of individual quadrotors that need to check for safety against each other, reducing overall computation burden.

### 2016-01-20 docs/AIAA 2016/plat_safety.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/solution.tex
@@
-% !TEX root = platooning.tex
-\section{Hamilton-Jacobi Reachability  \label{sec:HJI}}
-\subsection{General Framework}
-Consider a differential game between two players described by the system
-\begin{equation} \label{eq:dyn}
-\dot{x} = f(x, u_1, u_2), \text{for almost every }t\in [-T,0]
-\end{equation}
-
-\noindent where $x\in\mathbb{R}^n$ is the system state, $u_1\in \mathcal{U}_1$ is the control of Player 1, and $u_2\in\mathcal{U}_2$ is the control of Player 2.
-We assume $f:\mathbb{R}^n\times \mathcal{U}_1 \times \mathcal{U}_2 \rightarrow \mathbb{R}^n$ is uniformly continuous, bounded, and Lipschitz continuous in $x$ for fixed $u_1,u_2$, and the control functions $u_1(\cdot)\in\mathbb{U}_1,u_2(\cdot)\in\mathbb{U}_2$ are drawn from the set of measurable functions.
-Player 2 is allowed to use nonanticipative strategies \cite{Evans84,Varaiya67} $\gamma$, defined by
-
-\begin{equation}
-\begin{aligned}
-\gamma &\in \Gamma := \{\mathcal{N}: \mathbb{U}_1 \rightarrow \mathbb{U}_2 \mid  u_1(r) = \hat{u}_1(r) \\
-&\text{for almost every } r\in[t,s] \Rightarrow \mathcal{N}[u_1](r) \\
-&= \mathcal{N}[\hat{u}_1](r) \text{ for almost every } r\in[t,s]\}
-\end{aligned}
-\end{equation}
-
-In our differential game, the goal of Player 2 is to drive the system into some target set $\mathcal{L}$, and the goal of Player 1 is to drive the system away from it.
-The set $\mathcal{L}$ is represented as the zero sublevel set of a bounded, Lipschitz continuous function $l:\mathbb{R}^n\rightarrow\mathbb{R}$.
-We call $l(\cdot)$ the \textit{implicit surface function} representing the set $\mathcal L: \mathcal{L}=\{x\in\mathbb{R}^n \mid l(x)\le 0\}$.
-
-Given the dynamics \eqref{eq:dyn} and the target set $\mathcal{L}$, we would like to compute the backwards reachable set, $\mathcal{V}(t)$:
-
-\begin{equation}
-\begin{aligned}
-\mathcal{V}(t) &:= \{x\in\mathbb{R}^n \mid \exists \gamma\in\Gamma \text{ such that } \forall u_1(\cdot)\in\mathbb{U}_1, \\
-&\exists s \in [t,0], \xi_f(s; t, x, u_1(\cdot), \gamma[u_1](\cdot)) \in \mathcal{L} \}
-\end{aligned}
-\end{equation}
-where $\xi_f$ is the trajectory of the system satisfying initial conditions $\xi_f(t; x, t, u_1(\cdot), u_2(\cdot))=x$ and the following differential equation almost everywhere on $[-t, 0]$
-\begin{equation}
-\begin{aligned}
-\frac{d}{ds}&\xi_f(s; x, t, u_1(\cdot), u_2(\cdot)) \\
-&= f(\xi_f(s; x, t, u_1(\cdot), u_2(\cdot)), u_1(s), u_2(s))
-\end{aligned}
-\end{equation}
-
-For this paper, we use the HJ formulation in \cite{Mitchell05}, which has shown that the backwards reachable set $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
-
-\begin{equation} \label{eq:HJIPDE}
-\begin{aligned}
-D_t &V +\min \{0, \max_{u_1\in\mathcal{U}_1} \min_{u_2\in\mathcal{U}_2} D_x V \cdot f(x,u_1,u_2) \} = 0, \\
-&V(0,x) = l(x)
-\end{aligned}
-\end{equation}
-
-\noindent from which we obtain $\mathcal{V}(t) = \{x\in\mathbb{R}^n \mid V(t,x)\le 0\}$. From the solution $V(t,x)$, we can also obtain the optimal controls for both players via the following:
-
-\begin{equation} \label{eq:HJI_ctrl_syn}
-\begin{aligned}
-u_1^*(t,x) &= \arg \max_{u_1\in\mathcal{U}_1} \min_{u_2\in\mathcal U_2} D_x V(t,x) \cdot f(x,u_1,u_2)\\
-u_2^*(t,x) &= \arg \min_{u_2\in\mathcal{U}_2} D_x V(t,x) \cdot f(x,u_1^*,u_2)
-\end{aligned}
-\end{equation}
-
-In the special case where there is only one player (player 2 does not exist), we obtain an optimal control problem for a system with dynamics
-
-\begin{equation} \label{eq:dyn_d}
-\dot{x} = f(x, u), t\in [-T,0], u\in\mathcal U.
-\end{equation}
-
-The reachable set in this case would be given by the Hamilton-Jacobi-Bellman (HJB) PDE
-
-\begin{equation} \label{eq:HJBPDE}
-\begin{aligned}
-D_t V(t,x) + \min \{0, \min_{u\in\mathcal{U}} D_x V(t,x) \cdot f(x,u)\} &= 0 \\
-V(0,x) = l(x)&
-\end{aligned}
-\end{equation}
-
-\noindent where the optimal control is given by
-
-\begin{equation} \label{eq:HJB_ctrl_syn}
-u^*(t,x) = \arg \min_{u\in\mathcal{U}} D_x V(t,x) \cdot f(x,u)
-\end{equation}
-
-For our application, we will use a several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real time 4D reachable set computations and tractable 6D reachable set computations.
-
-\section{Liveness Controllers \label{sec:liveness}}
-\subsection{Merging onto a Highway \label{subsec:highway_merge}}
-We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity along the highway.
-Thus, a quadrotor would aim to drive the system \eqref{eq:dyn} to a state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}_H = \{x: |p_x-\bar{p}_x|\le r_{p_x}, |v_x-\bar{v}_x|\le r_{v_x}, \\
-|p_y - \bar{p}_y| \le r_{p_y}, |v_y - \bar{v}_y|\le r_{v_y} \}.
-\end{aligned}
-\end{equation}
-
-In this reachability problem, $\mathcal{L}_H$ is the target set, represented by the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE to be solved.
-The solution we obtain, $V_H(t,x)$, is the implicit surface function representing the reachable set $\mathcal V_H(t)$; $V_H(-T,x)\le 0$, then, specifies the reachable set $\mathcal{V}_H(T)$, the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.
-This gives the algorithm for merging onto the highway:
-
-\begin{enumerate}
-\item Move towards $\bar{x}_H$ in a straight line until $V_H(-T,x)\le 0$. This heuristic works well in practice. 
-\item Apply the optimal control extracted from $V_H(-T,x)$ according to \eqref{eq:HJB_ctrl_syn} until $\mathcal{L}_H$ is reached.
-\end{enumerate}
-
-\subsection{Merging into a Platoon \label{subsec:platoon_merge}}
-We again pose the merging of a quadrotor into a platoon on an air highway as a reachability problem.
-Here, we would like quadrotor $Q_i$ to merge onto the highway and follow another quadrotor $Q_j$ in a platoon.
-Thus, we would like to drive the system given by \eqref{eq:rel_dyn_aug} to a specific $\bar{x}_P = (\bar{p}_{x,r}, \bar{v}_{x,r}, \bar{p}_{y,r}, \bar{v}_{y,r})$, or a small range of relative states defined by the set
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}_P = \{x: |p_{x,r}-\bar{p}_{x,r}|\le r_{p_x}, |v_{x,r}-\bar{v}_{x,r}|\le r_{v_x}, \\
-|p_{y,r} - \bar{p}_{y,r}| \le r_{p_y}, |v_{y,r} - \bar{v}_{y,r}|\le r_{v_y} \}
-\end{aligned}
-\end{equation}
-
-The target set $\mathcal{L}_P$ is represented by the implicit surface function $l_P(x)$, which specifies the terminal condition of the HJI PDE \eqref{eq:HJIPDE}.
-The zero sublevel set of the solution to \eqref{eq:HJIPDE}, $V_P(-T,x)$, gives us the set of relative states from which $Q_i$ can reach the target and join the platoon following $Q_j$ within a duration of $T$.
-We assume that $Q_j$ moves along the highway at constant speed, so that $u_j(t)$ = 0.
-The following is a suitable algorithm for a quadrotor merging onto a highway and joining a platoon to follow $Q_j$:
-
-\begin{enumerate}
-\item Move towards $\bar{x}_P$ in a straight line until $V_P(-T,x)\le 0$.
-\item Apply the optimal control extracted from $V_P(-T,x)$ according to \eqref{eq:HJI_ctrl_syn} until $\mathcal{L}_P$ is reached.
-\end{enumerate}
-
-\subsection{Other Quadrotor Maneuvers}
-For the simpler maneuvers of traveling along a highway and following a platoon, we resort to simpler controllers described below.
-
-\subsubsection{Traveling along a highway} \label{sec:travel_hwy}
-We use a model-predictive controller (MPC) for traveling along a highway at a pre-specified speed.
-Here, a leader quadrotor tracks a constant-altitude path, defined as a curve $\bar{p}(s)$ parametrized by $s\in[0,1]$ in $p=(p_x, p_y)$ space (position space), while maintaining a velocity $\bar{v}(s)$ that corresponds to constant speed in the direction of the highway.
-
-\subsubsection{Following a Platoon} \label{sec:follow_platoon}
-Follower vehicles use a feedback control law tracking a nominal position and velocity in the platoon, with an additional feed-forward term given by the leader's acceleration input.
-
-The $i$-th member of the platoon, $Q_{P_i}$, is expected to track a relative position in the platoon $r^i = (r_x^i,r_y^i)$ with respect to the leader's position $p_{P_1}$, and the leader's velocity $v_{P_1}$ at all times.
-The resulting control law has the form:
-\begin{equation}\label{eq:follow}
-u^i(t) = k_p \big[p_{P_1}(t) + r^i(t) - p^i(t) \big] + k_v\big[v_{P_1}(t) - v^i(t)\big] + u_{P_1}(t)
-\end{equation}
-for some $k_p,k_v>0$. A simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
-\begin{equation}\label{eq:nominal_pos}
-r^i(t) = - (i-1) b \frac{v_{P_1}}{\|v_{P_1}\|_2}
-\end{equation}
-where $b$ is the spacing between vehicles along the platoon. and $\frac{v_{P_1}}{\|v_{P_1}\|_2}$ is the platoon leader's direction of travel.
-
-\section{Safety Controllers \label{sec:safety}}
-\subsection{Wrapping Reachability Around Existing Controllers}
-A quadrotor can use a liveness controller when it is not in any danger of collision with other quadrotors or obstacles.
-If the quadrotor could potentially be involved in a collision within the next short period of time, it must switch to a safety controller.
-In this section, we will demonstrate how HJ reachability can be used to both detect imminent danger and synthesize a controller that guarantees safety within a specified time horizon.
-For our safety analysis, we will use the model in Equation \eqref{eq:rel_dyn_aug}.
-
-We begin by defining the target set $\mathcal{L}_S$, which characterizes configurations in relative coordinates for which quadrotors $Q_i,Q_j$ are considered to be in collision:
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}_S = \{x: &|p_{x,r}|, |p_{y,r}|\le d \vee |v_{x,i}| \ge v_\text{max} \vee |v_{y,i}| \ge v_\text{max} \}
-\end{aligned}
-\end{equation}
-
-With this definition, $Q_i$ is considered to be unsafe if $Q_i$ and $Q_j$ are within a distance $d$ in both $x$- and $y$-directions simultaneously, or if $Q_i$ has exceeded some maximum speed $v_\text{max}$ in either $x$- or $y$-direction.
-For illustration purposes, we choose $d=2$ meters, and $v_\text{max}= 5$ m/s.
-
-We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJI PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition.
-As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the reachable set $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst case control.
-To avoid collisions, $Q_i$ must apply the safety controller according to \eqref{eq:HJI_ctrl_syn} on the boundary of the reachable set in order to avoid going into the reachable set.
-The following algorithm wraps our safety controller around liveness controllers:
-
-\begin{enumerate}
-\item For a specified time horizon $t$, evaluate$V_S(-t,x_i-x_j)$ for all $j\in \mathcal{Q}(i)$.
-
-$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against. We discuss $\mathcal{Q}(i)$ in Section \ref{subsec:safety_guarantees}.
-
-\item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:
-
-If $\exists j\in \mathcal{Q}(i),V_S(-t,x_i-x_j)\le 0$, then $Q_i,Q_j$ are in potential conflict, and $Q_i$ must use a safety controller; otherwise $Q_i$ uses a liveness controller.
-\end{enumerate}
-
-\subsection{Platoon Safety Guarantees \label{subsec:safety_guarantees}}
-Under normal operations in a single platoon, each follower quadrotor $Q_{P_i},i>1$ checks whether it is in the safety reachable set with respect to $Q_{P_{i-1}}$ and $Q_{P_{i+1}}$.
+% !TEX root = main.tex
+\subsection{Safety Analysis}
+Under normal operations in a single platoon, each follower quadrotor $Q_i,i=P_2,\ldots,P_{N-1}$ in a platoon checks whether it is in the safety reachable set with respect to $Q_{P_{i-1}}$ and $Q_{P_{i+1}}$.
 So $\mathcal{Q}(i) = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$.
@@
 So $\mathcal{Q}(P_1)=\{P_2\}, \mathcal{Q}(P_N)=\{P_{N-1}\}$.
-No pair of quadrotors should be in an unsafe configuration if the liveness controllers are well-designed.
-Occasionally, a quadrotor $Q_k$ may behave unexpectedly due to faults, which may lead to an unsafe configuration.
+When all quadrotors are using liveness controllers to perform their allowed maneuvers, no pair of quadrotors should be in an unsafe configuration if the liveness controllers are well-designed.
+However, occasionally a quadrotor $Q_k$ may behave unexpectedly due to faults or malfunctions, in which case it may come into an unsafe configuration with another quadrotor.
 

### 2016-01-20 docs/AIAA 2016/plat_sim.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/results.tex
@@
-% !TEX root = platooning.tex
-\section{Scenario Case Study \label{sec:scenarios}}
+% !TEX root = main.tex
+% 82 124 170 231
+\subsection{Numerical Simulations}
+
 In this section, we consider several situations that quadrotors in a platoon on an air highway may commonly encounter, and show via simulations the behaviors that emerge from the controllers we defined in Sections \ref{sec:liveness} and \ref{sec:safety}.
 
-\subsection{Forming a Platoon}
+\subsubsection{Forming a Platoon}
 We first consider the scenario in which some quadrotors are trying to merge onto an initially unoccupied highway.
@@
 
-For the simulation example, the highway is specified by the line $p_y = 0.5p_x$, the point of entry on the highway is chosen to be $(\bar{p}_x, \bar{p}_y) = (4,2)$, and the target velocity is such that the quadrotors travel at a speed $\bar{v}=3$ along the direction of the highway.
+For the simulation example, the highway is specified by the line $p_y = 0.5p_x$, the point of entry on the highway is chosen to be $(\bar{p}_x, \bar{p}_y) = (4,2)$, and the velocity on the highway is chosen to be ($\bar{v}_x, \bar{v}_y) = \frac{\bar{v}}{\sqrt{0.5^2 + 1^2}} (0.5, 1)$.
+The velocity simply states that the quadrotors must travel at a speed $\bar{v}=3$ along the direction of the highway.
 This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{subsec:highway_merge}.
@@
 Here, we choose $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $b$ behind the last quadrotor in the platoon, and $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$.
-This gives us the target set $\mathcal{L}_P$.
+This gives us the target set $\mathcal{L}_P$ that we need.
 
@@
 During the entire time, the $Q_1$ checks whether it may collide with $Q_2$ within a time horizon of $t_\text{external}$; we chose $t_\text{external}=3>t_\text{internal}$.
+However, since $Q_1$ never goes into the boundary of the safety reachable set (red dashed boundary), it uses the liveness controller the entire time.
 
@@
 $Q_2$ (blue disk), at $t=7$, begins joining the platoon behind $Q_1$, by moving towards the target $\bar{x}_P$ relative to the position of $Q_1$.
-When $Q_2$ moves inside the liveness reachable set boundary for joining the platoon (blue dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target whenever it is outside the safety reachable set (blue dashed boundary).
+Note that $\bar{x}_P$ moves with $Q_1$ as $\bar{x}_P$ is defined in terms of the relative states of the two quadrotors.
+When $Q_2$ moves inside the liveness reachable set boundary for joining the platoon (blue dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target as long as it stays out of the safety reachable set (blue dashed boundary).
 
@@
 
-\begin{figure}
+% 40 60 110 210
+\begin{figure} \label{fig:fp}
     \centering
-	\includegraphics[width=0.35\textwidth]{"fig/normal2"}
-	\caption{Reachable sets used to merge onto a highway to form a platoon (top subplots) and to join a platoon on the highway (bottom subplots).}
-	\label{fig:normal2}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:fp_40}
+        \includegraphics[width=\textwidth]{fig/fp_40}
+        \caption{40}
+    \end{subfigure}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:fp_60}
+        \includegraphics[width=\textwidth]{fig/fp_60}
+        \caption{60}
+    \end{subfigure}
+
+    \begin{subfigure}{0.23\textwidth} \label{subfig:fp_110}
+        \includegraphics[width=\textwidth]{fig/fp_110}
+        \caption{110}
+    \end{subfigure}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:fp_210}
+        \includegraphics[width=\textwidth]{fig/fp_210}
+        \caption{210}
+    \end{subfigure}   
+    \caption{form platoons}    
 \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.35\textwidth]{"fig/normal5"}
-	\caption{Five quadrotors merging onto a highway.}
-	\label{fig:normal5}
-\end{figure}
-
-\subsection{Malfunctioning Vehicle in Platoon}
-We now consider a scenario where a quadrotor in a platoon of five malfunctions while the platoon is traveling along a highway.
-To best demonstrate the behavior of the other quadrotors in the platoon, this simulation assumes that $Q_{P_3}$, the middle quadrotor, malfunctions and reverses direction.
-When this happens, all of the other quadrotors in the platoon begin checking safety against it.
-In addition, $Q_{P_3}$ is removed from the platoon, causing the other quadrotors to treat it as an intruder.
-Trailing quadrotors must leave the highway to avoid colliding with the faulty quadrotor.
-
-Figure \ref{fig:faulty2} shows the platoon of quadrotors, $Q_i,i = 1,...,5$ with $P_i = i$, traveling along the highway.
-At $t=0, Q_3$ malfunctions and begins to track the highway in reverse.
-Once $Q_3$ malfunctions, it is removed from the platoon and treated as an intruder.
-The platoon is then restructured with the faulty quadrotor removed ($Q_{P_i} = Q_{i+1}$ for $i=3,4$).
-After avoiding $Q_3$, the trailing quadrotors $Q_4$ and $Q_5$ accelerate to reach their new platoon positions.
-$Q_1$ and $Q_2$ are unaffected by the malfunctioning quadrotor.
-
-Figure \ref{fig:faulty2} also shows the safe reachable set of $Q_4$ with respect to $Q_3$ (green dashed line), and the safe reachable set of $Q_5$ with respect to $Q_4$ and $Q_3$ (purple dashed lines).
-
-At $t=1,Q_4$ applies the safe controller to avoid entering the safe reachable set with respect to $Q_3$.
-During $Q_4$'s avoidance maneuver, $Q_5$ simply follows $Q_4$, and does not come across any safety breaches, as shown by the $t=1$ and $t=2.1$ subplots.
-The safety breach ends soon after, and by $t=4.5$, $Q_4$ begins merging back onto the highway, followed by $Q_5$, in order to continue to follow the platoon.
-In this particular case, the safety breach is resolved even without any altitude change.
-
-%\begin{figure}
-%	\center
-%		\includegraphics[width=0.45\textwidth]{fig/faultyNoRsets}
-%		\caption{A quadrotor in the platoon becomes faulty. The rest of the platoon safely avoids the quadrotor and continues normal operation as a platoon once the faulty quadrotor has been cleared.}
-%		\label{fig:faulty1}
-%\end{figure}
-
-\begin{figure}
-	\center
-		\includegraphics[width=0.4\textwidth]{fig/faultyRsets}
-		\caption{Reachable sets used by trailing quadrotors to avoid colliding with the faulty quadrotor.}
-		\label{fig:faulty2}
-\end{figure}
-
-\subsection{Intruder Vehicle}
+\subsubsection{Intruder Vehicle}
 We now consider the scenario in which a platoon of quadrotors encounters an intruder vehicle.
 To avoid collision, each quadrotor checks for safety with respect to the intruder and any quadrotor in front and behind in the platoon.
-If necessary, each quadrotor switches to using the safety controller.
+If necessary, the quadrotor uses the safety controller, otherwise it uses the appropriate liveness controller, depending on whether it is a leader or follower.
 
 Figure \ref{fig:intruder1} shows the simulation result.
-At $t=0$, a platoon of 4 quadrotors, $Q_{P_i},i=1,\ldots,4$ with $P_i = i$, travel along the highway.
-An intruder vehicle $Q_0$ (red disk) starts from position $(40,30)$ and heads toward bottom-left of the grid.
+At $t=0$, a platoon of 4 quadrotors, $Q_{P_i},i=1,\ldots,4$ with $P_i = i$, travels along the highway defined by the line $p_y = p_x$.
+An intruder vehicle $Q_0$ (red disk) starts from position $(p_x, p_y) = (40,30)$ and heads toward bottom-left of the grid.
+As before, platoon members incur a safety breach if $V(-t_\text{internal},x_{P_i}-x_{P_j})\le 0$.
+However, with respect to $Q_0$, platoon members incur a safety breach if $V(-t_\text{external}, x_{P_i}-x_0) \le 0$ with $t_\text{external}>t_\text{internal}$.
 
-The platoon leader $Q_{P_1}$'s (black disk) safety is unaffected by the intruder.
+The platoon leader $Q_{P_1}$'s (black disk) safety is unaffected by the intruder, thus it simply follows its original path on the highway using the liveness controller described in Section \ref{sec:travel_hwy}.
 Followers $Q_{P_2}$ (blue disk), $Q_{P_3}$ (green disk) and $Q_{P_4}$ (pink disk), on the other hand, must use the safety controller in order to avoid collision with the intruder ($t=3.3,6.2$).
 This causes their paths to deviate off the highway.
-Once each quadrotor is safe relative to the intruder, they rejoin the original platoon ($t=12.4$).
+Once each quadrotor is safe relative to the intruder, they merge back onto the highway, join the original platoon and continue traveling along it ($t=12.4$).
+
 Figure \ref{fig:intruder2} illustrates the use of safety reachable sets in this scenario using only $Q_{P_2}$ as an example.
-The safety reachable sets of $Q_{P_2}$ with respect to the intruder $Q_0$, $Q_{P_1}$ and $Q_{P_3}$ (red, black, green dashed lines) are shown.
-%With respect to $Q_0$, $Q_{P_2}$'s safety is considered to be breached if $V_S(-t_\text{external},x_{P_2}-x_0) \le 0$.
+The safety reachable sets of $Q_{P_2}$ with respect to the intruder $Q_0$ (red dashed line), $Q_{P_1}$ (black dashed line) and $Q_{P_3}$ (green dashed line) are shown.
+With respect to $Q_0$, $Q_{P_2}$'s safety is considered to be breached if $V_S(-t_\text{external},x_{P_2}-x_0) \le 0$.
 To avoid possible collision with the intruder, $Q_{P_2}$ must remain outside the safety reachable set with respect to the intruder.
@@
 Initially, $Q_{P_2}$ ($P_2=2$) is a follower and is outside all 3 safety reachable sets.
+Hence it is allowed to use the liveness controller to follow the platoon as described in Section \ref{sec:follow_platoon}.
 At time $t=0.6$, $Q_2$ comes to the boundary of the safety set with respect to the intruder and therefore must apply the safety control law to avoid potential future collision.
 Thus it splits the original platoon and becomes the leader of a new platoon consisting of itself, $Q_3$ and $Q_4$.
-$Q_2$ keeps using the safety controller until it is safe with respect to the intruder again at $t=3$.
+$Q_2$ keeps using the safety controller until it is safe with respect to the intruder again at $t=3$, since if it tried to merge back to the highway before this time, it would enter the safety set with respect to the intruder and lose the $t_\text{external}$ safety guarantee.
 After $t=3$, $Q_2$ is safe to use the liveness controller again to merge back onto the highway and join the original platoon as a follower.
@@
 
-\begin{figure}
+% 100 120 140 200
+\begin{figure} \label{fig:in}
     \centering
-	\includegraphics[width=0.35\textwidth]{"fig/Intruder1"}
-	\caption{Reaction of a platoon of 4 quadrotors on a highway to an intruder.}
-	\label{fig:intruder1}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:in_100}
+        \includegraphics[width=\textwidth]{fig/in_100}
+        \caption{100}
+    \end{subfigure}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:in_120}
+        \includegraphics[width=\textwidth]{fig/in_120}
+        \caption{120}
+    \end{subfigure}
+
+    \begin{subfigure}{0.23\textwidth} \label{subfig:in_140}
+        \includegraphics[width=\textwidth]{fig/in_140}
+        \caption{140}
+    \end{subfigure}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:in_200}
+        \includegraphics[width=\textwidth]{fig/in_200}
+        \caption{200}
+    \end{subfigure}   
+    \caption{intruder}    
 \end{figure}
 
-\begin{figure}
+\subsubsection{Changing highways}
+
+\begin{figure} \label{fig:ch}
     \centering
-		\includegraphics[width=0.35\textwidth]{"fig/intruder2"}
-	\caption{Reachable sets used by quadrotor $Q_2$ to avoid collision with respect to the intruder and quadrotors $Q_1$ and $Q_3$ in front and behind it respectively.}
-	\label{fig:intruder2}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:ch_83}
+        \includegraphics[width=\textwidth]{fig/ch_83}
+        \caption{83}
+    \end{subfigure}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:ch_124}
+        \includegraphics[width=\textwidth]{fig/ch_124}
+        \caption{124}
+    \end{subfigure}
+
+    \begin{subfigure}{0.23\textwidth} \label{subfig:ch_170}
+        \includegraphics[width=\textwidth]{fig/ch_170}
+        \caption{170}
+    \end{subfigure}
+    \begin{subfigure}{0.23\textwidth} \label{subfig:ch_231}
+        \includegraphics[width=\textwidth]{fig/ch_231}
+        \caption{231}
+    \end{subfigure}   
+    \caption{change highways}    
 \end{figure}

### 2016-01-20 docs/AIAA 2016/fig/RSExample.m

@@ -1,0 +1,72 @@
+function RSExample()
+
+onlyTarget = 0;
+
+g.dim = 2;
+g.N = 101;
+g.min = [-10; -10];
+g.max = [10; 10];
+g.bdry = @addGhostExtrapolate;
+g = processGrid(g);
+
+x = g.xs{1};
+y = g.xs{2};
+R = 4;
+
+figure
+%%
+T = sqrt(x.^2 + y.^2) - R;
+surf(x,y,T, 'facecolor', 'r', 'facealpha', 0.3, 'edgecolor', 'none')
+hold on
+t = linspace(0, 2*pi, 101);
+plot(R*cos(t), R*sin(t), 'r-', 'linewidth', 4)
+
+%%
+surf(x, y, zeros(size(x)), 'facecolor', [0 0.25 0], ...
+  'facealpha', 0.3, 'edgecolor', 'none')
+
+if onlyTarget
+  xlabel('x')
+  ylabel('y')
+  legend('l(x)','Target set', 'Zero plane')
+  return
+end
+
+%%
+s = 5; % shift
+% Shifted circle
+C = sqrt((x-s).^2 + y.^2) - R;
+
+% Rectangle
+ledge = -x;
+redge = x-s;
+tedge = y-R;
+bedge = -y-R;
+rect = max(ledge, redge);
+rect = max(rect, tedge);
+rect = max(rect, bedge);
+
+% Union
+U = min(C, rect);
+U = min(U, T);
+U = signedDistanceIterative(g, U)/1.1;
+surf(x,y,U, 'facecolor', 'b', 'facealpha', 0.3, 'edgecolor', 'none')
+hold on
+
+HedgeX = linspace(0, s, 50);
+TedgeY = R*ones(size(HedgeX));
+plot(HedgeX, TedgeY, 'b-', 'linewidth', 4)
+BedgeY = -R*ones(size(HedgeX));
+plot(HedgeX, BedgeY, 'b-', 'linewidth', 4)
+
+t = linspace(pi/2, 3*pi/2, 50);
+plot(R*cos(t), R*sin(t),  'b-', 'linewidth', 4)
+t = linspace(-pi/2, pi/2, 50);
+plot(s+R*cos(t), R*sin(t),  'b-', 'linewidth', 4)
+
+
+xlabel('x')
+ylabel('y')
+legend('l(x)','Target set', 'Zero plane', 'V(t,x)', 'Reachable set')
+
+end

### 2016-01-29 docs/AIAA 2016/plat_form.tex
no message

@@
 
-\noindent where $x\in\mathbb{R}^n$ represents the state, and $u\in\mathbb{R}^{n_u}$ represents the control action.
-In this paper, we will assume that each vehicle has the following simple model of a quadrotor:
+\noindent where $x$ represents the state, and $u$ represents the control action. In this paper, we will assume that each vehicle has the following simple model of a quadrotor:
 
@@
 \noindent where the state $x=(\pos_x, \vel_x, \pos_y, \vel_y)\in\mathbb{R}^4$ represents the quadrotor's position in the $x$-direction, its velocity in the $x$-direction, and its position and velocity in the $y$-direction, respectively.
+The control input $u = (u_x, u_y)\in\mathbb{R}^2$ consists of the acceleration in the $x$- and $y$- directions.
 For convenience, we will denote the position and velocity $\pos=(\pos_x, \pos_y),\vel=(\vel_x,\vel_y)$, respectively.
@@
 In general, the problem of collision avoidance among $N$ vehicles cannot be tractably solved using traditional dynamic programming approaches because the computation complexity of these approaches scales exponentially with the number of vehicles.
-Thus, in our present work, we will consider the situation where UAVs travel on air highways in platoons, defined in the following secions.
+Thus, in our present work, we will consider the situation where UAVs travel on air highways in platoons, defined in the following sections.
 The structure imposed by air highways and the platoon enables us to analyze the liveness and safety of the vehicles in a tractable manner.
 
-\subsubsection{Vehicles in a Platoon\label{subsec:platoon_def}}
-We consider a platoon of quadrotors to be a group of $M$ quadrotors $Q_{P_1}, \ldots, Q_{P_M}$ in a single-file formation.
-Not all of the $N$ quadrotors need to be in a platoon: $\{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$.
-$Q_{P_1}$ is the leader of the platoon, and $Q_{P_2},\ldots,Q_{P_M}$ are the followers.
-We will assume that the quadrotors in a platoon travel along an air highway, which is defined by as a path inside a pre-defined altitude range.
-The quadrotors maintain a separation distance of $b$.
-In order to allow for close proximity of the quadrotors and the ability to resolve multiple simultaneous safety breaches, we assume that in the event of a malfunction, a quadrotor will be able to exit the altitude range of the highway within a duration of $t_\text{internal}=1.5$.
-Such a requirement may be implemented practically as an emergency landing procedure to which the quadrotors revert when a malfunction is detected.
+\subsubsection{Vehicles as Hybrid Systems}
+We model each vehicle as a hybrid system \cite{Lygeros98,Lygeros12} consisting of the modes "Free", "Leader", "Follower", and "Faulty".
+Within each mode, a set of maneuvers is available to allow the vehicle to change modes if desired.
+The modes and maneuvers are as follows:
 
-As part of a platoon, each quadrotor must be capable of performing a number of essential cooperative maneuvers. In this paper, we consider the following: 
 \begin{itemize}
-\item safely merging onto an air highway;
-\item safely joining a platoon;
-\item reacting to a malfunctioning vehicle in the platoon;
-\item reacting to an intruder vehicle;
-\item following the highway, a curve defined in space at constant altitude, at a specified speed;
-\item maintaining a constant relative position and velocity with the leader of a platoon.
+\item Free:
+
+A Free vehicle is not in a platoon or on a highway, and its possible maneuvers or mode transitions are
+\begin{itemize}
+\item remain a Free vehicle by staying away from highways,
+\item become a Leader by entering a highway to create a new platoon, and
+\item become a Follower by joining a platoon that is currently on a highway.
 \end{itemize}
 
-\subsubsection{Vehicles as Hybrid Systems}
-A UAV in general may be in a number of modes of operations, depending on whether it is part of a platoon, and in the affirmative case, whether it is a leader or a follower.
-Therefore, it is natural to model quadrotors as hybrid systems \cite{Lygeros98,Lygeros12}.
-In this paper, we restrict the available maneuvers of each quadrotor depending on the mode.
-We assume that each quadrotor in the airspace has the following modes:
+\item Leader: 
+A Leader vehicle is the vehicle at the front of a platoon (which could consist of only the vehicle itself). The available maneuvers and mode transitions are
 
 \begin{itemize}
-\item Free: Vehicle not in a platoon. Available maneuvers: merge onto a highway, join a platoon on a highway.
-\item Leader: Leader of platoon (could be by itself). Available maneuvers: travel along the highway at a pre-specified speed, merge current platoon with a platoon in front, leave the highway.
-\item Follower: Vehicle following the platoon leader. Available maneuvers: follow a platoon, create a new platoon.
-\item Faulty: Malfunctioned vehicle in a platoon: reverts to default behavior and descends after a duration of $t_\text{internal}$.
+\item remain a Leader by traveling along the highway at a pre-specified speed,
+\item become a Follower by merging the current platoon with a platoon in front, and
+\item become a Free vehicle by leaving the highway.
 \end{itemize}
 
-The available maneuvers and associated mode transitions are shown in Figure \ref{fig:vehicleModes}.
+\item Follower:
+
+A Follower vehicle is a vehicle that is following a platoon leader. The Available maneuvers and mode transitions are
+
+\begin{itemize}
+\item remain a Follower by staying a distance of $b$ behind the vehicle in front in the current platoon,
+\item become a Leader by splitting from the current platoon, and
+\item become a Free vehicle by leaving the highway.
+\end{itemize}
+
+\item Faulty:
+
+If a vehicle from any of the other modes malfunction, it transitions into the Faulty mode and descends after a duration of $t_\text{internal}$.
+\end{itemize}
+
+The available maneuvers and associated mode transitions are summarized in Figure \ref{fig:vehicleModes}.
 
@@
 
+Suppose that there are $N$ vehicles in total.
+We consider a platoon of vehicles to be a group of $M\le N$ vehicles, denoted $Q_{P_1}, \ldots, Q_{P_M}, \{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$, in a single-file formation.
+We will assume that the vehicles in a platoon travel along an air highway.
+The vehicles maintain a separation distance of $b$ with its neighbors inside the platoon.
+In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that in the event of a malfunction, a vehicle will be able to exit the altitude range of the highway within a duration of $t_\text{internal}=1.5$.
+Such a requirement may be implemented practically as an emergency landing procedure to which the vehicles revert when a malfunction is detected.
+
 \subsubsection{Objectives}
-Using the previously-mentioned modeling assumptions, we would like to address the following questions:
+Given the above modeling assumptions, our goal is to provide control strategies to guarantee the success and safety of all the mode transitions.
+The theoretical tool used to provide the liveness and safety guarantees is reachability.
+The reachable sets we compute will allow each vehicle to perform actions such as
+
+OK SHOULD EVASION BE A MODE?
+
+\begin{itemize}
+
+\item reacting to a malfunctioning vehicle in the platoon,
+\item reacting to an intruder vehicle,
+\item following the highway, a curve defined in space at constant altitude, at a specified speed, and
+\item maintaining a constant relative position and velocity with the leader of a platoon.
+\end{itemize}
 

### 2016-01-29 code/platoon/@Node/printInfo.m

@@ -65,7 +65,8 @@ elseif isa(obj, 'Vehicle')
     disp(['  BQ ID = ' num2str(obj.BQ.ID)])
   else
     disp('  Not in a platoon')
-    endelse
+  end
+else
     error('Unknown node type!')
   end
   disp('========================')

### 2016-01-29 code/platoon/@Plane/RSControl.m

@@ -1,0 +1,14 @@
+function u = RSControl(obj, RS)
+% u = RSControl(obj, reach, g, tau)
+
+u = [];
+for i = 1:length(RS.tau)
+  if eval_u(RS.g, RS.data(:,:,:,i), obj.x) <= 0
+    P = extractCostates(RS.g, RS.data(:,:,:,i));
+    p = calculateCostate(RS.g, P, obj.x);
+    u = (p(3) >= 0) * obj.wMin + (p(3) < 0) * obj.wMax;
+    return
+  end
+end
+
+end

### 2016-01-29 code/platoon/@Plane/getVelocity.m

@@ -2,10 +2,6 @@ function vel = getVelocity(obj)
 % vel = getPosition(obj)
 % Finds the velocity (v_x,v_y) of a plane
 
-if obj.nx == 3
-  vel = obj.speed * [cos(obj.x(3)); sin(obj.x(3))];
-else
-  vel = obj.x(4) * [cos(obj.x(3)); sin(obj.x(3))];
-end
+vel = obj.speed * [cos(obj.x(3)); sin(obj.x(3))];
 
 end

### 2016-02-03 docs/AIAA 2016/main.tex
no message

@@
 \newcommand{\pos}{p} % position
+\newcommand{\Pos}{\bar{p}} % a particular position (or desired position}
 \newcommand{\vel}{v} % velocity
+\newcommand{\Vel}{\bar{v}} % a particular position (or desired position}
 \newcommand{\hw}{\mathbb{H}} % a single highway
@@
 
-\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, firefighting, and fast disaster response.
+\abstract{(TO BE UPDATED!)
+
+Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, firefighting, and fast disaster response.
 As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met.

### 2016-02-03 docs/AIAA 2016/plat_form.tex
no message

@@
 
-\noindent where $x$ represents the state, and $u$ represents the control action. In this paper, we will assume that each vehicle has the following simple model of a quadrotor:
+\noindent where $x$ represents the state, and $u$ represents the control action.
+The techniques we present in this paper do not depend on the dynamics of the vehicles.
+However, for concreteness, we consider assume that the UAVs are quadrotors that fly at a constant altitude under non-faulty circumstances.
+For the quadrotor, we use a simple model in which the $x$ and $y$ dynamics are double integrators:
 
@@
 The theoretical tool used to provide the liveness and safety guarantees is reachability.
-The reachable sets we compute will allow each vehicle to perform actions such as
+The reachable sets we compute will allow each vehicle to perform complex actions such as
 
-OK SHOULD EVASION BE A MODE?
+SHOULD EVASION BE A MODE?
 
 \begin{itemize}
+\item merge onto a highway to form a platoon,
+\item join a new or different platoon,
+\item leave a platoon to create a new one,
+\item reacting to a malfunctioning or intruder vehicles.
+\end{itemize}
 
-\item reacting to a malfunctioning vehicle in the platoon,
-\item reacting to an intruder vehicle,
-\item following the highway, a curve defined in space at constant altitude, at a specified speed, and
+We also propose more basic controllers to perform other simpler actions such as
+\begin{itemize}
+\item following the highway at constant altitude at a specified speed,
 \item maintaining a constant relative position and velocity with the leader of a platoon.
@@
 
-\begin{enumerate}
-\item How do vehicles form platoons?
-\item How can the safety of the vehicles be ensured during normal operation and when there is a malfunctioning vehicle within the platoon?
-\item How can the platoon respond to intruders such as unresponsive UAVs, birds, or other aerial objects?
-\end{enumerate}
-
-The answers to these questions can be broken down into the maneuvers listed in Section \ref{subsec:platoon_def}.
 In general, the control strategies of each vehicle have a liveness component, which specifies a set of states towards which the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.
 Together, the liveness and safety controllers guarantee the success and safety of a vehicle in the airspace making any desired mode transition.
-In this paper, these guarantees are provided using reachability analysis.
+In this paper, these guarantees are provided using reachability analysis, and allow the multi-UAV system to perform joint maneuvers essential to maintaining structure in the airspace.

### 2016-02-03 docs/AIAA 2016/plat_intra.tex
no message

@@
 % !TEX root = main.tex
-\subsection{Intra-Platoon Controllers}
-\subsubsection{Merging onto a Highway \label{subsec:highway_merge}}
-We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity whose magnitude (the speed) is given by the highway specification, and whose direction is along the highway.
-Thus, for a quadrotor, the objective would be to drive the system in \eqref{eq:dyn} to a specific state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
+\subsection{Reachability-Based Controllers}
+Reachability analysis is useful for constructing controllers in a large variety of situations.
+In order to construct different controllers, an appropriate target set needs to be defined depending on the goal of the controller.
+If one defines the target set to be a set of desired states, the reachable set, once computed, would represent the states from which a system needs to first arrive at in order to reach the desired states.
+On the other hand, if the target set represents a set of undesirable states, then the reachable set would indicate the region of the state space that the system needs to avoid.
+In addition, the system dynamics with which the reachable set is computed provides additional flexibility when using reachability to construct controllers.
+
+Using a number of different target sets and dynamics, we now propose different reachability-based controllers used for vehicle mode transitions in our platooning concept.
+
+\subsubsection{Getting to a Target State}
+The controller used by a vehicle to a target state is important in a couple of situations in the platooning context.
+First, a vehicle in the ``Free'' mode can use the controller to merge onto a highway, forming a platoon and changing modes to a ``Leader'' vehicle.
+Second, a vehicle in either the ``Leader'' mode or the ``Follower'' mode can use this controller to change to a different highway, changing modes to a ``Leader'' vehicle.
+
+In both of the above cases, we use the dynamics of a single vehicle specified in \ref{eq:dyn}.
+The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)$ that corresponds to the speed and direction of travel specified by the highway.
+For the reachability computation, we define the target set to be a small range of states around the target state $x_H = (\Pos_x, \Pos_y, \Vel_x, \Vel_y)$:
 
@@
 \begin{aligned}
-\mathcal{L}_H = \{x: |p_x-\bar{p}_x|\le r_{p_x}, |v_x-\bar{v}_x|\le r_{v_x}, \\
-|p_y - \bar{p}_y| \le r_{p_y}, |v_y - \bar{v}_y|\le r_{v_y} \}.
+\mathcal{L}_H = \{x: |\pos_x-\Pos_x|\le r_{\pos_x}, |v_x-\Vel_x|\le r_{\vel_x}, \\
+|\pos_y - \Pos_y| \le r_{\pos_y}, |v_y - \Vel_y|\le r_{v\vel_y} \}.
 \end{aligned}
@@
 
-In this reachability problem, $\mathcal{L}_H$ is the target set, represented by the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE that we need to solve.
-The solution we obtain, $V_H(t,x)$, is the implicit surface function representing the reachable set $\mathcal V_H(t)$; $V_H(-T,x)\le 0$, then, specifies the reachable set $\mathcal{V}_H(T)$, the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.
-This gives the algorithm for merging onto the highway:
+Here, we represent the target set $\mathcal{L}_H$ as the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE that we need to solve.
+Once the HJB PDE is solved, we obtain the reachable set from the subzero level set of the solution $V_H(t,x)$: $\mathcal V_H(t)$.
+More concretely, $\mathcal{V}_H(T) = \{x: V_H(-T,x)\le 0\}$ is the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.
+
+Depending on the time horizon $T$, the size of the reachable set $\mathcal V_H(T)$ varies.
+In general, a vehicle may not initially be inside the reachable set $\mathcal V_H(T)$, yet it needs to be in order to get to its desired target state.
+Determining a control strategy to reach $\mathcal V_H(T)$ is itself a reachability problem (with $\mathcal V_H(T)$ as the target set), and it would seem like this reachability problem needs to be solved in order for us to use the results from our first reachability problem.
+However, practically, one could choose $T$ to be large enough to cover a sufficiently large area to include any practically conceivable initial state.
+From our simulations, a suitable algorithm for getting to a desired target state is as follows:
 
 \begin{enumerate}
-\item Move towards $\bar{x}_H$ in a straight line, with some velocity, until $V_H(-T,x)\le 0$.
+\item Move towards $\bar{x}_H$ in a straight line, with some velocity, until $V_H(-T,x)\le 0$. In practice, this step consistently drives the system into the reachable set.
 \item Apply the optimal control extracted from $V_H(-T,x)$ according to \eqref{eq:HJB_ctrl_syn} until $\mathcal{L}_H$ is reached.
@@
 
-\subsubsection{Merging into a Platoon \label{subsec:platoon_merge}}
-We again pose the merging of a quadrotor into a platoon on an air highway as a reachability problem.
-Here, we would like quadrotor $Q_i$ to merge onto the highway and follow another quadrotor $Q_j$ in a platoon.
-Thus, we would like to drive the system given by \eqref{eq:rel_dyn_aug} to a specific $\bar{x}_P = (\bar{p}_{x,r}, \bar{v}_{x,r}, \bar{p}_{y,r}, \bar{v}_{y,r})$, or a small range of relative states defined by the set
+\subsubsection{Getting to a State Relative to Another Vehicle}
+In the platooning context, being able to go to a state relative to another moving vehicle is important for the purpose of forming and joining platoons.
+For example, a ``Free'' vehicle may join an existing platoon that is on a highway and change modes to become a ``Follower''.
+Also, a ``Leader'' or ``Follower'' may join another platoon and afterwards go into the ``Follower'' mode.
+
+To construct a controller for getting to a state relative to another vehicle, we use the relative dynamics of two vehicles, given in \ref{eq:rel_dyn}.
+In general, the target state is specified to be some position $(\Pos_{x,r}, \Pos_{y,r}$ and velocity $(\Vel_{x,r}, \Vel_{y,r})$ relative to a reference vehicle.
+In the case of a vehicle joining a platoon that maintains a single file, the reference vehicle would be the platoon leader, the desired relative position would be a certain distance behind the leader, depending on how many other vehicles are already in the platoon, and the desired relative velocity would be $(0,0)$ so that the formation can be kept.
+
+For the reachability problem, we define the target set to be a small range of states around the target state $x_P = (\Pos_{x,r}, \Pos_{y,r}, \Vel_{x,r}, \Vel_{y,r}$:
 
@@
 \begin{aligned}
-\mathcal{L}_P = \{x: |p_{x,r}-\bar{p}_{x,r}|\le r_{p_x}, |v_{x,r}-\bar{v}_{x,r}|\le r_{v_x}, \\
-|p_{y,r} - \bar{p}_{y,r}| \le r_{p_y}, |v_{y,r} - \bar{v}_{y,r}|\le r_{v_y} \}
+\mathcal{L}_P = \{x: |\pos_{x,r}-\Pos_{x,r}|\le r_{\pos_x}, |\vel_{x,r}-\Vel_{x,r}|\le r_{\vel_x}, \\
+|\pos_{y,r} - \Pos_{y,r}| \le r_{\pos_y}, |\vel_{y,r} - \Vel_{y,r}|\le r_{\vel_y} \}
 \end{aligned}
@@
 
-The target set $\mathcal{L}_P$ is represented by the implicit surface function $l_P(x)$, which specifies the terminal condition of the HJI PDE \eqref{eq:HJIPDE}.
-The zero sublevel set of the solution to \eqref{eq:HJIPDE}, $V_P(-T,x)$, gives us the set of relative states from which $Q_i$ can reach the target and join the platoon following $Q_j$ within a duration of $T$.
-We assume that $Q_j$ moves along the highway at constant speed, so that $u_j(t)$ = 0.
-The following is a suitable algorithm for a quadrotor merging onto a highway and joining a platoon to follow $Q_j$:
+The target set $\mathcal{L}_P$ is represented by the zero sublevel set of the implicit surface function $l_P(x)$, which specifies the terminal condition of the HJI PDE \eqref{eq:HJIPDE}.
+The zero sublevel set of the solution to \eqref{eq:HJIPDE}, $V_P(-T,x)$, gives us the set of relative states from which a quadrotor can reach the target in the relative coordinates within a duration of $T$.
+In the reachable set computation, we assume that the reference vehicle moves along the highway at constant speed, so that $u_j(t)$ = 0.
+The following is a suitable algorithm for a vehicle joining a platoon to follow the platoon leader:
 
@@
 \end{enumerate}
+
+\subsubsection{Avoiding Collision}
+A vehicle can use a liveness controller described in the previous sections when it is not in any danger of collision with other vehicles.
+If the vehicle could potentially be involved in a collision within the next short period of time, it must switch to a safety controller.
+The safety controller is available in every mode, and executing the safety controller to perform an avoidance maneuver does not change a vehicle's mode.
+
+In the context of our platooning concept, we define an unsafe configuration as follows: a vehicle is either within a minimum separation distance $d$ to a reference vehicle in both the $x$ and $y$ directions, or is traveling with a speed above the speed limit $\vel_\text{max}$ in either of the $x$ and $y$ directions.
+To take this specification into account, we use the augmented relative dynamics given by \eqref{eq:rel_dyn_aug} for the reachability problem, and define the target set as follows:
+
+\begin{equation}
+\begin{aligned}
+\mathcal{L}_S = \{x: &|\pos_{x,r}|, |\pos_{y,r}|\le d \vee |\vel_{x,i}| \ge \vel_\text{max} \vee |\vel_{y,i}| \ge \vel_\text{max} \}
+\end{aligned}
+\end{equation}
+
+We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJI PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition.
+As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the reachable set $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst case control.
+To avoid collisions, $Q_i$ must apply the safety controller according to \eqref{eq:HJI_ctrl_syn} on the boundary of the reachable set in order to avoid going into the reachable set.
+The following algorithm wraps our safety controller around liveness controllers:
+
+\begin{enumerate}
+\item For a specified time horizon $t$, evaluate$V_S(-t,x_i-x_j)$ for all $j\in \mathcal{Q}(i)$.
+
+$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against. We discuss $\mathcal{Q}(i)$ in Section \ref{subsec:safety_guarantees}.
+
+\item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:
+
+If $\exists j\in \mathcal{Q}(i),V_S(-t,x_i-x_j)\le 0$, then $Q_i,Q_j$ are in potential conflict, and $Q_i$ must use a safety controller; otherwise $Q_i$ uses a liveness controller.
+\end{enumerate}
+
+THE FOLLOWING SHOULD BE IN ANOTHER SECTION
 
@@
 where $b$ is the spacing between vehicles along the platoon. and $\frac{v_{P_1}}{\|v_{P_1}\|_2}$ is the platoon leader's direction of travel.
-
-\subsection{Safety Controllers \label{sec:safety}}
-\subsubsection{Wrapping Reachability Around Existing Controllers}
-A quadrotor can use a liveness controller when it is not in any danger of collision with other quadrotors or obstacles.
-If the quadrotor could potentially be involved in a collision within the next short period of time, it must switch to a safety controller.
-In this section, we will demonstrate how HJ reachability can be used to both detect imminent danger and synthesize a controller that guarantees safety within a specified time horizon.
-For our safety analysis, we will use the model in Equation \eqref{eq:rel_dyn_aug}.
-
-We begin by defining the target set $\mathcal{L}_S$, which characterizes configurations in relative coordinates for which quadrotors $Q_i,Q_j$ are considered to be in collision:
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}_S = \{x: &|p_{x,r}|, |p_{y,r}|\le d \vee |v_{x,i}| \ge v_\text{max} \vee |v_{y,i}| \ge v_\text{max} \}
-\end{aligned}
-\end{equation}
-
-With this definition, $Q_i$ is considered to be unsafe if $Q_i$ and $Q_j$ are within a distance $d$ in both $x$- and $y$-directions simultaneously, or if $Q_i$ has exceeded some maximum speed $v_\text{max}$ in either $x$- or $y$-direction.
-For illustration purposes, we choose $d=2$ meters, and $v_\text{max}= 5$ m/s.
-
-We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJI PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition.
-As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the reachable set $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst case control.
-To avoid collisions, $Q_i$ must apply the safety controller according to \eqref{eq:HJI_ctrl_syn} on the boundary of the reachable set in order to avoid going into the reachable set.
-The following algorithm wraps our safety controller around liveness controllers:
-
-\begin{enumerate}
-\item For a specified time horizon $t$, evaluate$V_S(-t,x_i-x_j)$ for all $j\in \mathcal{Q}(i)$.
-
-$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against. We discuss $\mathcal{Q}(i)$ in Section \ref{subsec:safety_guarantees}.
-
-\item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:
-
-If $\exists j\in \mathcal{Q}(i),V_S(-t,x_i-x_j)\le 0$, then $Q_i,Q_j$ are in potential conflict, and $Q_i$ must use a safety controller; otherwise $Q_i$ uses a liveness controller.
-\end{enumerate}

### 2016-02-03 code/platoon/@Plane/RSControl.m

@@ -1,12 +1,12 @@
-function u = RSControl(obj, RS)
-% u = RSControl(obj, reach, g, tau)
+function u = RSControl(obj, BRS)
+% u = RSControl(obj, BRS)
 
 u = [];
-for i = 1:length(RS.tau)
-  if eval_u(RS.g, RS.data(:,:,:,i), obj.x) <= 0
-    P = extractCostates(RS.g, RS.data(:,:,:,i));
-    p = calculateCostate(RS.g, P, obj.x);
-    u = (p(3) >= 0) * obj.wMin + (p(3) < 0) * obj.wMax;
+for i = 1:length(BRS.tau)
+  if eval_u(BRS.g, BRS.data(:,:,:,i), obj.x) <= 0
+    P = extractCostates(BRS.g, BRS.data(:,:,:,i));
+    p = calculateCostate(BRS.g, P, obj.x);
+    u = (p(3) >= 0) * (-BRS.uMax) + (p(3) < 0) * BRS.uMax;
     return
   end
 end

### 2016-02-12 docs/AIAA 2016/introduction.tex
no message

@@
 Recently, however, there has been an immense surge of interest in using UAVs for civil applications.
-Through projects such as Amazon Prime Air and Google Project Wing, companies are looking to send UAVs into the airspace to deliver packages \cite{PrimeAir,ProjectWing}.
+Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commerical packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and .
 As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone.

### 2016-02-13 docs/AIAA 2016/high_sim.tex
no message
Updated AIAA 2016 paper

--- 2015-10-13 docs/AIAA 2015/high_sim.tex
@@
 \subsubsection{Cost-Minimizing Paths}
-Fig.
-\ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function.
+Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function.
 The region enclosed by the black boundary represent ``regoin around airports'', which have the highest cost.
@@
 	\centering
-	\includegraphics[width=0.75\textwidth]{"fig/airHighway_results"}
+	\includegraphics[width=0.5\textwidth]{"fig/airHighway_results"}
 	\caption{Cost-minimizing paths computed by the Fast Marching Method based on the assumed cost map of the San Francisco Bay Area}
@@
 	\centering
-	\includegraphics[width=0.75\textwidth]{"fig/airHighway_sparse"}
+	\includegraphics[width=0.5\textwidth]{"fig/airHighway_sparse"}
 	\caption{Results of conversion from cost-minimizing paths to highway way points.}

### 2016-02-13 docs/AIAA 2016/introduction.tex
Updated AIAA 2016 paper

--- 2016-01-20 docs/AIAA 2016/introduction.tex
@@
 Recently, however, there has been an immense surge of interest in using UAVs for civil applications.
-Through projects such as Amazon Prime Air and Google Project Wing, companies are looking to send UAVs into the airspace to deliver packages \cite{PrimeAir,ProjectWing}.
+Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commerical packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue.
+In the future, the applications of UAVs are only limited by human imagination.
+
 As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone.
-This would equate to thousands of vehicles simultaneously in the air.
-As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) of the United States are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13}.
+This would equate to thousands of vehicles simultaneously in the air just from package delivery services.
 Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to firefight in areas that are difficult to reach but require prompt response \cite{Debusk10}.
+As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13, NASA16}.
 
-Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving a small number of vehicles \cite{Fisac15,Chen14,Ding08}.
+Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving a small number of vehicles \cite{Fisac15,Chen14,Ding08}.
 These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
@@
 This makes the computation intractable for large numbers of vehicles.
+
+In order to accommodate potentially thousands of vehicles simultaneously flying in the air, additional structure is needed to allow for tractable analysis and intuitive monitoring.
+An air highway system on which platoons of vehicles travel accomplishes both goals.
+However, many details of such a concept need to be addressed.
+Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be daunting task.
+To address this, in the first part of this paper, we propose a flexible and computationally efficient way to perform optimal air highway replacement given an arbitrary cost map that can capture the desirability of having UAVs fly over any geographical location.
+We demonstrate our method using the San Francisco Bay Area as an example.
+Once air highways are in place, platoons of UAVs can then fly in fixed formations along the highway to get from origin to destination.
 
@@
 Previous analysis of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
-%In the context of HJ reachability, putting vehicles into platoons is desirable because of the additional structure that platoons impose on its members.
-With additional structure, pairwise safety guarantees of vehicles can be more easily translated into safety guarantees of all the vehicles in the platoon.
-In this paper, we attempt to reconciliate this trade-off by assuming a single-file platoon, which provides structure that allows pairwise safety guarantees from HJ reachability to translate to safety guarantees for the whole platoon.
-We first propose a hybrid systems model of UAVs in platoons to capture this structure.
-Then, we show how HJ reachability can be used to synthesize \textit{liveness controllers} that enable vehicles to reach a set of desired states, and wrap \textit{safety controllers} around the liveness controllers in order to prevent dangerous configurations such as collisions.
-Finally, we show simulation results of quadrotors forming a platoon, a platoon responding to a malfunctioning member, and a platoon responding to an outside intruder to illustrate the behavior of vehicles in these scenarios and demonstrate the guarantees provided by HJ reachability.
-
-%Motivation:
-%\begin{itemize}
-%\item Applications of UAVs, potential numbeurs
-%\item Importance of safety guarantees
-%\item Computation complexity
-%\end{itemize}
-%
-%Related work:
-%\begin{itemize}
-%\item Platooning references: lack of (?) safety guarantees
-%\begin{itemize}\item\textcolor{blue}{Mention PATH papers \& Lygeros thesis}\end{itemize}
-%\item HJI, safety guarantees, limited by dimensionality
-%\end{itemize}
-%
-%Summary of results
-%\begin{itemize}
-%\item Hybrid systems model of vehicles
-%\item Reachability guarantees wrapped around existing methods
-%\item Reachability offers flexibility in terms of design
-%\item Illustrative platoon functions
-%\end{itemize}
+In the second part of this paper, we propose organizing UAVs into platoons, which provide structure that allows pairwise safety guarantees from HJ reachability to translate to safety guarantees for the whole platoon.
+With respect to platooning, we first propose a hybrid systems model of UAVs in platoons to establish the modes of operation needed for our platooning concept.
+Then, we show how reachability-based controllers can be synthesized to enable vehicles successfully perform mode switching, as well as prevent dangerous configurations such as collisions.
+Finally, we show several simulations to illustrate the behavior of vehicles in various scenarios and demonstrate the guarantees provided by HJ reachability.

### 2016-02-13 docs/AIAA 2016/plat_controllers.tex
Updated AIAA 2016 paper

--- 2016-02-03 docs/AIAA 2016/plat_intra.tex
@@
 % !TEX root = main.tex
-\subsection{Reachability-Based Controllers}
+\subsection{Reachability-Based Controllers \label{sec:reach_ctrl}}
 Reachability analysis is useful for constructing controllers in a large variety of situations.
@@
 
-\subsubsection{Getting to a Target State}
+\subsubsection{Getting to a Target State \label{sec:abs_target_ctrl}}
 The controller used by a vehicle to a target state is important in a couple of situations in the platooning context.
@@
 
-\subsubsection{Getting to a State Relative to Another Vehicle}
+\subsubsection{Getting to a State Relative to Another Vehicle \label{sec:rel_target_ctrl}}
 In the platooning context, being able to go to a state relative to another moving vehicle is important for the purpose of forming and joining platoons.
@@
 
-\subsubsection{Avoiding Collision}
+\subsubsection{Avoiding Collisions \label{sec:collision_ctrl}}
 A vehicle can use a liveness controller described in the previous sections when it is not in any danger of collision with other vehicles.
@@
 
-THE FOLLOWING SHOULD BE IN ANOTHER SECTION
-
-\subsubsection{Other Quadrotor Maneuvers}
-Reachability was used in Sections \ref{subsec:highway_merge} and \ref{subsec:platoon_merge} for the relatively complex maneuvers.
-For the simpler maneuvers of traveling along a highway and following a platoon, we resort to simpler controllers described below.
+\subsection{Other Quadrotor Maneuvers \label{sec:other_ctrl}}
+Reachability was used in Section \ref{sec:reach_ctrl} for the relatively complex maneuvers that require safety and liveness guarantees.
+For the simpler maneuvers of traveling along a highway and following a platoon, many well-known classical controllers suffice.
+For illustration, we use the simple controllers described below.
 

### 2016-02-13 docs/AIAA 2016/plat_form.tex
Updated AIAA 2016 paper

@@
 
-If a vehicle from any of the other modes malfunction, it transitions into the Faulty mode and descends after a duration of $t_\text{internal}$.
+If a vehicle from any of the other modes malfunction, it transitions into the Faulty mode and descends after some pre-specified duration $t_\text{faulty}$.
 \end{itemize}
@@
 The vehicles maintain a separation distance of $b$ with its neighbors inside the platoon.
-In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that in the event of a malfunction, a vehicle will be able to exit the altitude range of the highway within a duration of $t_\text{internal}=1.5$.
+In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that in the event of a malfunction, a vehicle will be able to exit the altitude range of the highway within a duration of $t_\text{faulty}=1.5$.
 Such a requirement may be implemented practically as an emergency landing procedure to which the vehicles revert when a malfunction is detected.

### 2016-02-13 docs/AIAA 2016/plat_summary.tex
Updated AIAA 2016 paper

% !TEX root = main.tex
\subsection{Summary of Controllers}
We have introduced several reachability-based controllers, as well as some simple controllers. Pair wise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:collision_ctrl}. As long as a vehicle is not in potential danger according to the safety reachable sets, it is free to use any other controller. All of these other controllers and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.

The controller for getting to an absolute target state, described in Section \ref{sec:abs_target_ctrl}, is used whenever a vehicle needs to move onto a highway to become a platoon leader. This controller guarantees the success of the mode transitions shown in blue in Figure \ref{fig:modeControllers}.

The controller for getting to a relative target state, described in Section \ref{sec:rel_target_ctrl}, is used whenever a vehicle needs to join a platoon to become a follower. This controller guarantees the success of the mode transitions shown in green in Figure \ref{fig:modeControllers}.

For the simple maneuvers of traveling along a highway or following a platoon, many simple controllers such as the ones suggested in Section \ref{sec:other_ctrl} can be used. These controllers keep the vehicles in either the Leader or the Follower mode. Alternatively, additional controllers can be designed for exiting the highway, although these are not considered in this paper. All of these non-reachability-based controllers are shown in gray in Figure \ref{fig:modeControllers}.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{"fig/modeControllers"}
	\caption{}
	\label{fig:modeControllers}
\end{figure}

### 2016-02-13 docs/AIAA 2016/fig/RSExample.m

@@ -23,7 +23,7 @@ plot(R*cos(t), R*sin(t), 'r-', 'linewidth', 4)
 
 %%
 surf(x, y, zeros(size(x)), 'facecolor', [0 0.25 0], ...
-  'facealpha', 0.3, 'edgecolor', 'none')
+  'facealpha', 0.5, 'edgecolor', 'none')
 
 if onlyTarget
   xlabel('x')

### 2016-02-17 code/platoon/numSafetyChecks.m
Fixed computation errors in numSafetyChecks

@@ -26,6 +26,7 @@ for i = 1:length(lgd_text)
   lgd_text{i} = ['frac. of veh. in platoons: ' lgd_text{i}];
 end
 legend(hs, lgd_text, 'location', 'northwest','fontsize', 14)
+
 xlabel('Total number of vehicles','fontsize', 14)
 ylabel('Number of safety checks', 'fontsize', 14)
 
@@ -47,12 +48,19 @@ num_free = Ns - num_in_p;
 
 if p > 0
   % number of checks for each group
-  chks_in_full_p = (p-1) * (k-1);
-  chks_in_last_p = mod(p, k) - 1;
-  chks_in_free = num_free .* (num_free - 1)/2;
+  chks_in_full_p = (p-1) * numSafetyChecksInPlatoon(k);
+  chks_in_last_p = numSafetyChecksInPlatoon(num_in_p - (p-1)*k);
+  chks_in_free = (num_free+p) .* (num_free+p - 1)/2;
   
   checks = chks_in_full_p + chks_in_last_p + chks_in_free;
 else
   checks = num_free .* (num_free - 1) /2;
 end
+
+end
+
+function checks = numSafetyChecksInPlatoon(Np)
+% Np - number of vehicles in platoon
+
+checks = max(0, 2*(Np - 1));
 end

### 2016-02-17 docs/AIAA 2016/conclusions.tex
Finished rough draft of AIAA paper

@@
 \section{Conclusions}
-We considered single-file platoons of UAVs modeled by hybrid systems traveling along air highways.
-Using HJ reachability, we proposed liveness controllers for merging onto highways and merging into existing platoons, and wrapped a safety controller around liveness controllers to ensure no collision between the UAVs can occur.
+To address the important and urgent problem of the traffic management of UAVs, we proposed to have platoons of UAVs traveling on air highways.
+We showed how such an air space structure leads to a much easier safety and liveless analysis.
+We provided simulations which show that by putting vehicles into platoons, many complex maneuvers can be performed using just a few different reachable sets.
+
+For the placement of air highways over a region, we present the very intuitive and efficient fast marching algorithm for solving the Eikonal equation.
+Our algorithm allows us to take as input any arbitrary cost map representing the desirability of flying over any position in space, and produce a set of paths from any destination to a particular origin.
+Simple heurstic clustering methods can then be used to to convert the sets of paths into a set of air highways.
+
+On the air highways, we considered platoons of UAVs modeled by hybrid systems.
+We show how many required platoon functions such as merging onto an air highway and changing platoons can be implemented using only the Free, Leader, and Follower modes of operation.
+Using HJ reachability, we proposed liveness controllers that guarantee the success of all mode transitions, and wrapped a safety controller around liveness controllers to ensure no collision between the UAVs can occur.
 Under the assumption that faulty vehicles can descend after a pre-specified duration, our safety controller guarantees that no collisions will occur in a single altitude level as long as at most one safety breach occurs for each vehicle in the platoon.
 Additional safety breaches can be handled by multiple altitude ranges in the airspace.
-Our simulations show that by putting vehicles into single-file platoons, the likelihood of having multiple safety breaches is low, and conflicts involving a single malfunctioning UAV or intruder can be resolved in a single altitude level.
 
-Immediate future work includes exploring different vehicle models, investigating algorithms for resolving multiple safety breaches within the same altitude, and more broadly related problems such as airspace structure and air highway placement.
+Immediate future work includes exploring different vehicle models, investigating algorithms for resolving multiple safety breaches within the same altitude, and algorithms for off-highway short-range path planning of multiple UAVs.

### 2016-02-17 docs/AIAA 2016/high_eikon.tex
Finished rough draft of AIAA paper

@@
 
-More concretely, suppose a UAV flies from an origin point $p^o$ to a destination point $p^d$ along some path $\ppath(s)$ parametrizes by the parameters $s$.
+More concretely, suppose a UAV flies from an origin point $p^o$ to a destination point $p^d$ along some path $\ppath(s)$ parametrized by $s$.
 Then, $\ppath(s_0) = p^o$ would denote the origin, and $\ppath(s_1) = p^d$ would denote the destination.
@@
 
-The problem of finding the cost-minimizing path is finding the path such that the above cost is minimized.
-More generally, given an origin point $p^o$, we would like to compute the function $\ocost$ representing optimal cumulative cost for any destination point $\pos$:
+For an origin-destination pair, we would like to find the path such that the above cost is minimized.
+More generally, given an origin point $p^o$, we would like to compute the function $\ocost$ representing the optimal cumulative cost for any destination point $\pos^d$:
 
@@
 
-It is well known \cite{} that the solution to the Eikonal equation \eqref{eq:eikonal} precisely computes the function $\ocost(\pos^d)$ given the cost map $\cmap$.
-Note that a single function characterizes the minimum cost from an origin $\pos^o$ to any destination $\pos^d$.
+It is well known that the solution to the Eikonal equation \eqref{eq:eikonal} precisely computes the function $\ocost(\pos^d)$ given the cost map $\cmap$ \cite{Sethian96,Alton06}.
+Note that a single function characterizes the minimum cost from an origin $\pos^o$ to \textit{any} destination $\pos^d$.
 Once $\ocost$ is found, the optimal path $\ppath$ between $\pos^o$ and $\pos^d$ can be obtained via gradient descent.
@@
 
-\eqref{eq:eikonal} can be efficiently computed numerically using the fast marching method \cite{}.
+The Eikonal equation \eqref{eq:eikonal} can be efficiently computed numerically using the fast marching method \cite{Sethian96}.
 
@@
 Unlike \eqref{eq:ahpp}, the relaxation \eqref{eq:rahpp} can be quickly solved using currently available numerical tools.
-Thus, we first solve \eqref{eq:rahpp}, and then post-process the solution to \eqref{eq:rahpp} to obtain an approximation to \eqref{eq:ahpp}.
+Thus, we first solve the approximate air highway placement problem \eqref{eq:rahpp} by solving \eqref{eq:eikonal}, and then post-process the solution to \eqref{eq:rahpp} to obtain an approximation to \eqref{eq:ahpp}.
 
-Given a single origin point $\pos^o$, the optimal cumulative cost function $\ocost(p)$ can be computed.
+Given a single origin point $\pos^o$, the optimal cumulative cost function $\ocost(\pos^d)$ can be computed.
 Suppose $M$ different destination points $\pos^d_i,i=1,\ldots,M$ are chosen.

### 2016-02-17 docs/AIAA 2016/high_form.tex
no message
Finished rough draft of AIAA paper

@@
 \section{Air Highways}
-Air highways are virtual highways in the airspace on which a number of UAV platoons may be present.
+We consider air highways to be virtual highways in the airspace on which a number of UAV platoons may be present.
 UAVs seek to arrive at some desired destination starting from their origin by traveling along a sequence of air highways.
@@
 By routing platoons of UAVs onto a few common pathways, the air space becomes more tractable to analyze and intuitive to monitor.
-The concept of platoons will be proposed in Section \ref{sec:platooning}; for now, we will focus on air highways.
+The concept of platoons will be proposed in Section \ref{sec:platooning}; for now, we focus on air highways in this section.
 
@@
 two cities), air highways must connect the two points while potentially satisfying other criteria.
-We now define the air highway placement problem, and propose a simple and fast way to approximate its solution.
+With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution.
 
@@
 Consider a map $\cmap:\mathbb{R}^2 \rightarrow \mathbb{R}$ which defines the cost $\cmap(\pos)$ incurred when a UAV flies over the position $\pos=(\pos_x,\pos_y)\in\mathbb{R}^2$.
-Given any $\pos$, a large value of $\cmap(\pos)$ indicates that the position $\pos$ is costly or undesirable for a UAV to fly over.
-Locations with a high cost could be In general, the cost map $\cmap(\cdot)$ may be used to model cost of interference with commercial air spaces, cost of accidents, cost of noise pollution, etc., and can be designed by government regulation bodies.
+Given any position $\pos$, a large value of $\cmap(\pos)$ indicates that the position $\pos$ is costly or undesirable for a UAV to fly over.
+Locations with high cost could, for example, include densely populated areas and areas around airports.
+In general, the cost map $\cmap(\cdot)$ may be used to model cost of interference with commercial air spaces, cost of accidents, cost of noise pollution, etc., and can be designed by government regulation bodies.
 
-Let $\pos^o$ denote an origin point and $\pos^d$ denote a destination point. Consider a sequence of highways $\hws_N = {\hw_1, \hw_2, \ldots, \hw_N}$ that satisfies the following:
+Let $\pos^o$ denote an origin point and $\pos^d$ denote a destination point. Consider a sequence of highways $\hws_N = \{\hw_1, \hw_2, \ldots, \hw_N\}$ that satisfies the following:
 
@@
 
-The interpretation of the above conditions is that the start point of first highway is the origin, the end point of a highway is the end point of the next highway, and the end point of last highway is the destination.
+The interpretation of the above conditions is that the start point of first highway is the origin, the end point of a highway is the start point of the next highway, and the end point of last highway is the destination.
 The highways $\hw_1,\ldots,\hw_N$ form a sequence of waypoints for a UAV starting at the origin $\pos^o$ to reach its destination $\pos^d$.
@@
 Any UAV flying on a highway over some position $\pos$ incurs a cost of $\cmap(\pos)$, so that the total cost of flying from the origin to the destination is given by \eqref{eq:ahpp}.
-The air highway placement problem minimizes the cumulative cost of flying from some origin $p^o$ to some destination $p^d$ along the sequence of highways $\hws_N$.
+The air highway placement problem minimizes the cumulative cost of flying from some origin $p^o$ to some destination $p^d$ along the sequence of highways $\hws_N=\{\hw_1, \hw_2, \ldots, \hw_N\}$.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/highway_illustration"}
+	\includegraphics[width=0.35\textwidth]{"fig/highway_illustration"}
 	\caption{Highway illustration}

### 2016-02-17 docs/AIAA 2016/high_sim.tex
Finished rough draft of AIAA paper

@@
 \subsection{Results}
-To illustrate our air highway placement proposal, we used the San Francisco Bay Area as an example, and classified each point on the map into three different region.
+To illustrate our air highway placement proposal, we used the San Francisco Bay Area as an example, and classified each point on the map into four different regions: region around airports, highly populated cities, water, and other.
 Each region has an associated cost, reflecting the desirability of flying a vehicle over an area in the region.
@@
 
-\subsubsection{Cost-Minimizing Paths}
 Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function.
@@
 
-Fig. \ref{fig:airHighway_sparse} shows the result of converting the cost-minimizing paths to a small number of waypoints. The left subfigure shows
+Fig.
+\ref{fig:airHighway_sparse} shows the result of converting the cost-minimizing paths to a small number of waypoints.
+The left plot shows the waypoints, interpreted as the start and end points of air highways, over a white background for clarity.
+The right plot shows these air highways over the map of the Bay Area.
 

### 2016-02-17 docs/AIAA 2016/high_waypoints.tex
Finished rough draft of AIAA paper

@@
 Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a continuous set of points.
-Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexes by the corresponding path.
+Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexed by the corresponding path index $i$.
+The
 
@@
 
- we sparsify this set of points to obtain a collection of waypoints, $\wpt$, which are also endpoints of air highways, we first add the destination point to the collection and note the path's heading.
-Next, we add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$.
-This process is repeated along the entire path.
-Finally, we add the origin points to the collection.
-We create a collection of these points for all the cost-minimizing paths.
+To sparsify the continuous set of points on each path, we start at the destination point and note the path's heading.
+We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process is repeated along the entire path.
 
-If there is a large change in heading within a small section of the cost-minimizing path, then the collections $\wpt_{ij}$ may contain many points which are close together.
-In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), also cluttering the airspace with too many waypoints.
-We propose to sparsify the waypoints by clustering the points in $\wpt_{ij}$.
-Each cluster contains points that are within a certain distance to the closest point in the cluster, and all points in each cluster are replaced with a single point located at the centroid of the cluster.
+If there is a large change in heading within a small section of the cost-minimizing path, then the collection of point may contain many points which are close together.
+In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), which may contribute to cluttering the airspace with too many waypoints.
+We propose to sparsify the waypoints by clustering the points.
+After clustering, we replace each cluster of points with a single point located at the centroid of the cluster.
+
+To the collection of points resulting from the above process generates we add the origin and destination points to the collection.
+Repeating the entire process for every path, we waypoints for all the cost-minimizing paths under consideration.
+Figure \ref{fig:hw_ill} summarizes the entire air highway placement process.

### 2016-02-17 docs/AIAA 2016/introduction.tex
Finished rough draft of AIAA paper

@@
 This would equate to thousands of vehicles simultaneously in the air just from package delivery services.
-Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to firefight in areas that are difficult to reach but require prompt response \cite{Debusk10}.
+Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to respond to disasters in areas that are difficult to reach but require prompt response \cite{Debusk10,Tornado16}.
 As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13, NASA16}.
@@
 Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be daunting task.
-To address this, in the first part of this paper, we propose a flexible and computationally efficient way to perform optimal air highway replacement given an arbitrary cost map that can capture the desirability of having UAVs fly over any geographical location.
+To address this, in the first part of this paper, we propose a flexible and computationally efficient way based on \cite{Sethian96} to perform optimal air highway replacement given an arbitrary cost map that captures the desirability of having UAVs fly over any geographical location.
 We demonstrate our method using the San Francisco Bay Area as an example.
@@
 With respect to platooning, we first propose a hybrid systems model of UAVs in platoons to establish the modes of operation needed for our platooning concept.
-Then, we show how reachability-based controllers can be synthesized to enable vehicles successfully perform mode switching, as well as prevent dangerous configurations such as collisions.
+Then, we show how reachability-based controllers can be synthesized to enable vehicles to successfully perform mode switching, as well as prevent dangerous configurations such as collisions.
 Finally, we show several simulations to illustrate the behavior of vehicles in various scenarios and demonstrate the guarantees provided by HJ reachability.

### 2016-02-17 docs/AIAA 2016/main.tex
no message
Updated AIAA 2016 paper
Finished rough draft of AIAA paper

@@
-\documentclass[journal]{aiaa-pretty}
+\documentclass[submit]{aiaa-pretty}
 
@@
 
-\author{Mo Chen}
+\newcommand{\td}{t_\text{faulty}} % time to descend
+\newcommand{\veh}[1]{Q_{#1}}
+\newcommand{\vehSCS}[1]{\mathcal{Q}_{#1}} % vehicle safety check set
+
+\author{Mo Chen, Qie Hu, Jaime Fisac, Kene Akametalu, Casey Mackin, Claire Tomlin}
 \title{Guaranteeing Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}
 
-\abstract{(TO BE UPDATED!)
-
-Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, firefighting, and fast disaster response.
-As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met.
-Hamilton-Jacobi (HJ) reachability is a powerful framework for providing conditions under which these requirements can be met, and for synthesizing the optimal controller for meeting them.
-However, due to the curse of dimensionality, HJ reachability is only tractable for a small number of vehicles if their set of maneuvers is unrestricted.
-In this paper, we define a platoon to be a group of UAVs in a single-file formation.
-We model each vehicle as a hybrid system with modes corresponding to its role in the platoon, and specify the set of allowed maneuvers in each mode to make the analysis tractable.
-We propose several liveness controllers based on HJ reachability, and wrap a safety controller, also based on HJ reachability, around the liveness controllers.
-For a single altitude range, our approach guarantees safety for one safety breach; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.
+\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, aerial surveillance, and disaster response.
+As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the air space, in order to ensure their liveness and safety requirements are met.
+Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers are unrestricted.
+In this paper, we propose to have platoons of UAVs flying on air highways in order to impose the air space structure that allows for tractable analysis and intuitive monitoring.
+For the air highway placement problem, we use the flexible and efficient fast marching method to solve the Eikonal equation, which produces a sequence of air highways that minimizes the cost of flying from an origin to any destination.
+Within the platoons that travel on the air highways, we model each vehicle as a hybrid system with modes corresponding to its role in the platoon.
+Using HJ reachability, we propose several liveness controllers and a safety controller that guarantees the success and safety of all mode transitions.
+For a single altitude range, our approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.
 We demonstrate the satisfaction of liveness and safety requirements through simulations of three common scenarios.}
@@
 \noindent\begin{tabular}{@{}lcl@{}}
-$x$ &=& System state \\
-$\pos=(\pos_x, \pos_y)$ &$=$& Horizontal position \\
-$\vel=(\vel_x, \vel_y)$ &$=$& Horizontal velocity
+$\cmap$ &=& Cost map \\
+$\ccost$ &=& Cumulative cost of a path \\
+$\ocost$ &=& Optimal cumulative cost of a path \\
+$\hw$ &=& Air highway \\
+$\hwd$ &=& Direction of travel of air highway \\
+$\hws$ &=& A sequence of air highways \\
+$\wpt$ &=& Waypoint \\
+$x$ &=& System state (of a vehicle) \\
+$\pos=(\pos_x, \pos_y)$ &=& Horizontal position \\
+$\vel=(\vel_x, \vel_y)$ &=& Horizontal velocity \\
+$\td$ &=& Time limit for descent during potential conflict \\
+$\veh{i}$ &=& $i$th vehicle \\
+$\vehSCS{i}$ &=& Set of vehicles to consider for safety for vehicle $i$
 \end{tabular} \\
@@
 \input{plat_reach.tex}
-\input{plat_intra.tex}
-\input{plat_inter.tex}
+\input{plat_controllers.tex}
+\input{plat_summary.tex}
 \input{plat_safety.tex}
@@
 
+\bibliographystyle{aiaa}
 \bibliography{references}

### 2016-02-17 docs/AIAA 2016/plat_controllers.tex
Finished rough draft of AIAA paper

@@
 
-\subsection{Other Quadrotor Maneuvers \label{sec:other_ctrl}}
+\subsection{Other Controllers \label{sec:other_ctrl}}
 Reachability was used in Section \ref{sec:reach_ctrl} for the relatively complex maneuvers that require safety and liveness guarantees.

### 2016-02-17 docs/AIAA 2016/plat_form.tex
Finished rough draft of AIAA paper

@@
 \section{Unmanned Aerial Vehicle Platooning \label{sec:platooning}}
-\subsection{Problem Formulation}
+\subsection{UAVs in Platoons}
 \subsubsection{Vehicle Dynamics}
@@
 For convenience, we will denote the position and velocity $\pos=(\pos_x, \pos_y),\vel=(\vel_x,\vel_y)$, respectively.
-We will consider a group of $N$ quadrotors $Q_i, i=1\ldots,N$.
 
@@
 Suppose that there are $N$ vehicles in total.
-We consider a platoon of vehicles to be a group of $M\le N$ vehicles, denoted $Q_{P_1}, \ldots, Q_{P_M}, \{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$, in a single-file formation.
+We will denote the $N$ vehicles as $\veh{i}, i=1\ldots,N$.
+We consider a platoon of vehicles to be a group of $M\le N$ vehicles, denoted $\veh{P_1}, \ldots, \veh{P_M}, \{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$, in a single-file formation; for convenience, we also denote $P_0 = P_{M+1} = \emptyset$.
+When necessary, we will use superscripts to denote vehicles of different platoons: $\veh{P_i^j}$ represents the $i$th vehicle in the $j$th platoon.
+
+For convenience, let $\vehSCS{i}$ denote the set of indices of vehicles with respect to which $Q_i$ checks safety against.
+If vehicle $\veh{i}$ is in a free vehicle, then it must check for safety with respect to all other vehicles, $\vehSCS{i} = \{j: j\neq i\}$.
+If the vehicle is part of a platoon, then it checks safety with respect to the platoon member in front and behind, $\vehSCS{i} = \{P_{j+1}, P_{j-1}\}$.
+Figure \ref{fig:vehicleNotation} summarizes the the indexing system of the vehicles.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{"fig/vehicleNotation"}
+	\caption{Notation for vehicles in platoons.}
+	\label{fig:vehicleNotation}
+\end{figure}
+
 We will assume that the vehicles in a platoon travel along an air highway.
@@
 
-SHOULD EVASION BE A MODE?
+%SHOULD EVASION BE A MODE?
 

### 2016-02-17 docs/AIAA 2016/plat_safety.tex
Finished rough draft of AIAA paper

@@
 \subsection{Safety Analysis}
-Under normal operations in a single platoon, each follower quadrotor $Q_i,i=P_2,\ldots,P_{N-1}$ in a platoon checks whether it is in the safety reachable set with respect to $Q_{P_{i-1}}$ and $Q_{P_{i+1}}$.
-So $\mathcal{Q}(i) = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$.
-Assuming there are no nearby quadrotors outside of the platoon, the platoon leader $Q_{P_1}$ checks safety against $Q_{P_2}$, and the platoon trailer $Q_{P_N}$ checks safety against $Q_{P_{N-1}}$.
-So $\mathcal{Q}(P_1)=\{P_2\}, \mathcal{Q}(P_N)=\{P_{N-1}\}$.
-When all quadrotors are using liveness controllers to perform their allowed maneuvers, no pair of quadrotors should be in an unsafe configuration if the liveness controllers are well-designed.
-However, occasionally a quadrotor $Q_k$ may behave unexpectedly due to faults or malfunctions, in which case it may come into an unsafe configuration with another quadrotor.
+Under normal operations in a single platoon, each follower vehicle $\veh{i},i=P_2,\ldots,P_{N-1}$ in a platoon checks whether it is in the safety reachable set with respect to $\veh{P_{i-1}}$ and $\veh{P_{i+1}}$.
+So $\vehSCS{i} = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$.
+Assuming there are no nearby vehicle outside of the platoon, the platoon leader $\veh{P_1}$ checks safety against $\veh{P_2}$, and the platoon trailer $Q_{P_N}$ checks safety against $Q_{P_{N-1}}$.
+So $\vehSCS{P_1}=\{P_2\}, \mathcal{Q}(P_N)=\{P_{N-1}\}$.
+When all vehicles are using liveness controllers to perform their allowed maneuvers, no pair of vehicles should be in an unsafe configuration if the liveness controllers are well-designed.
+However, occasionally a vehicles $\veh{k}$ may behave unexpectedly due to faults or malfunctions, in which case it may come into an unsafe configuration with another vehicles.
 
-With our choice of $\mathcal{Q}(i)$ and the assumption that the platoon is in a single-file formation, some quadrotor $Q_i$ would get into an unsafe configuration with $Q_k$, where $Q_k$ is likely to be the quadrotor in front or behind of $Q_i$.
+With our choice of $\vehSCS{i}$ and the assumption that the platoon is in a single-file formation, some vehicle $\veh{i}$ would get into an unsafe configuration with $\veh{k}$, where $\veh{k}$ is likely to be the vehicle in front or behind of $\veh{i}$.
 In this case, a ``safety breach" occurs.
-Our synthesis of the safety controller guarantees that between every pair of quadrotors $Q_i,Q_k$, as long as $V_S(-t,x_i- x_k)>0$, $\exists u_i$ to keep $Q_i$ from colliding with $Q_k$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $Q_k$.
-Therefore, as long as the number of ``safety breaches" is at most one, $Q_i$ can simply use the optimal control to avoid $Q_k$ and avoid collision for the time horizon of $t$.
-Since quadrotors in platoons are able to exit the current altitude range within a duration of $t_\text{internal}$, if we choose $t=t_\text{internal}$, the safety breach would always end before any collision can occur.
+Our synthesis of the safety controller guarantees that between every pair of vehicles $\veh{i},\veh{k}$, as long as $V_S(-t,x_i- x_k)>0$, $\exists u_i$ to keep $\veh{i}$ from colliding with $\veh{k}$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $\veh{k}$.
+Therefore, as long as the number of ``safety breaches" is at most one for $\veh{i}$, $Q_i$ can simply use the optimal control to avoid $\veh{k}$ and avoid collision for the time horizon of $t$.
+Under the assumption that vehicles are able to exit the current altitude range within a duration of $\td$, if we choose $t=t_\text{faulty}$, the safety breach would always end before any collision can occur.
 
-Within a duration of $t_\text{internal}$, there is a small chance that additional safety breaches may occur.
-However, as long as the total number of safety breaches does not exceed the number of affected quadrotors, collision avoidance of all the quadrotors can be guaranteed for the duration $t_\text{internal}$.
-However, as our simulation results show, putting quadrotors in single-file platoons makes the likelihood of multiple safety breaches low during a quadrotor malfunction and during the presence of one intruder vehicle.
+Within a duration of $\td$, there is a small chance that additional safety breaches may occur.
+However, as long as the total number of safety breaches does not exceed the number of affected quadrotors, collision avoidance of all the vehicles can be guaranteed for the duration $\td$.
+However, as our simulation results show, putting vehicles in single-file platoons makes the likelihood of multiple safety breaches low during a vehicle's malfunction and during the presence of one intruder vehicle.
 
-In the event that multiple safety breaches occur for some of the quadrotors due to a malfunctioning quadrotor within the platoon or an intruding quadrotor outside of the platoon, those quadrotors with more than one safety breach still have the option of exiting the highway altitude range in order to avoid collisions.
+In the event that multiple safety breaches occur for some of the vehicles due to a malfunctioning vehicle within the platoon or an intruding vehicles outside of the platoon, those vehicles with more than one safety breach still have the option of exiting the highway altitude range in order to avoid collisions.
 Every extra altitude range reduces the number of simultaneous safety breaches by $1$, so $K$ simultaneous safety breaches can be resolved using $K-1$ different altitude ranges.
 
-Given that quadrotors within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons.
-By treating each platoon as a single unit, we reduce the number of individual quadrotors that need to check for safety against each other, reducing overall computation burden.
+The concept of platooning can be coupled with any collision avoidance algorithm that provides safety guarantees.
+In this paper, we have only proposed the simplest reachability-based collision avoidance scheme.
+Existing collision avoidance algorithms such as \cite{SPPPaper} and \cite{MIPPaper} have the potential to provide safety guarantees for many vehicles in order to resolve multiple safety breaches at once.
+Coupling the platooning concept with the more advanced collision avoidance methods that provide guarantees for a larger number of vehicles would reduce the risks of multiple safety breaches.
+
+Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons.
+By treating each platoon as a single unit, we reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.

### 2016-02-17 docs/AIAA 2016/plat_sim.tex
Finished rough draft of AIAA paper

@@
 \subsection{Numerical Simulations}
-
-In this section, we consider several situations that quadrotors in a platoon on an air highway may commonly encounter, and show via simulations the behaviors that emerge from the controllers we defined in Sections \ref{sec:liveness} and \ref{sec:safety}.
+In this section, we consider several situations that vehicles in a platoon on an air highway may commonly encounter, and show via simulations the behaviors that emerge from the controllers we defined in Sections \ref{sec:reach_ctrl} and \ref{sec:other_ctrl}.
 
 \subsubsection{Forming a Platoon}
-We first consider the scenario in which some quadrotors are trying to merge onto an initially unoccupied highway.
-In order to do this, each quadrotor first checks for safety with respect to the other quadrotors, and uses the safety controller if necessary, according to Section \ref{sec:safety}.
-Otherwise, the quadrotor uses the liveness controller described in Section \ref{sec:liveness}.
+We first consider the scenario in which Free vehicles merge onto an initially unoccupied highway.
+In order to do this, each vehicle first checks for safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:reach_ctrl}\ref{sec:collision_ctrl}.
+Otherwise, the vehicle uses the liveness controller for getting to an absolute target set described in Section \ref{sec:reach_ctrl}\ref{sec:abs_target_ctrl} in order to merge onto the highway, create a platoon, and become a Leader vehicle if there are no platoons on the highway.
+If there is already a platoon on the highway, then the vehicle would use the liveness controller for getting to a target set relative to the platoon leader as described in Section \ref{sec:reach_ctrl}\ref{sec:rel_target_ctrl} to join the platoon and become a Follower.
 
-For the simulation example, the highway is specified by the line $p_y = 0.5p_x$, the point of entry on the highway is chosen to be $(\bar{p}_x, \bar{p}_y) = (4,2)$, and the velocity on the highway is chosen to be ($\bar{v}_x, \bar{v}_y) = \frac{\bar{v}}{\sqrt{0.5^2 + 1^2}} (0.5, 1)$.
-The velocity simply states that the quadrotors must travel at a speed $\bar{v}=3$ along the direction of the highway.
-This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{subsec:highway_merge}.
+For the simulation example, shown in Figure \ref{fig:fp}, the highway is specified by a line segment beginning at the origin.
+The five vehicles, $\veh{1}, \veh{2}, \ldots, \veh{5}$ are colored red, purple, light blue, dark blue, and yellow, respectively.
 
-The first quadrotor that completes merging onto the empty highway creates a platoon and becomes its leader, while subsequent quadrotors form a platoon behind the leader in a pre-specified order according to the process described in Section \ref{subsec:platoon_merge}.
-Here, we choose $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $b$ behind the last quadrotor in the platoon, and $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$.
+The first two plots in Figure \ref{fig:fp} illustrate the use of liveness and safety reachable sets for the first two vehicles.
+Since the liveness reachable sets are in 4D and the safety reachable sets are in 6D, we compute and plot their 2D slices based on the vehicles' velocities and relative velocities.
+All vehicles begin as Free vehicles, so they each need to take into account five different reachable sets: four safety reachable sets and one liveness reachable set.
+For clarity, we only show the liveness reachable set and one safety reachable set.
+
+For $\veh{1}$ (red), an arbitrary point of entry on the highway is chosen as the target absolute position, and the velocity corresponding to a speed of $10$ in the direction of the highway is chosen as the target absolute velocity.
+This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{sec:reach_ctrl}\ref{sec:abs_target_ctrl}.
+
+At $t=3.9$, $\veh{1}$ (red) is inside the liveness reachable set for getting to an absolute state shown as the dotted red boundary.
+Therefore, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$.
+During the entire time, $\veh{1}$ checks whether it may collide with all of the other vehicles within a time horizon of $\td$.
+To do this, it simply checks whether its state relative to each of the other vehicles is within the corresponding safety reachable set.
+As an example, the safety reachable set boundary with respect to $\veh{2}$ (purple) is shown as the red dashed boundary; $\veh{1}$ (red) is safe with respect to $\veh{2}$ (purple) since $\veh{1}$ (red) is outside of the boundary.
+
+After completing merging onto the empty highway, $\veh{1}$ (red) creates a platoon and becomes its leader, while subsequent vehicles begin to form a platoon behind the leader in the order of ascending distance to $\veh{1}$ (red) according to the process described in Section \ref{sec:reach_ctrl}\ref{sec:rel_target_ctrl}.
+Here, we choose the target relative position $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $b$ behind the last reserved slot in the platoon, and the target relative velocity $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$ with respect to the leader in order to maintain the platoon formation.
 This gives us the target set $\mathcal{L}_P$ that we need.
 
-Figures \ref{fig:normal2} and \ref{fig:normal5} show the simulation results.
-Since the liveness reachable sets are in 4D and the safety reachable sets are in 6D, we compute and plot their 2D slices based on the quadrotors' velocities and relative velocities.
+At $t=5.9$, $Q_2$ (purple) begins joining the platoon behind $\veh{1}$ (red), by moving towards the target $\bar{x}_P$ relative to the position of $\veh{1}$ (red).
+Note that $\bar{x}_P$ moves with $\veh{1}$ (red) as $\bar{x}_P$ is defined in terms of the relative states of the two vehicles.
+Since $\veh{2}$ is inside the liveness reachable set boundary for joining the platoon (purple dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target as long as it stays out of all safety reachable sets.
+For example, at $t=5.9$, $\veh{2}$ (purple) is outside of the safety reachable set with respect to $\veh{1}$ (red), shown as the purple dashed boundary.
 
-Figure \ref{fig:normal2} illustrates the use of liveness and safety reachable sets using just two quadrotors to reduce visual clutter.
-The first quadrotor $Q_1$ (red disk) first travels in a straight line towards the highway merging point $\bar{x}$ (red circle) at $t=1.5$, because it is not yet in the liveness reachable set for merging onto the highway (red dotted boundary).
-When it is within the liveness reachable set boundary at $t=2.8$, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$.
-During the entire time, the $Q_1$ checks whether it may collide with $Q_2$ within a time horizon of $t_\text{external}$; we chose $t_\text{external}=3>t_\text{internal}$.
-However, since $Q_1$ never goes into the boundary of the safety reachable set (red dashed boundary), it uses the liveness controller the entire time.
-
-After $Q_1$ has reached $\bar{x}_H$, it forms a platoon, becomes the platoon leader, and continues to travel along the highway.
-$Q_2$ (blue disk), at $t=7$, begins joining the platoon behind $Q_1$, by moving towards the target $\bar{x}_P$ relative to the position of $Q_1$.
-Note that $\bar{x}_P$ moves with $Q_1$ as $\bar{x}_P$ is defined in terms of the relative states of the two quadrotors.
-When $Q_2$ moves inside the liveness reachable set boundary for joining the platoon (blue dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target as long as it stays out of the safety reachable set (blue dashed boundary).
-
-Figure \ref{fig:normal5} shows the behavior of all 5 quadrotors which eventually form a platoon and travel along the highway together.
-The liveness controllers allow the quadrotors to optimally and smoothly enter the highway and join platoons, while the safety controllers prevent collisions from occurring.
+In the bottom plots of Figure \ref{fig:fp}, $\veh{1}$ (red) and $\veh{2}$ have already become the platoon leader and follower, respectively.
+The rest of the vehicles follow the same process to join the platoon.
+All 5 vehicles eventually form a single platoon and travel along the highway together.
+As with the first two vehicles, the liveness controllers allow the remaining vehicles to optimally and smoothly join the platoon, while the safety controllers prevent collisions from occurring.
 
 % 40 60 110 210
-\begin{figure} \label{fig:fp}
+\begin{figure} 
     \centering
@@
         \includegraphics[width=\textwidth]{fig/fp_40}
-        \caption{40}
+        \caption{The red vehicle follows the reachability-based liveness controller for getting to an absolute target state to merge onto the highway, while avoiding collisions using the reachability-based safety controller.
+The liveness reachable set and one safety reachable set are shown as the dotted and dashed boundaries, respectively.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/fp_60}
-        \caption{60}
+        \caption{After the red vehicle successfully merges onto the highway and becomes the platoon leader, the purple vehicle uses the reachability-based liveness controller for getting to a relative target state to join the platoon, while avoiding collisions using the reachability-based safety controller.
+The liveness and safety reachable sets are shown as the dotted and dashed boundaries, respectively.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/fp_110}
-        \caption{110}
+        \caption{After the first two vehicles successfully form a two-vehicle platoon, the rest of the vehicles follow the same process to join the platoon.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/fp_210}
-        \caption{210}
+        \caption{All five vehicles have successfully joined the platoon and now travel on the highway together.}
     \end{subfigure}   
-    \caption{form platoons}    
+    \caption{A simulation showing how five vehicles initially in the Free mode can form a platoon. \label{fig:fp}}
 \end{figure}
@@
 \subsubsection{Intruder Vehicle}
-We now consider the scenario in which a platoon of quadrotors encounters an intruder vehicle.
-To avoid collision, each quadrotor checks for safety with respect to the intruder and any quadrotor in front and behind in the platoon.
-If necessary, the quadrotor uses the safety controller, otherwise it uses the appropriate liveness controller, depending on whether it is a leader or follower.
+We now consider the scenario in which a platoon of vehicles encounters an intruder vehicle.
+To avoid collision, each vehicle checks for safety with respect to the intruder and any vehicles in front and behind of it in the platoon.
+If necessary, the vehicle uses the reachability-based safety controller to avoid collision, otherwise it uses the appropriate controller to travel on the highway if it is a leader, or follow the leader if it is a follower.
+After danger has passed, the vehicles in the platoon resume normal operation.
 
-Figure \ref{fig:intruder1} shows the simulation result.
-At $t=0$, a platoon of 4 quadrotors, $Q_{P_i},i=1,\ldots,4$ with $P_i = i$, travels along the highway defined by the line $p_y = p_x$.
-An intruder vehicle $Q_0$ (red disk) starts from position $(p_x, p_y) = (40,30)$ and heads toward bottom-left of the grid.
-As before, platoon members incur a safety breach if $V(-t_\text{internal},x_{P_i}-x_{P_j})\le 0$.
-However, with respect to $Q_0$, platoon members incur a safety breach if $V(-t_\text{external}, x_{P_i}-x_0) \le 0$ with $t_\text{external}>t_\text{internal}$.
+Figure \ref{fig:in} shows the simulation result.
+At $t=9.9$, a platoon of four vehicles, $\veh{i},i=1,\ldots,4$ (with $P_i = i$), travels along the highway shown.
+An intruder vehicle $\veh{5}$ (yellow) heads left, disregarding the presence of the platoon.
+At $t=11.9$, the platoon leader $\veh{1}$ (red) detects that it has gone near the boundary of the safety reachable set (not shown) with respect to the intruder $\veh{5}$ (yellow).
+In response, $\veh{1}$ (red) starts using the safety controller to optimally avoid the intruder according to \eqref{eq:HJI_ctrl_syn}; in doing so, it steers slightly off the highway.
 
-The platoon leader $Q_{P_1}$'s (black disk) safety is unaffected by the intruder, thus it simply follows its original path on the highway using the liveness controller described in Section \ref{sec:travel_hwy}.
-Followers $Q_{P_2}$ (blue disk), $Q_{P_3}$ (green disk) and $Q_{P_4}$ (pink disk), on the other hand, must use the safety controller in order to avoid collision with the intruder ($t=3.3,6.2$).
-This causes their paths to deviate off the highway.
-Once each quadrotor is safe relative to the intruder, they merge back onto the highway, join the original platoon and continue traveling along it ($t=12.4$).
+Note that although in this particular simulation, the intruder travels in a straight line, a straight line motion of the intruder was \textit{not} assumed.
+Rather, the safety reachable sets are computed assuming the worst case control of the intruder, according to \eqref{eq:HJI_ctrl_syn}.
 
-Figure \ref{fig:intruder2} illustrates the use of safety reachable sets in this scenario using only $Q_{P_2}$ as an example.
-The safety reachable sets of $Q_{P_2}$ with respect to the intruder $Q_0$ (red dashed line), $Q_{P_1}$ (black dashed line) and $Q_{P_3}$ (green dashed line) are shown.
-With respect to $Q_0$, $Q_{P_2}$'s safety is considered to be breached if $V_S(-t_\text{external},x_{P_2}-x_0) \le 0$.
-To avoid possible collision with the intruder, $Q_{P_2}$ must remain outside the safety reachable set with respect to the intruder.
-The same applies to collision avoidance with $Q_{P_1}$ and $Q_{P_3}$.
-%\textcolor{red}{\sout{Note that safety reachable sets with $Q_{P_1}$ and $Q_{P_3}$ are much smaller than that with the intruder.
-This is because under normal conditions, vehicles in the same platoon have near-zero relative velocity.
-For this reason, they may only check possible collisions within the next 1.5 seconds, instead of 3 seconds for vehicles outside of the platoon.
-This allows vehicles to travel closer together within a platoon and thus increasing throughput on the air highway.}} \textcolor{blue}{The 1.5 seconds is because we made the assumption that malfunctioning vehicles will change altitude within 1.5 seconds.}
+As the intruder $\veh{5}$ (yellow) continue to disregard other vehicles, the followers of the platoon also get near the respective boundaries of the safety reachable set with respect to the intruder.
+This occurs at $t=13.9$, where the platoon ``makes room'' for the intruder to pass by to avoid collisions; all vehicles deviate from their intended path, which is to follow the platoon leader or the highway.
 
-Initially, $Q_{P_2}$ ($P_2=2$) is a follower and is outside all 3 safety reachable sets.
-Hence it is allowed to use the liveness controller to follow the platoon as described in Section \ref{sec:follow_platoon}.
-At time $t=0.6$, $Q_2$ comes to the boundary of the safety set with respect to the intruder and therefore must apply the safety control law to avoid potential future collision.
-Thus it splits the original platoon and becomes the leader of a new platoon consisting of itself, $Q_3$ and $Q_4$.
-$Q_2$ keeps using the safety controller until it is safe with respect to the intruder again at $t=3$, since if it tried to merge back to the highway before this time, it would enter the safety set with respect to the intruder and lose the $t_\text{external}$ safety guarantee.
-After $t=3$, $Q_2$ is safe to use the liveness controller again to merge back onto the highway and join the original platoon as a follower.
-Note that during the entire time, $Q_2$ maintains safety against the intruder, $Q_1$ and $Q_3$ by always staying outside of all three safety reachable sets.
+After the intruder has passed, eventually all vehicles become far away from any safety reachable sets.
+When this occurs, the leader resumes following the highway, and the followers resume following the leader.
+At $t=19.9$, the platoon successfully gets back onto the highway.
 
 % 100 120 140 200
-\begin{figure} \label{fig:in}
+\begin{figure}
     \centering
@@
         \includegraphics[width=\textwidth]{fig/in_100}
-        \caption{100}
+        \caption{Four vehicles in a platoon are traveling along the highway. The yellow intruder disregards other vehicles.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/in_120}
-        \caption{120}
+        \caption{Platoon members begin avoidance maneuvers as they get near the safety reachable set boundaries with respect to the intruder.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/in_140}
-        \caption{140}
+        \caption{As the intruder (yellow) crosses the highway, the safety controller causes platoon members spread out to ``make room'' for the intruder to pass.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/in_200}
-        \caption{200}
+        \caption{After danger has passed, the platoon resumes normal operation.}
     \end{subfigure}   
-    \caption{intruder}    
+    \caption{A simulation showing how a platoon of four vehicles react to an intruder. \label{fig:in}}
 \end{figure}
@@
 \subsubsection{Changing highways}
+In order to travel from origin to destination, a vehicle may need to change highways several times before exiting an air highway system.
+In this simulation, shown in Figure \ref{fig:ch}, two platoons are traveling on two different highways that intersect.
+When the platoons are near the highway intersection, two of the vehicles in the four-vehicle platoon changes highways and joins the other platoon.
 
-\begin{figure} \label{fig:ch}
+The $t=8.2$ shows the two platoons of vehicles traveling on the two air highways.
+One platoon has three vehicles, and the other has four vehicles.
+At $t=12.3$, the yellow vehicle begins steering off its original highway in order to join the other platoon.
+In terms of the hybrid systems modes, the yellow vehicle transitions from the Leader mode to the Follower mode.
+At the same time, the green vehicle transitions from the Follower mode to the Leader mode, since the previous platoon leader, the yellow vehicle, has left the platoon.
+By $t=16.9$, the yellow vehicle successfully changes highways and is now a follower in its new platoon.
+
+At $t=16.9$, the dark red vehicle is in the process of changing highways.
+In this case, it remains in the Follower mode, since it is a follower in both its old and new platoons.
+While the dark red vehicle changes highways, the orange vehicle moves forward to catch up to its new platoon leader, the green vehicle.
+By $t=23$, all the vehicles have finishes performing their desired maneuvers, resulting in a two-vehicle platoon and a five-vehicle platoon traveling on their respective highways.
+
+\begin{figure}
     \centering
@@
         \includegraphics[width=\textwidth]{fig/ch_83}
-        \caption{83}
+        \caption{A three-vehicle platoon and a four-vehicle platoon are traveling on their respective air highways.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/ch_124}
-        \caption{124}
+        \caption{As the four-vehicle platoon nears the intersection, the yellow vehicle steers off its old highway to join the new platoon. The green vehicle becomes the old platoon's new leader.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/ch_170}
-        \caption{170}
+        \caption{The dark red vehicle also changes highways to join a new platoon, while the orange vehicle catches up to the new platoon leader to maintain a proper formation.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/ch_231}
-        \caption{231}
+        \caption{New platoons now travel on their respective air highways.}
     \end{subfigure}   
-    \caption{change highways}    
+    \caption{A simulation showing two vehicles changing highways and joining a new platoon. \label{fig:ch}}
 \end{figure}

### 2016-02-25 code/platoon/multiagent_convex_experiments/checkCases.m
Added function to check all coefficient matrices for MIP approach

@@ -1,0 +1,102 @@
+function checkCases(Cs)
+
+if isempty(Cs)
+  return
+end
+
+if ~iscell(Cs)
+  error('Input must be a cell structure of square matrices!')
+end
+
+numVehicles = size(Cs{1}, 1);
+U = createFeasibleSet(numVehicles);
+
+for i = 1:length(Cs)
+  disp(['===== Case ' num2str(i) ' ====='])
+
+  if size(Cs{i},1) ~= size(Cs{i},2)
+    error(['The ' num2str(i) 'th cost coefficient matrix is not square!'])
+  end
+  
+  if size(Cs{i},1) ~= size(Cs{i},2)
+    error(['The ' num2str(i) 'th cost coefficient matrix has vehicles!'])
+  end
+  
+  disp(Cs{i})
+  [Uopt, Vopt, Iopt] = getOptSoln(Cs{i}, U);
+  for j = 1:length(Uopt)
+    disp('Uopt = ')
+    disp(Uopt{j});
+  end
+end
+
+end
+
+function [Uopt, Vopt, Iopt] = getOptSoln(C, U)
+V = zeros(size(U));
+for i = 1:length(U)
+  V(i) = objVal(C, U{i});
+end
+
+Iopt = find(V==max(V));
+Vopt = V(Iopt);
+Uopt = U(Iopt);
+end
+
+function val = objVal(C, U)
+val = C.*U;
+val = sum(val(:));
+end
+
+function U = createFeasibleSet(numVehicles)
+
+if numVehicles == 2
+  inds = {[1 2]; [2 1]};
+elseif numVehicles == 3
+  inds = {[1 2]; [1 3]; [2 1]; [2 3]; [3 1]; [3 2]};
+else
+  error('Only 2 or 3 vehicles is allowed!')
+end
+
+
+% Count up all possibilities as a binary in string form
+Ustr = cell(2^length(inds),1);
+for k = 1:2^length(inds)
+  Ustr{k} = dec2bin(k-1);
+  
+  while length(Ustr{k}) < length(inds)
+    Ustr{k} = ['0' Ustr{k}];
+  end
+end
+
+% Convert the strings to a control matrix
+U = cell(2^length(inds),1);
+for k = 1:length(Ustr)
+  for j = 1:length(Ustr{k})
+    U{k}(inds{j}(1), inds{j}(2)) = str2double(Ustr{k}(j));
+  end
+end
+
[…]

### 2016-02-25 code/platoon/multiagent_convex_experiments/min_sij_approach.m

@@ -1,0 +1,65 @@
+function min_sij_approach()
+numVehicles = 3;
+
+% 1 has lower safety value
+C = -ones(numVehicles);
+C(1,2) = 2;
+C(2,1) = 1;
+Cs = {C};
+
+% Three agents in conflict
+% Case 12, 23
+C = -ones(numVehicles);
+C(1,2) = 2;
+C(2,1) = 1;
+
+C(2,3) = 2;
+C(3,2) = 1;
+Cs = [Cs; C];
+
+% Case 12, 32
+C = -ones(numVehicles);
+C(1,2) = 2;
+C(2,1) = 1;
+
+C(3,2) = 2;
+C(2,3) = 1;
+Cs = [Cs; C];
+
+
+% Case 12, 13
+C = -ones(numVehicles);
+C(1,2) = 2;
+C(2,1) = 1;
+
+C(1,3) = 2;
+C(3,1) = 1;
+Cs = [Cs; C];
+
+% Case 12, 23, 31
+C = -ones(numVehicles);
+C(1,2) = 2;
+C(2,1) = 1;
+
+C(2,3) = 2;
+C(3,2) = 1;
+
+C(3,1) = 2;
+C(1,3) = 1;
+Cs = [Cs; C];
+
+% Case 12, 23, 13
+C = -ones(numVehicles);
+C(1,2) = 2;
+C(2,1) = 1;
+
+C(2,3) = 1;
+C(3,2) = 2;
+
+C(1,3) = 2;
+C(3,1) = 1;
+Cs = [Cs; C];
+
+%% Test all cases
+checkCases(Cs);
+end

### 2016-02-25 code/platoon/multiagent_convex_experiments/proof.m

@@ -1,173 +1,0 @@
-function proof()
-
-
-
-%% Two agents in conflict only
-numVehicles = 2;
-U = createFeasibleSet(numVehicles);
-
-% 1 has lower safety value
-disp('Case 12')
-C = -ones(numVehicles);
-C(1,2) = 2;
-C(2,1) = 1;
-
-[Uopt, Vopt, Iopt] = getOptSoln(C, U);
-for i = 1:length(Uopt)
-  disp('Uopt = ')
-  disp(Uopt{i});
-end
-
-%% Three agents in conflict
-numVehicles = 3;
-U = createFeasibleSet(numVehicles);
-
-% Case 12, 23
-disp('Case 12, 23')
-C = -ones(numVehicles);
-C(1,2) = 2;
-C(2,1) = 1;
-
-C(2,3) = 2;
-C(3,2) = 1;
-[Uopt, Vopt, Iopt] = getOptSoln(C, U);
-for i = 1:length(Uopt)
-  disp('Uopt = ')
-  disp(Uopt{i});
-end
-
-% Case 12, 32
-disp('Case 12, 32')
-C = -ones(numVehicles);
-C(1,2) = 2;
-C(2,1) = 1;
-
-C(3,2) = 2;
-C(2,3) = 1;
-
-[Uopt, Vopt, Iopt] = getOptSoln(C, U);
-for i = 1:length(Uopt)
-  disp('Uopt = ')
-  disp(Uopt{i});
-end
-
-% Case 12, 13
-disp('Case 12, 13')
-C = -ones(numVehicles);
-C(1,2) = 2+0.1;
-C(2,1) = 1+0.2;
-
-C(1,3) = 2+0.1;
-C(3,1) = 1+0.3;
-
-[Uopt, Vopt, Iopt] = getOptSoln(C, U);
-for i = 1:length(Uopt)
-  disp('Uopt = ')
-  disp(Uopt{i});
-end
-
-% Case 12, 23, 31
-disp('Case 12, 23, 31')
-C = -ones(numVehicles);
-C(1,2) = 2;
-C(2,1) = 1;
-
-C(2,3) = 2;
-C(3,2) = 1;
-
-C(3,1) = 2;
-C(1,3) = 1;
-
-[Uopt, Vopt, Iopt] = getOptSoln(C, U);
-for i = 1:length(Uopt)
-  disp('Uopt = ')
-  disp(Uopt{i});
-end
-
[…]

### 2016-02-25 docs/CDC 2016 multi-agent/introduction.tex
Renamed MIP paper folder

% !TEX root = MIP.tex
\section{Introduction}
- motivation
-- UAVs for civil purposes
-- difficult problem

- previous methods for dealing with multi-agent systems
-- references
-- limitations (especially with respect to HJ formulation)
--- linear/simple dynamics
--- non-cooperative settings
--- applications that don't directly address the problem

- HJ background
-- references
-- normal limitations

- HJ for multi-UAV systems
-- assumed structure (platooning, SPP)

- summary

### 2016-02-26 docs/AIAA 2016/arXiv_v1/plat_safety.tex
Updated AIAA 2016 paper and added arXiv version 1

--- 2016-02-17 docs/AIAA 2016/plat_safety.tex
@@
 \subsection{Safety Analysis}
-Under normal operations in a single platoon, each follower vehicle $\veh{i},i=P_2,\ldots,P_{N-1}$ in a platoon checks whether it is in the safety reachable set with respect to $\veh{P_{i-1}}$ and $\veh{P_{i+1}}$.
+Under normal operations in a single platoon, each follower vehicle $\veh{i},i=P_2,\ldots,P_{M-1}$ in a platoon checks whether it is in the safety reachable set with respect to $\veh{P_{i-1}}$ and $\veh{P_{i+1}}$.
 So $\vehSCS{i} = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$.
-Assuming there are no nearby vehicle outside of the platoon, the platoon leader $\veh{P_1}$ checks safety against $\veh{P_2}$, and the platoon trailer $Q_{P_N}$ checks safety against $Q_{P_{N-1}}$.
-So $\vehSCS{P_1}=\{P_2\}, \mathcal{Q}(P_N)=\{P_{N-1}\}$.
+Assuming there are no nearby vehicles outside of the platoon, the platoon leader $\veh{P_1}$ checks safety against $\veh{P_2}$, and the platoon trailer $Q_{P_N}$ checks safety against $Q_{P_{N-1}}$.
+So $\vehSCS{P_1}=\{P_2\}, \vehSCS{P_N}=\{P_{N-1}\}$.
 When all vehicles are using liveness controllers to perform their allowed maneuvers, no pair of vehicles should be in an unsafe configuration if the liveness controllers are well-designed.
-However, occasionally a vehicles $\veh{k}$ may behave unexpectedly due to faults or malfunctions, in which case it may come into an unsafe configuration with another vehicles.
+However, occasionally a vehicle $\veh{k}$ may behave unexpectedly due to faults or malfunctions, in which case it may come into an unsafe configuration with another vehicle.
 
@@
 
-In the event that multiple safety breaches occur for some of the vehicles due to a malfunctioning vehicle within the platoon or an intruding vehicles outside of the platoon, those vehicles with more than one safety breach still have the option of exiting the highway altitude range in order to avoid collisions.
+In the event that multiple safety breaches occur for some of the vehicles due to a malfunctioning vehicle within the platoon or intruding vehicles outside of the platoon, those vehicles with more than one safety breach still have the option of exiting the highway altitude range in order to avoid collisions.
 Every extra altitude range reduces the number of simultaneous safety breaches by $1$, so $K$ simultaneous safety breaches can be resolved using $K-1$ different altitude ranges.
@@
 In this paper, we have only proposed the simplest reachability-based collision avoidance scheme.
-Existing collision avoidance algorithms such as \cite{SPPPaper} and \cite{MIPPaper} have the potential to provide safety guarantees for many vehicles in order to resolve multiple safety breaches at once.
+Existing collision avoidance algorithms such as \cite{Bansal16} and \cite{Chen16} have the potential to provide safety guarantees for many vehicles in order to resolve multiple safety breaches at once.
 Coupling the platooning concept with the more advanced collision avoidance methods that provide guarantees for a larger number of vehicles would reduce the risks of multiple safety breaches.

### 2016-02-29 docs/CDC 2016 multi-agent/introduction.tex
Updated AIAA 2016 paper and added arXiv version 1
Updated MIP paper introduction

@@
 - motivation
--- UAVs for civil purposes
+-- UAVs for civil purposes \cite{Tice91, Debusk10, FAA13, AUVSI16, Amazon16, BBC16, NASA16}. For example, package delivery, aerial surveillance, disaster response, ...
 -- difficult problem
@@
 - previous methods for dealing with multi-agent systems
--- references
 -- limitations (especially with respect to HJ formulation)
---- linear/simple dynamics
---- non-cooperative settings
---- applications that don't directly address the problem
+
+In \cite{Tanimoto78}, the author discuss a class of three-player differential game in which two of the players oppose the third player in order to neutralize the third player's attempts to alter their joint cost function.
+
+\cite{Lin13} considers multiple agent games in which communication follows a graphical structure.
+
+In \cite{Su14}, the authors propose a control law derived from a differential game that models the protection of a target from a homing missile.
+
+Most recently, \cite{Fisac15} uses time-dependent Hamilton-Jacobi reachability analysis to approximate the solution to a pursuit-evasion game in which a third player, the defender, attempts to capture the pursuer.
+
+However, all of the above makes assumptions such as linear dynamics and the assumption of agent roles, and describes non-cooperative situations, making them insufficient for addressing the multi-vehicle collision avoidance problem
 
@@
 -- references
+-- theory \cite{Mitchell05}
+-- success in applications \cite{Ding08, Chen14}
 -- normal limitations
@@
 - HJ for multi-UAV systems
+-- \cite{Chen15, Chen15b, Chen16}
 -- assumed structure (platooning, SPP)

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/high_sim.tex
no message

--- 2016-02-17 docs/AIAA 2016/high_sim.tex
@@
 
-This assumption assigns costs in descending order to the categories ``region around airports'', ``cities'', ``water'', and ``other''.
+This assumption assigns costs in descending order to the categories ``region around airports'', ``cities'', ``other'', and ``water''.
 Flying a UAV in each category is more costly by a factor of $b$ compared to the next most important category.
@@
 Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function.
-The region enclosed by the black boundary represent ``regoin around airports'', which have the highest cost.
+The region enclosed by the black boundary represent ``region around airports'', which have the highest cost.
 The dark blue, yellow, and light blue regions represent the ``cities'', the ``water'', and the ``other''' categories, respectively.

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/introduction.tex
no message

--- 2016-02-17 docs/AIAA 2016/introduction.tex
@@
 However, many details of such a concept need to be addressed.
-Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be daunting task.
+Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be a daunting task.
 To address this, in the first part of this paper, we propose a flexible and computationally efficient way based on \cite{Sethian96} to perform optimal air highway replacement given an arbitrary cost map that captures the desirability of having UAVs fly over any geographical location.

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_form.tex
no message

--- 2016-02-17 docs/AIAA 2016/plat_form.tex
@@
 The techniques we present in this paper do not depend on the dynamics of the vehicles.
-However, for concreteness, we consider assume that the UAVs are quadrotors that fly at a constant altitude under non-faulty circumstances.
+However, for concreteness, we assume that the UAVs are quadrotors that fly at a constant altitude under non-faulty circumstances.
 For the quadrotor, we use a simple model in which the $x$ and $y$ dynamics are double integrators:
@@
 \subsubsection{Vehicles as Hybrid Systems}
-We model each vehicle as a hybrid system \cite{Lygeros98,Lygeros12} consisting of the modes "Free", "Leader", "Follower", and "Faulty".
+We model each vehicle as a hybrid system \cite{Lygeros98,Lygeros12} consisting of the modes ``Free", ``Leader", ``Follower", and ``Faulty".
 Within each mode, a set of maneuvers is available to allow the vehicle to change modes if desired.
@@
 
-A Follower vehicle is a vehicle that is following a platoon leader. The Available maneuvers and mode transitions are
+A Follower vehicle is a vehicle that is following a platoon leader. The available maneuvers and mode transitions are
 
 \begin{itemize}
-\item remain a Follower by staying a distance of $b$ behind the vehicle in front in the current platoon,
+\item remain a Follower by staying a distance of $d_\text{sep}$ behind the vehicle in front in the current platoon,
 \item become a Leader by splitting from the current platoon, and
@@
 
-If a vehicle from any of the other modes malfunction, it transitions into the Faulty mode and descends after some pre-specified duration $t_\text{faulty}$.
+If a vehicle from any of the other modes malfunctions, it transitions into the Faulty mode and descends after some pre-specified duration $t_\text{faulty}$.
 \end{itemize}
@@
 For convenience, let $\vehSCS{i}$ denote the set of indices of vehicles with respect to which $Q_i$ checks safety against.
-If vehicle $\veh{i}$ is in a free vehicle, then it must check for safety with respect to all other vehicles, $\vehSCS{i} = \{j: j\neq i\}$.
+If vehicle $\veh{i}$ is a free vehicle, then it must check for safety with respect to all other vehicles, $\vehSCS{i} = \{j: j\neq i\}$.
 If the vehicle is part of a platoon, then it checks safety with respect to the platoon member in front and behind, $\vehSCS{i} = \{P_{j+1}, P_{j-1}\}$.
@@
 \item leave a platoon to create a new one,
-\item reacting to a malfunctioning or intruder vehicles.
+\item reacting to malfunctioning or intruder vehicles.
 \end{itemize}

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_reach.tex
no message

--- 2016-01-20 docs/AIAA 2016/plat_reach.tex
@@
 
-For our application, we will use a several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real time 4D reachable set computations and tractable 6D reachable set computations.
+For our application, we will use several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real time 4D reachable set computations and tractable 6D reachable set computations.
 
@@
 
-\begin{equation}
+\begin{equation} \label{eq:rel_dyn}
 \begin{aligned}

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_sim.tex
no message

--- 2016-02-17 docs/AIAA 2016/plat_sim.tex
@@
 We first consider the scenario in which Free vehicles merge onto an initially unoccupied highway.
-In order to do this, each vehicle first checks for safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:reach_ctrl}\ref{sec:collision_ctrl}.
-Otherwise, the vehicle uses the liveness controller for getting to an absolute target set described in Section \ref{sec:reach_ctrl}\ref{sec:abs_target_ctrl} in order to merge onto the highway, create a platoon, and become a Leader vehicle if there are no platoons on the highway.
-If there is already a platoon on the highway, then the vehicle would use the liveness controller for getting to a target set relative to the platoon leader as described in Section \ref{sec:reach_ctrl}\ref{sec:rel_target_ctrl} to join the platoon and become a Follower.
+In order to do this, each vehicle first checks for safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:collision_ctrl}.
+Otherwise, the vehicle uses the liveness controller for getting to an absolute target set described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl} in order to merge onto the highway, create a platoon, and become a Leader vehicle if there are no platoons on the highway.
+If there is already a platoon on the highway, then the vehicle would use the liveness controller for getting to a target set relative to the platoon leader as described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl} to join the platoon and become a Follower.
 
@@
 For $\veh{1}$ (red), an arbitrary point of entry on the highway is chosen as the target absolute position, and the velocity corresponding to a speed of $10$ in the direction of the highway is chosen as the target absolute velocity.
-This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{sec:reach_ctrl}\ref{sec:abs_target_ctrl}.
+This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl}.
 
@@
 
-After completing merging onto the empty highway, $\veh{1}$ (red) creates a platoon and becomes its leader, while subsequent vehicles begin to form a platoon behind the leader in the order of ascending distance to $\veh{1}$ (red) according to the process described in Section \ref{sec:reach_ctrl}\ref{sec:rel_target_ctrl}.
+After completing merging onto the empty highway, $\veh{1}$ (red) creates a platoon and becomes its leader, while subsequent vehicles begin to form a platoon behind the leader in the order of ascending distance to $\veh{1}$ (red) according to the process described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl}.
 Here, we choose the target relative position $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $b$ behind the last reserved slot in the platoon, and the target relative velocity $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$ with respect to the leader in order to maintain the platoon formation.
@@
 
-The $t=8.2$ shows the two platoons of vehicles traveling on the two air highways.
+The $t=8.2$ plot shows the two platoons of vehicles traveling on the two air highways.
 One platoon has three vehicles, and the other has four vehicles.

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_summary.tex
no message

--- 2016-02-13 docs/AIAA 2016/plat_summary.tex
@@
 We have introduced several reachability-based controllers, as well as some simple controllers.
-Pair wise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:collision_ctrl}.
+Pair-wise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:collision_ctrl}.
 As long as a vehicle is not in potential danger according to the safety reachable sets, it is free to use any other controller.
@@
 
-The controller for getting to an absolute target state, described in Section \ref{sec:abs_target_ctrl}, is used whenever a vehicle needs to move onto a highway to become a platoon leader.
+The controller for getting to an absolute target state, described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl}, is used whenever a vehicle needs to move onto a highway to become a platoon leader.
 This controller guarantees the success of the mode transitions shown in blue in Figure \ref{fig:modeControllers}.
 
-The controller for getting to a relative target state, described in Section \ref{sec:rel_target_ctrl}, is used whenever a vehicle needs to join a platoon to become a follower.
+The controller for getting to a relative target state, described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl}, is used whenever a vehicle needs to join a platoon to become a follower.
 This controller guarantees the success of the mode transitions shown in green in Figure \ref{fig:modeControllers}.
 
-For the simple maneuvers of traveling along a highway or following a platoon, many simple controllers such as the ones suggested in Section \ref{sec:other_ctrl} can be used.
+For the simple maneuvers of traveling along a highway or following a platoon, many simple controllers such as the ones suggested in Section \ref{sec:platooning}-\ref{sec:other_ctrl} can be used.
 These controllers keep the vehicles in either the Leader or the Follower mode.

### 2016-03-03 docs/AIAA 2016 highway platooning/high_waypoints.tex
no message

--- 2016-02-17 docs/AIAA 2016/high_waypoints.tex
@@
 Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexed by the corresponding path index $i$.
-The
 
@@
 To sparsify the continuous set of points on each path, we start at the destination point and note the path's heading.
-We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process is repeated along the entire path.
+We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process along the entire path.
 
@@
 
-To the collection of points resulting from the above process generates we add the origin and destination points to the collection.
-Repeating the entire process for every path, we waypoints for all the cost-minimizing paths under consideration.
+To the collection of points resulting from the above process, we add the origin and destination points.
+Repeating the entire process for every path, we obtain waypoints for all the cost-minimizing paths under consideration.
 Figure \ref{fig:hw_ill} summarizes the entire air highway placement process.

### 2016-03-03 docs/AIAA 2016 highway platooning/main.tex
no message

--- 2016-02-17 docs/AIAA 2016/main.tex
@@
 Within the platoons that travel on the air highways, we model each vehicle as a hybrid system with modes corresponding to its role in the platoon.
-Using HJ reachability, we propose several liveness controllers and a safety controller that guarantees the success and safety of all mode transitions.
+Using Hamilton-Jacobi reachability, we propose several liveness controllers and a safety controller that guarantee the success and safety of all mode transitions.
 For a single altitude range, our approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.
@@
 $\veh{i}$ &=& $i$th vehicle \\
-$\vehSCS{i}$ &=& Set of vehicles to consider for safety for vehicle $i$
+$\vehSCS{i}$ &=& Set of vehicles for vehicle $i$ to consider for safety 
 \end{tabular} \\

### 2016-03-03 docs/AIAA 2016 highway platooning/plat_controllers.tex
no message

--- 2016-02-17 docs/AIAA 2016/plat_controllers.tex
@@
 
-In both of the above cases, we use the dynamics of a single vehicle specified in \ref{eq:dyn}.
+In both of the above cases, we use the dynamics of a single vehicle specified in \eqref{eq:dyn}.
 The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)$ that corresponds to the speed and direction of travel specified by the highway.
@@
 \mathcal{L}_H = \{x: |\pos_x-\Pos_x|\le r_{\pos_x}, |v_x-\Vel_x|\le r_{\vel_x}, \\
-|\pos_y - \Pos_y| \le r_{\pos_y}, |v_y - \Vel_y|\le r_{v\vel_y} \}.
+|\pos_y - \Pos_y| \le r_{\pos_y}, |v_y - \Vel_y|\le r_{\vel_y} \}.
 \end{aligned}
@@
 Here, we represent the target set $\mathcal{L}_H$ as the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE that we need to solve.
-Once the HJB PDE is solved, we obtain the reachable set from the subzero level set of the solution $V_H(t,x)$: $\mathcal V_H(t)$.
+Once the HJB PDE is solved, we obtain the reachable set $\mathcal V_H(t)$ from the subzero level set of the solution $V_H(t,x)$.
 More concretely, $\mathcal{V}_H(T) = \{x: V_H(-T,x)\le 0\}$ is the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.
@@
 
-To construct a controller for getting to a state relative to another vehicle, we use the relative dynamics of two vehicles, given in \ref{eq:rel_dyn}.
-In general, the target state is specified to be some position $(\Pos_{x,r}, \Pos_{y,r}$ and velocity $(\Vel_{x,r}, \Vel_{y,r})$ relative to a reference vehicle.
+To construct a controller for getting to a state relative to another vehicle, we use the relative dynamics of two vehicles, given in \eqref{eq:rel_dyn}.
+In general, the target state is specified to be some position $(\Pos_{x,r}, \Pos_{y,r})$ and velocity $(\Vel_{x,r}, \Vel_{y,r})$ relative to a reference vehicle.
 In the case of a vehicle joining a platoon that maintains a single file, the reference vehicle would be the platoon leader, the desired relative position would be a certain distance behind the leader, depending on how many other vehicles are already in the platoon, and the desired relative velocity would be $(0,0)$ so that the formation can be kept.
 
-For the reachability problem, we define the target set to be a small range of states around the target state $x_P = (\Pos_{x,r}, \Pos_{y,r}, \Vel_{x,r}, \Vel_{y,r}$:
+For the reachability problem, we define the target set to be a small range of states around the target state $x_P = (\Pos_{x,r}, \Pos_{y,r}, \Vel_{x,r}, \Vel_{y,r})$:
 
@@
 
-$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against. We discuss $\mathcal{Q}(i)$ in Section \ref{subsec:safety_guarantees}.
-
+$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against.
 \item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:

### 2016-03-03 docs/CDC 2015 platooning/arXiv/conclusion.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/conclusion.tex
@@
 We considered single-file platoons of UAVs modeled by hybrid systems traveling along air highways.
-Using HJ reachability, we proposed liveness controllers and wrapped a safety controller around them to ensure no collision can occur from a single safety breach.
+Using HJ reachability, we proposed liveness controllers for merging onto highways and merging into existing platoons, and wrapped a safety controller around liveness controllers to ensure no collision between the UAVs can occur.
+Under the assumption that faulty vehicles can descend after a pre-specified duration, our safety controller guarantees that no collisions will occur in a single altitude level as long as at most one safety breach occurs for each vehicle in the platoon.
 Additional safety breaches can be handled by multiple altitude ranges in the airspace.
 Our simulations show that by putting vehicles into single-file platoons, the likelihood of having multiple safety breaches is low, and conflicts involving a single malfunctioning UAV or intruder can be resolved in a single altitude level.
+
+Immediate future work includes exploring different vehicle models, investigating algorithms for resolving multiple safety breaches within the same altitude, and more broadly related problems such as airspace structure and air highway placement.

### 2016-03-03 docs/CDC 2015 platooning/arXiv/formulation.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/formulation.tex
@@
 The structure imposed by the platoon enables us to analyze the liveness and safety of the quadrotors in a tractable manner.
-
-\subsection{Relative Dynamics and Augmented Relative Dynamics}
-Besides Equation \eqref{eq:dyn}, we will also consider the relative dynamics between two quadrotors $Q_i,Q_j$. These dynamics can be obtained by defining the relative variables
-
-\begin{equation} \label{eq:rel_var}
-\begin{aligned}
-p_{x,r} &= p_{x,i} - p_{x,j}, \qquad p_{y,r} = p_{y,i} - p_{y,j}\\
-v_{x,r} &= v_{x,i} - v_{x,j}, \qquad v_{y,r} = v_{y,i} - v_{y,j}
-\end{aligned}
-\end{equation}
-
-We treat $Q_i$ as Player 1, the evader who wishes to avoid collision, and we treat $Q_j$ as Player 2, the pursuer, or disturbance, that wishes to cause a collision.
-In terms of the relative variables given in \eqref{eq:rel_var}, we have
-
-\begin{equation}
-\begin{aligned}
-\dot{p}_{x,r}& = v_{x,r}, &\dot{p}_{y,r} &= v_{y,r} \\
-\dot{v}_{x,r}& = u_{x,i} - u_{x,j}, &\dot{v}_{y,r} &= u_{y,i} - u_{y,j}\\
-\end{aligned}
-\end{equation}
-
-We also augment \eqref{eq:rel_var} with the velocity of $Q_i$ to impose a velocity limit when performing the avoidance maneuver.
-
-\begin{equation} \label{eq:rel_dyn_aug}
-\begin{aligned}
-\dot{p}_{x,r} &= v_{x,r}, &\dot{p}_{y,r} &= v_{y,r} \\
-\dot{v}_{x,r} &= u_{x,i} - u_{x,j}, &\dot{v}_{y,r}&= u_{y,i} - u_{y,j}\\
-\dot{v}_{x,i} &= u_{x,i}, &\dot{v}_{y,i} &= u_{y,i} \\
-\end{aligned}
-\end{equation}
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/vehicleModes"}
+	\includegraphics[width=0.45\textwidth]{"vehicleModes"}
 	\caption{Hybrid modes for vehicles in platoons.}

### 2016-03-03 docs/CDC 2015 platooning/arXiv/results.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/results.tex
@@
 	\centering
-	\includegraphics[width=0.35\textwidth]{"fig/normal2"}
+	\includegraphics[width=0.4\textwidth]{"normal2"}
 	\caption{Reachable sets used to merge onto a highway to form a platoon (top subplots) and to join a platoon on the highway (bottom subplots).}
@@
 	\centering
-	\includegraphics[width=0.35\textwidth]{"fig/normal5"}
-	\caption{Five quadrotors merging onto a highway.}
+	\includegraphics[width=0.4\textwidth]{"normal5"}
+	\caption{Five quadrotors merging onto a highway.
+The first quadrotor forms a platoon on the highway and becomes the platoon leader; the rest of the quadrotors join the platoon behind the first quadrotor.}
 	\label{fig:normal5}
@@
 \subsection{Malfunctioning Vehicle in Platoon}
-We now consider a scenario where a quadrotor in a platoon of five malfunctions while the platoon is traveling along a highway.
-To best demonstrate the behavior of the other quadrotors in the platoon, this simulation assumes that $Q_{P_3}$, the middle quadrotor, malfunctions and reverses direction.
-When this happens, all of the other quadrotors in the platoon begin checking safety against it.
+We now consider a scenario where a quadrotor in a platoon of five malfunctions while the platoon is traveling along a highway specified by the line $p_y = 0.5p_x$.
+To best demonstrate the behavior of the other quadrotors in the platoon, this simulation assumes that $Q_{P_3}$, the middle quadrotor, malfunctions and reverses direction on the highway.
+When $Q_{P_3}$ becomes faulty, all of the other quadrotors in the platoon begin checking safety against it.
 In addition, $Q_{P_3}$ is removed from the platoon, causing the other quadrotors to treat it as an intruder.
@@
 
-Figure \ref{fig:faulty2} shows the platoon of quadrotors, $Q_i,i = 1,...,5$ with $P_i = i$, traveling along the highway.
+Figure \ref{fig:faulty2} shows the platoon of quadrotors, $Q_i,i = 1,...,5$ with $P_i = i$, traveling along the highway at a nominal velocity.
 At $t=0, Q_3$ malfunctions and begins to track the highway in reverse.
@@
 After avoiding $Q_3$, the trailing quadrotors $Q_4$ and $Q_5$ accelerate to reach their new platoon positions.
-$Q_1$ and $Q_2$ are unaffected by the malfunctioning quadrotor.
+$Q_1$ and $Q_2$ are unaffected by the malfunctioning quadrotor and continue down the highway using the liveness controller.
 
 Figure \ref{fig:faulty2} also shows the safe reachable set of $Q_4$ with respect to $Q_3$ (green dashed line), and the safe reachable set of $Q_5$ with respect to $Q_4$ and $Q_3$ (purple dashed lines).
+Note that since the velocities of $Q_4$ and $Q_5$, which is following $Q_4$, are very similar, so the safe reachable sets of $Q_4,Q_5$ with respect to $Q_3$ are overlapping most of the time.
 
 At $t=1,Q_4$ applies the safe controller to avoid entering the safe reachable set with respect to $Q_3$.
-During $Q_4$'s avoidance maneuver, $Q_5$ simply follows $Q_4$, and does not come across any safety breaches, as shown by the $t=1$ and $t=2.1$ subplots.
-The safety breach ends soon after, and by $t=4.5$, $Q_4$ begins merging back onto the highway, followed by $Q_5$, in order to continue to follow the platoon.
-In this particular case, the safety breach is resolved even without any altitude change.
+During the $Q_4$'s avoidance maneuver, $Q_5$ simply follows $Q_4$, and does not come across any safety breaches, as shown by the $t=1$ and $t=2.1$ subplots.
+The safety breach ends soon after, and by $t=4.5$, $Q_4$ begins merging back onto the highway, followed by $Q_5$, in order to continue to follow the platoon, which is now under normal operation again.
+
+We assumed that the faulty quadrotor would exit the highway's altitude range within a duration of $t_\text{internal}$.
+However, here we allow the quadrotor to remain at the highway altitude throughout the simulation, showing that only a single safety breach resulted from the malfunction, and the safety breach is resolved even without any altitude change.
 
@@
 	\center
-		\includegraphics[width=0.4\textwidth]{fig/faultyRsets}
+		\includegraphics[width=0.4\textwidth]{faultyRsets}
 		\caption{Reachable sets used by trailing quadrotors to avoid colliding with the faulty quadrotor.}
@@
 To avoid collision, each quadrotor checks for safety with respect to the intruder and any quadrotor in front and behind in the platoon.
-If necessary, each quadrotor switches to using the safety controller.
+If necessary, the quadrotor uses the safety controller, otherwise it uses the appropriate liveness controller, depending on whether it is a leader or follower.
 
 Figure \ref{fig:intruder1} shows the simulation result.
-At $t=0$, a platoon of 4 quadrotors, $Q_{P_i},i=1,\ldots,4$ with $P_i = i$, travel along the highway.
-An intruder vehicle $Q_0$ (red disk) starts from position $(40,30)$ and heads toward bottom-left of the grid.
+At $t=0$, a platoon of 4 quadrotors, $Q_{P_i},i=1,\ldots,4$ with $P_i = i$, travels along the highway defined by the line $p_y = p_x$.
+An intruder vehicle $Q_0$ (red disk) starts from position $(p_x, p_y) = (40,30)$ and heads toward bottom-left of the grid.
+As before, platoon members incur a safety breach if $V(-t_\text{internal},x_{P_i}-x_{P_j})\le 0$.
+However, with respect to $Q_0$, platoon members incur a safety breach if $V(-t_\text{external}, x_{P_i}-x_0) \le 0$ with $t_\text{external}>t_\text{internal}$.
 
-The platoon leader $Q_{P_1}$'s (black disk) safety is unaffected by the intruder.
+The platoon leader $Q_{P_1}$'s (black disk) safety is unaffected by the intruder, thus it simply follows its original path on the highway using the liveness controller described in Section \ref{sec:travel_hwy}.
 Followers $Q_{P_2}$ (blue disk), $Q_{P_3}$ (green disk) and $Q_{P_4}$ (pink disk), on the other hand, must use the safety controller in order to avoid collision with the intruder ($t=3.3,6.2$).
 This causes their paths to deviate off the highway.
-Once each quadrotor is safe relative to the intruder, they rejoin the original platoon ($t=12.4$).
+Once each quadrotor is safe relative to the intruder, they merge back onto the highway, join the original platoon and continue traveling along it ($t=12.4$).
+
 Figure \ref{fig:intruder2} illustrates the use of safety reachable sets in this scenario using only $Q_{P_2}$ as an example.
-The safety reachable sets of $Q_{P_2}$ with respect to the intruder $Q_0$, $Q_{P_1}$ and $Q_{P_3}$ (red, black, green dashed lines) are shown.
-%With respect to $Q_0$, $Q_{P_2}$'s safety is considered to be breached if $V_S(-t_\text{external},x_{P_2}-x_0) \le 0$.
+The safety reachable sets of $Q_{P_2}$ with respect to the intruder $Q_0$ (red dashed line), $Q_{P_1}$ (black dashed line) and $Q_{P_3}$ (green dashed line) are shown.
+With respect to $Q_0$, $Q_{P_2}$'s safety is considered to be breached if $V_S(-t_\text{external},x_{P_2}-x_0) \le 0$.
 To avoid possible collision with the intruder, $Q_{P_2}$ must remain outside the safety reachable set with respect to the intruder.
@@
 	\centering
-	\includegraphics[width=0.35\textwidth]{"fig/Intruder1"}
-	\caption{Reaction of a platoon of 4 quadrotors on a highway to an intruder.}
+	\includegraphics[width=0.4\textwidth]{"Intruder1"}
+	\caption{Reaction of a platoon of 4 quadrotors on a highway to an intruder.
+Quadrotors in the platoon avoid collision with the intruder and return to follow their path on the highway once they are safe.}
 	\label{fig:intruder1}
@@
 	\centering
-		\includegraphics[width=0.35\textwidth]{"fig/intruder2"}
+		\includegraphics[width=0.4\textwidth]{"Intruder2"}
 	\caption{Reachable sets used by quadrotor $Q_2$ to avoid collision with respect to the intruder and quadrotors $Q_1$ and $Q_3$ in front and behind it respectively.}

### 2016-03-03 docs/CDC 2015 platooning/arXiv/solution.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/solution.tex
@@
 
+\subsection{Relative Dynamics and Augmented Relative Dynamics}
+Besides Equation \eqref{eq:dyn}, we will also consider the relative dynamics between two quadrotors $Q_i,Q_j$. These dynamics can be obtained by defining the relative variables
+
+\begin{equation} \label{eq:rel_var}
+\begin{aligned}
+p_{x,r} &= p_{x,i} - p_{x,j}, \qquad p_{y,r} = p_{y,i} - p_{y,j}\\
+v_{x,r} &= v_{x,i} - v_{x,j}, \qquad v_{y,r} = v_{y,i} - v_{y,j}
+\end{aligned}
+\end{equation}
+
+We treat $Q_i$ as Player 1, the evader who wishes to avoid collision, and we treat $Q_j$ as Player 2, the pursuer, or disturbance, that wishes to cause a collision.
+In terms of the relative variables given in \eqref{eq:rel_var}, we have
+
+\begin{equation}
+\begin{aligned}
+\dot{p}_{x,r}& = v_{x,r}, &\dot{p}_{y,r} &= v_{y,r} \\
+\dot{v}_{x,r}& = u_{x,i} - u_{x,j}, &\dot{v}_{y,r} &= u_{y,i} - u_{y,j}\\
+\end{aligned}
+\end{equation}
+
+We also augment \eqref{eq:rel_var} with the velocity of $Q_i$, given in \eqref{eq:rel_dyn_aug}, to impose a velocity limit on the quadrotor.
+
+\begin{equation} \label{eq:rel_dyn_aug}
+\begin{aligned}
+\dot{p}_{x,r} &= v_{x,r}, &\dot{p}_{y,r} &= v_{y,r} \\
+\dot{v}_{x,r} &= u_{x,i} - u_{x,j}, &\dot{v}_{y,r}&= u_{y,i} - u_{y,j}\\
+\dot{v}_{x,i} &= u_{x,i}, &\dot{v}_{y,i} &= u_{y,i} \\
+\end{aligned}
+\end{equation}
+
 \section{Liveness Controllers \label{sec:liveness}}
 \subsection{Merging onto a Highway \label{subsec:highway_merge}}
-We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity along the highway.
-Thus, a quadrotor would aim to drive the system \eqref{eq:dyn} to a state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
+We model the merging of a vehicle onto an air highway as a path planning problem, where we specify a target position and velocity whose magnitude (the speed) is given by the highway specification, and whose direction is along the highway.
+Thus, for a quadrotor, the objective would be to drive the system in \eqref{eq:dyn} to a specific state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, or a small range of states defined by the set
 
@@
 \subsection{Other Quadrotor Maneuvers}
+Reachability was used in Sections \ref{subsec:highway_merge} and \ref{subsec:platoon_merge} for the relatively complex maneuvers.
 For the simpler maneuvers of traveling along a highway and following a platoon, we resort to simpler controllers described below.
@@
 \subsection{Platoon Safety Guarantees \label{subsec:safety_guarantees}}
-Under normal operations in a single platoon, each follower quadrotor $Q_{P_i},i>1$ checks whether it is in the safety reachable set with respect to $Q_{P_{i-1}}$ and $Q_{P_{i+1}}$.
+Under normal operations in a single platoon, each follower quadrotor $Q_i,i=P_2,\ldots,P_{N-1}$ in a platoon checks whether it is in the safety reachable set with respect to $Q_{P_{i-1}}$ and $Q_{P_{i+1}}$.
 So $\mathcal{Q}(i) = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$.

### 2016-03-03 docs/CDC 2015 platooning/final version/conclusion.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/conclusion.tex
@@
 We considered single-file platoons of UAVs modeled by hybrid systems traveling along air highways.
-Using HJ reachability, we proposed liveness controllers and wrapped a safety controller around them to ensure no collision can occur from a single safety breach.
+Using HJ reachability, we proposed liveness controllers and built a safety controller around them to ensure no collision can occur from a single safety breach.
 Additional safety breaches can be handled by multiple altitude ranges in the airspace.

### 2016-03-03 docs/CDC 2015 platooning/final version/results.tex
no message

--- 2015-09-12 docs/CDC 2015/final version/results.tex
@@
 When it is within the liveness reachable set boundary at $t=2.8$, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$.
-During the entire time, the $Q_1$ checks whether it may collide with $Q_2$ within a time horizon of $t_\text{external}$; we chose $t_\text{external}=3>t_\text{internal}$.
+During the entire time, $Q_1$ checks whether it may collide with $Q_2$ within a time horizon of $t_\text{external}$; we chose $t_\text{external}=3>t_\text{internal}$.
 
@@
 
-Initially, $Q_{P_2}$ ($P_2=2$) is a follower and is outside all 3 safety reachable sets.
-At time $t=0.6$, $Q_2$ comes to the boundary of the safety set with respect to the intruder and therefore must apply the safety control law to avoid potential future collision.
-Thus it splits the original platoon and becomes the leader of a new platoon consisting of itself, $Q_3$ and $Q_4$.
+Initially, $Q_{P_2}$ ($P_2=2$) is a follower outside all 3 safety reachable sets.
+At $t=0.6$, $Q_2$ comes to the boundary of the safety set with respect to the intruder and must apply the safety control law to avoid potential future collision.
+Thus it splits from the original platoon and becomes the leader of a new platoon consisting of itself, $Q_3$ and $Q_4$.
 $Q_2$ keeps using the safety controller until it is safe with respect to the intruder again at $t=3$.
-After $t=3$, $Q_2$ is safe to use the liveness controller again to merge back onto the highway and join the original platoon as a follower.
+After $t=3$, $Q_2$ is safe to use the liveness controller again to merge back onto the highway and join the original platoon.
 Note that during the entire time, $Q_2$ maintains safety against the intruder, $Q_1$ and $Q_3$ by always staying outside of all three safety reachable sets.

### 2016-03-03 docs/CDC 2015 platooning/initial version/introduction.tex
no message

--- 2016-02-13 docs/AIAA 2016/introduction.tex
@@
-% !TEX root = main.tex
+% !TEX root = platooning.tex
 \section{Introduction}
@@
 Recently, however, there has been an immense surge of interest in using UAVs for civil applications.
-Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commerical packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue.
-In the future, the applications of UAVs are only limited by human imagination.
+Through projects such as Amazon Prime Air and Google Project Wing, companies are looking to send UAVs into the airspace to deliver packages \cite{PrimeAir,ProjectWing}.
+As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone.
+This would equate to thousands of vehicles simultaneously in the air.
+As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) of the United States are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13}.
+Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to firefight in areas that are difficult to reach but require prompt response \cite{Debusk10}.
 
-As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone.
-This would equate to thousands of vehicles simultaneously in the air just from package delivery services.
-Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to firefight in areas that are difficult to reach but require prompt response \cite{Debusk10}.
-As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13, NASA16}.
-
-Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving a small number of vehicles \cite{Fisac15,Chen14,Ding08}.
+Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving a small number of vehicles \cite{Fisac15,Chen14,Ding08}.
 These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
@@
 This makes the computation intractable for large numbers of vehicles.
-
-In order to accommodate potentially thousands of vehicles simultaneously flying in the air, additional structure is needed to allow for tractable analysis and intuitive monitoring.
-An air highway system on which platoons of vehicles travel accomplishes both goals.
-However, many details of such a concept need to be addressed.
-Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be daunting task.
-To address this, in the first part of this paper, we propose a flexible and computationally efficient way to perform optimal air highway replacement given an arbitrary cost map that can capture the desirability of having UAVs fly over any geographical location.
-We demonstrate our method using the San Francisco Bay Area as an example.
-Once air highways are in place, platoons of UAVs can then fly in fixed formations along the highway to get from origin to destination.
 
@@
 Previous analysis of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
-In the second part of this paper, we propose organizing UAVs into platoons, which provide structure that allows pairwise safety guarantees from HJ reachability to translate to safety guarantees for the whole platoon.
-With respect to platooning, we first propose a hybrid systems model of UAVs in platoons to establish the modes of operation needed for our platooning concept.
-Then, we show how reachability-based controllers can be synthesized to enable vehicles successfully perform mode switching, as well as prevent dangerous configurations such as collisions.
-Finally, we show several simulations to illustrate the behavior of vehicles in various scenarios and demonstrate the guarantees provided by HJ reachability.
+%In the context of HJ reachability, putting vehicles into platoons is desirable because of the additional structure that platoons impose on its members.
+With additional structure, pairwise safety guarantees of vehicles can be more easily translated into safety guarantees of all the vehicles in the platoon.
+In this paper, we attempt to reconciliate this trade-off by assuming a single-file platoon, which provides structure that allows pairwise safety guarantees from HJ reachability to translate to safety guarantees for the whole platoon.
+We first propose a hybrid systems model of UAVs in platoons to capture this structure.
+Then, we show how HJ reachability can be used to synthesize \textit{liveness controllers} that enable vehicles to reach a set of desired states, and wrap \textit{safety controllers} around the liveness controllers in order to prevent dangerous configurations such as collisions.
+Finally, we show simulation results of quadrotors forming a platoon, a platoon responding to a malfunctioning member, and a platoon responding to an outside intruder to illustrate the behavior of vehicles in these scenarios and demonstrate the guarantees provided by HJ reachability.
+
+%Motivation:
+%\begin{itemize}
+%\item Applications of UAVs, potential numbeurs
+%\item Importance of safety guarantees
+%\item Computation complexity
+%\end{itemize}
+%
+%Related work:
+%\begin{itemize}
+%\item Platooning references: lack of (?) safety guarantees
+%\begin{itemize}\item\textcolor{blue}{Mention PATH papers \& Lygeros thesis}\end{itemize}
+%\item HJI, safety guarantees, limited by dimensionality
+%\end{itemize}
+%
+%Summary of results
+%\begin{itemize}
+%\item Hybrid systems model of vehicles
+%\item Reachability guarantees wrapped around existing methods
+%\item Reachability offers flexibility in terms of design
+%\item Illustrative platoon functions
+%\end{itemize}

### 2016-04-13 docs/AIAA 2016 highway platooning/conclusions.tex
Incorporated Casey's comments to platooning paper

--- 2016-02-17 docs/AIAA 2016/conclusions.tex
@@
 To address the important and urgent problem of the traffic management of UAVs, we proposed to have platoons of UAVs traveling on air highways.
-We showed how such an air space structure leads to a much easier safety and liveless analysis.
+We showed how such an airspace structure leads to a much easier safety and liveless analysis.
 We provided simulations which show that by putting vehicles into platoons, many complex maneuvers can be performed using just a few different reachable sets.
@@
 Our algorithm allows us to take as input any arbitrary cost map representing the desirability of flying over any position in space, and produce a set of paths from any destination to a particular origin.
-Simple heurstic clustering methods can then be used to to convert the sets of paths into a set of air highways.
+Simple heurstic clustering methods can then be used to convert the sets of paths into a set of air highways.
 
 On the air highways, we considered platoons of UAVs modeled by hybrid systems.
-We show how many required platoon functions such as merging onto an air highway and changing platoons can be implemented using only the Free, Leader, and Follower modes of operation.
+We show how various required platoon functions (merging onto an air highway, changing platoons, etc.) can be implemented using only the Free, Leader, and Follower modes of operation.
 Using HJ reachability, we proposed liveness controllers that guarantee the success of all mode transitions, and wrapped a safety controller around liveness controllers to ensure no collision between the UAVs can occur.

### 2016-04-13 docs/AIAA 2016 highway platooning/high_form.tex
Incorporated Casey's comments to platooning paper

--- 2016-02-17 docs/AIAA 2016/high_form.tex
@@
 
-Air highways must not only provide structure to make the analysis of a large number of vehicles tractable, but also allow vehicles reach their destinations while minimizing any relevant costs to the vehicles and to the surrounding regions.
+Air highways must not only provide structure to make the analysis of a large number of vehicles tractable, but also allow vehicles to reach their destinations while minimizing any relevant costs to the vehicles and to the surrounding regions.
 Thus, given a origin-destination pair (eg.
@@
 	\centering
-	\includegraphics[width=0.35\textwidth]{"fig/highway_illustration"}
+	\includegraphics[width=0.5\textwidth]{"fig/highway_illustration"}
 	\caption{Highway illustration}

### 2016-04-13 docs/AIAA 2016 highway platooning/high_sim.tex
Incorporated Casey's comments to platooning paper

--- 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/high_sim.tex
@@
 \subsection{Results}
-To illustrate our air highway placement proposal, we used the San Francisco Bay Area as an example, and classified each point on the map into four different regions: region around airports, highly populated cities, water, and other.
+To illustrate our air highway placement proposal, we used the San Francisco Bay Area as an example, and classified each point on the map into four different regions: ``regions around airports'', ``highly populated cities'', ``water'', and ``other''.
 Each region has an associated cost, reflecting the desirability of flying a vehicle over an area in the region.
@@
 
-This assumption assigns costs in descending order to the categories ``region around airports'', ``cities'', ``other'', and ``water''.
+This assumption assigns costs in descending order to the categories ``regions around airports'', ``cities'', ``other'', and ``water''.
 Flying a UAV in each category is more costly by a factor of $b$ compared to the next most important category.

### 2016-04-13 docs/AIAA 2016 highway platooning/introduction.tex
Incorporated Casey's comments to platooning paper

--- 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/introduction.tex
@@
 Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be a daunting task.
-To address this, in the first part of this paper, we propose a flexible and computationally efficient way based on \cite{Sethian96} to perform optimal air highway replacement given an arbitrary cost map that captures the desirability of having UAVs fly over any geographical location.
+To address this, in the first part of this paper, we propose a flexible and computationally efficient way based on \cite{Sethian96} to perform optimal air highway placement given an arbitrary cost map that captures the desirability of having UAVs fly over any geographical location.
 We demonstrate our method using the San Francisco Bay Area as an example.
@@
 
-Previous analysis of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
+Previous analyses of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
 In the second part of this paper, we propose organizing UAVs into platoons, which provide structure that allows pairwise safety guarantees from HJ reachability to translate to safety guarantees for the whole platoon.

### 2016-04-13 docs/AIAA 2016 highway platooning/main.tex
Incorporated Casey's comments to platooning paper

@@
 \abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, aerial surveillance, and disaster response.
-As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the air space, in order to ensure their liveness and safety requirements are met.
+As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met.
 Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers are unrestricted.

### 2016-04-13 docs/AIAA 2016 highway platooning/plat_controllers.tex
Incorporated Casey's comments to platooning paper

@@
 \subsubsection{Getting to a Target State \label{sec:abs_target_ctrl}}
-The controller used by a vehicle to a target state is important in a couple of situations in the platooning context.
+The controller used by a vehicle to reach a target state is important in a couple of situations in the platooning context.
 First, a vehicle in the ``Free'' mode can use the controller to merge onto a highway, forming a platoon and changing modes to a ``Leader'' vehicle.
@@
 In general, the target state is specified to be some position $(\Pos_{x,r}, \Pos_{y,r})$ and velocity $(\Vel_{x,r}, \Vel_{y,r})$ relative to a reference vehicle.
-In the case of a vehicle joining a platoon that maintains a single file, the reference vehicle would be the platoon leader, the desired relative position would be a certain distance behind the leader, depending on how many other vehicles are already in the platoon, and the desired relative velocity would be $(0,0)$ so that the formation can be kept.
+In the case of a vehicle joining a platoon that maintains a single file, the reference vehicle would be the platoon leader, the desired relative position would be a certain distance behind the leader, depending on how many other vehicles are already in the platoon; the desired relative velocity would be $(0,0)$ so that the formation can be kept.
 
@@
 \end{equation}
-for some $k_p,k_v>0$.
-The leader can modify the nominal position of vehicles in the platoon, for example to command the formation to turn.
-In particular, a simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
+for some $k_p,k_v>0$. In particular, a simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
 \begin{equation}\label{eq:nominal_pos}
@@
 \end{equation}
-where $b$ is the spacing between vehicles along the platoon. and $\frac{v_{P_1}}{\|v_{P_1}\|_2}$ is the platoon leader's direction of travel.
+where $b$ is the spacing between vehicles along the platoon and $\frac{v_{P_1}}{\|v_{P_1}\|_2}$ is the platoon leader's direction of travel.

### 2016-04-13 docs/AIAA 2016 highway platooning/plat_form.tex
Incorporated Casey's comments to platooning paper

--- 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_form.tex
@@
 Thus, in our present work, we will consider the situation where UAVs travel on air highways in platoons, defined in the following sections.
-The structure imposed by air highways and the platoon enables us to analyze the liveness and safety of the vehicles in a tractable manner.
+The structure imposed by air highways and platooning enables us to analyze the liveness and safety of the vehicles in a tractable manner.
 
@@
 \begin{itemize}
-\item remain a Free vehicle by staying away from highways,
-\item become a Leader by entering a highway to create a new platoon, and
-\item become a Follower by joining a platoon that is currently on a highway.
+\item remain a Free vehicle by staying away from highways
+\item become a Leader by entering a highway to create a new platoon
+\item become a Follower by joining a platoon that is currently on a highway
 \end{itemize}
@@
 \begin{itemize}
-\item remain a Leader by traveling along the highway at a pre-specified speed,
-\item become a Follower by merging the current platoon with a platoon in front, and
-\item become a Free vehicle by leaving the highway.
+\item remain a Leader by traveling along the highway at a pre-specified speed
+\item become a Follower by merging the current platoon with a platoon in front
+\item become a Free vehicle by leaving the highway
 \end{itemize}
@@
 \begin{itemize}
-\item remain a Follower by staying a distance of $d_\text{sep}$ behind the vehicle in front in the current platoon,
-\item become a Leader by splitting from the current platoon, and
-\item become a Free vehicle by leaving the highway.
+\item remain a Follower by staying a distance of $d_\text{sep}$ behind the vehicle in front in the current platoon
+\item become a Leader by splitting from the current platoon
+\item become a Free vehicle by leaving the highway
 \end{itemize}
@@
 If the vehicle is part of a platoon, then it checks safety with respect to the platoon member in front and behind, $\vehSCS{i} = \{P_{j+1}, P_{j-1}\}$.
-Figure \ref{fig:vehicleNotation} summarizes the the indexing system of the vehicles.
+Figure \ref{fig:vehicleNotation} summarizes the indexing system of the vehicles.
 
@@
 \begin{itemize}
-\item merge onto a highway to form a platoon,
-\item join a new or different platoon,
-\item leave a platoon to create a new one,
-\item reacting to malfunctioning or intruder vehicles.
+\item merge onto a highway to form a platoon
+\item join a new or different platoon
+\item leave a platoon to create a new one
+\item reacting to malfunctioning or intruder vehicles
 \end{itemize}
@@
 \begin{itemize}
-\item following the highway at constant altitude at a specified speed,
-\item maintaining a constant relative position and velocity with the leader of a platoon.
+\item following the highway at constant altitude at a specified speed
+\item maintaining a constant relative position and velocity with the leader of a platoon
 \end{itemize}

### 2016-04-13 docs/AIAA 2016 highway platooning/plat_safety.tex
Incorporated Casey's comments to platooning paper

--- 2016-02-26 docs/AIAA 2016/arXiv_v1/plat_safety.tex
@@
 Existing collision avoidance algorithms such as \cite{Bansal16} and \cite{Chen16} have the potential to provide safety guarantees for many vehicles in order to resolve multiple safety breaches at once.
-Coupling the platooning concept with the more advanced collision avoidance methods that provide guarantees for a larger number of vehicles would reduce the risks of multiple safety breaches.
+Coupling the platooning concept with the more advanced collision avoidance methods that provide guarantees for a larger number of vehicles would reduce the risk of multiple safety breaches.
 

### 2016-04-13 docs/AIAA 2016 highway platooning/plat_sim.tex
Incorporated Casey's comments to platooning paper

--- 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_sim.tex
@@
 
-For $\veh{1}$ (red), an arbitrary point of entry on the highway is chosen as the target absolute position, and the velocity corresponding to a speed of $10$ in the direction of the highway is chosen as the target absolute velocity.
+For $\veh{1}$ (red), an arbitrary point of entry on the highway is chosen as the target absolute position, and the velocity corresponding to a speed of $10$ m/s in the direction of the highway is chosen as the target absolute velocity.
 This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl}.
@@
     \centering
-    \begin{subfigure}{0.23\textwidth} \label{subfig:fp_40}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:fp_40}
         \includegraphics[width=\textwidth]{fig/fp_40}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth} \label{subfig:fp_60}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:fp_60}
         \includegraphics[width=\textwidth]{fig/fp_60}
@@
 
-    \begin{subfigure}{0.23\textwidth} \label{subfig:fp_110}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:fp_110}
         \includegraphics[width=\textwidth]{fig/fp_110}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth} \label{subfig:fp_210}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:fp_210}
         \includegraphics[width=\textwidth]{fig/fp_210}
@@
 
-As the intruder $\veh{5}$ (yellow) continue to disregard other vehicles, the followers of the platoon also get near the respective boundaries of the safety reachable set with respect to the intruder.
+As the intruder $\veh{5}$ (yellow) continues to disregard other vehicles, the followers of the platoon also get near the respective boundaries of the safety reachable set with respect to the intruder.
 This occurs at $t=13.9$, where the platoon ``makes room'' for the intruder to pass by to avoid collisions; all vehicles deviate from their intended path, which is to follow the platoon leader or the highway.
@@
     \centering
-    \begin{subfigure}{0.23\textwidth} \label{subfig:in_100}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:in_100}
         \includegraphics[width=\textwidth]{fig/in_100}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth} \label{subfig:in_120}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:in_120}
         \includegraphics[width=\textwidth]{fig/in_120}
@@
 
-    \begin{subfigure}{0.23\textwidth} \label{subfig:in_140}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:in_140}
         \includegraphics[width=\textwidth]{fig/in_140}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth} \label{subfig:in_200}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:in_200}
         \includegraphics[width=\textwidth]{fig/in_200}
@@
 In this simulation, shown in Figure \ref{fig:ch}, two platoons are traveling on two different highways that intersect.
-When the platoons are near the highway intersection, two of the vehicles in the four-vehicle platoon changes highways and joins the other platoon.
+When the platoons are near the highway intersection, two of the vehicles in the four-vehicle platoon change highways and join the other platoon.
 
@@
 While the dark red vehicle changes highways, the orange vehicle moves forward to catch up to its new platoon leader, the green vehicle.
-By $t=23$, all the vehicles have finishes performing their desired maneuvers, resulting in a two-vehicle platoon and a five-vehicle platoon traveling on their respective highways.
+By $t=23$, all the vehicles have finished performing their desired maneuvers, resulting in a two-vehicle platoon and a five-vehicle platoon traveling on their respective highways.
 
@@
     \centering
-    \begin{subfigure}{0.23\textwidth} \label{subfig:ch_83}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:ch_83}
         \includegraphics[width=\textwidth]{fig/ch_83}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth} \label{subfig:ch_124}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:ch_124}
         \includegraphics[width=\textwidth]{fig/ch_124}
@@
 
-    \begin{subfigure}{0.23\textwidth} \label{subfig:ch_170}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:ch_170}
         \includegraphics[width=\textwidth]{fig/ch_170}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth} \label{subfig:ch_231}
+    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:ch_231}
         \includegraphics[width=\textwidth]{fig/ch_231}

### 2016-04-29 docs/AIAA 2016 highway platooning/high_eikon.tex
Made the "easy" changes to AIAA paper according to Claire's comments

--- 2016-02-17 docs/AIAA 2016/high_eikon.tex
@@
 Let $s_0, s_1\in \mathbb{R}$, and let $\ppath: [s_0, s_1] \rightarrow \mathbb{R}^2$ be a path starting from an origin point $\pos^o = \ppath(s_0)$ and ending at a destination point $\pos^d = \ppath(s_1)$.
-Note that the sequence $\hws_N$ in \eqref{eq:ahpp} is a piece-wise affine example of a path $\ppath(s), s\in[s_0, s_1]$; however, a path $\ppath$ that is not piece-wise affine cannot be written as a sequence of highways $\hws_N$.
+Note that the sequence $\hws_N$ in \eqref{eq:ahpp} is a piecewise affine example of a path $\ppath(s), s\in[s_0, s_1]$; however, a path $\ppath$ that is not piecewise affine cannot be written as a sequence of highways $\hws_N$.
 

### 2016-04-29 docs/AIAA 2016 highway platooning/introduction.tex
Made the "easy" changes to AIAA paper according to Claire's comments

@@
 Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to respond to disasters in areas that are difficult to reach but require prompt response \cite{Debusk10,Tornado16}.
-As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Administration (NASA) are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13, NASA16}.
+As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Space Administration (NASA) are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13, NASA16}.
 
-Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving a small number of vehicles \cite{Fisac15,Chen14,Ding08}.
+Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Ding08}.
 These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
@@
 
-A considerable body of work has been done on the platooning of vehicles \cite{Kavathekar11}.
+A considerable body of work has been done on the platooning of ground vehicles \cite{Kavathekar11}.
 For example, \cite{McMahon90} investigated the feasibility of vehicle platooning in terms of tracking errors in the presence of disturbances, taking into account complex nonlinear dynamics of each vehicle.

### 2016-05-09 docs/AIAA 2016 highway platooning/high_form.tex
Made the "easy" changes to AIAA paper according to Claire's comments
Made some modifications according to Jaime's comments; still need to incorporate the rest of Jaime's comments

@@
 Air highways are intended to be the common pathways for many UAV platoons, whose members may have different origins and destinations.
-By routing platoons of UAVs onto a few common pathways, the air space becomes more tractable to analyze and intuitive to monitor.
-The concept of platoons will be proposed in Section \ref{sec:platooning}; for now, we focus on air highways in this section.
+By routing platoons of UAVs onto a few common pathways, the airspace becomes more tractable to analyze and intuitive to monitor.
+The concept of platoons will be proposed in Section \ref{sec:platooning}; in this section, we focus on air highways.
 
-Let an air highway be denoted by the function $\hw: [0, 1] \rightarrow \mathbb{R}^2$.
+Let an air highway be denoted by the continuous function $\hw: [0, 1] \rightarrow \mathbb{R}^2$.
 Such a highway lies in a horizontal plane of fixed altitude, with start and end points given by $\hw(0)\in\mathbb{R}^2$ and $\hw(1)\in\mathbb{R}^2$ respectively.
@@
 Locations with high cost could, for example, include densely populated areas and areas around airports.
-In general, the cost map $\cmap(\cdot)$ may be used to model cost of interference with commercial air spaces, cost of accidents, cost of noise pollution, etc., and can be designed by government regulation bodies.
+In general, the cost map $\cmap(\cdot)$ may be used to model cost of interference with commercial airspaces, cost of accidents, cost of noise pollution, etc., and can be designed by government regulation bodies.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/highway_illustration"}
+	\includegraphics[width=0.95\textwidth]{"fig/highway_illustration"}
 	\caption{Highway illustration}

### 2016-05-09 docs/AIAA 2016 highway platooning/introduction.tex
Made some modifications according to Jaime's comments; still need to incorporate the rest of Jaime's comments

@@
 Furthermore, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems.
-The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ Partial Differential Equation (PDE) \cite{LSToolbox,Osher02,Sethian96}.
+The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox,Osher02,Sethian96}.
 However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles.
@@
 
-In order to accommodate potentially thousands of vehicles simultaneously flying in the air, additional structure is needed to allow for tractable analysis and intuitive monitoring.
+In order to accommodate potentially thousands of vehicles simultaneously flying in the air, additional structure is needed to allow for tractable analysis and intuitive monitoring by human beings.
 An air highway system on which platoons of vehicles travel accomplishes both goals.
@@
 Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be a daunting task.
-To address this, in the first part of this paper, we propose a flexible and computationally efficient way based on \cite{Sethian96} to perform optimal air highway placement given an arbitrary cost map that captures the desirability of having UAVs fly over any geographical location.
+To address this, in the first part of this paper, we propose a flexible and computationally efficient method based on \cite{Sethian96} to perform optimal air highway placement given an arbitrary cost map that captures the desirability of having UAVs fly over any geographical location.
 We demonstrate our method using the San Francisco Bay Area as an example.

### 2016-05-09 docs/AIAA 2016 highway platooning/main.tex
Made the "easy" changes to AIAA paper according to Claire's comments
Made some modifications according to Jaime's comments; still need to incorporate the rest of Jaime's comments

@@
 As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met.
-Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers are unrestricted.
-In this paper, we propose to have platoons of UAVs flying on air highways in order to impose the air space structure that allows for tractable analysis and intuitive monitoring.
+Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers is unrestricted.
+In this paper, we propose to have platoons of UAVs flying on air highways in order to impose the airspace structure that allows for tractable analysis and intuitive monitoring.
 For the air highway placement problem, we use the flexible and efficient fast marching method to solve the Eikonal equation, which produces a sequence of air highways that minimizes the cost of flying from an origin to any destination.
@@
 \section*{Nomenclature}
-(Nomenclature entries should have the units identified)\\
 \noindent\begin{tabular}{@{}lcl@{}}

### 2016-05-10 docs/AIAA 2016 highway platooning/conclusions.tex
Made minor to medium changes according to Claire and Jaime's comments

@@
 To address the important and urgent problem of the traffic management of UAVs, we proposed to have platoons of UAVs traveling on air highways.
-We showed how such an airspace structure leads to a much easier safety and liveless analysis.
-We provided simulations which show that by putting vehicles into platoons, many complex maneuvers can be performed using just a few different reachable sets.
+We showed how such an airspace structure leads to a much easier safety and liveness analysis.
+We provided simulations which show that by organizing vehicles into platoons, many complex maneuvers can be performed using just a few different reachable sets.
 

### 2016-05-10 docs/AIAA 2016 highway platooning/high_eikon.tex
Made minor to medium changes according to Claire and Jaime's comments

@@
 
-The Eikonal equation \eqref{eq:eikonal} can be efficiently computed numerically using the fast marching method \cite{Sethian96}.
+The Eikonal equation \eqref{eq:eikonal} can be efficiently computed numerically using the fast marching method \cite{Sethian96}; each computation takes on the order of merely a second.
 

### 2016-05-10 docs/AIAA 2016 highway platooning/high_form.tex
Made minor to medium changes according to Claire and Jaime's comments

@@
 \begin{aligned}
-& \min_{\hws_N, N} \sum_{i=1}^N \int_0^1 \cmap(\hw_i(s)) ds \\
+& \min_{\hws_N, N} \left\{\left(\sum_{i=1}^N \int_0^1 \cmap(\hw_i(s)) ds\right) + R(N)\right\}\\
 & \text{subject to \eqref{eq:hw_seq}} 
@@
 
+\noindent where $R(\cdot)$ is a regularizer such as $R(N) = N^2$.
+
 In other words, we consider air highways to be line segments of constant altitude over a region, and UAV platoons travel on these air highways to get from some origin to some destination.
@@
 The air highway placement problem minimizes the cumulative cost of flying from some origin $p^o$ to some destination $p^d$ along the sequence of highways $\hws_N=\{\hw_1, \hw_2, \ldots, \hw_N\}$.
+The regularization term is used to prevent $N$ from being arbitrarily large.
 

### 2016-05-10 docs/AIAA 2016 highway platooning/high_sim.tex
Made the "easy" changes to AIAA paper according to Claire's comments
Made minor to medium changes according to Claire and Jaime's comments

@@
 This assumption assigns costs in descending order to the categories ``regions around airports'', ``cities'', ``other'', and ``water''.
-Flying a UAV in each category is more costly by a factor of $b$ compared to the next most important category.
+Flying a UAV in each category is more costly by a factor of $b\ge1$ compared to the next most important category.
 The factor $b$ is a tuning parameter that we adjusted to vary the relative importance of the different categories, and we used $b=4$ in the figures below.
@@
 Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function.
-The region enclosed by the black boundary represent ``region around airports'', which have the highest cost.
+The region enclosed by the black boundary represents ``region around airports'', which have the highest cost.
 The dark blue, yellow, and light blue regions represent the ``cities'', the ``water'', and the ``other''' categories, respectively.
@@
 In addition, the cost of flying in the airspace according to the cost map is minimized.
-Secondly, the spacing of the contours, which correspond to level curves of the value function, have a spacing corresponding to the cost map.
+Secondly, the contours, which correspond to level curves of the value function, have a spacing corresponding to the cost map.
 This provides insight into the placement of air highways to destinations that were not shown in this example.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/airHighway_results"}
+	\includegraphics[width=0.95\textwidth]{"fig/airHighway_results"}
 	\caption{Cost-minimizing paths computed by the Fast Marching Method based on the assumed cost map of the San Francisco Bay Area}
@@
 
-Fig.
-\ref{fig:airHighway_sparse} shows the result of converting the cost-minimizing paths to a small number of waypoints.
+Figure \ref{fig:airHighway_sparse} shows the result of converting the cost-minimizing paths to a small number of waypoints.
 The left plot shows the waypoints, interpreted as the start and end points of air highways, over a white background for clarity.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/airHighway_sparse"}
+	\includegraphics[width=0.95\textwidth]{"fig/airHighway_sparse"}
 	\caption{Results of conversion from cost-minimizing paths to highway way points.}
@@
 \end{figure}
+
+\subsection{Real-Time Highway Location Updates}
+Since \eqref{eq:eikonal} can be solved in approximately a second, the air highway placement process can be redone in real-time if the cost map changes.
+This flexibility can be useful in any situation in which unforeseen circumstances cause a change in the cost of a particular region of the airspace.
+For example, accidents or disaster response vehicles may result in an area temporarily having a high cost.
+On the other hand, depending on for instance the time of day, it may be most desirable to fly in different regions of the airspace, resulting in those regions temporarily having a low cost.

### 2016-05-10 docs/AIAA 2016 highway platooning/high_waypoints.tex
Made minor to medium changes according to Claire and Jaime's comments

@@
 \subsection{From Paths to Waypoints}
-Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a continuous set of points.
+Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a closely-spaced set of points.
 Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexed by the corresponding path index $i$.
@@
 
-If there is a large change in heading within a small section of the cost-minimizing path, then the collection of point may contain many points which are close together.
+If there is a large change in heading within a small section of the cost-minimizing path, then the collection of points may contain many points which are close together.
 In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), which may contribute to cluttering the airspace with too many waypoints.

### 2016-05-10 docs/AIAA 2016 highway platooning/introduction.tex
Made minor to medium changes according to Claire and Jaime's comments

@@
 \section{Introduction}
-Unmanned aerial vehicle (UAV) systems have in the past been mainly used for military operations \cite{Tice91}.
-Recently, however, there has been an immense surge of interest in using UAVs for civil applications.
-Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commerical packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue.
+\MCnote{Add reference suggested by Claire}
+\MCnote{Be consistent with UAS vs UAV}
+Unmanned aerial systems (UAS) have in the past been mainly used for military operations \cite{Tice91}.
+Recently, however, there has been an immense surge of interest in using UASs for civil applications.
+Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue.
 In the future, the applications of UAVs are only limited by human imagination.

### 2016-05-10 docs/AIAA 2016 highway platooning/plat_controllers.tex
Made the "easy" changes to AIAA paper according to Claire's comments
Made minor to medium changes according to Claire and Jaime's comments

@@
 In order to construct different controllers, an appropriate target set needs to be defined depending on the goal of the controller.
-If one defines the target set to be a set of desired states, the reachable set, once computed, would represent the states from which a system needs to first arrive at in order to reach the desired states.
+If one defines the target set to be a set of desired states, the reachable set would represent the states that a system needs to first arrive at in order to reach the desired states.
 On the other hand, if the target set represents a set of undesirable states, then the reachable set would indicate the region of the state space that the system needs to avoid.
-In addition, the system dynamics with which the reachable set is computed provides additional flexibility when using reachability to construct controllers.
+In addition, the system dynamics with which the reachable set is computed provide additional flexibility when using reachability to construct controllers.
 
@@
 \subsubsection{Getting to a Target State \label{sec:abs_target_ctrl}}
-The controller used by a vehicle to reach a target state is important in a couple of situations in the platooning context.
+The controller used by a vehicle to reach a target state is important in two situations in the platooning context.
 First, a vehicle in the ``Free'' mode can use the controller to merge onto a highway, forming a platoon and changing modes to a ``Leader'' vehicle.
-Second, a vehicle in either the ``Leader'' mode or the ``Follower'' mode can use this controller to change to a different highway, changing modes to a ``Leader'' vehicle.
+Second, a vehicle in either the ``Leader'' mode or the ``Follower'' mode can use this controller to change to a different highway, becoming a ``Leader'' vehicle.
 
@@
 The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)$ that corresponds to the speed and direction of travel specified by the highway.
-For the reachability computation, we define the target set to be a small range of states around the target state $x_H = (\Pos_x, \Pos_y, \Vel_x, \Vel_y)$:
+For the reachability computation, we define the target set to be a small range of states around the target state $\bar x_H = (\Pos_x, \Pos_y, \Vel_x, \Vel_y)$:
 
@@
 \begin{enumerate}
-\item Move towards $\bar{x}_H$ in a straight line, with some velocity, until $V_H(-T,x)\le 0$. In practice, this step consistently drives the system into the reachable set.
+\item Move towards $\bar{x}_H$ in pure pursuit with some velocity, until $V_H(-T,x)\le 0$. In practice, this step consistently drives the system into the reachable set.
 \item Apply the optimal control extracted from $V_H(-T,x)$ according to \eqref{eq:HJB_ctrl_syn} until $\mathcal{L}_H$ is reached.
@@
 We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJI PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition.
-As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the reachable set $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst case control.
+As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the reachable set $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst-case control.
 To avoid collisions, $Q_i$ must apply the safety controller according to \eqref{eq:HJI_ctrl_syn} on the boundary of the reachable set in order to avoid going into the reachable set.
@@
 \begin{enumerate}
-\item For a specified time horizon $t$, evaluate$V_S(-t,x_i-x_j)$ for all $j\in \mathcal{Q}(i)$.
+\item For a specified time horizon $t$, evaluate $V_S(-t,x_i-x_j)$ for all $j\in \mathcal{Q}(i)$.
 
-$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against.
+$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety.
 \item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:
@@
 \subsubsection{Following a Platoon} \label{sec:follow_platoon}
-Follower vehicles use a feedback control law tracking a nominal position and velocity in the platoon, with an additional feed-forward term given by the leader's acceleration input; here, for simplicity, we assume perfect communication between the leader and the follower vehicles.
+Follower vehicles use a feedback control law tracking a nominal position and velocity in the platoon, with an additional feedforward term given by the leader's acceleration input; here, for simplicity, we assume perfect communication between the leader and the follower vehicles.
 This following law enables smooth vehicle trajectories in the relative platoon frame, while allowing the platoon as a whole to perform agile maneuvers by transmitting the leader's acceleration command $u_{P_1}(t)$ to all vehicles.
@@
 \begin{equation}\label{eq:nominal_pos}
-r^i(t) = - (i-1) b \frac{v_{P_1}}{\|v_{P_1}\|_2}
+r^i(t) = - (i-1) \sepdist \frac{v_{P_1}}{\|v_{P_1}\|_2}
 \end{equation}

### 2016-05-10 docs/AIAA 2016 highway platooning/plat_form.tex
Made the "easy" changes to AIAA paper according to Claire's comments
Made minor to medium changes according to Claire and Jaime's comments

@@
 \section{Unmanned Aerial Vehicle Platooning \label{sec:platooning}}
+\MCnote{Add introduction section}
 \subsection{UAVs in Platoons}
@@
 \item Leader:
+
 A Leader vehicle is the vehicle at the front of a platoon (which could consist of only the vehicle itself). The available maneuvers and mode transitions are
@@
 
-If a vehicle from any of the other modes malfunctions, it transitions into the Faulty mode and descends after some pre-specified duration $t_\text{faulty}$.
+If a vehicle from any of the other modes malfunctions, it transitions into the Faulty mode.
+A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $t_\text{faulty}$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system.
 \end{itemize}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/vehicleModes"}
+	\includegraphics[width=0.95\textwidth]{"fig/vehicleModes"}
 	\caption{Hybrid modes for vehicles in platoons.}
@@
 
-Suppose that there are $N$ vehicles in total.
+Suppose that there are $N$ vehicles in total in the airspace containing the highway system.
 We will denote the $N$ vehicles as $\veh{i}, i=1\ldots,N$.
@@
 
-For convenience, let $\vehSCS{i}$ denote the set of indices of vehicles with respect to which $Q_i$ checks safety against.
+For convenience, let $\vehSCS{i}$ denote the set of indices of vehicles with respect to which $Q_i$ checks safety.
 If vehicle $\veh{i}$ is a free vehicle, then it must check for safety with respect to all other vehicles, $\vehSCS{i} = \{j: j\neq i\}$.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/vehicleNotation"}
+	\includegraphics[width=0.95\textwidth]{"fig/vehicleNotation"}
 	\caption{Notation for vehicles in platoons.}
@@
 
-We will assume that the vehicles in a platoon travel along an air highway.
-The vehicles maintain a separation distance of $b$ with its neighbors inside the platoon.
+We will organize the vehicles into platoons travel along air highways.
+The vehicles maintain a separation distance of $\sepdist$ with their neighbors inside the platoon.
 In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that in the event of a malfunction, a vehicle will be able to exit the altitude range of the highway within a duration of $t_\text{faulty}=1.5$.
-Such a requirement may be implemented practically as an emergency landing procedure to which the vehicles revert when a malfunction is detected.
+Such a requirement may be implemented practically as an fail-safe mechanism to which the vehicles revert when a malfunction is detected.
 
@@
 \item leave a platoon to create a new one
-\item reacting to malfunctioning or intruder vehicles
+\item react to malfunctioning or intruder vehicles
 \end{itemize}
@@
 \begin{itemize}
-\item following the highway at constant altitude at a specified speed
-\item maintaining a constant relative position and velocity with the leader of a platoon
+\item follow the highway at constant altitude at a specified speed
+\item maintain a constant relative position and velocity with respect to the leader of a platoon
 \end{itemize}
 
-In general, the control strategies of each vehicle have a liveness component, which specifies a set of states towards which the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.
+In general, the control strategies of each vehicle have a liveness component, which specifies a set of states that the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.
 Together, the liveness and safety controllers guarantee the success and safety of a vehicle in the airspace making any desired mode transition.

### 2016-05-10 docs/AIAA 2016 highway platooning/plat_reach.tex
Made the "easy" changes to AIAA paper according to Claire's comments
Made minor to medium changes according to Claire and Jaime's comments

--- 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_reach.tex
@@
 \begin{aligned}
-\mathcal{V}(t) &:= \{x\in\mathbb{R}^n \mid \exists \gamma\in\Gamma \text{ such that} \forall u_1(\cdot)\in\mathbb{U}_1, \\
+\mathcal{V}(t) &:= \{x\in\mathbb{R}^n \mid \exists \gamma\in\Gamma \text{ such that } \forall u_1(\cdot)\in\mathbb{U}_1, \\
 &\exists s \in [t,0], \xi_f(s; t, x, u_1(\cdot), \gamma[u_1](\cdot)) \in \mathcal{L} \}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/RSExample"}
+	\includegraphics[width=0.95\textwidth]{"fig/RSExample"}
 	\caption{Illustration of a target set, reachable set, and their implicit surface functions.}
@@
 
-For our application, we will use several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real time 4D reachable set computations and tractable 6D reachable set computations.
+For our application, we will use several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real-time 4D reachable set computations and tractable 6D reachable set computations.
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.25\textwidth]{"fig/rel_coords"}
-	\caption{Relative coordinates}
-	\label{fig:rel_coords}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.25\textwidth]{"fig/rel_coords"}
+%	\caption{Relative coordinates}
+%	\label{fig:rel_coords}
+%\end{figure}
 

### 2016-05-10 docs/AIAA 2016 highway platooning/plat_safety.tex
Made minor to medium changes according to Claire and Jaime's comments

@@
 However, as long as the total number of safety breaches does not exceed the number of affected quadrotors, collision avoidance of all the vehicles can be guaranteed for the duration $\td$.
-However, as our simulation results show, putting vehicles in single-file platoons makes the likelihood of multiple safety breaches low during a vehicle's malfunction and during the presence of one intruder vehicle.
+However, as our simulation results show, placing vehicles in single-file platoons makes the likelihood of multiple safety breaches low during a vehicle's malfunction and during the presence of one intruder vehicle.
 

### 2016-05-10 docs/AIAA 2016 highway platooning/plat_sim.tex
Made the "easy" changes to AIAA paper according to Claire's comments
Made minor to medium changes according to Claire and Jaime's comments

@@
 \subsubsection{Forming a Platoon}
-We first consider the scenario in which Free vehicles merge onto an initially unoccupied highway.
+\MCnote{Show all reachable sets for first two subfigures}We first consider the scenario in which Free vehicles merge onto an initially unoccupied highway.
 In order to do this, each vehicle first checks for safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:collision_ctrl}.
@@
 Therefore, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$.
-During the entire time, $\veh{1}$ checks whether it may collide with all of the other vehicles within a time horizon of $\td$.
+During the entire time, $\veh{1}$ checks whether it may collide with any of the other vehicles within a time horizon of $\td$.
 To do this, it simply checks whether its state relative to each of the other vehicles is within the corresponding safety reachable set.
@@
     \centering
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:fp_40}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_40}
         \includegraphics[width=\textwidth]{fig/fp_40}
@@
     \end{subfigure}
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:fp_60}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_60}
         \includegraphics[width=\textwidth]{fig/fp_60}
@@
 
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:fp_110}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_110}
         \includegraphics[width=\textwidth]{fig/fp_110}
@@
     \end{subfigure}
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:fp_210}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_210}
         \includegraphics[width=\textwidth]{fig/fp_210}
@@
     \centering
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:in_100}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:in_100}
         \includegraphics[width=\textwidth]{fig/in_100}
@@
     \end{subfigure}
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:in_120}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:in_120}
         \includegraphics[width=\textwidth]{fig/in_120}
@@
 
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:in_140}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:in_140}
         \includegraphics[width=\textwidth]{fig/in_140}
@@
     \end{subfigure}
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:in_200}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:in_200}
         \includegraphics[width=\textwidth]{fig/in_200}
@@
     \centering
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:ch_83}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:ch_83}
         \includegraphics[width=\textwidth]{fig/ch_83}
@@
     \end{subfigure}
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:ch_124}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:ch_124}
         \includegraphics[width=\textwidth]{fig/ch_124}
@@
 
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:ch_170}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:ch_170}
         \includegraphics[width=\textwidth]{fig/ch_170}
@@
     \end{subfigure}
-    \begin{subfigure}[t]{0.23\textwidth} \label{subfig:ch_231}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:ch_231}
         \includegraphics[width=\textwidth]{fig/ch_231}

### 2016-05-10 docs/AIAA 2016 highway platooning/plat_summary.tex
Made the "easy" changes to AIAA paper according to Claire's comments
Made minor to medium changes according to Claire and Jaime's comments

--- 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_summary.tex
@@
 We have introduced several reachability-based controllers, as well as some simple controllers.
-Pair-wise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:collision_ctrl}.
+Pairwise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:collision_ctrl}.
 As long as a vehicle is not in potential danger according to the safety reachable sets, it is free to use any other controller.
-All of these other controllers and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.
+All of these other controllers are \textit{liveness controllers}, and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{"fig/modeControllers"}
-	\caption{}
+	\includegraphics[width=0.75\textwidth]{"fig/modeControllers"}
+	\caption{Summary of mode switching controllers. Reachability-based controllers are shown as the blue and green arrows.}
 	\label{fig:modeControllers}

### 2016-05-11 docs/AIAA 2016 highway platooning/introduction.tex
Made all minor changes to AIAA paper. Safety analysis is the last remaining issue.

@@
 \section{Introduction}
-\MCnote{Add reference suggested by Claire}
-\MCnote{Be consistent with UAS vs UAV}
-Unmanned aerial systems (UAS) have in the past been mainly used for military operations \cite{Tice91}.
-Recently, however, there has been an immense surge of interest in using UASs for civil applications.
+Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91}.
+Recently, however, there has been an immense surge of interest in using UAVs for civil applications.
 Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue.
@@
 In \cite{Lygeros98}, the authors modeled vehicles in platoons as hybrid systems, synthesized safety controllers, and analyzed throughput.
-Finally, reachability analysis was used in \cite{Alam11} to analyze a platoon of two trucks in order to minimize drag by minimizing the following distance while maintaining collision avoidance safety guarantees.
+Reachability analysis was used in \cite{Alam11} to analyze a platoon of two trucks in order to minimize drag by minimizing the following distance while maintaining collision avoidance safety guarantees.
+Finally, \cite{Sabau16} provided a method for guaranteeing string stability and eliminating accordion effects for a heterogeneous platoon of vehicles with linear time-invariant dynamics.
 

### 2016-05-11 docs/AIAA 2016 highway platooning/plat_form.tex
Made all minor changes to AIAA paper. Safety analysis is the last remaining issue.

@@
 \section{Unmanned Aerial Vehicle Platooning \label{sec:platooning}}
-\MCnote{Add introduction section}
+Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways.
+The platooning concept provides a structural solution for monitoring and ensuring the safety of a large number of UAVs.
+The structured imposed by air highways reduces number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all vehicles.
+
+Organizing UAVs into platoons implies that the UAVs cannot fly in an unstructured way, and must have a restricted set of controllers or maneuvers depending on the UAV's role in the airspace.
+To model UAVs flying in platoons on air highways, we propose a hybrid system whose modes of operations describe the UAV's role in the highway structure.
+For the hybrid system model, reachability is used to enable successful and safe operation and mode transitions.
+
 \subsection{UAVs in Platoons}

### 2016-05-12 docs/AIAA 2016 highway platooning/high_form.tex
Updated AIAA 2016 paper; all comments are incorporated

@@
 \end{equation}
+\MCnote{The number of constraints here change with the decision variable $N$, but I'm ignoring this fact as the point is that this optimization is hard to solve, and therefore we solve the Eikonal equation instead.}
 
-\noindent where $R(\cdot)$ is a regularizer such as $R(N) = N^2$.
+\noindent where $R(\cdot)$ is a regularizer, such as $R(N) = N^2$. \MCnote{Added regularizer to prevent $N\rightarrow\infty$}
 
-In other words, we consider air highways to be line segments of constant altitude over a region, and UAV platoons travel on these air highways to get from some origin to some destination.
+The interpretation of \eqref{eq:ahpp} is that we consider air highways to be line segments of constant altitude over a region, and UAV platoons travel on these air highways to get from some origin to some destination.
 Any UAV flying on a highway over some position $\pos$ incurs a cost of $\cmap(\pos)$, so that the total cost of flying from the origin to the destination is given by \eqref{eq:ahpp}.

### 2016-05-12 docs/AIAA 2016 highway platooning/high_sim.tex
Updated AIAA 2016 paper; all comments are incorporated

@@
 The right plot shows these air highways over the map of the Bay Area.
+Note that we could have gone further to merge some of the overlapping highways.
+However, the purpose of this section is to illustrate the natural occurence of air highways from cost-minimizing paths; post-processing of the cost-minimizing paths is not the focus.
 
@@
 \subsection{Real-Time Highway Location Updates}
-Since \eqref{eq:eikonal} can be solved in approximately a second, the air highway placement process can be redone in real-time if the cost map changes.
+\MCnote{Added section to emphasize that highway locations can be updated in real time}Since \eqref{eq:eikonal} can be solved in approximately a second, the air highway placement process can be redone in real-time if the cost map changes.
 This flexibility can be useful in any situation in which unforeseen circumstances cause a change in the cost of a particular region of the airspace.

### 2016-05-12 docs/AIAA 2016 highway platooning/introduction.tex
Updated AIAA 2016 paper; all comments are incorporated

@@
 Reachability analysis was used in \cite{Alam11} to analyze a platoon of two trucks in order to minimize drag by minimizing the following distance while maintaining collision avoidance safety guarantees.
-Finally, \cite{Sabau16} provided a method for guaranteeing string stability and eliminating accordion effects for a heterogeneous platoon of vehicles with linear time-invariant dynamics.
+Finally, \cite{Sabau16} provided a method for guaranteeing string stability and eliminating accordion effects for a heterogeneous platoon of vehicles with linear time-invariant dynamics.\MCnote{Added Sabau's paper}
 
 Previous analyses of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
-In the second part of this paper, we propose organizing UAVs into platoons, which provide structure that allows pairwise safety guarantees from HJ reachability to translate to safety guarantees for the whole platoon.
+In the second part of this paper, we propose organizing UAVs into platoons, which provide structure that allows pairwise safety guarantees from HJ reachability to better translate to safety guarantees for the whole platoon.
 With respect to platooning, we first propose a hybrid systems model of UAVs in platoons to establish the modes of operation needed for our platooning concept.
 Then, we show how reachability-based controllers can be synthesized to enable vehicles to successfully perform mode switching, as well as prevent dangerous configurations such as collisions.
-Finally, we show several simulations to illustrate the behavior of vehicles in various scenarios and demonstrate the guarantees provided by HJ reachability.
+Finally, we show several simulations to illustrate the behavior of vehicles in various scenarios.
+\MCnote{Slightly weakened claims about guaranteeing safety in last paragraph.}

### 2016-05-12 docs/AIAA 2016 highway platooning/plat_form.tex
Updated AIAA 2016 paper; all comments are incorporated

@@
 \section{Unmanned Aerial Vehicle Platooning \label{sec:platooning}}
-Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways.
+\MCnote{Added introduction to this section}Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways.
 The platooning concept provides a structural solution for monitoring and ensuring the safety of a large number of UAVs.
-The structured imposed by air highways reduces number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all vehicles.
+The structure imposed by air highways reduces number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all vehicles.
 

### 2016-05-12 docs/AIAA 2016 highway platooning/plat_safety.tex
Updated AIAA 2016 paper; all comments are incorporated

@@
 So $\vehSCS{P_1}=\{P_2\}, \vehSCS{P_N}=\{P_{N-1}\}$.
-When all vehicles are using liveness controllers to perform their allowed maneuvers, no pair of vehicles should be in an unsafe configuration if the liveness controllers are well-designed.
+When all vehicles are using liveness controllers to perform their allowed maneuvers, in most situations no pair of vehicles should be in an unsafe configuration.
 However, occasionally a vehicle $\veh{k}$ may behave unexpectedly due to faults or malfunctions, in which case it may come into an unsafe configuration with another vehicle.
 
-With our choice of $\vehSCS{i}$ and the assumption that the platoon is in a single-file formation, some vehicle $\veh{i}$ would get into an unsafe configuration with $\veh{k}$, where $\veh{k}$ is likely to be the vehicle in front or behind of $\veh{i}$.
+With our choice of $\vehSCS{i}$ and the assumption that the platoon is in a single-file formation, some vehicle $\veh{i}$ would get near the safety reachable set with respect to $\veh{k}$, where $\veh{k}$ is likely to be the vehicle in front or behind of $\veh{i}$.
 In this case, a ``safety breach" occurs.
@@
 Within a duration of $\td$, there is a small chance that additional safety breaches may occur.
-However, as long as the total number of safety breaches does not exceed the number of affected quadrotors, collision avoidance of all the vehicles can be guaranteed for the duration $\td$.
+However, as long as the total number of safety breaches does not exceed the number of affected vehicles, collision avoidance of all the vehicles can be guaranteed for the duration $\td$.
 However, as our simulation results show, placing vehicles in single-file platoons makes the likelihood of multiple safety breaches low during a vehicle's malfunction and during the presence of one intruder vehicle.
 
-In the event that multiple safety breaches occur for some of the vehicles due to a malfunctioning vehicle within the platoon or intruding vehicles outside of the platoon, those vehicles with more than one safety breach still have the option of exiting the highway altitude range in order to avoid collisions.
+In the event that multiple safety breaches occur for some of the vehicles due to a malfunctioning vehicle within the platoon or intruding vehicles outside of the platoon, vehicles that are causing safety breaches must exit the highway altitude range in order to avoid collisions.
 Every extra altitude range reduces the number of simultaneous safety breaches by $1$, so $K$ simultaneous safety breaches can be resolved using $K-1$ different altitude ranges.
+The general process and details of the complete picture of multi-altitude collision avoidance is part of our future work.
+\MCnote{Now states vehicles causing safety breaches must exit altitude range; also mentions multi-altitude collision avoidance is future work.}
 
@@
 By treating each platoon as a single unit, we reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.
+\MCnote{Should we discuss inter-platoon safety in more detail through an additional section or simulation?}

### 2016-05-12 docs/AIAA 2016 highway platooning/plat_sim.tex
Updated AIAA 2016 paper; all comments are incorporated

@@
 \subsubsection{Forming a Platoon}
-\MCnote{Show all reachable sets for first two subfigures}We first consider the scenario in which Free vehicles merge onto an initially unoccupied highway.
-In order to do this, each vehicle first checks for safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:collision_ctrl}.
+We first consider the scenario in which Free vehicles merge onto an initially unoccupied highway.
+In order to do this, each vehicle first checks safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:collision_ctrl}.
 Otherwise, the vehicle uses the liveness controller for getting to an absolute target set described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl} in order to merge onto the highway, create a platoon, and become a Leader vehicle if there are no platoons on the highway.
@@
 For the simulation example, shown in Figure \ref{fig:fp}, the highway is specified by a line segment beginning at the origin.
-The five vehicles, $\veh{1}, \veh{2}, \ldots, \veh{5}$ are colored red, purple, light blue, dark blue, and yellow, respectively.
+The five vehicles, $\veh{1}, \veh{2}, \ldots, \veh{5}$ are colored orange, purple, light blue, dark blue, and yellow, respectively.
 
@@
 All vehicles begin as Free vehicles, so they each need to take into account five different reachable sets: four safety reachable sets and one liveness reachable set.
-For clarity, we only show the liveness reachable set and one safety reachable set.
+For clarity, we only show the liveness reachable set and the four safety reachable sets for one of the vehicles.
 
-For $\veh{1}$ (red), an arbitrary point of entry on the highway is chosen as the target absolute position, and the velocity corresponding to a speed of $10$ m/s in the direction of the highway is chosen as the target absolute velocity.
+For $\veh{1}$ (orange), an arbitrary point of entry on the highway is chosen as the target absolute position, and the velocity corresponding to a speed of $10$ m/s in the direction of the highway is chosen as the target absolute velocity.
 This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl}.
 
-At $t=3.9$, $\veh{1}$ (red) is inside the liveness reachable set for getting to an absolute state shown as the dotted red boundary.
+At $t=4.2$, $\veh{1}$ (orange) is inside the liveness reachable set for getting to an absolute state shown as the dotted orange boundary.
 Therefore, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$.
@@
 To do this, it simply checks whether its state relative to each of the other vehicles is within the corresponding safety reachable set.
-As an example, the safety reachable set boundary with respect to $\veh{2}$ (purple) is shown as the red dashed boundary; $\veh{1}$ (red) is safe with respect to $\veh{2}$ (purple) since $\veh{1}$ (red) is outside of the boundary.
+As an example, the safety reachable set boundary with respect to $\veh{2}$ (purple) is shown as the orange dashed boundary around $\veh{2}$ (purple); $\veh{1}$ (orange) is safe with respect to $\veh{2}$ (purple) since $\veh{1}$ (orange) is outside of the boundary.
+In fact, $\veh{1}$ is safe with respect to all vehicles.
 
-After completing merging onto the empty highway, $\veh{1}$ (red) creates a platoon and becomes its leader, while subsequent vehicles begin to form a platoon behind the leader in the order of ascending distance to $\veh{1}$ (red) according to the process described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl}.
-Here, we choose the target relative position $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $b$ behind the last reserved slot in the platoon, and the target relative velocity $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$ with respect to the leader in order to maintain the platoon formation.
+After completing merging onto the empty highway, $\veh{1}$ (orange) creates a platoon and becomes its leader, while subsequent vehicles begin to form a platoon behind the leader in the order of ascending distance to $\veh{1}$ (orange) according to the process described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl}.
+Here, we choose the target relative position $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $\sepdist$ behind the last reserved slot in the platoon, and the target relative velocity $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$ with respect to the leader in order to maintain the platoon formation.
 This gives us the target set $\mathcal{L}_P$ that we need.
 
-At $t=5.9$, $Q_2$ (purple) begins joining the platoon behind $\veh{1}$ (red), by moving towards the target $\bar{x}_P$ relative to the position of $\veh{1}$ (red).
-Note that $\bar{x}_P$ moves with $\veh{1}$ (red) as $\bar{x}_P$ is defined in terms of the relative states of the two vehicles.
+At $t=8.0$, $Q_2$ (purple) is in the process of joining the platoon behind $\veh{1}$ (orange) by moving towards the target $\bar{x}_P$ relative to the position of $\veh{1}$ (orange).
+Note that $\bar{x}_P$ moves with $\veh{1}$ (orange) as $\bar{x}_P$ is defined in terms of the relative states of the two vehicles.
 Since $\veh{2}$ is inside the liveness reachable set boundary for joining the platoon (purple dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target as long as it stays out of all safety reachable sets.
-For example, at $t=5.9$, $\veh{2}$ (purple) is outside of the safety reachable set with respect to $\veh{1}$ (red), shown as the purple dashed boundary.
+For example, at $t=5.9$, $\veh{2}$ (purple) is outside of the safety reachable set with respect to $\veh{1}$ (orange), shown as the purple dashed boundary around $\veh{1}$ (orange).
+Again, from the other safety reachable set boundaries, we can see that $\veh{2}$ is in fact safe with respect to all vehicles.
 
-In the bottom plots of Figure \ref{fig:fp}, $\veh{1}$ (red) and $\veh{2}$ have already become the platoon leader and follower, respectively.
+In the bottom plots of Figure \ref{fig:fp}, $\veh{1}$ (orange) and $\veh{2}$ (purple) have already become the platoon leader and follower, respectively.
 The rest of the vehicles follow the same process to join the platoon.
@@
     \centering
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_40}
-        \includegraphics[width=\textwidth]{fig/fp_40}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_43}
+        \includegraphics[width=\textwidth]{fig/fp_43}
         \caption{The red vehicle follows the reachability-based liveness controller for getting to an absolute target state to merge onto the highway, while avoiding collisions using the reachability-based safety controller.
@@
     \end{subfigure}
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_60}
-        \includegraphics[width=\textwidth]{fig/fp_60}
+    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_81}
+        \includegraphics[width=\textwidth]{fig/fp_81}
         \caption{After the red vehicle successfully merges onto the highway and becomes the platoon leader, the purple vehicle uses the reachability-based liveness controller for getting to a relative target state to join the platoon, while avoiding collisions using the reachability-based safety controller.
@@
 \end{figure}
+
+\MCnote{Showing all safety reachable sets for the vehicle of interest in first two subplots of Figure \ref{fig:fp}}
 

### 2016-05-12 code/platoon/@Vehicle/Vehicle.m

@@ -44,7 +44,7 @@ classdef Vehicle < Node
     h_abs_target_V     % for getting to an absolute target
     h_rel_target_V     % for getting to a relative target
     h_safe_V           % Safety sets
-
+    h_safe_V_list      % List of vehicles for which safety set is being plotted
   end % end properties
 
   % No constructor in vehicle class. Use constructors in the subclasses

### 2016-05-12 code/platoon/@Vehicle/plot_safe_V.m

@@ -32,7 +32,7 @@ switch safe_V.g.dim
     while rel_heading >= 2*pi
       rel_heading = rel_heading - 2*pi;
     end
-
+    
     while rel_heading < 0
       rel_heading = rel_heading + 2*pi;
     end
@@ -62,16 +62,33 @@ data2D(:,1) = max(data2D(:));
 data2D(:,end) = max(data2D(:));
 
 % Plot result
-if isempty(obj.h_safe_V)
-  [~, obj.h_safe_V] = contour(gFinal.xs{1}, gFinal.xs{2}, data2D, ...
-    level, 'linestyle', '--', 'linewidth', linewidth, 'color', obj.hpxpy.Color);
+% Find existing plots
+found = false;
+for i = 1:length(obj.h_safe_V_list)
+  if isequal(obj.h_safe_V_list(i), other)
+    found = true;
+    break
+  end
+end
+
+if found
+  obj.h_safe_V(i).XData = gFinal.xs{1};
+  obj.h_safe_V(i).YData = gFinal.xs{2};
+  obj.h_safe_V(i).ZData = data2D;
+  obj.h_safe_V(i).LevelList = level;
+  obj.h_safe_V(i).LineWidth = linewidth;
+  obj.h_safe_V(i).Visible = 'on';
 else
-  obj.h_safe_V.XData = gFinal.xs{1};
-  obj.h_safe_V.YData = gFinal.xs{2};
-  obj.h_safe_V.ZData = data2D;
-  obj.h_safe_V.LevelList = level;
-  obj.h_safe_V.LineWidth = linewidth;
-  obj.h_safe_V.Visible = 'on';
+  if isempty(obj.h_safe_V)
+    [~, obj.h_safe_V] = contour(gFinal.xs{1}, gFinal.xs{2}, data2D, level, ...
+      'linestyle', '--', 'linewidth', linewidth, 'color', obj.hpxpy.Color);
+    obj.h_safe_V_list = other;
+  else
+    [~, obj.h_safe_V(end+1)] = contour(gFinal.xs{1}, gFinal.xs{2}, data2D, ...
+      level, 'linestyle', '--', 'linewidth', linewidth, ...
+        'color', obj.hpxpy.Color);
+    obj.h_safe_V_list(end+1) = other;
+  end
 end
 
 end

### 2016-05-12 code/platoon/@Vehicle/unplot_safe_V.m

@@ -7,6 +7,8 @@ function unplot_safe_V(obj)
 % Qie Hu, 2015-07-25
 % Modified: Mo Chen, 2015-12-13
 
-obj.h_safe_V.Visible = 'off';
+for i = 1:length(obj.h_safe_V)
+  obj.h_safe_V(i).Visible = 'off';
+end
 
 end

### 2016-05-12 code/platoon/simulations/simulateFormPlatoon.m

@@ -129,7 +129,10 @@ if isempty(tfm.hws{1}.ps)
   u = veh.goOnHighway(tfm.hws{1}, tep, tfm);
   tfm.aas{1}.plot_abs_target_V(tfm.qr_abs_target_V, tep, ...
   tfm.hws{1}.getHeading, tfm.rtt);
-  tfm.aas{1}.plot_safe_V(tfm.aas{2}, tfm.qr_qr_safe_V, tfm.safetyTime)
+  for i = 2:length(tfm.aas)
+    tfm.aas{1}.plot_safe_V(tfm.aas{i}, tfm.qr_qr_safe_V, tfm.safetyTime)
+  end
+  
   return
 else
   tfm.aas{1}.unplot_abs_target_V;
@@ -147,7 +150,12 @@ end
 if strcmp(tfm.aas{2}.q, 'Free')
   tfm.aas{2}.plot_rel_target_V(tfm.qr_rel_target_V, ...
     tfm.hws{1}.ps{1}.vehicles{1}, tfm.rtt);
-  tfm.aas{2}.plot_safe_V(tfm.aas{1}, tfm.qr_qr_safe_V, tfm.safetyTime)
+  
+  for i = 1:length(tfm.aas)
+    if i ~= 2
+      tfm.aas{2}.plot_safe_V(tfm.aas{i}, tfm.qr_qr_safe_V, tfm.safetyTime)
+    end
+  end
 else
   tfm.aas{2}.unplot_rel_target_V
   tfm.aas{2}.unplot_safe_V
@@ -157,8 +165,6 @@ if strcmp(veh.q, 'Free')
   u = veh.joinPlatoon(tfm.hws{1}.ps{1}, tfm);
   return
 end
-
-
 
 %% If already in the platoon, simply follow it
 u = veh.followPlatoon(tfm);

### 2016-05-13 docs/AIAA 2016 highway platooning/high_form.tex
Part way through proofreading; currently on page 18, section III-C

@@
 The interpretation of \eqref{eq:ahpp} is that we consider air highways to be line segments of constant altitude over a region, and UAV platoons travel on these air highways to get from some origin to some destination.
-Any UAV flying on a highway over some position $\pos$ incurs a cost of $\cmap(\pos)$, so that the total cost of flying from the origin to the destination is given by \eqref{eq:ahpp}.
+Any UAV flying on a highway over some position $\pos$ incurs a cost of $\cmap(\pos)$, so that the total cost of flying from the origin to the destination is given by the summation in \eqref{eq:ahpp}.
 The air highway placement problem minimizes the cumulative cost of flying from some origin $p^o$ to some destination $p^d$ along the sequence of highways $\hws_N=\{\hw_1, \hw_2, \ldots, \hw_N\}$.
@@
 	\includegraphics[width=0.95\textwidth]{"fig/highway_illustration"}
-	\caption{Highway illustration}
+	\caption{Illustration of the air highway placement procedure.}
 	\label{fig:hw_ill}

### 2016-05-13 docs/AIAA 2016 highway platooning/high_sim.tex
Part way through proofreading; currently on page 18, section III-C

--- 2016-05-10 docs/AIAA 2016 highway platooning/high_sim.tex
@@
 This assumption assigns costs in descending order to the categories ``regions around airports'', ``cities'', ``other'', and ``water''.
-Flying a UAV in each category is more costly by a factor of $b\ge1$ compared to the next most important category.
-The factor $b$ is a tuning parameter that we adjusted to vary the relative importance of the different categories, and we used $b=4$ in the figures below.
+Flying a UAV in each category is more costly by a factor of $b$ compared to the next most important category.
+The factor $b>1$ is a tuning parameter that we adjusted to vary the relative importance of the different categories, and we used $b=4$ in the figures below.
 
-Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function.
+Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function $V$.
 The region enclosed by the black boundary represents ``region around airports'', which have the highest cost.
@@
 The right plot shows these air highways over the map of the Bay Area.
+Note that we could have gone further to merge some of the overlapping highways.
+However, the purpose of this section is to illustrate the natural occurrence of air highways from cost-minimizing paths; post-processing of the cost-minimizing paths is not our focus.
 
@@
 \subsection{Real-Time Highway Location Updates}
-Since \eqref{eq:eikonal} can be solved in approximately a second, the air highway placement process can be redone in real-time if the cost map changes.
-This flexibility can be useful in any situation in which unforeseen circumstances cause a change in the cost of a particular region of the airspace.
+\MCnote{New section}Since \eqref{eq:eikonal} can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost map changes.
+This flexibility can be useful in any situation in which unforeseen circumstances could cause a change in the cost of a particular region of the airspace.
 For example, accidents or disaster response vehicles may result in an area temporarily having a high cost.

### 2016-05-13 docs/AIAA 2016 highway platooning/high_waypoints.tex
Part way through proofreading; currently on page 18, section III-C

@@
 \subsection{From Paths to Waypoints}
+\MCnote{Changed wording in this section to say the sparsification of points on a path is not our focus, but just an illustration.}
 Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a closely-spaced set of points.
@@
 
-To sparsify the continuous set of points on each path, we start at the destination point and note the path's heading.
+There are many different ways to sparsify the close-spaced set of points on each path, and this process will not be our focus.
+However, for illustrative purposes, we show how this process may be started.
+We begin by noting the path's heading at the destination point.
 We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process along the entire path.
@@
 In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), which may contribute to cluttering the airspace with too many waypoints.
-We propose to sparsify the waypoints by clustering the points.
-After clustering, we replace each cluster of points with a single point located at the centroid of the cluster.
+One way to sparsify the waypoints is to cluster the points.
+Afterwards, each cluster of points can be replaced by a single point located at the centroid of the cluster.
 
@@
 Repeating the entire process for every path, we obtain waypoints for all the cost-minimizing paths under consideration.
-Figure \ref{fig:hw_ill} summarizes the entire air highway placement process.
+Figure \ref{fig:hw_ill} summarizes the entire air highway placement process, including our example of how the closely-space set of points on a path can be sparsified.

### 2016-05-13 docs/AIAA 2016 highway platooning/introduction.tex
Part way through proofreading; currently on page 18, section III-C

@@
 \section{Introduction}
-Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91}.
-Recently, however, there has been an immense surge of interest in using UAVs for civil applications.
+Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91}; however, recently there has been an immense surge of interest in using UAVs for civil applications.
 Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue.
@@
 
-As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone.
-This would equate to thousands of vehicles simultaneously in the air just from package delivery services.
+As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30-minute trip for a UAV.
+This would equate to thousands of UAVs simultaneously in the air just from package delivery services.
 Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to respond to disasters in areas that are difficult to reach but require prompt response \cite{Debusk10,Tornado16}.
@@
 However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles.
-This makes the computation intractable for large numbers of vehicles.
+Consequently, HJ reachability computations are intractable for large numbers of vehicles.
 
@@
 Previous analyses of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
-In the second part of this paper, we propose organizing UAVs into platoons, which provide structure that allows pairwise safety guarantees from HJ reachability to better translate to safety guarantees for the whole platoon.
+In the second part of this paper, we propose organizing UAVs into platoons, which provide a structure that allows pairwise safety guarantees from HJ reachability to better translate to safety guarantees for the whole platoon.
 With respect to platooning, we first propose a hybrid systems model of UAVs in platoons to establish the modes of operation needed for our platooning concept.
-Then, we show how reachability-based controllers can be synthesized to enable vehicles to successfully perform mode switching, as well as prevent dangerous configurations such as collisions.
-Finally, we show several simulations to illustrate the behavior of vehicles in various scenarios.
+Then, we show how reachability-based controllers can be synthesized to enable UAVs to successfully perform mode switching, as well as prevent dangerous configurations such as collisions.
+Finally, we show several simulations to illustrate the behavior of UAVs in various scenarios.
 \MCnote{Slightly weakened claims about guaranteeing safety in last paragraph.}

### 2016-05-13 docs/AIAA 2016 highway platooning/main.tex
Made minor to medium changes according to Claire and Jaime's comments
Updated AIAA 2016 paper; all comments are incorporated
Part way through proofreading; currently on page 18, section III-C

@@
 \documentclass[submit]{aiaa-pretty}
+
+\usepackage{todonotes} \setlength{\marginparwidth}{2.3cm}
+
+\newcommand{\MCnote}{\todo[size=\footnotesize,author=MC,color=cyan]}
 
@@
 
+\newcommand{\sepdist}{d_\text{sep}} % separation distance
+
 \newcommand{\td}{t_\text{faulty}} % time to descend
@@
 \author{Mo Chen, Qie Hu, Jaime Fisac, Kene Akametalu, Casey Mackin, Claire Tomlin}
-\title{Guaranteeing Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}
+\title{Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}
 
@@
 \begin{document}
-
 \maketitle
-
+\MCnote{Changed title (used to be ``Guaranteeing Safety ...''}
 \section*{Nomenclature}
@@
 $\cmap$ &=& Cost map \\
+$\ppath$ &=& A path between two points \\
 $\ccost$ &=& Cumulative cost of a path \\
-$\ocost$ &=& Optimal cumulative cost of a path \\
+$\ocost$ &=& Value function of partial differential equations \\
 $\hw$ &=& Air highway \\
@@
 $\vel=(\vel_x, \vel_y)$ &=& Horizontal velocity \\
+$\Pos$ &=& Target position \\
+$\Vel$ &=& Target velocity \\
+$\sepdist$ &=& Separation distance of vehicles within a platoon \\
 $\td$ &=& Time limit for descent during potential conflict \\
 $\veh{i}$ &=& $i$th vehicle \\
-$\vehSCS{i}$ &=& Set of vehicles for vehicle $i$ to consider for safety 
+$\vehSCS{i}$ &=& Set of vehicles for vehicle $\veh{i}$ to consider for safety 
 \end{tabular} \\
@@
 
-\section*{Appendix}
+%\section*{Appendix}
 

### 2016-05-13 docs/AIAA 2016 highway platooning/plat_controllers.tex
Part way through proofreading; currently on page 18, section III-C

@@
 In both of the above cases, we use the dynamics of a single vehicle specified in \eqref{eq:dyn}.
-The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)$ that corresponds to the speed and direction of travel specified by the highway.
+The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)=\vel_\hw$ that corresponds to the speed and direction of travel specified by the highway.
 For the reachability computation, we define the target set to be a small range of states around the target state $\bar x_H = (\Pos_x, \Pos_y, \Vel_x, \Vel_y)$:
@@
 \begin{equation}\label{eq:nominal_pos}
-r^i(t) = - (i-1) \sepdist \frac{v_{P_1}}{\|v_{P_1}\|_2}
+r^i(t) = - (i-1) \sepdist \hwd
 \end{equation}
-where $b$ is the spacing between vehicles along the platoon and $\frac{v_{P_1}}{\|v_{P_1}\|_2}$ is the platoon leader's direction of travel.
+where $\sepdist$ is the spacing between vehicles along the platoon and $\hwd$ is the highway's direction of travel.

### 2016-05-13 docs/AIAA 2016 highway platooning/plat_form.tex
Part way through proofreading; currently on page 18, section III-C

@@
 The platooning concept provides a structural solution for monitoring and ensuring the safety of a large number of UAVs.
-The structure imposed by air highways reduces number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all vehicles.
+The structure imposed by air highways reduces the number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all UAVs.
 
 Organizing UAVs into platoons implies that the UAVs cannot fly in an unstructured way, and must have a restricted set of controllers or maneuvers depending on the UAV's role in the airspace.
-To model UAVs flying in platoons on air highways, we propose a hybrid system whose modes of operations describe the UAV's role in the highway structure.
-For the hybrid system model, reachability is used to enable successful and safe operation and mode transitions.
+To model UAVs flying in platoons on air highways, we propose a hybrid system whose modes of operations describe a UAV's role in the highway structure.
+For the hybrid system model, reachability analysis is used to enable successful and safe operation and mode transitions.
 
@@
 \begin{itemize}
-\item remain a Leader by traveling along the highway at a pre-specified speed
+\item remain a Leader by traveling along the highway at a pre-specified speed $\vel_\hw$
 \item become a Follower by merging the current platoon with a platoon in front
@@
 \item remain a Follower by staying a distance of $d_\text{sep}$ behind the vehicle in front in the current platoon
+\item remain a Follower by joining a different platoon on another highway
 \item become a Leader by splitting from the current platoon
@@
 
-If a vehicle from any of the other modes malfunctions, it transitions into the Faulty mode.
+If a vehicle from any of the other modes becomes unable to operate within the allowed set of maneuvers, it transitions into the Faulty mode.
+Reasons for transitioning to the Faulty mode include vehicle malfunctions, performing collision avoidance with respect to another Faulty vehicle, etc.
 A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $t_\text{faulty}$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system.
+\MCnote{Faulty mode now includes vehicles which could cause additional conflicts by avoiding another faulty vehicle}
 \end{itemize}
@@
 The vehicles maintain a separation distance of $\sepdist$ with their neighbors inside the platoon.
-In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that in the event of a malfunction, a vehicle will be able to exit the altitude range of the highway within a duration of $t_\text{faulty}=1.5$.
-Such a requirement may be implemented practically as an fail-safe mechanism to which the vehicles revert when a malfunction is detected.
+In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that when a vehicle exhibits unpredictable behavior, it will be able to exit the altitude range of the highway within a duration of $t_\text{faulty}=1.5$.
+Such a requirement may be implemented practically as an fail-safe mechanism to which the vehicles revert when needed.
 

### 2016-05-13 docs/AIAA 2016 highway platooning/plat_sim.tex
A bit more proofreading

@@
 \subsection{Numerical Simulations}
-In this section, we consider several situations that vehicles in a platoon on an air highway may commonly encounter, and show via simulations the behaviors that emerge from the controllers we defined in Sections \ref{sec:reach_ctrl} and \ref{sec:other_ctrl}.
+In this section, we consider several situations that vehicles in a platoon on an air highway may commonly encounter, and show via simulations the behaviors that emerge from the controllers we defined in Sections \ref{sec:platooning}-\ref{sec:reach_ctrl} and \ref{sec:platooning}-\ref{sec:other_ctrl}.
 

### 2016-05-14 docs/AIAA 2016 highway platooning/conclusions.tex
Minor changes

@@
 To address the important and urgent problem of the traffic management of UAVs, we proposed to have platoons of UAVs traveling on air highways.
-We showed how such an airspace structure leads to a much easier safety and liveness analysis.
+We showed how such an airspace structure leads to much easier safety and liveness analysis.
 We provided simulations which show that by organizing vehicles into platoons, many complex maneuvers can be performed using just a few different reachable sets.
 
-For the placement of air highways over a region, we present the very intuitive and efficient fast marching algorithm for solving the Eikonal equation.
+For the placement of air highways over a region, we utilize the very intuitive and efficient fast marching algorithm for solving the Eikonal equation.
 Our algorithm allows us to take as input any arbitrary cost map representing the desirability of flying over any position in space, and produce a set of paths from any destination to a particular origin.
-Simple heurstic clustering methods can then be used to convert the sets of paths into a set of air highways.
+Simple heuristic clustering methods can then be used to convert the sets of paths into a set of air highways.
 

### 2016-05-21 docs/bayArea airHighway/airHighway.tex
Copied commit but removed a large mat file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
%\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage{graphicx}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{algorithm, algorithmic}
\usepackage{subcaption}
\numberwithin{algorithm}{section}

\newtheorem{defn}{Definition}
\newtheorem{thm}{Proposition}[section]
\newtheorem{cor}{Corollary}[section]
\newtheorem{rem}{Remark}
\newtheorem{lem}{Lemma}
%\newtheorem{IEEEproof}{Proof of Lemma}
%\usepackage{"../../my_macros"}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\title{\LARGE \bf Air Highways in the Bay Area}

\author{}

\begin{document}

\maketitle

\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
...
\end{abstract}

\section{Introduction}

\section{Map Processing}
Cities we are considering are shown in Figure \ref{fig:mapSpeed}.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{"fig/mapSpeed"}
	\caption{Yellow: $v_{\text{water}} = b^2$. Dark blue: $v_{\text{city}} = b^0$. Light blue: $v_{\text{other}} = b^1$}
	\label{fig:mapSpeed}
\end{figure}

The locations on the map are classified into three different regions, each with an associated cost. The cost deflects the desirability of flying an quadrotor over an area; a higher cost is less desirable. Water has the lowest cost, city has the highest cost, and everywhere else has an intermediate cost. Having assigned a cost to every location, we consider the problem of computing the lowest-cost path that connects two locations.

For path planning, we solve the Eikonal equation in which costs can be equivalently expressed as speed. We assign the following speeds to each region:

\begin{equation}
\begin{aligned}
v_{\text{water}} &= b^2 \\
v_{\text{city}} &= b^0 \\
v_{\text{other}} &= b^1
\end{aligned}
\end{equation}

\noindent where $b$ is a tuning parameter that adjusts the relative speeds/costs of each region. The speed profile we obtain is shown in Figure \ref{fig:mapSpeed}.

If we also consider the effect of airports by assigning a speed of $v_{\text{airport}}=b^-1$ to areas within a certain radius around airports, then we would obtain the speed profile in Figure \ref{fig:mapSpeedAirport}, in which region inside the black circles have speed $b^{-1}$:
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{"fig/mapSpeedAirport"}
	\caption{Yellow: $v_{\text{water}} = b^2$. Dark blue: $v_{\text{city}} = b^0$. Light blue: $v_{\text{other}} = b^1$. Black: $v_{\text{airport}} = b^{-1}$}
	\label{fig:mapSpeedAirport}
\end{figure}

\section{Highway Planning}
Having obtained the speed profiles, we now solve the Eikonal equation to determine the shortest paths from Concord (the assumed warehouse location) to the other 9 cities labeled on the map. These shortest paths give an idea of where air highways may be established, and are shown in red in Figures \ref{fig:pathsValue} and \ref{fig:pathsValueAirport}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{"fig/pathsValue"}
	\caption{}
	\label{fig:pathsValue}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{"fig/pathsValueAirport"}
	\caption{}
	\label{fig:pathsValueAirport}
\end{figure}

The plots on the right show a contour plot of the value function overlaid on top of the speed profile and the air highways. Notice that the highways are mostly over water, as expected, and the lengths of portions over cities is minimized. The presence of airports reroute some of the highways in order to minimize lengths of portions near the airport. Another interesting behavior to note that under the specified speeds the highways seem to naturally coincide with each other and split off only when the destination is nearby.

\end{document}

### 2016-05-21 code/airHighway/bayAreaMap.m

@@ -1,0 +1,138 @@
+clear all;
+close all;
+
+% ----- Grid -----
+g.dim = 2;
+g.min = -1;
+g.max = 1;
+g.N = 201;
+g.bdry = @addGhostExtrapolate;
+g2 = g;
+g = processGrid(g);
+
+% ----- Load images -----
+% Image indices
+imInd1 = 150:800;
+imInd2 = 850:1500;
+
+% Picture of Bay Area with city labels
+dots = imread('bayAreaLabels.png');
+dots = dots(imInd1, imInd2, :);
+
+% Bay Area converted to different region types
+colored = imread('bayAreaRegions.png');
+colored = colored(imInd1, imInd2, :);
+
+g2.N = size(dots,1);
+g2 = processGrid(g2);
+
+% ----- Plot raw data -----
+f1 = figure;
+
+% Bay area map with city names
+subplot(1,2,1), imagesc(g2.vs{1}, g2.vs{2}, dots); hold on
+
+% Compute speed profile based on region types
+speed = zeros(size(colored));
+
+b = 4;  % Region speed factor (tuning parameter)
+speed(colored==1) = b^2;   % Water
+speed(colored==0) = b^0;   % City
+speed(colored==2) = b^1;   % Other (trees, rocks, mountains)
+
+% Plot speed profile
+subplot(1,2,2), imagesc(g2.vs{1}, g2.vs{2}, speed); hold on
+
+% Figure window size
+f1.Position(3:4) = [1043 420];
+
+% ----- Airports -----
+SFO = [0.5785 -0.3354];
+rSFO = 0.3;
+obsSFO = sqrt((g2.xs{1}-SFO(1)).^2 + (g2.xs{2}-SFO(2)).^2) - rSFO;
+
+OAK = [0.3231 0.0006];
+rOAK = 0.2;
+obsOAK = sqrt((g2.xs{1}-OAK(1)).^2 + (g2.xs{2}-OAK(2)).^2) - rOAK;
+
+obs = shapeUnion(obsSFO, obsOAK);
+
+speed(obs<=0) = b^-1;
+
+% Plot obstacles
+subplot(1,2,1)
+contour(g2.xs{2}, g2.xs{1}, obs, [0 0], 'k-', 'linewidth', 2); 
+plot(SFO(2), SFO(1), 'k+', 'linewidth', 2)
+plot(OAK(2), OAK(1), 'k+', 'linewidth', 2)
+axis(g.axis)
+axis square
+
+subplot(1,2,2)
[…]

### 2016-05-21 code/platoon/@platoon/pVisualize.m
Get rid of mat files in July 8, 2015 commit

@@ -1,0 +1,12 @@
+function pVisualize(obj, f)
+% function pVisualize(obj)
+% Visualizes platoon
+% f - figure handle
+
+if nargin<2
+    f = figure;
+end
+
+visualizeVehicles(obj.vehicle, f)
+
+end

### 2016-05-21 code/platoon/pVisualizeTest.m

@@ -1,0 +1,6 @@
+clear all; close all;
+hw = highway([-100 0], [100 0]);
+
+p = popPlatoon(hw);
+
+p.pVisualize;

### 2016-05-21 code/platoon/@quadrotor/isSafe.m
got rid of a large file

@@ -1,0 +1,169 @@
+function [safe, uSafe, valuex, valueSx, valueCx] = ...
+  isSafe(obj, other, safeV, t)
+% function [safe, uSafe, valuex, valueSx, valueCx]
+%                                            = isSafe(obj, other, safeV, t)
+%
+% Checks whether this vehicle is safe within a time horizon of t with
+% respect to the other vehicle
+%
+% Inputs:  obj   - this vehicle
+%          other - other vehicle
+%          t     - time horizon
+%
+% Outputs: safe  - boolean variable indicating whether the relative state
+%                  is safe
+%          uSafe - the optimal safe controller
+%          valuex -the value of levelset function
+% Dynamics:
+%    \dot{p}_{x,r}   = v_{x,r}
+%    \dot{v}_{x,r}   = obj.u_x - other.u_x
+%    \dot{v}_{x,obj} = obj.u_x
+%    \dot{p}_{y,r}   = v_{y,r}
+%    \dot{v}_{y,r}   = obj.u_y - other.u_y
+%    \dot{v}_{y,obj} = obj.u_y
+%
+% Mo Chen, 2015-05-23
+% Modified: Qie Hu, 2015-07-01
+% Modified: Mo Chen. 2015-07-14
+
+% Unpack reachable set
+tau = safeV.tau;
+g = safeV.g;
+
+if safeV.g.dim == 3
+  dataC = safeV.dataC;
+  dataS = safeV.dataS;
+  
+  
+  % States in 6D reachable set
+  xr = obj.x(1) - other.x(1);
+  vxr = obj.x(2) - other.x(2);
+  vx = obj.x(2);
+  yr = obj.x(3) - other.x(3);
+  vyr = obj.x(4) - other.x(4);
+  vy = obj.x(4);
+  x = [xr vxr vx yr vyr vy];
+  
+  % If the state is more than a grid point away from the computation domain,
+  % then the relative system is safe
+  if any(x' <= [g.min+g.dx; g.min+g.dx])
+    safe = 1;
+    uSafe = [0; 0];
+    valueCx = max(dataC(:));
+    valuex = valueCx;
+    return
+  end
+  
+  if any(x' >= [g.max-g.dx; g.max-g.dx])
+    safe = 1;
+    uSafe = [0; 0];
+    valueCx = max(dataC(:));
+    valuex = valueCx;
+    return
+  end
+  
[…]

### 2016-05-21 docs/AIAA 2015/high_form.tex
no message
removed many big files

@@
 \subsection{Problem Formulation}
-We consider air highways to be line segments of constant altitude over a region.
-On the highway, a number of platoons may be present.
-The concept of platoons will be proposed in Section \ref{sec:platooning}.
-For now, denote the line segments $\hw(s), s\in[0,1]$.
-In a horizontal plane of fixed altitude, the end points of the line segment are given by $x_0 = \hw(0)$ and $y_0\hw(1)$.
-We assign a speed of travel $v_\hw$ and specify the direction of travel to be the direction from $\hw(0)$ to $\hw(1)$, denoted using a unit vector $\hwd = \frac{\hw(1) - \hw(0)}{\lVert\hw(1) - \hw(0)\rVert_2}$.
-
-Air highways not only provide structure to make the analysis of a large number of vehicles tractable, but also allow vehicles reach their destinations.
-Thus, given a origin-destination pair (eg.
-two cities), air highways must connect the two points while potentially satisfying other criteria.
-We call this the ``air highway placement problem'', and propose to address it in the following way:
-
-\begin{enumerate}
-\item Establish a cost map over a region of space.
-This cost map represents the aggregate cost of placing air highways over any point in space.
-The costs of placing air highways may include interference with commercial air spaces, cost of accidents, noise pollution, etc., and can be designed by government regulation bodies.
-\item Compute the cost-minimizing path from an origin to multiple destinations. 
-\item Convert the cost-minimizing path into a sequence of air highways. The endpoints of the resulting air highways can be thought of as waypoints in the airspace.
-\end{enumerate}

### 2016-05-21 code/airHighway/angle_diff.m

@@ -1,0 +1,9 @@
+function diff = angle_diff(angle1, angle2)
+% Computes the difference between two angles, taking into account wrapping
+% at pi
+
+diff = abs(angle2 - angle1);
+if diff >= pi;
+  diff = 2*pi - diff;
+end
+end

### 2016-05-21 code/airHighway/angle_diff_test.m

@@ -1,0 +1,9 @@
+function angle_diff_test()
+
+disp(['True angle difference = 0.2; computed angle difference = ' ...
+  num2str(angle_diff(0.1, -0.1))])
+
+disp(['True angle difference = 0.2; computed angle difference = ' ...
+  num2str(angle_diff(pi-0.1, -pi+0.1))])
+
+end

### 2016-05-21 code/airHighway/angle_mean.m

@@ -1,0 +1,15 @@
+function th_out = angle_mean(th_in, thresh)
+% Computes the average angle taking into account wrapping at +/-pi
+%
+% thresh - threshold for being considered close to pi
+
+if nargin<2
+  thresh = 5 * pi / 180;
+end
+
+if (min(th_in)-(-pi) < thresh) && (pi-max(th_in) < thresh)
+  th_in(th_in<0) = th_in(th_in<0) + 2*pi;
+end
+
+th_out = mean(th_in);
+end

### 2016-05-21 code/airHighway/angle_mean_test.m

@@ -1,0 +1,32 @@
+function angle_mean_test()
+% Create a bunch of angles near pi
+N = 100;
+noise = pi/4;
+
+mean = pi;
+[raw_thetas, thetas] = gen_angles(mean, noise, N);
+
+figure;
+plot(raw_thetas, 'k-'); hold on
+plot(thetas, 'b.'); 
+refline(0, angle_mean(thetas,noise))
+title(['Horizontal line should be near ' num2str(mean)])
+
+% Create a bunch of angles away from pi
+mean = -pi+noise + 2*(pi-noise)*rand;
+[raw_thetas, thetas] = gen_angles(mean, noise, N);
+
+figure;
+plot(raw_thetas, 'k-'); hold on
+plot(thetas, 'b.'); 
+refline(0, angle_mean(thetas))
+title(['Horizontal line should be near ' num2str(mean)])
+end
+
+function [raw_thetas, thetas] = gen_angles(mean, noise, N)
+% Generates N angles with some mean and noise around the mean
+% Outputs both the raw angles and the wrapped angles around pi
+raw_thetas = mean-noise + 2*noise*rand(N,1);
+thetas = raw_thetas;
+thetas(thetas>pi) = thetas(thetas>pi) - 2*pi;
+end

### 2016-05-21 code/airHighway/bayAreaMap.m

@@ -61,14 +61,14 @@ speed(obs<=0) = b^-1;
 
 % Plot obstacles
 subplot(1,2,1)
-contour(g2.xs{2}, g2.xs{1}, obs, [0 0], 'k-', 'linewidth', 2); 
+contour(g2.xs{2}, g2.xs{1}, obs, [0 0], 'k-', 'linewidth', 2);
 plot(SFO(2), SFO(1), 'k+', 'linewidth', 2)
 plot(OAK(2), OAK(1), 'k+', 'linewidth', 2)
 axis(g.axis)
 axis square
 
 subplot(1,2,2)
-contour(g2.xs{2}, g2.xs{1}, obs, [0 0], 'k-' , 'linewidth', 2); 
+contour(g2.xs{2}, g2.xs{1}, obs, [0 0], 'k-' , 'linewidth', 2);
 plot(SFO(2), SFO(1), 'k+', 'linewidth', 2)
 plot(OAK(2), OAK(1), 'k+', 'linewidth', 2)
 axis(g.axis)
@@ -76,25 +76,25 @@ axis square
 
 % ----- Compute time to reach from "warehouse" in Concord -----
 target = [-0.4338 0.4185];  % Concord
-u = compute_value(g, target, speed); 
+u = compute_value(g, target, speed);
 
 % ----- Paths to warehouse from different cities
 IC = [0.1354 -0.4431; ...   % San Francisco
-    -0.7877 -0.08;          % Vallejo
-    -0.4215 -0.6862;        % San Rafael
-    -0.1169 -0.1354;        % Berkeley
-    -0.5108 0.9169;         % Antioch
-    0.4369 0.3108;          % Hayward
-    0.5908 -0.5938;         % Pacifica
-    0.7323 -0.2338;         % San Mateo
-    0.7723 0.5169];         % Fremont
+  -0.7877 -0.08;          % Vallejo
+  -0.4215 -0.6862;        % San Rafael
+  -0.1169 -0.1354;        % Berkeley
+  -0.5108 0.9169;         % Antioch
+  0.4369 0.3108;          % Hayward
+  0.5908 -0.5938;         % Pacifica
+  0.7323 -0.2338;         % San Mateo
+  0.7723 0.5169];         % Fremont
 
 P = extractCostates(g,u, @upwindFirstWENO5, true);   % Gradient of value function
 
[…]

### 2016-05-21 code/airHighway/first_endpt.m

@@ -1,0 +1,53 @@
+function ind = first_endpt(path, Navg, threshold)
+% function ind = first_endpt(path, Navg, threshold)
+%
+% Given a path, returns the first highway end point, determined by a change
+% in direction of more than threshold degrees.
+%
+% Inputs:  path      - a list of points representing the path
+%          Navg      - number of points around any given point on path for
+%                      which the average is taken in order to compute the
+%                      direction
+%          threshold - angle threshold in degrees at which a new segment of
+%                      highway begins
+%
+% Output: ind        - the index of path at which a new highway segment
+%                      begins
+%
+% Mo Chen, 2015-09-30
+
+% Default number of angles to average
+if nargin<2
+  Navg = 0;
+end
+
+% Default angle threshold (in degrees) for ending a highway
+if nargin<3
+  threshold = 15;
+end
+
+% Convert angle to radians
+threshold = threshold * pi / 180;
+
+% Initial heading
+x0 = path(1,1);
+y0 = path(2,1);
+theta0 = angle_mean( ...
+  atan2(y0-path(2,2:2+2*Navg), x0-path(1,2:2+2*Navg)) );
+ind = 2+Navg;
+
+% Subsequent headings along the path
+for i = 3+Navg:size(path,2)-Navg
+  x0 = path(1,i-Navg-1);
+  y0 = path(2,i-Navg-1);
+  theta = angle_mean(atan2(y0-path(2,i-Navg:i+Navg), x0-path(1,i-Navg:i+Navg)) );
+  
+  diff = angle_diff(theta, theta0);
+  
+  ind = i;
+  if diff >= threshold
+    break;
+  end
+end
+
+end

### 2016-05-21 code/airHighway/first_endpt_test.m

@@ -1,0 +1,48 @@
+function first_endpt_test()
+%% Load path
+load('bay_area_raw_paths', 'spath');
+i = randi(length(spath));
+path = spath{i};
+
+%% Compute first endpoint
+x0 = path(2,1);
+y0 = path(1,1);
+
+thetas = atan2(y0-path(2,2:end), x0-path(1,2:end));
+ind = first_endpt(path);
+
+disp(['Index of first endpoint: ' num2str(ind)])
+
+%% Load images
+% Image indices
+imInd1 = 150:800;
+imInd2 = 850:1500;
+
+% Picture of Bay Area with city labels
+dots = imread('bayAreaLabels.png');
+dots = dots(imInd1, imInd2, :);
+
+%% Grid
+g.dim = 2;
+g.min = -1;
+g.max = 1;
+g.N = size(dots,1);
+g.bdry = @addGhostExtrapolate;
+g = processGrid(g);
+
+%% Plot results
+f=figure;
+subplot(1,2,1)
+plot(thetas); hold on;
+plot(ind, thetas(ind), 'ro')
+
+subplot(1,2,2)
+% Bay area map with city names
+imagesc(g.vs{1}, g.vs{2}, dots); hold on
+plot(path(2, :), path(1, :), 'r.')
+plot(path(2, ind), path(1, ind), 'ro')
+
+% Figure window size
+f.Position(3:4) = [1043 420];
+
+end

### 2016-05-21 code/airHighway/path2hws.m

@@ -1,0 +1,39 @@
+function pts = path2hws(path, Navg, threshold)
+% function pts = path2hws(path)
+%
+% Converts a finely spaced sequence of points (eg. from FMM) to a sparse
+% sequence of waypoints which form the start and ending points of air
+% highways
+%
+% Input: path - 2 x N matrix representing the sequence of points
+%        threshold - angle threshold in degrees for starting a new segment
+%                    of air highway
+% Ouptut: pts - The starting and ending points of air highways
+%
+% Mo Chen, 2015-09-30
+
+% Default parameters
+if nargin<2
+  Navg = 0;
+end
+
+if nargin<3
+  threshold = 15;
+end
+
+% Initial point
+ind = 1;
+pts = [path(1,ind); path(2,ind)];
+
+% Create segments
+while size(path,2) > 2*Navg
+  ind = first_endpt(path, Navg, threshold);
+  pts = [pts [path(1,ind); path(2,ind)]];
+  path(:, 1:ind) = [];
+end
+
+% Final point
+if ~isempty(path)
+  pts = [pts [path(1,end); path(2,end)]];
+end
+end

### 2016-05-21 code/airHighway/path2hws_test.m

@@ -1,0 +1,39 @@
+clear all;
+close all;
+
+% ----- Grid -----
+g.dim = 2;
+g.min = -1;
+g.max = 1;
+g.N = 201;
+g.bdry = @addGhostExtrapolate;
+g2 = g;
+g = processGrid(g);
+
+% ----- Load path -----
+load('bay_area_raw_paths')
+
+i = randi(length(spath));
+raw_path = spath{i};
+
+% Compute indices
+pts = path2hws(raw_path);
+
+% ----- Load images -----
+% Image indices
+imInd1 = 150:800;
+imInd2 = 850:1500;
+
+% Picture of Bay Area with city labels
+dots = imread('bayAreaLabels.png');
+dots = dots(imInd1, imInd2, :);
+
+g2.N = size(dots,1);
+g2 = processGrid(g2);
+
+% ----- Plot -----
+figure;
+image(g2.vs{1}, g2.vs{2},dots); hold on
+plot(raw_path(2,:), raw_path(1,:), 'b-')
+plot(pts(2,:), pts(1,:), 'ro-')
+axis square

### 2016-05-21 code/platoon/@platoon/assimVehicle.m

@@ -24,18 +24,20 @@ function assimVehicle(obj, vehicle)
 % end
 
 % Check if the platoon is already full
-if strcmp(vehicle.q, 'Free')
-    % Vehicle is free
-    if obj.loIdx >= obj.nmax
-        fprintf('Platoon is already full! \n');
-        return;
-    end
-else
-    % Vehicle is a leader
-    % Last occupied index of vehicle's platoon
-    if obj.loIdx + vehicle.p.loIdx > obj.nmax
-        fprintf('Platoon is already full! \n');
-        return
+if isempty(vehicle.idxJoin) %HACK ALERT: there is a problem when a higher indexed uav reaches its target position in the platoon before a lowersimulateNormal2.m indexed uav
+    if strcmp(vehicle.q, 'Free')
+        % Vehicle is free
+        if obj.loIdx >= obj.nmax
+            fprintf('Platoon is already full! \n');
+            return;
+        end
+    else
+        % Vehicle is a leader
+        % Last occupied index of vehicle's platoon
+        if obj.loIdx + vehicle.p.loIdx > obj.nmax
+            fprintf('Platoon is already full! \n');
+            return
+        end
     end
 end
 
@@ -47,7 +49,7 @@ if dist > obj.hw.width
 end
 
 % Find idxJoin 
-if strcmp(vehicle.q, 'Free')
+if strcmp(vehicle.q, 'Free') 
     % vehicle is free
     % join vehicle at first empty slot in obj
     if isempty(vehicle.idxJoin)

### 2016-05-21 code/platoon/@platoon/phantomPosition.m

@@ -9,9 +9,10 @@ function xPhantom = phantomPosition(obj, idx)
 % Output:  xPhantom - phantom position
 %
 % Mo Chen, Qie Hu, Jaime Fisac, 2015-06-14
+% Modified: Mo Chen, 2015-07-06
 
 % Get leader vehicle and highway heading
-Leader = obj.vehicle(1);
+Leader = obj.vehicles{1};
 
 % Vehicle spacing is 3*2*sqrt(2) between each vehicle
 spacing = 3*(2*sqrt(2));

### 2016-05-21 code/platoon/@platoon/platoon.m

@@ -39,10 +39,13 @@ classdef platoon < handle
     
     % Footprint of platoon
     safeV
+    
+    %Liveness reachable set for tracking platoon positions
+    liveV
   end
   
   methods
-    function obj = platoon(leader, hw, nmax, followTime)
+    function obj = platoon(leader, hw, nmax, followTime,FourD)
       % function obj = platoon(leader, hw, nmax, followTime)
       % Constructor for platoon object
       %
@@ -111,6 +114,24 @@ classdef platoon < handle
       
       % Remove merge highway value function
       obj.vehicles{1}.mergeHighwayV = [];
+      
+      if nargin < 5
+         FourD=1;
+      end
+      
+      if FourD
+         filename = '../../data/quad_liveness_4D.mat';
+      else 
+         filename = '../../data/quad_liveness_2x2D.mat';
+      end
+      
+      load(filename)
+      
+      obj.liveV=liveV;
+      
+      
+      
+      
     end
   end
 end

### 2016-05-21 code/platoon/@quadrotor/quadrotor.m

@@ -47,9 +47,9 @@ classdef quadrotor < handle
     hvxvy           % Velocity
     hvxvyhist       % Velocity history
     
-    % Safety sets (with respect to 5 nearest vehicles, or vehicles in the same platoon)
-    hsafeV = cell(5,1);
-    
+    % Safety sets (with respect to 5 nearest vehicles, or vehicles in the same platoon; + intruder/faulty)
+    hsafeV = cell(6,1);
+        
     hmergeHighwayV  % Merging reachable set
     hmergePlatoonV  % Merging reachable set
 

### 2016-05-21 code/platoon/createLivenessSet.m

@@ -1,0 +1,19 @@
+[datax, datay, g1, g2, tau]=quad2D_joinHighwayPlatoon([0 0 0 0],0);
+
+liveV.datax=datax;
+liveV.datay=datay;
+liveV.g1=g1;
+liveV.g2=g2;
+liveV.tau=tau;
+liveV.gdim=2;
+
+save quad_liveness_2x2D liveV
+
+clear liveV
+
+[~,~,liveV.g,liveV.data,~,~,liveV.grad,~]=recon2x2D(tau,g1,datax,g2,datay,...
+[g1.min-1 g1.max+1;g2.min-1 g2.max+1]);                                       
+liveV.tau=tau;
+liveV.gdim=4;
+
+save quad_liveness_4D liveV

### 2016-05-21 code/platoon/createSafeSet.m

@@ -1,0 +1,10 @@
+[dataC,g,tau]=quad2Dcollision(2,0);
+
+save quad_safe_2x2D dataC g tau
+
+clear safeV
+
+[~,~,g,dataC,~,~,grad,~]=recon2x2D(tau,g,dataC,g,dataC,...
+[g.min-1 g.max+1;g.min-1 g.max+1]);                                       
+
+save quad_safe_4D g dataC grad tau

### 2016-05-21 code/platoon/generateReachInfo.m

@@ -1,15 +1,33 @@
 function [reachInfo, safeV] = generateReachInfo( filename )
+% function [reachInfo, safeV] = generateReachInfo( filename )
+%
+% Generates the reachable set information from a saved data file
+%
+% Mo Chen, 2015-07-14
 
 if nargin < 1
-    filename = '../../data/quad3D.mat';
+%   filename = '../../data/quad3D.mat';
+  filename = '../../data/quad2Dcollision.mat';
+%    filename = '../../data/quad_safe_2x2D.mat';
+
 end
 
 load(filename)
 
 safeV.tau = tau;
-safeV.dataS = dataS;
-safeV.dataC = dataC;
 safeV.g = g;
+
+if g.dim == 3
+  safeV.dataS = dataS;
+  safeV.dataC = dataC;
+elseif g.dim == 2
+  safeV.dataC = dataC;
+elseif g.dim == 4
+  safeV.dataC = dataC;
+  safeV.grad  = grad;
+else
+  error('The safety reachable set must be 2, 3 or 4D!')
+end
 
 reachInfo.uMax = 1.7;
 reachInfo.uMin = -1.7;
@@ -17,7 +35,3 @@ reachInfo.vMax = 5;
 reachInfo.vMin = -5;
 
 end
-
-
-
-

### 2016-05-21 code/platoon/popPlatoon.m

@@ -7,8 +7,9 @@ function p = popPlatoon(hw, leaderPos, leaderVel, numVehicles, ID1)
 % ID1 - starting ID
 %
 
-if nargin<3, leaderVel = [0;0]; end
-if nargin<4, numVehicles = 1; end
+if nargin<2, leaderPos = [0 0]; end
+if nargin<3, leaderVel = [0 0]; end
+if nargin<4, numVehicles = 5; end
 if nargin<5,         ID1 = 1; end
 
 % % Hard code time discretization for now

### 2016-05-21 code/platoon/quad2D_joinHighway.m

@@ -35,12 +35,12 @@ if nargin<2
 end
 
 if nargin<1
-    x = [0 3 0 0];
+    x = [0 0 0 0];
 end
 
 %---------------------------------------------------------------------------
 % Integration parameters.
-tMax = 5;                    % End time.
+tMax = 3.8;                    % End time.
 plotSteps = 1;               % How many intermediate plots to produce?
 t0 = 0;                      % Start time.
 singleStep = 1;              % Plot at each timestep (overrides tPlot).
@@ -64,12 +64,12 @@ vMin = -5;
 %---------------------------------------------------------------------------
 % Approximately how many grid cells?
 %   (Slightly different grid cell counts will be chosen for each dimension.)
-Nx = 101;
+Nx = 41;
 
 % Create the grid.
 g.dim = 2;                              % Number of dimensions
-g.min = [ -30 ; 1.1*vMin ];     % Bounds on computational domain
-g.max = [ 30 ; 1.1*vMax ];
+g.min = [ -10 ; 2.1*vMin ];     % Bounds on computational domain
+g.max = [ 10 ; 2.1*vMax ];
 g.bdry = @addGhostExtrapolate;
 g.N = [ Nx; ceil(Nx/(g.max(1)-g.min(1))*(g.max(2)-g.min(2)))];
 g = processGrid(g);
@@ -184,7 +184,7 @@ while(tMax - tNow > small * tMax)
         h2.ZData = datay(:,:,end);
     end
     %
-    %     drawnow;
+         drawnow;
 end
 
 %---------------------------------------------------------------------------

### 2016-05-21 code/platoon/quad2Dcollision.m

@@ -43,7 +43,7 @@ end
 
 %---------------------------------------------------------------------------
 % Integration parameters.
-tMax = 3.5;                    % End time.
+tMax = 4;                    % End time.
 plotSteps = 1;               % How many intermediate plots to produce?
 t0 = 0;                      % Start time.
 singleStep = 1;              % Plot at each timestep (overrides tPlot).
@@ -68,23 +68,24 @@ v1Max = 5;
 %---------------------------------------------------------------------------
 % Approximately how many grid cells?
 %   (Slightly different grid cell counts will be chosen for each dimension.)
-Nx = 81;
+Nx = 41;
 
 % Create the grid.
 g2D.dim = 2;                           % Number of dimensions
-g2D.min = [-25; -2.1*v1Min ];     % Bounds on computational domain
-g2D.max = [ 25;  2.1*v1Max ];
+g2D.min = [-15; -2.1*v1Min ];     % Bounds on computational domain
+g2D.max = [ 15;  2.1*v1Max ];
 g2D.bdry = @addGhostExtrapolate;
 g2D.N = [ Nx; ceil(1.5*Nx/(g2D.max(1)-g2D.min(1))*(g2D.max(2)-g2D.min(2)))];
 g2D = processGrid(g2D);
 
 % Create the grid.
 gy.dim = 2;                              % Number of dimensions
-gy.min = [-25; -2.1*v1Min ];     % Bounds on computational domain
-gy.max = [ 25;  2.1*v1Max ];
+gy.min = [-15; -2.1*v1Min ];     % Bounds on computational domain
+gy.max = [ 15;  2.1*v1Max ];
 gy.bdry = @addGhostExtrapolate;
 gy.N = [ Nx; ceil(1.5*Nx/(gy.max(1)-gy.min(1))*(gy.max(2)-gy.min(2)))];
 gy = processGrid(gy);
+
 
 % ----------------- Target -----------------
 % Below separation distance for any relative velocity

### 2016-05-21 code/platoon/@Plane/getPosition.m
Plane class now works with TFM

@@ -1,0 +1,6 @@
+function [p, phist] = getPosition(obj)
+% pos = getPosition(obj)
+% Gets the position (x,y) of a plane
+p = obj.x(1:2);
+phist = obj.xhist(1:2, :);
+end

### 2016-05-21 code/platoon/@Plane/getRelativeStates.m

@@ -1,0 +1,38 @@
+function relStates = getRelativeStates(obj, others)
+% function relStates = getRelativeStates(obj, others)
+% Finds state of other plane objects with respect to one plane
+%
+% Inputs:   obj - current plane object
+%           others - other planes whose relative states relative
+%                    to obj are to be found; this
+%                    should be a n x 1 or 1 x n cell.
+%
+% Outputs:  relStates - relative state of each other plane
+%
+% Mahesh Vashishtha, 2015-10-27
+others = checkVehiclesList(others, 'Plane');
+relStates = zeros(length(others),4);
+xp = obj.x;
+for i=1:length(others)
+  xe = others{i}.x;
+  if size(xe, 1) ~= 4
+    xe = xe';
+  end
+  if size(xp, 1) ~= 4
+    xp = xp';
+  end
+  xr = xp -xe;
+  % rotate position vector so it is correct relative to xe heading
+  xr(1:2) = [cos(-xe(3)) -sin(-xe(3)); sin(-xe(3)) cos(-xe(3))] * xr(1:2);
+  xr = xr';
+  if xr(3) >= 2*pi
+    xr(3) = xr(3) - 2*pi;
+  end
+  if xr(3) < 0
+    xr(3) = xr(3) + 2*pi;
+  end
+  vel_comps = arrayfun(@getVelocity, [obj; others{i}],'un',0);
+  xr(4) = norm(cell2mat(vel_comps(1,:)) - cell2mat(vel_comps(2,:)));
+  relStates(i,:) = xr;
+end
+end

### 2016-05-21 code/platoon/@Plane/getVelocity.m

@@ -1,0 +1,11 @@
+function vel = getVelocity(obj)
+% vel = getPosition(obj)
+% Finds the velocity (v_x,v_y) of a plane
+
+if obj.nx == 3
+  vel = obj.speed * [cos(obj.x(3)) sin(obj.x(3))];
+else
+  vel = obj.x(4) * [cos(obj.x(3)) sin(obj.x(3))];
+end
+
+end

### 2016-05-21 code/platoon/RS_core/pl_pl_collision_3D.m

@@ -1,0 +1,397 @@
+function [g, data, grad] = pl_pl_collision_3D(d, speed, visualize)
+% function [ data, g, data0 ] = pl_pl_collision_3D(d)
+%
+% In this example, the target set is a circle at the origin (cylinder in 3D)
+% that represents a collision in relative coordinates between the evader
+% (player a, fixed at the origin facing right) and the pursuer (player b).
+%
+% The relative coordinate dynamics are
+%
+%   \dot x    = -v_a + v_b \cos \psi + a y
+%	  \dot y    = v_b \sin \psi - a x
+%	  \dot \psi = b - a
+%
+% where v_a and v_b are constants, input a is trying to avoid the target
+%	input b is trying to hit the target.
+%
+% For more details, see my PhD thesis, section 3.1.
+%
+% This function was originally designed as a script file, so most of the
+% options can only be modified in the file.  For example, edit the file to
+% change the grid dimension, boundary conditions, aircraft parameters, etc.
+%
+% To get exactly the result from the thesis choose:
+%   targetRadius = 5, velocityA = velocityB = 5, inputA = inputB = +1.
+%
+% Input Parameters:
+%
+%   accuracy: Controls the order of approximations.
+%     'low': Use odeCFL1 and upwindFirstFirst.
+%     'medium': Use odeCFL2 and upwindFirstENO2 (default).
+%     'high': Use odeCFL3 and upwindFirstENO3.
+%     'veryHigh': Use odeCFL3 and upwindFirstWENO5.
+%
+% Output Parameters:
+%
+%   data: Implicit surface function at t_max.
+%
+%   g: Grid structure on which data was computed.
+%
+%   data0: Implicit surface function at t_0.
+
+% Copyright 2004 Ian M. Mitchell (mitchell@cs.ubc.ca).
+% This software is used, copied and distributed under the licensing
+%   agreement contained in the file LICENSE in the top directory of
+%   the distribution.
+%
+% Ian Mitchell, 3/26/04
+% Subversion tags for version control purposes.
+% $Date: 2012-07-04 14:27:00 -0700 (Wed, 04 Jul 2012) $
+% $Id: air3D.m 74 2012-07-04 21:27:00Z mitchell $
+
+if nargin < 1
+  d = 2;
+end
+
+if nargin < 2
+  speed = 10;
+end
+
+if nargin < 3
+  visualize = true;
+end
+
+%---------------------------------------------------------------------------
[…]

### 2016-05-21 code/platoon/tests/Plane_test.m

@@ -1,0 +1,91 @@
+function Plane_test()
+% Tests the Plane class (a little bit)
+% Also an example if using the Plane class.
+%
+% In this example, plane 2 always goes straight, and plane 1 avoids plane
+% 2 if needed
+%
+% Mahesh Vashishtha, 2015-11-04
+
+%% Preliminaries
+addpath('..') % needed for Plane class
+
+% load the output g and data from running air3D.m in the levelset toolbox
+load('Plane_test_data/air3D_data') 
+capture_radius = 5;
+speed = 5;
+
+% Initialize Planes
+pl1 = Plane([0 20 -pi/4]);
+pl1.speed = speed; % This is needed if the state is 3D!
+pl2 = Plane([20 0 3*pi/4]);
+pl2.speed = speed;
+safety_threshold = 1;
+
+% Compute gradients from value function
+costates = extractCostates(g, data);
+
+figure;
+pl1.plotPosition;
+pl2.plotPosition;
+axis([-5 25 -5 25]);
+
+% Integration parameters
+tMax = 5;
+dt = 0.1;
+t = dt:dt:tMax;
+
+for i = 1:length(t)
+  %% Check if the planes have collided (should not happen!)
+  p1_pos  = pl1.getPosition;
+  p2_pos = pl2.getPosition;
+  
+  if norm(pl1.getPosition - pl2.getPosition) <= capture_radius
+    error('Planes collided!')
+  end
+  
+  %% Get relative state of planes to plug into the value function
+  xr = pl2.x - pl1.x;
+
+  % rotate position vector so it is correct relative to xe heading
+  xr(1:2) = rotate2D(xr(1:2), -pl1.x(3));
+
+  % Wrap angle if needed
+  if xr(3) >= 2*pi
+    xr(3) = xr(3) - 2*pi;
+  end
+
+  if xr(3) < 0
+    xr(3) = xr(3) + 2*pi;
+  end
+
+  %% Compute controls
+  valuex = eval_u(g, data, xr); % Plug relative state into value function
+  disp(['Safety value: ' num2str(valuex)])
+  
+  % Plane 2 goes straight
+  u2 = 0;
+  if valuex <= safety_threshold
+    % Plane 1 computes optimal control to avoid plane 2 if unsafe
+    p = calculateCostate(g, costates, xr);
+    if p(1) * xr(2) - p(2) * xr(1) - p(3) >= 0
+      u1 = 1;
[…]

### 2016-05-21 code/platoon/tests/checkPWSafety_pl_pl_test.m

@@ -1,0 +1,48 @@
+function checkPWSafety_pl_pl_test()
+addpath('..')
+addpath('../RS_core')
+
+% Initialize TFM
+tfm = TFM;
+tfm.computeRS('pl_pl_safe_V');
+
+% Create planes and add them to TFM
+pl1 = Plane([0 0 0]);
+pl1.speed = 10;
+pl2 = Plane([100 0 pi]);
+pl2.speed = 10;
+tfm.addActiveAgents(pl1);
+tfm.addActiveAgents(pl2);
+
+% Plot initial setup
+figure;
+for j = 1:length(tfm.aas)
+  tfm.aas{j}.plotPosition;
+  hold on
+end
+xlim([-10 110])
+ylim([-60 60])
+axis square
+
+% Integration parameters
+tMax = 10;
+t = 0:tfm.dt:tMax;
+
+% Integrate
+for i = 1:length(t)
+  [safe, uSafe] = tfm.checkAASafety;
+
+  for j = 1:length(tfm.aas)
+    if safe(j)
+      u = 0;
+    else
+      u = uSafe{j};
+    end
+    
+    tfm.aas{j}.updateState(u, tfm.dt);
+    tfm.aas{j}.plotPosition;
+  end
+  drawnow;
+
+end
+end

### 2016-05-21 code/platoon/tests/checkPWSafety_qr_qr_test.m

@@ -1,0 +1,46 @@
+function checkPWSafety_qr_qr_test()
+addpath('..')
+addpath('../RS_core')
+
+% Initialize TFM
+tfm = TFM;
+tfm.computeRS('qr_qr_safeV');
+
+% Add quadrotors to TFM
+tfm.addActiveAgents(Quadrotor([0 3 0 0]));
+tfm.addActiveAgents(Quadrotor([20 -3 0 0]));
+
+% Plot initial setup
+figure;
+for j = 1:length(tfm.aas)
+  tfm.aas{j}.plotPosition;
+  hold on
+end
+xlim([-1 21])
+ylim([-11 11])
+axis square
+
+% Integration parameters
+tMax = 15;
+t = 0:tfm.dt:tMax;
+
+% Integrate
+for i = 1:length(t)
+  [safe, uSafe] = tfm.checkAASafety;
+
+  
+  for j = 1:length(tfm.aas)
+    if safe(j)
+      u = [0; 0];
+    else
+      u = uSafe{j};
+    end
+    
+    tfm.aas{j}.updateState(u, tfm.dt);
+    tfm.aas{j}.plotPosition;
+  end
+  drawnow;
+end
+
+
+end

### 2016-05-21 code/platoon/tests/legacy/collision_demo/save_air3d.m

@@ -1,0 +1,13 @@
+
+% from demo: (r, v_a, v_b, max_a, max_b, tMax) = (5, 5, 5, 1, 1, 5)
+RADIUS = 5;
+V_A = 5;
+V_B = 5;
+MAX_A = 1;
+MAX_B = 1;
+
+% compute g
+[ data, g, data0 ] = air3D('low', RADIUS, V_A, V_B, MAX_A, MAX_B, 5);
+
+save datafile.mat data
+save gfile.mat g

### 2016-07-06 docs/AIAA 2016 highway platooning/high_form.tex
removed comments

@@
 two cities), air highways must connect the two points while potentially satisfying other criteria.
-With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution.
+In addition, optimal air highway locations should ideally be able to be recomputed in real time when necessary.
+With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution that allows for real time recomputation.
 
@@
 \end{equation}
-\MCnote{The number of constraints here change with the decision variable $N$, but I'm ignoring this fact as the point is that this optimization is hard to solve, and therefore we solve the Eikonal equation instead.}
 
-\noindent where $R(\cdot)$ is a regularizer, such as $R(N) = N^2$. \MCnote{Added regularizer to prevent $N\rightarrow\infty$}
+\noindent where $R(\cdot)$ is a regularizer, such as $R(N) = N^2$.
 

### 2016-07-06 docs/AIAA 2016 highway platooning/high_sim.tex
removed comments

@@
 \subsection{Real-Time Highway Location Updates}
-\MCnote{New section}Since \eqref{eq:eikonal} can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost map changes.
+Since \eqref{eq:eikonal} can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost map changes.
 This flexibility can be useful in any situation in which unforeseen circumstances could cause a change in the cost of a particular region of the airspace.

### 2016-07-06 docs/AIAA 2016 highway platooning/high_waypoints.tex
removed comments

@@
 \subsection{From Paths to Waypoints}
-\MCnote{Changed wording in this section to say the sparsification of points on a path is not our focus, but just an illustration.}
 Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a closely-spaced set of points.

### 2016-07-06 docs/AIAA 2016 highway platooning/introduction.tex
removed comments

@@
 Reachability analysis was used in \cite{Alam11} to analyze a platoon of two trucks in order to minimize drag by minimizing the following distance while maintaining collision avoidance safety guarantees.
-Finally, \cite{Sabau16} provided a method for guaranteeing string stability and eliminating accordion effects for a heterogeneous platoon of vehicles with linear time-invariant dynamics.\MCnote{Added Sabau's paper}
+Finally, \cite{Sabau16} provided a method for guaranteeing string stability and eliminating accordion effects for a heterogeneous platoon of vehicles with linear time-invariant dynamics.
 
@@
 Finally, we show several simulations to illustrate the behavior of UAVs in various scenarios.
-\MCnote{Slightly weakened claims about guaranteeing safety in last paragraph.}

### 2016-07-06 docs/AIAA 2016 highway platooning/plat_form.tex
A bit more proofreading
removed comments

@@
 \section{Unmanned Aerial Vehicle Platooning \label{sec:platooning}}
-\MCnote{Added introduction to this section}Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways.
+Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways.
 The platooning concept provides a structural solution for monitoring and ensuring the safety of a large number of UAVs.
@@
 \begin{equation}
+\label{eq:veh_dyn}
 \dot{x} = f(x,u)
@@
 A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $t_\text{faulty}$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system.
-\MCnote{Faulty mode now includes vehicles which could cause additional conflicts by avoiding another faulty vehicle}
 \end{itemize}
@@
 \item merge onto a highway to form a platoon
-\item join a new or different platoon
+\item join a new platoon
 \item leave a platoon to create a new one

### 2016-07-07 docs/AIAA 2016 highway platooning/high_form.tex
added NASA UTM paper AIAA 2016, and partly done proofreading (currently at the end of page 4)

@@
 Air highways must not only provide structure to make the analysis of a large number of vehicles tractable, but also allow vehicles to reach their destinations while minimizing any relevant costs to the vehicles and to the surrounding regions.
-Thus, given a origin-destination pair (eg.
+Such costs can for example take into account people, assets on the ground, and manned aviation, entities to which UAVs pose the biggest risks \cite{Kopardekar16}.
+Thus, given an origin-destination pair (eg.
 two cities), air highways must connect the two points while potentially satisfying other criteria.
-In addition, optimal air highway locations should ideally be able to be recomputed in real time when necessary.
-With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution that allows for real time recomputation.
+In addition, optimal air highway locations should ideally be able to be recomputed in real-time when necessary in order to update airspace constraints on-the-fly, in case, for example, airport configurations change or certain airspaces have to be closed \cite{Kopardekar16}.
+With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution that allows for real-time recomputation.
 
@@
 Locations with high cost could, for example, include densely populated areas and areas around airports.
-In general, the cost map $\cmap(\cdot)$ may be used to model cost of interference with commercial airspaces, cost of accidents, cost of noise pollution, etc., and can be designed by government regulation bodies.
+In general, the cost map $\cmap(\cdot)$ may be used to model cost of interference with commercial airspaces, cost of accidents, cost of noise pollution, risks incurred, etc., and can be flexibly specified by government regulation bodies.
 

### 2016-07-07 docs/AIAA 2016 highway platooning/main.tex
removed comments
added NASA UTM paper AIAA 2016, and partly done proofreading (currently at the end of page 4)

@@
 
-\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, aerial surveillance, and disaster response.
-As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met.
+\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, aerial surveillance, videography, and disaster response.
+As a result, unmanned aerial systems (UAS) traffic management (UTM) has become necessary to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met.
 Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers is unrestricted.
@@
 For the air highway placement problem, we use the flexible and efficient fast marching method to solve the Eikonal equation, which produces a sequence of air highways that minimizes the cost of flying from an origin to any destination.
+Under our proposed method, the placement of air highways can be updated in real-time to accommodate sudden changes in the airspace.
 Within the platoons that travel on the air highways, we model each vehicle as a hybrid system with modes corresponding to its role in the platoon.
@@
 \maketitle
-\MCnote{Changed title (used to be ``Guaranteeing Safety ...''}
 \section*{Nomenclature}

### 2016-07-08 docs/AIAA 2016 highway platooning/high_waypoints.tex
proofreading... on page 15

@@
 Repeating the entire process for every path, we obtain waypoints for all the cost-minimizing paths under consideration.
-Figure \ref{fig:hw_ill} summarizes the entire air highway placement process, including our example of how the closely-space set of points on a path can be sparsified.
+Figure \ref{fig:hw_ill} summarizes the entire air highway placement process, including our example of how the closely-spaced set of points on a path can be sparsified.

### 2016-07-08 docs/AIAA 2016 highway platooning/plat_form.tex
proofreading... on page 15

@@
 \subsubsection{Vehicles as Hybrid Systems}
-We model each vehicle as a hybrid system \cite{Lygeros98,Lygeros12} consisting of the modes ``Free", ``Leader", ``Follower", and ``Faulty".
-Within each mode, a set of maneuvers is available to allow the vehicle to change modes if desired.
+We model each vehicle as a hybrid system \cite{Lygeros98, Lygeros12} consisting of the modes ``Free", ``Leader", ``Follower", and ``Faulty".
+Within each mode, a vehicle has a set of restricted maneuvers, including one that allows the vehicle to change modes if desired.
 The modes and maneuvers are as follows:
@@
 \item remain a Follower by joining a different platoon on another highway
-\item become a Leader by splitting from the current platoon
+\item become a Leader by splitting from the current platoon while remaining on the highway
 \item become a Free vehicle by leaving the highway
@@
 Reasons for transitioning to the Faulty mode include vehicle malfunctions, performing collision avoidance with respect to another Faulty vehicle, etc.
-A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $t_\text{faulty}$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system.
+A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $\td$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system.
 \end{itemize}
@@
 The vehicles maintain a separation distance of $\sepdist$ with their neighbors inside the platoon.
-In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that when a vehicle exhibits unpredictable behavior, it will be able to exit the altitude range of the highway within a duration of $t_\text{faulty}=1.5$.
+In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that when a vehicle exhibits unpredictable behavior, it will be able to exit the altitude range of the highway within a duration of $\td$.
 Such a requirement may be implemented practically as an fail-safe mechanism to which the vehicles revert when needed.

### 2016-07-09 docs/AIAA 2016 highway platooning/plat_reach.tex
proofreading; now on page 25

@@
 
-Given the dynamics \eqref{eq:dyn} and the target set $\mathcal{L}$, we would like to compute the backwards reachable set, $\mathcal{V}(t)$:
+Given the dynamics \eqref{eq:dyn} and the target set $\mathcal{L}$, we would like to compute the reachable set, $\mathcal{V}(t)$:
 
@@
 These HJ PDEs and HJ VIs can be solved using well-established numerical methods.
-For this paper, we use the formulation in \cite{Mitchell05}, which has shown that the backwards reachable set $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
+For this paper, we use the formulation in \cite{Mitchell05}, which has shown that the reachable set $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
 

### 2016-07-09 docs/AIAA 2016 highway platooning/plat_sim.tex
removed comments
proofreading; now on page 25

@@
 
-At $t=4.2$, $\veh{1}$ (orange) is inside the liveness reachable set for getting to an absolute state shown as the dotted orange boundary.
+At $t=4.2$, $\veh{1}$ (orange) is inside the liveness reachable set for getting to an absolute state, shown as the dotted orange boundary.
 Therefore, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$.
@@
 \end{figure}
-
-\MCnote{Showing all safety reachable sets for the vehicle of interest in first two subplots of Figure \ref{fig:fp}}
 

### 2016-07-10 docs/AIAA 2016 highway platooning/plat_sim.tex
finished proofreading platooning paper

@@
 
-As the intruder $\veh{5}$ (yellow) continues to disregard other vehicles, the followers of the platoon also get near the respective boundaries of the safety reachable set with respect to the intruder.
+As the intruder $\veh{5}$ (yellow) continues to disregard other vehicles, the followers of the platoon also get near the respective boundaries of their safety reachable sets with respect to the intruder.
 This occurs at $t=13.9$, where the platoon ``makes room'' for the intruder to pass by to avoid collisions; all vehicles deviate from their intended path, which is to follow the platoon leader or the highway.

### 2016-07-11 docs/AIAA 2016 highway platooning/high_sim.tex
minor changes according to AIAA guidelines

@@
 
-Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function $V$.
+Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area geographic map, cost map, cost-minimizing paths, and contours of the value function $V$.
 The region enclosed by the black boundary represents ``region around airports'', which have the highest cost.
@@
 First, the cost-minimizing paths to the various destinations in general overlap, and only split up when they are very close to entering their destination cities.
-This is intuitively desirable because the number of air highways is kept low.
-In addition, the cost of flying in the airspace according to the cost map is minimized.
-Secondly, the contours, which correspond to level curves of the value function, have a spacing corresponding to the cost map.
+This is intuitively desirable because having overlapping cost-minimizing paths keeps the number of distinct air highways low.
+Secondly, the contours, which correspond to level curves of the value function, have a spacings corresponding to the cost map: the spacings are large in areas of low cost, and vice versa.
 This provides insight into the placement of air highways to destinations that were not shown in this example.
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{"fig/airHighway_results"}
+	\includegraphics[width=\textwidth]{"fig/airHighway_results"}
 	\caption{Cost-minimizing paths computed by the Fast Marching Method based on the assumed cost map of the San Francisco Bay Area}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{"fig/airHighway_sparse"}
+	\includegraphics[width=\textwidth]{"fig/airHighway_sparse"}
 	\caption{Results of conversion from cost-minimizing paths to highway way points.}

### 2016-07-11 docs/AIAA 2016 highway platooning/introduction.tex
minor changes according to AIAA guidelines

@@
 Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91}; however, recently there has been an immense surge of interest in using UAVs for civil applications.
-Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue.
+Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, videography, and search and rescue \cite{Kopardekar16}.
 In the future, the applications of UAVs are only limited by human imagination.
@@
 Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to respond to disasters in areas that are difficult to reach but require prompt response \cite{Debusk10,Tornado16}.
-As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Space Administration (NASA) are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13, NASA16}.
+As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Space Administration (NASA) are also investigating unmanned aerial systems (UAS) traffic management (UTM) in order to prevent collisions among potentially numerous UAVs \cite{Kopardekar16, FAA13, NASA16}.
 
-Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Ding08}.
+Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Chen17,Ding08}.
 These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.

### 2016-07-11 docs/AIAA 2016 highway platooning/main.tex
minor changes according to AIAA guidelines

--- 2016-05-13 docs/AIAA 2016 highway platooning/main.tex
@@
 
-\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, aerial surveillance, and disaster response.
-As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the airspace, in order to ensure their liveness and safety requirements are met.
-Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers is unrestricted.
-In this paper, we propose to have platoons of UAVs flying on air highways in order to impose the airspace structure that allows for tractable analysis and intuitive monitoring.
-For the air highway placement problem, we use the flexible and efficient fast marching method to solve the Eikonal equation, which produces a sequence of air highways that minimizes the cost of flying from an origin to any destination.
-Within the platoons that travel on the air highways, we model each vehicle as a hybrid system with modes corresponding to its role in the platoon.
-Using Hamilton-Jacobi reachability, we propose several liveness controllers and a safety controller that guarantee the success and safety of all mode transitions.
-For a single altitude range, our approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.
-We demonstrate the satisfaction of liveness and safety requirements through simulations of three common scenarios.}
+\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations.
+As a result, unmanned aerial systems traffic management is needed to ensure the safety and liveness of thousands of UAVs flying simultaneously.
+Currently, the analysis of large multi-agent systems cannot tractably provide safety and liveness guarantees if the agents' set of maneuvers is unrestricted.
+In this paper, platoons of UAVs flying on air highways is proposed to impose an airspace structure that allows for tractable analysis.
+For the air highway placement problem, the fast marching method is used to produce a sequence of air highways that minimizes the cost of flying from an origin to any destination.
+The placement of air highways can be updated in real-time to accommodate sudden airspace changes.
+Within platoons that travel on air highways, each vehicle is modeled as a hybrid system.
+Using Hamilton-Jacobi reachability, safety and liveness are guaranteed for all mode transitions.
+For a single altitude range, the proposed approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.
+The satisfaction of safety and liveness requirements is demonstrated through simulations of three scenarios.}
 

### 2016-07-19 docs/AIAA 2016 highway platooning/main.tex
generated eps figures and finalized AIAA submission

@@
 \documentclass[submit]{aiaa-pretty}
+%\documentclass[submit]{AIAA}
 
-\usepackage{todonotes} \setlength{\marginparwidth}{2.3cm}
+%\usepackage{todonotes} \setlength{\marginparwidth}{2.3cm}
 
-\newcommand{\MCnote}{\todo[size=\footnotesize,author=MC,color=cyan]}
+%\newcommand{\MCnote}{\todo[size=\footnotesize,author=MC,color=cyan]}
 
@@
 
-\author{Mo Chen, Qie Hu, Jaime Fisac, Kene Akametalu, Casey Mackin, Claire Tomlin}
-\title{Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}
+\author{Mo Chen, Qie Hu, Jaime F. Fisac, Kene Akametalu, Casey Mackin, Claire J. Tomlin}
+\title{Reachability-Based Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}
 
 \abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations.
-As a result, unmanned aerial systems traffic management is needed to ensure the safety and liveness of thousands of UAVs flying simultaneously.
+As a result, unmanned aerial systems traffic management is needed to ensure the safety and liveness of potentially thousands of UAVs flying simultaneously.
 Currently, the analysis of large multi-agent systems cannot tractably provide safety and liveness guarantees if the agents' set of maneuvers is unrestricted.
@@
 The placement of air highways can be updated in real-time to accommodate sudden airspace changes.
-Within platoons that travel on air highways, each vehicle is modeled as a hybrid system.
+Within platoons traveling on air highways, each vehicle is modeled as a hybrid system.
 Using Hamilton-Jacobi reachability, safety and liveness are guaranteed for all mode transitions.

### 2016-07-27 docs/NASA Report 2016 Platooning/introduction.tex
Added NASA report

--- 2016-07-11 docs/AIAA 2016 highway platooning/introduction.tex
@@
 
-Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Chen17,Ding08}.
+Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Ding08}.
 These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.

### 2016-07-27 docs/NASA Report 2016 Platooning/main.tex
Added NASA report

--- 2016-07-07 docs/AIAA 2016 highway platooning/main.tex
@@
-\documentclass[submit]{aiaa-pretty}
+\documentclass[plain]{aiaa-pretty}
 
@@
 \author{Mo Chen, Qie Hu, Jaime Fisac, Kene Akametalu, Casey Mackin, Claire Tomlin}
-\title{Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}
+\title{\Large Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways \\
+\normalsize Final Report for NASA UARC Grant NAS2-03144 Task TO.030.21.MD.D-3 Aligned Research Program (ARP) \\
+\normalsize Technological Feasibility of an Air Parcel Approach to Low Altitude UTM}
 

### 2016-07-27 docs/NASA Report 2016 Platooning/plat_controllers.tex
Added NASA report

--- 2016-05-13 docs/AIAA 2016 highway platooning/plat_controllers.tex
@@
 
-For the reachability problem, we define the target set to be a small range of states around the target state $x_P = (\Pos_{x,r}, \Pos_{y,r}, \Vel_{x,r}, \Vel_{y,r})$:
+For the reachability problem, we define the target set to be a small range of states around the target state $\bar x_P = (\Pos_{x,r}, \Pos_{y,r}, \Vel_{x,r}, \Vel_{y,r})$:
 
@@
 
-$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety.
+$\mathcal{Q}(i)$ is the set of quadrotors with which vehicle $\veh{i}$ checks safety.
 \item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:
@@
 We use a model-predictive controller (MPC) for traveling along a highway; this controller allows the leader to travel along a highway at a pre-specified speed.
-Here, the goal is for a leader quadrotor to track a constant-altitude path, defined as a curve $\bar{p}(s)$ parametrized by $s\in[0,1]$ in $p=(p_x, p_y)$ space (position space), while maintaining a velocity $\bar{v}(s)$ that corresponds to constant speed in the direction of the highway.
+Here, the goal is for a leader vehicle to track an air highway $\hw(s), s\in[0,1]$ while maintaining some constant velocity $\vel_\hw$ specified by the highway.
+The highway and the specified velocity can be written as a desired position and velocity over time, $\bar \pos(t), \bar \vel (t)$.
 Assuming that the initial position on the highway, $s_0=s(t_0)$ is specified, such a controller can be obtained from the following optimization problem over the time horizon $[t_0, t_1]$:
@@
 \begin{aligned}
-\text{minimize } & \int_{t_0}^{t_1} \big\{\| p(t)-\bar{p}(s(t)) \|_2 + \\ 
-&\qquad \| v(t) - \bar{v}(s(t)) \|_2 + 1-s \big\} dt \\
-\text{subject to } & \dot{x} = f(x,u) \text{ where } f \text{ is given in \eqref{eq:dyn}} \\
+\text{minimize } & \int_{t_0}^{t_1} \big\{\| p(t)-\bar\pos(t) \|_2 + \\ 
+&\qquad \| v(t) - \bar\vel(t) \|_2 + 1-s \big\} dt \\
+\text{subject to } & \text{vehicle dynamics } \eqref{eq:veh_dyn} \\
 & |u_x|, |u_y| \le u_\text{max}, |v_x|, |v_y| \le v_\text{max} \\
@@
 
-If we discretize time, and assume that $\bar{p}(\cdot)$ is linear, then the above optimization is convex, and can be quickly solved.
+If we discretize time, the above optimization is becomes convex optimization over a small number of decision variables, and can be quickly solved.
 

### 2016-07-27 docs/NASA Report 2016 Platooning/plat_form.tex
Added NASA report

--- 2016-07-08 docs/AIAA 2016 highway platooning/plat_form.tex
@@
 We will denote the $N$ vehicles as $\veh{i}, i=1\ldots,N$.
-We consider a platoon of vehicles to be a group of $M\le N$ vehicles, denoted $\veh{P_1}, \ldots, \veh{P_M}, \{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$, in a single-file formation; for convenience, we also denote $P_0 = P_{M+1} = \emptyset$.
+We consider a platoon of vehicles to be a group of $M\le N$ vehicles, denoted $\veh{P_1}, \ldots, \veh{P_M}, \{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$, in a single-file formation.
 When necessary, we will use superscripts to denote vehicles of different platoons: $\veh{P_i^j}$ represents the $i$th vehicle in the $j$th platoon.

### 2016-07-27 docs/NASA Report 2016 Platooning/plat_safety.tex
Added NASA report

--- 2016-05-12 docs/AIAA 2016 highway platooning/plat_safety.tex
@@
 Therefore, as long as the number of ``safety breaches" is at most one for $\veh{i}$, $Q_i$ can simply use the optimal control to avoid $\veh{k}$ and avoid collision for the time horizon of $t$.
-Under the assumption that vehicles are able to exit the current altitude range within a duration of $\td$, if we choose $t=t_\text{faulty}$, the safety breach would always end before any collision can occur.
+Under the assumption that vehicles are able to exit the current altitude range within a duration of $\td$, if we choose $t=\td$, the safety breach would always end before any collision can occur.
 
@@
 However, as long as the total number of safety breaches does not exceed the number of affected vehicles, collision avoidance of all the vehicles can be guaranteed for the duration $\td$.
-However, as our simulation results show, placing vehicles in single-file platoons makes the likelihood of multiple safety breaches low during a vehicle's malfunction and during the presence of one intruder vehicle.
+However, as our simulation results show, placing vehicles in single-file platoons makes the likelihood of multiple safety breaches low during the presence of one intruder vehicle.
 
@@
 The general process and details of the complete picture of multi-altitude collision avoidance is part of our future work.
-\MCnote{Now states vehicles causing safety breaches must exit altitude range; also mentions multi-altitude collision avoidance is future work.}
 
@@
 Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons.
-By treating each platoon as a single unit, we reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.
-\MCnote{Should we discuss inter-platoon safety in more detail through an additional section or simulation?}
+By treating each platoon as a single unit, we can reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.

### 2016-07-27 docs/NASA Report 2016 Platooning/fig/RSExample.m

@@ -1,0 +1,72 @@
+function RSExample()
+
+onlyTarget = 0;
+
+g.dim = 2;
+g.N = 101;
+g.min = [-10; -10];
+g.max = [10; 10];
+g.bdry = @addGhostExtrapolate;
+g = processGrid(g);
+
+x = g.xs{1};
+y = g.xs{2};
+R = 4;
+
+figure
+%%
+T = sqrt(x.^2 + y.^2) - R;
+surf(x,y,T, 'facecolor', 'r', 'facealpha', 0.3, 'edgecolor', 'none')
+hold on
+t = linspace(0, 2*pi, 101);
+plot(R*cos(t), R*sin(t), 'r-', 'linewidth', 4)
+
+%%
+surf(x, y, zeros(size(x)), 'facecolor', [0 0.25 0], ...
+  'facealpha', 0.5, 'edgecolor', 'none')
+
+if onlyTarget
+  xlabel('x')
+  ylabel('y')
+  legend('l(x)','Target set', 'Zero plane')
+  return
+end
+
+%%
+s = 5; % shift
+% Shifted circle
+C = sqrt((x-s).^2 + y.^2) - R;
+
+% Rectangle
+ledge = -x;
+redge = x-s;
+tedge = y-R;
+bedge = -y-R;
+rect = max(ledge, redge);
+rect = max(rect, tedge);
+rect = max(rect, bedge);
+
+% Union
+U = min(C, rect);
+U = min(U, T);
+U = signedDistanceIterative(g, U)/1.1;
+surf(x,y,U, 'facecolor', 'b', 'facealpha', 0.3, 'edgecolor', 'none')
+hold on
+
+HedgeX = linspace(0, s, 50);
+TedgeY = R*ones(size(HedgeX));
+plot(HedgeX, TedgeY, 'b-', 'linewidth', 4)
+BedgeY = -R*ones(size(HedgeX));
+plot(HedgeX, BedgeY, 'b-', 'linewidth', 4)
+
+t = linspace(pi/2, 3*pi/2, 50);
+plot(R*cos(t), R*sin(t),  'b-', 'linewidth', 4)
+t = linspace(-pi/2, pi/2, 50);
+plot(s+R*cos(t), R*sin(t),  'b-', 'linewidth', 4)
+
+
+xlabel('x')
+ylabel('y')
+legend('l(x)','Target set', 'Zero plane', 'V(t,x)', 'Reachable set')
+
+end

### 2016-11-01 docs/AIAA 2016 highway platooning/response1/response1.tex
added reviewer comments and draft of response

\documentclass[submit]{aiaa-pretty}

\title{Response to reviewers}

\begin{document}
\maketitle

\section{Associate Editor's Comments to Author}
\begin{itemize}
\item\textbf{How is convective weather, for example, and winds taken into account when computing an optimal path from the origin to the destination?  As a follow-on, how is uncertainty in the forecast accounted for?}

How each individual vehicle responds to disturbances such as weather is a separate problem from the air highway placement process, which only specifies the location of the highways. Disturbances are accounted for by controllers for following the highway or following the platoon (Fig. 4).

However, any forecast, however uncertain it may be, can be incorporated into the cost map. Given the cost map, air highways can then be placed. The exact process of converting everything including population density, geography, forecast information, etc. to a cost map is not discussed in the paper. One primary purpose of the paper is to highlight that air highway placement can be done in real-time given the cost map.

\item\textbf{For realtime applications, how would you know to update the cost map?  A runway configuration change is straight forward since presumably there is a clear indication that a change was made, but if such a notification isn’t available how would this happen?}

This is great point. The cost map would be changed based on many factors such as weather forecasts (eg. impending hurricane), commercial air traffic, etc. This could either be done manually or automatically. In terms of communicating this information, all vehicles and users could have an interface showing the current highway map.

\item\textbf{Section III.A.2: Are there downsides if the majority of operators continue to operate as Free vehicles and not join the highway structure (essentially becoming intruder vehicles)?  From Section III.G.2, the onus of avoiding collisions with the free vehicles appears to be on the vehicles in the platoon.  The required avoidance maneuvers could become extreme if there are many Free vehicles, right?}

Under the assumption that UAVs can only fly when they're guaranteed to be safe, then as the demand for flying increases, vehicles would no longer be guaranteed-safe when they are free. The platooning structure allows safety guarantees to be made, and the multi-UAV system to be easily monitored, thereby allowing more vehicles to fly at once. Whether the vehicles are allowed to be free during their entire flight would be subject to traffic rules to be established by government agencies (or some centralized governing body).

\item\textbf{Section III.A.2: It would seem that there might be potential costs for a Free vehicle to join a platoon.  For example, a vehicle may need to delay its departure time or alter its “optimal trajectory” to rendezvous with the Lead vehicle.  How is this additional cost weighed against the decision to remain “Free”, or to wait for a new platoon to be established, or to lead the formation of a new platoon?}

Definitely, being part of the highway structure has a cost to the individual vehicle. However, remaining free may not be an option depending on traffic rules. When the number of vehicles increases to a point where all vehicles being free is no longer manageable, each vehicle would need to use the highways, and effectively ``pay'' for a structure that guarantees safety.

\item\textbf{What is there a maximum number of UAVs that can be safely accommodated in a platoon before a second platoon should be created?}

Strictly speaking there is no maximum. However, practically speaking it is unclear what the best size for a platoon would be on a single highway. Further research would be needed to understand this.

\item\textit{No future work in Conclusions.  The Conclusions section is only for conclusions that can be drawn directly from the manuscript.}
\end{itemize}

\textbf{Additional Minor Comments:}
\begin{enumerate}
\item \textit{Please ensure that the captions of all figures are not longer than two lines.  Additional text can be included in the main body of the pager.}
\item \textit{Please re-define all acronyms in the Conclusions.}
\item \textit{The Conclusions section is reserved for conclusions that can be drawn from the body of the paper.  Please delete the last sentence since it is referring to future work.}
\item \textit{DOI numbers are required for the references whenever available}
\item \textit{AIAA conference papers need paper numbers}
\end{enumerate}

\section{Reviewer 1's comments}

\textit{A well-written paper on a topic of increasing importance.  The issue of traffic flow management as applied to low-altitude, small UAS is undervalued by many in ATM and aviation.  It is encouraging to see solid work being done in this area.}

\textit{Overall the presentation of the paper is clear.  However, as a reader, I was left with several (small) open questions.  Those questions need not be deeply answered by the paper, however, I think addressing them explicitly (even if to state they will not be detailed) will provide a more complete feeling to the paper.}

\begin{enumerate}
\item\textit{This work is like platooning research from traditional TFM.  The problem with those solutions was typically that through the implementation of platooning, often there was such a loss of efficiency to form the platoon, that it was ultimately not worth while.  The authors should probably look at some of that previous work for citation rather than relying solely on ground vehicle platooning.}

\item\textbf{At what densities do the authors feel that airspace structure (such as the proposed "highways") would begin to show value?  If there is only one vehicle flying in the airspace, platoons are impossible and unnecessary.  If there are 1M vehicles, then we might think structure would be good.  What is that breaking point or how to we find it?}

This point is very important and requires further investigation. As long as multiple conflicts do not occur, pairwise collision avoidance would be sufficient to keep vehicles safe in an unstructured environment. However, it is difficult to predict whether multiple conflicts would occur, and in addition, unstructured flight can be very unintuitive to monitor.

An initial idea on how to determine a breakpoint would be to implement large-scale simulations to compare different numbers of vehicles flying in structured and unstructured environments.

\item\textbf{What can be said about more realistic vehicle faults?  Many UAS faults would preclude them from cleanly just finding another altitude to operate at.  In that case your safety modeling is very insufficient.  A brief discussion on some practical UAS faults and the potential need for better modeling in your framework is probably warranted.}

There has been some work done on emergency landing of vehicles, which could provide a way for vehicles to exit the current altitude range. These types of analysis usually involve multiple steps, including identifying most likely types of faults, the dynamics of the vehicles during the fault, etc.

One assumption implicitly made in this paper is that the mechanism for exiting the altitude range can be abstracted or summarized into just a time-to-exit-altitude-range parameter.

\item\textit{A few sentences about the policy implications may help ground the reader in terms of how such a system might find its way in to the airspace in the future.  Is this platooning a requirement of operators?  Optional?  If optional, what is the critical mass that makes it effective?}

\item\textit{Should your state diagram (Figure 4) have a terminal state of some kind?  Like a "Closed" state where they just aren't flying anymore?  Perhaps reachable from "Free" and "Faulty"?  Otherwise it seems like all vehicles are in the air at all times.  If so, you may want to consider an entry point to the state diagram as well.  Where can the vehicles start out?}
\end{enumerate}

\textit{Again, I don't think all of these questions need to be answered in detail, but addressing them will strengthen the paper.}

\textit{The only style point I have, is in that the introduction sounds a bit too "salesman" like.  In the first paragraph, terms like "important" and "human imagination" feel like they may be a tad overplayed.  Later terms like "cannot be denied" and perhaps a couple others detract from the technical work in some way.  Not required that these be changed, just a style note from one reader.}

\section{Reviewer 2's comments}

\textit{The paper draws inspiration from the Automated Highway Systems (AHS) concept developed at Berkeley in the 90s. The paper proposes the introduction of structure, namely Air Highways and platoons, to airspace control, which is bound to be congested in a near future because of the drone revolution. This seems to be the contribution of the paper.}

\textit{The problem is that there is no technical justification (or discussion) for this approach. True, that corridors (or Air Highways) make sense, especially in congested areas. But platooning, as proposed, is difficult to justify (in fact there is no justification for platoons in the paper).}

\textbf{Moreover, the proposed approach does not really address the problem of designing corridors (or Air Highways) for a given region. True, that it produces corridors for the problem of going from one “source” to multiple destinations. But it does not address the interesting problem of finding an Air Highway network connecting multiple “sources” and destinations. It is interesting that the proposed approach is not aligned with the idea of “free flight” that has been advocated by some of the authors.}

Free flight may not be scalable in the sense that safety guarantees can no longer be made once the vehicle density reaches some threshold. Having an air highway structure provides a way to guarantee safety and to intuitively monitor the airspace.

In addition, practically there may be many different levels of abstraction of the airspace, and perhaps free flight may be a good idea on the level of a small neighborhood, while structured flight makes more sense for larger regions like a city.

\textbf{Other than the idea of using AHS concepts for airspace control the paper adds nothing to the state of the art. The path planning and the reachability frameworks used in the paper have been extensively documented in the literature. This may be the reason why the presented material is quite “standard”. This may also be the reason why a few subtle technicalities may have been overlooked (e.g., conditions for the application of the principle of optimality and lack of smoothness of the value function). Moreover, the discussion of related work could have been more extensive.}

The current methods cannot be used to directly analyze a large-scale system of many UAVs, unless a structural assumption is made. By organizing the airspace into air highways, and having UAVs fly in platoons on the air highways, the numerous existing methods can be used a lot more reliably.

\subsection{DETAILED COMMENTS}
\subsubsection{Abstract}
\begin{itemize}
\item \textbf{“Hamilton-Jacobi reachability” – what is special about this HB reachability? Aren’t you just talking about reachability?}

HJ reachability can obtain optimal solutions for nonlinear continuous-time systems involving control and disturbance

\item \textbf{Liveness is not defined. This has a precise meaning in the CS community, but not in the controls community.}

Good point. Here, liveness refers to the system eventually being able to reach a set of goal states. In the context of HJ reachability, the guarantee is actually being able to reach a set of goal states within some time horizon. The text has been modified to reflect this point, and a reference in the introduction has been added.
\end{itemize}
\subsubsection{Introduction}
\begin{itemize}
\item \textbf{``As a rough estimate...'' – Isn’t this example just too naive?}
This back-of-the-envelope calculation is meant to motivate the number of vehicles that could be present in the airspace simultaneously

\item \textit{“liveness” – Please cite optimal control work on liveness.}

\item \textbf{``... formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states'' – isn’t this just backward reachability? What about time? A more precise definition is needed.}
Added the word ``backward'' for clarity. Precise definitions are found in III.B.1

\item \textbf{``... power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ partial differential equation'' – the claim is a bit courageous because of the curse of dimensionality. There are limitations on the dimension of the state-space that can be handled by this approach.}

The limitation on system dimension is what this paper tries to address using the structural assumption of a platoon; the language has been changed to address this comment.

\item \textit{''HJ reachability computations are intractable for a large number of vehicles'' – Actually it is not tractable for one single vehicle if we consider dynamics evolving in a high dimension state-space.}

\item \textbf{``A considerable body of work has been done on the platooning of ground vehicles'' – this is true. But it is also true that this is because there is already an infrastructure in place. There are no convincing arguments in the paper leading to the conclusion that the problem of routing and execution control for multiple UAVs is better solved by highways and platoons. In fact, the reader may conclude that the proposed approach has the purpose of finding a problem to a solution that has been proposed for automated highway systems. The proposed approach lacks solids arguments and would be very difficult to implement in practice: information structures; safety; required infra-structure; security; and, UAV diversity.}

This paper is not meant to provide an exhaustive solution. It illustrates that having a highway structure in the airspace allows HJ reachability, a method that normally can only analyze small-scale systems, to be used for large-scale systems. There are definitely those issues mentioned in the comment, as well as many other challenges that need to be overcome. Hopefully this paper can provide a starting point on which future research can be built, and make future research problems more concrete.
\end{itemize}

\subsubsection{Air highways}
\begin{itemize}
\item \textbf{''By routing platoons of UAVs onto a few common pathways'' – actually this problem is not addressed in the paper. There is no solution to the problem of finding common pathways for a given demand profile.}

The paper does not explicitly address the problem of finding common pathways, but the air highway placement method presented here naturally leads to common pathways as seen in figures 2 and 3

\item \textbf{``... air highway be denoted by'' – why is it that an air highway has to be flat?}

Just for simplicity and intuitive monitoring. This is not strictly a requirement.

II.A The air highway placement problem
\item \textit{``... to each air highway we assign a speed of travel'' – shouldn’t this be a control setting? This varies a lot with the type of UAVs.}
\item \textit{``...air highway locations should ideally be able to be recomputed in real-time when necessary in order to update airspace constraints on-the fly'' – how practical is this under the limitations discussed above?}
\item \textbf{ ``... air highway placement problem, and'' – the title can be misleading. The problem is not about finding all highways for a given region. In fact the formulation considers just one “source” and multiple destinations. It is unclear how it would work for the problem of multiple ``sources'' and destinations}

True, but the process can be done for multiple sources, and intersections would need to be managed perhaps by having different highway networks on different altitudes. This is a great direction of future research.

\item \textbf{``... sequence of highways'' – a sequence of highways or the set of all highways joining some initial and final points with N segments?}

A sequence of highways joining a single initial point and a single final point. This should be clear since $p^o$ and $p^d$ are single points.

\item \textit{Cost function – shouldn’t the cost function depend on the type of UAV?}
\end{itemize}

II.B. The Eikonal equation
\begin{itemize}
\item \textit{``sequence of paths'' – same problem as above for highways}
\item \textbf{``It is well known that the solution to the Eikonal equation (5)'' – this statement is misleading. This is only true if the dynamics of the UAV are of a special form. This is poorly explanined in this paragraph. It neglects to discuss how the Eikonal equation is derived for a special form of dynamics. Moreover, in the tradition of optimal control theory V is called the value function.}

The Eikonal equation is only used for the air highway placement, which is done in a relatively large region of the airspace. Leader vehicles on a highway would track the highway using a controller that takes the vehicle dynamics into account. (figure 4)

\item \textbf{``can be viewed as a relaxation of the air highway placement problem defined in (2). Unlike'' – one wonders if it would have not been better to work on a discretized space space and use Dijkstra’s algorithm. A discussion of related work or related techniques is in order.}

A continuous space is convenient since the cost map is defined on a geographic map, which is a continuous space.

\item \textit{``Given a single origin point po, the optimal cumulative cost function V (pd) can be computed. Suppose M different destination points. Then, M different optimal paths Pi; i = 1; : : : ;M are obtained from V'' – True, but misleading. In fact any number of M will do since the value function is defined for the whole state space.}
\item \textit{ Equation (3) – Are there any assumptions on the cost function? If not it may happen that V may not be differentiable. What about the interpretation of equation (5) for this case?}
\end{itemize}

E. Real-Time Highway Location Updates
\begin{itemize}
\item \textit{``Since (5) can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost'' – True, but the results will no longer satisfy the Principle of Optimality which is at the root of the derivation of the Eikonal equation.}
\item \textit{On the other hand, depending on for instance the time of day, it may be most desirable to fly in different regions of the airspace'' – Again, if the cost varies with time, then the Eikonal equation no longer solves for the value function V.}
\item \textbf{``We add to the collection of waypoints the first point on the path at which the heading changes by some threshold C, and repeat this process along the entire path.'' – The paths arising from the Eikonal equation can have kinks and jumps in curvature. How to address that?}

As mentioned, post-processing is not the focus of this paper.
\end{itemize}

\subsubsection{UAV platooning}
A. UAVs in platoons
\begin{itemize}
\item \textbf{``The techniques we present in this paper do not depend on the dynamics of the vehicles.'' – This is somewhat misleading because reachability analysis depends on the dynamics of the vehicles. Especially when these switch from one highway to the next one.}

Yes, slightly confusing. Changed wording accordingly

\item \textit{``... problem of collision avoidance among N vehicles cannot be tractably solved using traditional dynamic programming approaches because the computation complexity of these approaches scales exponentially with the number ...'' – This needs clarification. What are the information structures for this problem?}

\item \textit{``liveness and safety of the vehicles in a tractable manner'' – liveness and safety are not properly defined.}
\item \textit{''We consider a platoon of vehicles to be a group of $M \le N$ vehicles, ...'' – This is not clear.}
\item \textit{''If the vehicle is part of platoon, then it checks safety...” – what it the vehicle is the leader of a platoon? This case is addressed in Figure 5, but not here.}
\item \textit{``... have a liveness component, which specifies a set of states that the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.'' – This is not a definition of liveness.}

B. Hamilton-Jacobi reachability
\item \textit{Equation (10) – Some of the symbols in the equation were not defined.}
\item \textit{What is the difference between the HJB and the HJ equations?}
\item \textit{Figure 6 – What is the zero plane and where is it in the picture?}
\end{itemize}

C. Reachability based controllers
\begin{itemize}
\item \textit{``Reachability analysis is useful for constructing controllers ...'' – This does not say much. Please elaborate on it.}
\item \textit{``The system dynamics with which the reachable set is computed provide additional flexibility when using reachability to construct controller...'' – Not clear.}
\item \textbf{Aren’t all calculations made much simple because you are in an air highway? Please elaborate on this.}

Yes. While on the highway, vehicles can use simple controllers to follow the highway or the platoon leader. However, some mode transitions involve more complex movements in both dimensions of the position space.

\item \textit{``liveness controller described in the previous sections when it is not in any danger of collision with other vehicles'' – As before, the concept of liveness has not been introduced before, so it may be difficult to the reader to understand what is going on.}
\item \textit{``3. Avoiding collisions'' – What happens when a potential collision is detected and there is no solution to the obstacle avoidance problem? Not clear from the text if the approach will work for the case when multiple UAVs are using safety controllers? This is even more interesting for the case of UAVs in a platoon. It is not clear from the text if the safety set is defined only for motions along the highway, or if there are additional degrees of freedom.}
\end{itemize}

D. Other controllers
\begin{itemize}
\item \textit{``$\hat d$ is the highway’s direction of travel.'' – The direction of travel is not properly defined.}
\end{itemize}

E. Safety analysis
\begin{itemize}
\item \textit{The discussion seems to overlook the definition of the information structures for the problem. The same happens with considerations about sensor performance.}
\item \textit{``Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons. By treating each platoon as a single unit, we can reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.'' – This seems to be in contradiction with the example with an intruder vehicle.}
\end{itemize}

F. Numerical simulations
\begin{itemize}
\item \textit{What are the information structures for these problems?}
\item \textit{The maneuvers described in Fig 9 seem to go against our intuition. A more detailed description of what is going on is needed.}
\end{itemize}

IV. Conclusions
\begin{itemize}
\item \textit{``Many complex maneuvers can be performed using only a few reachability sets.'' – This phrase does not say much.}
\end{itemize}

\end{document}

### 2016-11-06 docs/AIAA 2016 highway platooning/review response.txt

Associate Editor's Comments to Author:
- How is convective weather, for example, and winds taken into account when computing an optimal path from the origin to the destination?  As a follow-on, how is uncertainty in the forecast accounted for?

How each individual vehicle responds to disturbances such as weather is a separate problem from the air highway placement process, which only specifies the location of the highways. Disturbances are accounted for by controllers for following the highway or following the platoon (Fig. 4).

However, any forecast, however uncertain it may be, can be incorporated into the cost map. Given the cost map, air highways can then be placed. The exact process of converting everything including population density, geography, forecast information, etc. to a cost map is not discussed in the paper. One primary purpose of the paper is to highlight that air highway placement can be done in real-time given the cost map.

- For realtime applications, how would you know to update the cost map?  A runway configuration change is straight forward since presumably there is a clear indication that a change was made, but if such a notification isn’t available how would this happen?
- Section III.A.2: Are there downsides if the majority of operators continue to operate as Free vehicles and not join the highway structure (essentially becoming intruder vehicles)?  From Section III.G.2, the onus of avoiding collisions with the free vehicles appears to be on the vehicles in the platoon.  The required avoidance maneuvers could become extreme if there are many Free vehicles, right?
- Section III.A.2: It would seem that there might be potential costs for a Free vehicle to join a platoon.  For example, a vehicle may need to delay its departure time or alter its “optimal trajectory” to rendezvous with the Lead vehicle.  How is this additional cost weighed against the decision to remain “Free”, or to wait for a new platoon to be established, or to lead the formation of a new platoon?
- What is there a maximum number of UAVs that can be safely accommodated in a platoon before a second platoon should be created?
- No future work in Conclusions.  The Conclusions section is only for conclusions that can be drawn directly from the manuscript.

Additional Minor Comments:
1. Please ensure that the captions of all figures are not longer than two lines.  Additional text can be included in the main body of the pager.
2. Please re-define all acronyms in the Conclusions.
3. The Conclusions section is reserved for conclusions that can be drawn from the body of the paper.  Please delete the last sentence since it is referring to future work.
4. DOI numbers are required for the references whenever available
5. AIAA conference papers need paper numbers

Reviewer(s)' Comments to Author:
Reviewer: 1

<b>Comments to the Author.</b> The Editors particularly desire your specific comments on technical content, overall value, relevancy, accuracy of computed results or experimental data, and revisions needed for conciseness, clarity, and/or completeness.
A well-written paper on a topic of increasing importance.  The issue of traffic flow management as applied to low-altitude, small UAS is undervalued by many in ATM and aviation.  It is encouraging to see solid work being done in this area.

Overall the presentation of the paper is clear.  However, as a reader, I was left with several (small) open questions.  Those questions need not be deeply answered by the paper, however, I think addressing them explicitly (even if to state they will not be detailed) will provide a more complete feeling to the paper.

1.  This work is like platooning research from traditional TFM.  The problem with those solutions was typically that through the implementation of platooning, often there was such a loss of efficiency to form the platoon, that it was ultimately not worth while.  The authors should probably look at some of that previous work for citation rather than relying solely on ground vehicle platooning.

2.  At what densities do the authors feel that airspace structure (such as the proposed "highways") would begin to show value?  If there is only one vehicle flying in the airspace, platoons are impossible and unnecessary.  If there are 1M vehicles, then we might think structure would be good.  What is that breaking point or how to we find it?

3.  What can be said about more realistic vehicle faults?  Many UAS faults would preclude them from cleanly just finding another altitude to operate at.  In that case your safety modeling is very insufficient.  A brief discussion on some practical UAS faults and the potential need for better modeling in your framework is probably warranted.

4.  A few sentences about the policy implications may help ground the reader in terms of how such a system might find its way in to the airspace in the future.  Is this platooning a requirement of operators?  Optional?  If optional, what is the critical mass that makes it effective?

5.  Should your state diagram (Figure 4) have a terminal state of some kind?  Like a "Closed" state where they just aren't flying anymore?  Perhaps reachable from "Free" and "Faulty"?  Otherwise it seems like all vehicles are in the air at all times.  If so, you may want to consider an entry point to the state diagram as well.  Where can the vehicles start out?

Again, I don't think all of these questions need to be answered in detail, but addressing them will strengthen the paper.

The only style point I have, is in that the introduction sounds a bit too "salesman" like.  In the first paragraph, terms like "important" and "human imagination" feel like they may be a tad overplayed.  Later terms like "cannot be denied" and perhaps a couple others detract from the technical work in some way.  Not required that these be changed, just a style note from one reader.

Reviewer: 2

<b>Comments to the Author.</b> The Editors particularly desire your specific comments on technical content, overall value, relevancy, accuracy of computed results or experimental data, and revisions needed for conciseness, clarity, and/or completeness.
GENERAL COMMENTS
The paper draws inspiration from the Automated Highway Systems (AHS) concept developed at Berkeley in the 90s. The paper proposes the introduction of structure, namely Air Highways and platoons, to airspace control, which is bound to be congested in a near future because of the drone revolution. This seems to be the contribution of the paper. The problem is that there is no technical justification (or discussion) for this approach. True, that corridors (or Air Highways) make sense, especially in congested areas. But platooning, as proposed, is difficult to justify (in fact there is no justification for platoons in the paper). Moreover, the proposed approach does not really address the problem of designing corridors (or Air Highways) for a given region. True, that it produces corridors for the problem of going from one “source” to multiple destinations. But it does not address the interesting problem of finding an Air Highway network connecting multiple “sources” and destinations. It is interesting that the proposed approach is not aligned with the idea of “free flight” that has been advocated by some of the authors.
Other than the idea of using AHS concepts for airspace control the paper adds nothing to the state of the art. The path planning and the reachability frameworks used in the paper have been extensively documented in the literature. This may be the reason why the presented material is quite “standard”. This may also be the reason why a few subtle technicalities may have been overlooked (e.g., conditions for the application of the principle of optimality and lack of smoothness of the value function). Moreover, the discussion of related work could have been more extensive.

DETAILED COMMENTS

Abstract
•       “Hamilton-Jacobi reachability” – what is special about this HB reachability? Aren’t you just talking about reachability?
•       Liveness is not defined. This has a precise meaning in the CS community, but not in the controls community.
Introduction
•       “As a rough estimate … ” – Isn’t this example just too naïve?
•       “liveness” – Please cite optimal control work on liveness.
•       “… formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states” – isn’t this just backward reachability? What about time? A more precise definition is needed.
•       “… power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ partial differential equation” – the claim is a bit courageous because of the curse of dimensionality. There are limitations on the dimension of the state-space that can be handled by this approach.
•       “HJ reachability computations are intractable for a large number of vehicles“ – Actually it is not tractable for one single vehicle if we consider dynamics evolving in a high dimension state-space.
•       “A considerable body of work has been done on the platooning of ground vehicles” – this is true. But it is also true that this is because there is already an infrastructure in place. There are no convincing arguments in the paper leading to the conclusion that the problem of routing and execution control for multiple UAVs is better solved by highways and platoons. In fact, the reader may conclude that the proposed approach has the purpose of finding a problem to a solution that has been proposed for automated highway systems. The proposed approach lacks solids arguments and would be very difficult to implement in practice: information structures; safety; required infra-structure; security; and, UAV diversity.

II. Air highways
•       “By routing platoons of UAVs onto a few common pathways” – actually this problem is not addressed in the paper. There is no solution to the problem of finding common pathways for a given demand profile.
•       “.. air highway be denoted by” – why is it that an air highway has to be flat?

II.A The air highway placement problem
•       “… to each air highway we assign a speed of travel” – shouldn’t this be a control setting? This varies a lot with the type of UAVs.
•       “… air highway locations should ideally be able to be recomputed in real-time when necessary in order to update airspace constraints on-the fly” – how practical is this under the limitations discussed above?
•       “… air highway placement problem, and” – the title can be misleading. The problem is not about finding all highways for a given region. In fact the formulation considers just one “source” and multiple destinations. It is unclear how it would work for the problem of multiple “sources” and destinations
•       “… sequence of highways” – a sequence of highways or the set of all highways joining some initial and final points with N segments?
•       Cost function – shouldn’t the cost function depend on the type of UAV?

II.B. The Eikonal equation
•       “sequence of paths” – same problem as above for highways
•       “It is well known that the solution to the Eikonal equation (5)” – this statement is misleading. This is only true if the dynamics of the UAV are of a special form. This is poorly explaneined in this paragraph. It neglects to discuss how the Eikonal equation is derived for a special form of dynamics. Moreover, in the tradition of optimal control theory V is called the value function.
•       “can be viewed as a relaxation of the air highway placement problem defined in (2). Unlike” – one wonders if it would have not been better to work on a discretized space space and use Dijkstra’s algorithm. A discussion of related work or related techniques is in order.
•       “Given a single origin point po, the optimal cumulative cost function V (pd) can be computed. Suppose M different destination points. Then, M different optimal paths Pi; i = 1; : : : ;M are obtained from V” – True, but misleading. In fact any number of M will do since the value function is defined for the whole state space.
•       Equation (3) – Are there any assumptions on the cost function? If not it may happen that V may not be differentiable. What about the interpretation of equation (5) for this case?

E. Real-Time Highway Location Updates
•       “Since (5) can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost” – True, but the results will no longer satisfy the Principle of Optimality which is at the root of the derivation of the Eikonal equation.
•       “On the other hand, depending on for instance the time of day, it may be most desirable to fly in different regions of the airspace” – Again, if the cost varies with time, then the Eikonal equation no longer solves for the value function V.
•       “We add to the collection of waypoints the first point on the path at which the heading changes by some threshold  C, and repeat this process along the entire path.” – The paths arising from the Eikonal equation can have kinks and jumps in curvature. How to address that?

III. UAV platooning
A. UAVs in platoons
•       “The techniques we present in this paper do not depend on the dynamics of the vehicles.” – This is somewhat misleading because reachability analysis depends on the dynamics of the vehicles. Especially when these switch from one highway to the next one.
•       “… problem of collision avoidance among N vehicles cannot be tractably solved using traditional dynamic programming approaches because the computation complexity of these approaches scales exponentially with the number …” – This needs clarification. What are the information structures for this problem?
•       “liveness and safety of the vehicles in a tractable manner” – liveness and safety are not properly defined.
•       “We consider a platoon of vehicles to be a group of M   N vehicles, denoted QP1 ; : : : ;QPM;  fPjgMj =1 _ figNi =1” – This is not clear.
•       “If the vehicle is part of platoon, then it checks safety …” – what it the vehicle is the leader of a platoon? This case is addressed in Figure 5, but not here.
•       “… have a liveness component, which specifies a set of states that the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.” – This is not a definition of liveness.

B. Hamilton-Jacobi reachability
•       Equation (10) – Some of the symbols in the equation were not defined.
•       What is the difference between the HJB and the HJ equations?
•       Figure 6 – What is the zero plane and where is it in the picture?

C. Reachability based controllers
•       “Reachability analysis is useful for constructing controllers …” – This does not say much. Please elaborate on it.
•       “The system dynamics with which the reachable set is computed provide additional flexibility when using reachability to construct controller …” – Not clear.
•       Aren’t all calculations made much simple because you are in an air highway? Please elaborate on this.
•        “liveness controller described in the previous sections when it is not in any danger of collision with other vehicles” – As before, the concept of liveness has not been introduced before, so it may be difficult to the reader to understand what is going on.
•       “3. Avoiding collisions” – What happens when a potential collision is detected and there is no solution to the obstacle avoidance problem? Not clear from the text if the approach will work for the case when multiple UAVs are using safety controllers? This is even more interesting for the case of UAVs in a platoon. It is not clear from the text if the safety set is defined only for motions along the highway, or if there are additional degrees of freedom.

D. Other controllers
•       “d^^ is the highway’s direction of travel.” – The direction of travel is not properly defined.

E. Safety analysis
•       The discussion seems to overlook the definition of the information structures for the problem. The same happens with considerations about sensor performance.
•       “Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons. By treating each platoon as a single unit, we can reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.” – This seems to be in contradiction with the example with an intruder vehicle.

F. Numerical simulations
•       What are the information structures for these problems?
•       The maneuvers described in Fig 9 seem to go against our intuition. A more detailed description of what is going on is needed.

IV. Conclusions
•       “Many complex maneuvers can be performed using only a few reachability sets.” – This phrase does not say much.

### 2016-11-07 docs/AIAA 2016 highway platooning/conclusions.tex
edited AIAA paper up to reviewer 2's comments

@@
 \section{Conclusions}
-To address the important and urgent problem of the traffic management of UAVs, we proposed to have platoons of UAVs traveling on air highways.
+To address the important and urgent problem of the traffic management of unmanned aerial vehicles (UAVs), we proposed to have platoons of UAVs traveling on air highways.
 We showed how such an airspace structure leads to much easier safety and liveness analysis.
@@
 
-Immediate future work includes exploring different vehicle models, investigating algorithms for resolving multiple safety breaches within the same altitude, and algorithms for off-highway short-range path planning of multiple UAVs.
+%Immediate future work includes exploring different vehicle models, investigating algorithms for resolving multiple safety breaches within the same altitude, and algorithms for off-highway short-range path planning of multiple UAVs.

### 2016-11-07 docs/AIAA 2016 highway platooning/high_form.tex
edited AIAA paper up to reviewer 2's comments

@@
 With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution that allows for real-time recomputation.
+
+\AEnote{Note that the primary purpose of this section is to provide a method for the real-time placement of air highways.
+The specifics of coming up with the cost map based on population density, geography, weather forecast information, etc., as well as the criteria for updating the air highway locations, is not discussed.}
 
@@
 The air highway placement problem minimizes the cumulative cost of flying from some origin $p^o$ to some destination $p^d$ along the sequence of highways $\hws_N=\{\hw_1, \hw_2, \ldots, \hw_N\}$.
-The regularization term is used to prevent $N$ from being arbitrarily large.
+The regularization term $R(N)$ is used to prevent $N$ from being arbitrarily large.
 

### 2016-11-07 docs/AIAA 2016 highway platooning/introduction.tex
edited AIAA paper up to reviewer 2's comments

@@
 Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, videography, and search and rescue \cite{Kopardekar16}.
-In the future, the applications of UAVs are only limited by human imagination.
+In the future, the use of UAVs \ROnote{is likely to become more and more prevalent.}
 
@@
 
-Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Chen17,Ding08}.
+Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10, Mitchell05, Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15, Chen14, Chen17, Ding08}.
 These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
@@
 Furthermore, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems.
-The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox,Osher02,Sethian96}.
+The success of HJ reachability analysis in previous applications \ROnote{is partly due to} the numerical tools readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox, Osher02, Sethian96}.
 However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles.
@@
 Once air highways are in place, platoons of UAVs can then fly in fixed formations along the highway to get from origin to destination.
+\AEnote{The air highway structure greatly simplifies safety analysis, while at the same time intuitively allows human participation in airspace management.}
 

### 2016-11-07 docs/AIAA 2016 highway platooning/plat_form.tex
edited AIAA paper up to reviewer 2's comments

@@
 Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways.
-The platooning concept provides a structural solution for monitoring and ensuring the safety of a large number of UAVs.
-The structure imposed by air highways reduces the number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all UAVs.
+\AEnote{The air highway structure along with the UAV platooning concept together enable the use of reachability to analyze liveness and safety.} The structure reduces the likelihood of multiple-way conflicts, and makes pairwise analysis more indicative of the joint safety of all UAVs.
+\AEnote{In addition to reducing complexity, the proposed structure is intuitive, and allows human participation in the monitoring and management of the unmanned airspace.}
 
@@
 A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $\td$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system.
+
+\ROnote{Such a fail-safe mechanism could be an emergency landing procedure such as those analyzed in \cite{Adler2012,Coombes2014,Idicula2015}.
+Typically, emergency landing involves identifying types of faults, and finding feasible landing locations given the dynamics during the fault.}
 \end{itemize}
@@
 In this paper, these guarantees are provided using reachability analysis, and allow the multi-UAV system to perform joint maneuvers essential to maintaining structure in the airspace.
+
+\ROnote{Note that if vehicles in the airspace are far away from each other, it may be reasonable for all vehicles to remain in the ``free'' mode and fly in an unstructured manner.
+As long as multiple-way conflicts do not occur, pairwise collision avoidance maneuvers would be sufficient to ensure safety.
+Unstructured flight is likely to result in more efficient trajectories for each individual vehicle.
+However, whether multiple-way conflicts occur cannot be predicted ahead of time, and are not resolvable when they occur.
+By organizing vehicles into platoons, the likelihood of multiple-way conflicts is vastly reduced.
+Structured flight is in general less efficient for the individual vehicle, and this loss of efficiency can be thought of as a cost incurred by the vehicles in order ensure higher levels of safety.
+Further research is needed to better understand parameters such as the best size for a platoon and the density of vehicles above which unstructured flight is no longer manageable.}

### 2016-11-07 docs/AIAA 2016 highway platooning/plat_sim.tex
edited AIAA paper up to reviewer 2's comments

@@
         \includegraphics[width=\textwidth]{fig/in_100}
-        \caption{Four vehicles in a platoon are traveling along the highway. The yellow intruder disregards other vehicles.}
+        \caption{A four-vehicle platoon travels along the highway. The yellow vehicle disregards the others.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/in_120}
-        \caption{Platoon members begin avoidance maneuvers as they get near the safety reachable set boundaries with respect to the intruder.}
+        \caption{Vehicles begin avoidance maneuvers as they get near safety reachable set boundaries.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/in_140}
-        \caption{As the intruder (yellow) crosses the highway, the safety controller causes platoon members spread out to ``make room'' for the intruder to pass.}
+        \caption{Safety controllers cause vehicles to spread out to ``make room'' for the intruder to pass.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/ch_83}
-        \caption{A three-vehicle platoon and a four-vehicle platoon are traveling on their respective air highways.}
+        \caption{A three-vehicle platoon and a four-vehicle platoon travel on their respective air highways.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/ch_124}
-        \caption{As the four-vehicle platoon nears the intersection, the yellow vehicle steers off its old highway to join the new platoon. The green vehicle becomes the old platoon's new leader.}
+        \caption{The yellow vehicle begins to join the new platoon; The green vehicle becomes a leader.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{fig/ch_170}
-        \caption{The dark red vehicle also changes highways to join a new platoon, while the orange vehicle catches up to the new platoon leader to maintain a proper formation.}
+        \caption{The dark red vehicle joins a new platoon; the orange vehicle catches up to new platoon leader.}
     \end{subfigure}

### 2016-11-09 docs/AIAA 2016 highway platooning/high_form.tex
going through reviewer 2 comments; currently changing reachable set to BRS

@@
 
-\AEnote{Note that the primary purpose of this section is to provide a method for the real-time placement of air highways.
+\MCnote{Note that the primary purpose of this section is to provide a method for the real-time placement of air highways.
 The specifics of coming up with the cost map based on population density, geography, weather forecast information, etc., as well as the criteria for updating the air highway locations, is not discussed.}
+
+\MCnote{Note that if vehicles in the airspace are far away from each other, it may be reasonable for all vehicles to remain in the ``free'' mode and fly in an unstructured manner.
+As long as multiple-way conflicts do not occur, pairwise collision avoidance maneuvers would be sufficient to ensure safety.
+Unstructured flight is likely to result in more efficient trajectories for each individual vehicle.}
+
+\MCnote{However, whether multiple-way conflicts occur cannot be predicted ahead of time, and are not resolvable when they occur.
+By organizing vehicles into platoons, the likelihood of multiple-way conflicts is vastly reduced.
+Structured flight is in general less efficient for the individual vehicle, and this loss of efficiency can be thought of as a cost incurred by the vehicles in order ensure higher levels of safety.}
+
+\MCnote{In general, there may be many different levels of abstractions in the airspace.
+For larger regions such as cities, air highways may prove beneficial, and for a small region such as a neighborhood, perhaps unstructured flight is sufficiently safe.
+Further research is needed to better understand parameters such as the density of vehicles above which unstructured flight is no longer manageable, and other details like platoon size.}
 

### 2016-11-09 docs/AIAA 2016 highway platooning/introduction.tex
going through reviewer 2 comments; currently changing reachable set to BRS

--- 2016-07-11 docs/AIAA 2016 highway platooning/introduction.tex
@@
 Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, videography, and search and rescue \cite{Kopardekar16}.
-In the future, the applications of UAVs are only limited by human imagination.
+In the future, the use of UAVs \MCnote{is likely to become more and more prevalent.}
 
@@
 
-Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Chen17,Ding08}.
-These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
-Reachability is a powerful tool because reachable sets can be used for synthesizing both controllers that steer the system towards a set of goal states (liveness controllers), and controllers that steer the system away from a set of unsafe states (safety controllers).
-Furthermore, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems.
-The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox,Osher02,Sethian96}.
+Optimal control and game theory present powerful tools for providing safety and goal satisfaction guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10, Mitchell05, Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15, Chen14, Chen17, Ding08}.
+These formulations are based on Hamilton-Jacobi (HJ) reachability, which can compute the \MCnote{backward reachable set (BRS)}, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
+HJ reachability is a powerful tool because BRS can be used for synthesizing both controllers that steer the system away from a set of unsafe states (``safety controllers'') to guarantee safety, and controllers that steer the system into a set of goal states (``goal satisfaction controllers'') to guarantee goal satisfaction.
+\MCnote{Unlike many formulations of reachability, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of controlled non-linear systems under disturbances}.
+Furthermore, HJ reachability analysis \MCnote{is complemented by} many numerical tools readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox, Osher02, Sethian96}.
 However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles.
@@
 Once air highways are in place, platoons of UAVs can then fly in fixed formations along the highway to get from origin to destination.
+\MCnote{The air highway structure greatly simplifies safety analysis, while at the same time intuitively allows human participation in airspace management.}
 
@@
 
-Previous analyses of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
-In the second part of this paper, we propose organizing UAVs into platoons, which provide a structure that allows pairwise safety guarantees from HJ reachability to better translate to safety guarantees for the whole platoon.
+Previous analyses of a large number of vehicles typically do not provide safety and \MCnote{goal satisfaction} guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
+In the second part of this paper, we propose organizing UAVs into platoons, which provides a structure that allows pairwise safety guarantees from HJ reachability to better translate to safety guarantees for the whole platoon.
 With respect to platooning, we first propose a hybrid systems model of UAVs in platoons to establish the modes of operation needed for our platooning concept.

### 2016-11-09 docs/AIAA 2016 highway platooning/main.tex
edited AIAA paper up to reviewer 2's comments
going through reviewer 2 comments; currently changing reachable set to BRS

@@
 %\newcommand{\MCnote}{\todo[size=\footnotesize,author=MC,color=cyan]}
+\usepackage{cite}
+\newcommand{\MCnote}{\textcolor{red}}
 
@@
 \author{Mo Chen, Qie Hu, Jaime F. Fisac, Kene Akametalu, Casey Mackin, Claire J. Tomlin}
-\title{Reachability-Based Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}
+\title{\MCnote{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}}
 
 \abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations.
-As a result, unmanned aerial systems traffic management is needed to ensure the safety and liveness of potentially thousands of UAVs flying simultaneously.
-Currently, the analysis of large multi-agent systems cannot tractably provide safety and liveness guarantees if the agents' set of maneuvers is unrestricted.
+As a result, unmanned aerial systems traffic management is needed to ensure the safety and \MCnote{goal satisfaction} of potentially thousands of UAVs flying simultaneously.
+Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers is unrestricted.
 In this paper, platoons of UAVs flying on air highways is proposed to impose an airspace structure that allows for tractable analysis.
@@
 Within platoons traveling on air highways, each vehicle is modeled as a hybrid system.
-Using Hamilton-Jacobi reachability, safety and liveness are guaranteed for all mode transitions.
+Using Hamilton-Jacobi reachability, safety and \MCnote{goal satisfaction} are guaranteed for all mode transitions.
 For a single altitude range, the proposed approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.
-The satisfaction of safety and liveness requirements is demonstrated through simulations of three scenarios.}
+Safety and \MCnote{goal satisfaction} are demonstrated through simulations of three scenarios.}
 

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_controllers.tex
going through reviewer 2 comments; currently changing reachable set to BRS

@@
 In order to construct different controllers, an appropriate target set needs to be defined depending on the goal of the controller.
-If one defines the target set to be a set of desired states, the reachable set would represent the states that a system needs to first arrive at in order to reach the desired states.
-On the other hand, if the target set represents a set of undesirable states, then the reachable set would indicate the region of the state space that the system needs to avoid.
-In addition, the system dynamics with which the reachable set is computed provide additional flexibility when using reachability to construct controllers.
+If one defines the target set to be a set of desired states, the BRS would represent the states that a system needs to first arrive at in order to reach the desired states.
+On the other hand, if the target set represents a set of undesirable states, then the BRS would indicate the region of the state space that the system needs to avoid.
+In addition, the system dynamics with which the BRS is computed provide additional flexibility when using reachability to construct controllers.
 
@@
 Here, we represent the target set $\mathcal{L}_H$ as the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE that we need to solve.
-Once the HJB PDE is solved, we obtain the reachable set $\mathcal V_H(t)$ from the subzero level set of the solution $V_H(t,x)$.
+Once the HJB PDE is solved, we obtain the BRS $\mathcal V_H(t)$ from the subzero level set of the solution $V_H(t,x)$.
 More concretely, $\mathcal{V}_H(T) = \{x: V_H(-T,x)\le 0\}$ is the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.
 
-Depending on the time horizon $T$, the size of the reachable set $\mathcal V_H(T)$ varies.
-In general, a vehicle may not initially be inside the reachable set $\mathcal V_H(T)$, yet it needs to be in order to get to its desired target state.
+Depending on the time horizon $T$, the size of the BRS $\mathcal V_H(T)$ varies.
+In general, a vehicle may not initially be inside the BRS $\mathcal V_H(T)$, yet it needs to be in order to get to its desired target state.
 Determining a control strategy to reach $\mathcal V_H(T)$ is itself a reachability problem (with $\mathcal V_H(T)$ as the target set), and it would seem like this reachability problem needs to be solved in order for us to use the results from our first reachability problem.
@@
 \begin{enumerate}
-\item Move towards $\bar{x}_H$ in pure pursuit with some velocity, until $V_H(-T,x)\le 0$. In practice, this step consistently drives the system into the reachable set.
+\item Move towards $\bar{x}_H$ in pure pursuit with some velocity, until $V_H(-T,x)\le 0$. In practice, this step consistently drives the system into the BRS.
 \item Apply the optimal control extracted from $V_H(-T,x)$ according to \eqref{eq:HJB_ctrl_syn} until $\mathcal{L}_H$ is reached.
@@
 The zero sublevel set of the solution to \eqref{eq:HJIPDE}, $V_P(-T,x)$, gives us the set of relative states from which a quadrotor can reach the target in the relative coordinates within a duration of $T$.
-In the reachable set computation, we assume that the reference vehicle moves along the highway at constant speed, so that $u_j(t)$ = 0.
+In the BRS computation, we assume that the reference vehicle moves along the highway at constant speed, so that $u_j(t)$ = 0.
 The following is a suitable algorithm for a vehicle joining a platoon to follow the platoon leader:
@@
 \subsubsection{Avoiding Collisions \label{sec:collision_ctrl}}
-A vehicle can use a liveness controller described in the previous sections when it is not in any danger of collision with other vehicles.
+A vehicle can use a goal satisfaction controller described in the previous sections when it is not in any danger of collision with other vehicles.
 If the vehicle could potentially be involved in a collision within the next short period of time, it must switch to a safety controller.
@@
 We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJI PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition.
-As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the reachable set $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst-case control.
-To avoid collisions, $Q_i$ must apply the safety controller according to \eqref{eq:HJI_ctrl_syn} on the boundary of the reachable set in order to avoid going into the reachable set.
-The following algorithm wraps our safety controller around liveness controllers:
+As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the BRS $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst-case control.
+To avoid collisions, $Q_i$ must apply the safety controller according to \eqref{eq:HJI_ctrl_syn} on the boundary of the BRS in order to avoid going into the BRS.
+The following algorithm wraps our safety controller around goal satisfaction controllers:
 
@@
 
-$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety.
-\item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:
+$\mathcal{Q}(i)$ is the set of quadrotors with which vehicle $\veh{i}$ checks safety.
+\item Use the safety or goal satisfaction controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:
 
-If $\exists j\in \mathcal{Q}(i),V_S(-t,x_i-x_j)\le 0$, then $Q_i,Q_j$ are in potential conflict, and $Q_i$ must use a safety controller; otherwise $Q_i$ uses a liveness controller.
+If $\exists j\in \mathcal{Q}(i),V_S(-t,x_i-x_j)\le 0$, then $Q_i,Q_j$ are in potential conflict, and $Q_i$ must use a safety controller; otherwise $Q_i$ may use a goal satisfaction controller.
 \end{enumerate}
@@
 \subsection{Other Controllers \label{sec:other_ctrl}}
-Reachability was used in Section \ref{sec:reach_ctrl} for the relatively complex maneuvers that require safety and liveness guarantees.
+Reachability was used in Section \ref{sec:reach_ctrl} for the relatively complex maneuvers that require safety and goal satisfaction guarantees.
 For the simpler maneuvers of traveling along a highway and following a platoon, many well-known classical controllers suffice.

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_form.tex
going through reviewer 2 comments; currently changing reachable set to BRS

--- 2016-07-08 docs/AIAA 2016 highway platooning/plat_form.tex
@@
 Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways.
-The platooning concept provides a structural solution for monitoring and ensuring the safety of a large number of UAVs.
-The structure imposed by air highways reduces the number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all UAVs.
+\MCnote{The air highway structure along with the UAV platooning concept together enable the use of reachability to analyze safety and goal satisfaction properties.} The structure reduces the likelihood of multiple-way conflicts, and makes pairwise analysis more indicative of the joint safety of all UAVs.
+\MCnote{In addition to reducing complexity, the proposed structure is intuitive, and allows human participation in the monitoring and management of the unmanned airspace.}
 
@@
 Thus, in our present work, we will consider the situation where UAVs travel on air highways in platoons, defined in the following sections.
-The structure imposed by air highways and platooning enables us to analyze the liveness and safety of the vehicles in a tractable manner.
+The structure imposed by air highways and platooning enables us to analyze the safety and goal satisfaction properties of the vehicles in a tractable manner.
 
@@
 A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $\td$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system.
+
+\MCnote{Such a fail-safe mechanism could be an emergency landing procedure such as those analyzed in \cite{Adler2012,Coombes2014,Idicula2015}.
+Typically, emergency landing involves identifying types of faults, and finding feasible landing locations given the dynamics during the fault.}
 \end{itemize}
@@
 Given the above modeling assumptions, our goal is to provide control strategies to guarantee the success and safety of all the mode transitions.
-The theoretical tool used to provide the liveness and safety guarantees is reachability.
+The theoretical tool used to provide the safety and goal satisfaction guarantees is reachability.
 The reachable sets we compute will allow each vehicle to perform complex actions such as
@@
 
-In general, the control strategies of each vehicle have a liveness component, which specifies a set of states that the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.
-Together, the liveness and safety controllers guarantee the success and safety of a vehicle in the airspace making any desired mode transition.
+In general, the control strategy of each vehicle has a safety component, which specifies a set of states that it must avoid, and \MCnote{a goal satisfaction component}, which specifies a set of states that the vehicle aims to reach.
+Together, the safety and goal satisfaction controllers guarantee the safety and success of a vehicle in the airspace making any desired mode transition.
 In this paper, these guarantees are provided using reachability analysis, and allow the multi-UAV system to perform joint maneuvers essential to maintaining structure in the airspace.

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_reach.tex
going through reviewer 2 comments; currently changing reachable set to BRS

@@
 
-Given the dynamics \eqref{eq:dyn} and the target set $\mathcal{L}$, we would like to compute the reachable set, $\mathcal{V}(t)$:
+Given the dynamics \eqref{eq:dyn} and the target set $\mathcal{L}$, we would like to compute the BRS, $\mathcal{V}(t)$:
 
@@
 
-Many methods involving solving HJ PDEs \cite{Mitchell05} and HJ variational inequalities (VI) \cite{Bokanowski10,Barron89,Fisac15} have been developed for computing the reachable set.
+Many methods involving solving HJ PDEs \cite{Mitchell05} and HJ variational inequalities (VI) \cite{Bokanowski10,Barron89,Fisac15} have been developed for computing the BRS.
 These HJ PDEs and HJ VIs can be solved using well-established numerical methods.
-For this paper, we use the formulation in \cite{Mitchell05}, which has shown that the reachable set $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
+For this paper, we use the formulation in \cite{Mitchell05}, which shows that the BRS $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
 
@@
 	\includegraphics[width=0.95\textwidth]{"fig/RSExample"}
-	\caption{Illustration of a target set, reachable set, and their implicit surface functions.}
+	\caption{Illustration of a target set, a BRS, and their implicit surface functions.}
 	\label{fig:RSExample}
@@
 
-The reachable set in this case would be given by the Hamilton-Jacobi-Bellman (HJB) PDE
+The BRS in this case would be given by the Hamilton-Jacobi-Bellman (HJB) PDE
 
@@
 
-For our application, we will use several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real-time 4D reachable set computations and tractable 6D reachable set computations.
+For our application, we will use several decoupled system models and utilize decomposition techniques \cite{Chen15, Chen17b, Chen2016a}, which enables real-time 4D BRS computations and tractable 6D BRS computations.
 

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_safety.tex
removed comments
going through reviewer 2 comments; currently changing reachable set to BRS

@@
 So $\vehSCS{P_1}=\{P_2\}, \vehSCS{P_N}=\{P_{N-1}\}$.
-When all vehicles are using liveness controllers to perform their allowed maneuvers, in most situations no pair of vehicles should be in an unsafe configuration.
+When all vehicles are using goal satisfaction controllers to perform their allowed maneuvers, in most situations no pair of vehicles should be in an unsafe configuration.
 However, occasionally a vehicle $\veh{k}$ may behave unexpectedly due to faults or malfunctions, in which case it may come into an unsafe configuration with another vehicle.

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_sim.tex
going through reviewer 2 comments; currently changing reachable set to BRS

@@
 In order to do this, each vehicle first checks safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:collision_ctrl}.
-Otherwise, the vehicle uses the liveness controller for getting to an absolute target set described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl} in order to merge onto the highway, create a platoon, and become a Leader vehicle if there are no platoons on the highway.
-If there is already a platoon on the highway, then the vehicle would use the liveness controller for getting to a target set relative to the platoon leader as described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl} to join the platoon and become a Follower.
+Otherwise, the vehicle uses the goal satisfaction controller for getting to an absolute target set described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl} in order to merge onto the highway, create a platoon, and become a Leader vehicle if there are no platoons on the highway.
+If there is already a platoon on the highway, then the vehicle would use the goal satisfaction controller for getting to a target set relative to the platoon leader as described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl} to join the platoon and become a Follower.
 
@@
 
-The first two plots in Figure \ref{fig:fp} illustrate the use of liveness and safety reachable sets for the first two vehicles.
-Since the liveness reachable sets are in 4D and the safety reachable sets are in 6D, we compute and plot their 2D slices based on the vehicles' velocities and relative velocities.
-All vehicles begin as Free vehicles, so they each need to take into account five different reachable sets: four safety reachable sets and one liveness reachable set.
-For clarity, we only show the liveness reachable set and the four safety reachable sets for one of the vehicles.
+The first two plots in Figure \ref{fig:fp} illustrate the use of goal satisfaction and safety reachable sets for the first two vehicles.
+Since the goal satisfaction reachable sets are in 4D and the safety reachable sets are in 6D, we compute and plot their 2D slices based on the vehicles' velocities and relative velocities.
+All vehicles begin as Free vehicles, so they each need to take into account five different reachable sets: four safety reachable sets and one goal satisfaction reachable set.
+For clarity, we only show the goal satisfaction reachable set and the four safety reachable sets for one of the vehicles.
 
@@
 
-At $t=4.2$, $\veh{1}$ (orange) is inside the liveness reachable set for getting to an absolute state, shown as the dotted orange boundary.
+At $t=4.2$, $\veh{1}$ (orange) is inside the goal satisfaction reachable set for getting to an absolute state, shown as the dotted orange boundary.
 Therefore, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$.
@@
 Note that $\bar{x}_P$ moves with $\veh{1}$ (orange) as $\bar{x}_P$ is defined in terms of the relative states of the two vehicles.
-Since $\veh{2}$ is inside the liveness reachable set boundary for joining the platoon (purple dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target as long as it stays out of all safety reachable sets.
+Since $\veh{2}$ is inside the goal satisfaction reachable set boundary for joining the platoon (purple dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target as long as it stays out of all safety reachable sets.
 For example, at $t=5.9$, $\veh{2}$ (purple) is outside of the safety reachable set with respect to $\veh{1}$ (orange), shown as the purple dashed boundary around $\veh{1}$ (orange).
@@
 All 5 vehicles eventually form a single platoon and travel along the highway together.
-As with the first two vehicles, the liveness controllers allow the remaining vehicles to optimally and smoothly join the platoon, while the safety controllers prevent collisions from occurring.
+As with the first two vehicles, the goal satisfaction controllers allow the remaining vehicles to optimally and smoothly join the platoon, while the safety controllers prevent collisions from occurring.
 
@@
     \centering
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_43}
-        \includegraphics[width=\textwidth]{fig/fp_43}
-        \caption{The red vehicle follows the reachability-based liveness controller for getting to an absolute target state to merge onto the highway, while avoiding collisions using the reachability-based safety controller.
-The liveness reachable set and one safety reachable set are shown as the dotted and dashed boundaries, respectively.}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:fp_43}
+        \includegraphics[width=\columnwidth]{fig/fp_43}
+        \caption{The red vehicle is merging onto the highway while avoiding collisions.}
     \end{subfigure}
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_81}
-        \includegraphics[width=\textwidth]{fig/fp_81}
-        \caption{After the red vehicle successfully merges onto the highway and becomes the platoon leader, the purple vehicle uses the reachability-based liveness controller for getting to a relative target state to join the platoon, while avoiding collisions using the reachability-based safety controller.
-The liveness and safety reachable sets are shown as the dotted and dashed boundaries, respectively.}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:fp_81}
+        \includegraphics[width=\columnwidth]{fig/fp_81}
+        \caption{The purple vehicle is joining the platoon while avoiding collisions.}
     \end{subfigure}
 
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_110}
-        \includegraphics[width=\textwidth]{fig/fp_110}
-        \caption{After the first two vehicles successfully form a two-vehicle platoon, the rest of the vehicles follow the same process to join the platoon.}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:fp_110}
+        \includegraphics[width=\columnwidth]{fig/fp_110}
+        \caption{The last three vehicles follow the same process to join the platoon.}
     \end{subfigure}
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:fp_210}
-        \includegraphics[width=\textwidth]{fig/fp_210}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:fp_210}
+        \includegraphics[width=\columnwidth]{fig/fp_210}
         \caption{All five vehicles have successfully joined the platoon and now travel on the highway together.}
@@
     \centering
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:in_100}
-        \includegraphics[width=\textwidth]{fig/in_100}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:in_100}
+        \includegraphics[width=\columnwidth]{fig/in_100}
         \caption{A four-vehicle platoon travels along the highway. The yellow vehicle disregards the others.}
     \end{subfigure}
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:in_120}
-        \includegraphics[width=\textwidth]{fig/in_120}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:in_120}
+        \includegraphics[width=\columnwidth]{fig/in_120}
         \caption{Vehicles begin avoidance maneuvers as they get near safety reachable set boundaries.}
@@
 
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:in_140}
-        \includegraphics[width=\textwidth]{fig/in_140}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:in_140}
+        \includegraphics[width=\columnwidth]{fig/in_140}
         \caption{Safety controllers cause vehicles to spread out to ``make room'' for the intruder to pass.}
     \end{subfigure}
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:in_200}
-        \includegraphics[width=\textwidth]{fig/in_200}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:in_200}
+        \includegraphics[width=\columnwidth]{fig/in_200}
         \caption{After danger has passed, the platoon resumes normal operation.}
@@
     \centering
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:ch_83}
-        \includegraphics[width=\textwidth]{fig/ch_83}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:ch_83}
+        \includegraphics[width=\columnwidth]{fig/ch_83}
         \caption{A three-vehicle platoon and a four-vehicle platoon travel on their respective air highways.}
     \end{subfigure}
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:ch_124}
-        \includegraphics[width=\textwidth]{fig/ch_124}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:ch_124}
+        \includegraphics[width=\columnwidth]{fig/ch_124}
         \caption{The yellow vehicle begins to join the new platoon; The green vehicle becomes a leader.}
@@
 
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:ch_170}
-        \includegraphics[width=\textwidth]{fig/ch_170}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:ch_170}
+        \includegraphics[width=\columnwidth]{fig/ch_170}
         \caption{The dark red vehicle joins a new platoon; the orange vehicle catches up to new platoon leader.}
     \end{subfigure}
-    \begin{subfigure}[t]{0.45\textwidth} \label{subfig:ch_231}
-        \includegraphics[width=\textwidth]{fig/ch_231}
+    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:ch_231}
+        \includegraphics[width=\columnwidth]{fig/ch_231}
         \caption{New platoons now travel on their respective air highways.}

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_summary.tex
going through reviewer 2 comments; currently changing reachable set to BRS

@@
 We have introduced several reachability-based controllers, as well as some simple controllers.
-Pairwise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:collision_ctrl}.
-As long as a vehicle is not in potential danger according to the safety reachable sets, it is free to use any other controller.
-All of these other controllers are \textit{liveness controllers}, and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.
+Pairwise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:collision_ctrl}.
+As long as a vehicle is not in potential danger according to the safety BRSs, it is free to use any other controller.
+All of these other controllers are \MCnote{\textit{goal satisfaction controllers}}, and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.
 

### 2016-11-09 docs/AIAA 2016 highway platooning/response1/response1.tex
edited AIAA paper up to reviewer 2's comments
going through reviewer 2 comments; currently changing reachable set to BRS

@@
 \maketitle
+
+Comments and questions from reviewers have been either bolded or italicized.
+The bolded comments and questions have been directly addressed below.
+All comments have been addressed in the paper as much as possible without major changes to the core of the paper.
 
@@
 Good point.
-Here, liveness refers to the system eventually being able to reach a set of goal states.
-In the context of HJ reachability, the guarantee is actually being able to reach a set of goal states within some time horizon.
-The text has been modified to reflect this point, and a reference in the introduction has been added.
+In the context of HJ reachability, liveness refers to being able to reach a set of goal states within some time horizon.
+To avoid confusion, ``liveness'' has been changed to ``goal satisfaction''.
 \end{itemize}

### 2016-11-09 docs/AIAA 2016 highway platooning/conclusions.tex
edited up to reviewer 2: air highways

@@
 We showed how such an airspace structure leads to much easier safety and liveness analysis.
-We provided simulations which show that by organizing vehicles into platoons, many complex maneuvers can be performed using just a few different reachable sets.
+We provided simulations which show that by organizing vehicles into platoons, many complex maneuvers can be performed using just a few different backward reachable sets.
 

### 2016-11-09 docs/AIAA 2016 highway platooning/high_form.tex
edited up to reviewer 2: air highways

@@
 
-\MCnote{Note that if vehicles in the airspace are far away from each other, it may be reasonable for all vehicles to remain in the ``free'' mode and fly in an unstructured manner.
+\MCnote{In addition, if vehicles in the airspace are far away from each other, it may be reasonable for all vehicles to remain in the ``free'' mode and fly in an unstructured manner.
 As long as multiple-way conflicts do not occur, pairwise collision avoidance maneuvers would be sufficient to ensure safety.

### 2016-11-09 docs/AIAA 2016 highway platooning/introduction.tex
edited up to reviewer 2: air highways

@@
 Finally, we show several simulations to illustrate the behavior of UAVs in various scenarios.
+
+\MCnote{Overall, this paper is not meant to provide an exhaustive solution to the airspace management problem.
+Instead, this paper illustrates that the computation intractability of HJ reachability can be overcome using an air highway structure with UAVs flying in platoons.
+In addition, the results are intuitive, which can facilitate human participation in managing the airspace.
+Although many challenges not addressed in this paper still need to be overcome, this paper can provide a starting point for future research in large-scale UASs with safety and goal satisfaction guarantees.}

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_safety.tex
edited up to reviewer 2: air highways

@@
 \subsection{Safety Analysis}
-Under normal operations in a single platoon, each follower vehicle $\veh{i},i=P_2,\ldots,P_{M-1}$ in a platoon checks whether it is in the safety reachable set with respect to $\veh{P_{i-1}}$ and $\veh{P_{i+1}}$.
+Under normal operations in a single platoon, each follower vehicle $\veh{i},i=P_2,\ldots,P_{M-1}$ in a platoon checks whether it is in the safety BRS with respect to $\veh{P_{i-1}}$ and $\veh{P_{i+1}}$.
 So $\vehSCS{i} = \{P_{i+1}, P_{i-1}\}$ for $i=P_2,\ldots,P_{N-1}$.
@@
 
-With our choice of $\vehSCS{i}$ and the assumption that the platoon is in a single-file formation, some vehicle $\veh{i}$ would get near the safety reachable set with respect to $\veh{k}$, where $\veh{k}$ is likely to be the vehicle in front or behind of $\veh{i}$.
+With our choice of $\vehSCS{i}$ and the assumption that the platoon is in a single-file formation, some vehicle $\veh{i}$ would get near the safety BRS with respect to $\veh{k}$, where $\veh{k}$ is likely to be the vehicle in front or behind of $\veh{i}$.
 In this case, a ``safety breach" occurs.

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_sim.tex
edited up to reviewer 2: air highways

@@
 
-The first two plots in Figure \ref{fig:fp} illustrate the use of goal satisfaction and safety reachable sets for the first two vehicles.
-Since the goal satisfaction reachable sets are in 4D and the safety reachable sets are in 6D, we compute and plot their 2D slices based on the vehicles' velocities and relative velocities.
-All vehicles begin as Free vehicles, so they each need to take into account five different reachable sets: four safety reachable sets and one goal satisfaction reachable set.
-For clarity, we only show the goal satisfaction reachable set and the four safety reachable sets for one of the vehicles.
+The first two plots in Figure \ref{fig:fp} illustrate the use of safety and goal satisfaction BRS for the first two vehicles.
+Since the goal satisfaction BRSs are in 4D and the safety BRSs are in 6D, we compute and plot their 2D slices based on the vehicles' velocities and relative velocities.
+All vehicles begin as Free vehicles, so they each need to take into account five different BRSs: four safety BRSs and one goal satisfaction BRS.
+For clarity, we only show the goal satisfaction BRS and the four safety BRSs for one of the vehicles.
 
@@
 
-At $t=4.2$, $\veh{1}$ (orange) is inside the goal satisfaction reachable set for getting to an absolute state, shown as the dotted orange boundary.
+At $t=4.2$, $\veh{1}$ (orange) is inside the goal satisfaction BRS for getting to an absolute state, shown as the dotted orange boundary.
 Therefore, it is ``locked-in" to the target state $\bar{x}_H$, and follows the optimal control in \eqref{eq:HJB_ctrl_syn} to $\bar{x}_H$.
 During the entire time, $\veh{1}$ checks whether it may collide with any of the other vehicles within a time horizon of $\td$.
-To do this, it simply checks whether its state relative to each of the other vehicles is within the corresponding safety reachable set.
-As an example, the safety reachable set boundary with respect to $\veh{2}$ (purple) is shown as the orange dashed boundary around $\veh{2}$ (purple); $\veh{1}$ (orange) is safe with respect to $\veh{2}$ (purple) since $\veh{1}$ (orange) is outside of the boundary.
+To do this, it simply checks whether its state relative to each of the other vehicles is within the corresponding safety BRS.
+As an example, the safety BRS boundary with respect to $\veh{2}$ (purple) is shown as the orange dashed boundary around $\veh{2}$ (purple); $\veh{1}$ (orange) is safe with respect to $\veh{2}$ (purple) since $\veh{1}$ (orange) is outside of the boundary.
 In fact, $\veh{1}$ is safe with respect to all vehicles.
@@
 Note that $\bar{x}_P$ moves with $\veh{1}$ (orange) as $\bar{x}_P$ is defined in terms of the relative states of the two vehicles.
-Since $\veh{2}$ is inside the goal satisfaction reachable set boundary for joining the platoon (purple dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target as long as it stays out of all safety reachable sets.
-For example, at $t=5.9$, $\veh{2}$ (purple) is outside of the safety reachable set with respect to $\veh{1}$ (orange), shown as the purple dashed boundary around $\veh{1}$ (orange).
-Again, from the other safety reachable set boundaries, we can see that $\veh{2}$ is in fact safe with respect to all vehicles.
+Since $\veh{2}$ is inside the goal satisfaction BRS boundary for joining the platoon (purple dotted boundary), it is ``locked-in" to the target relative state $\bar{x}_P$, and begins following the optimal control in \eqref{eq:HJI_ctrl_syn} towards the target as long as it stays out of all safety BRSs.
+For example, at $t=5.9$, $\veh{2}$ (purple) is outside of the safety BRS with respect to $\veh{1}$ (orange), shown as the purple dashed boundary around $\veh{1}$ (orange).
+Again, from the other safety BRS boundaries, we can see that $\veh{2}$ is in fact safe with respect to all vehicles.
 
@@
 An intruder vehicle $\veh{5}$ (yellow) heads left, disregarding the presence of the platoon.
-At $t=11.9$, the platoon leader $\veh{1}$ (red) detects that it has gone near the boundary of the safety reachable set (not shown) with respect to the intruder $\veh{5}$ (yellow).
+At $t=11.9$, the platoon leader $\veh{1}$ (red) detects that it has gone near the boundary of the safety BRS (not shown) with respect to the intruder $\veh{5}$ (yellow).
 In response, $\veh{1}$ (red) starts using the safety controller to optimally avoid the intruder according to \eqref{eq:HJI_ctrl_syn}; in doing so, it steers slightly off the highway.
@@
 Note that although in this particular simulation, the intruder travels in a straight line, a straight line motion of the intruder was \textit{not} assumed.
-Rather, the safety reachable sets are computed assuming the worst case control of the intruder, according to \eqref{eq:HJI_ctrl_syn}.
+Rather, the safety BRSs are computed assuming the worst case control of the intruder, according to \eqref{eq:HJI_ctrl_syn}.
 
-As the intruder $\veh{5}$ (yellow) continues to disregard other vehicles, the followers of the platoon also get near the respective boundaries of their safety reachable sets with respect to the intruder.
+As the intruder $\veh{5}$ (yellow) continues to disregard other vehicles, the followers of the platoon also get near the respective boundaries of their safety BRSs with respect to the intruder.
 This occurs at $t=13.9$, where the platoon ``makes room'' for the intruder to pass by to avoid collisions; all vehicles deviate from their intended path, which is to follow the platoon leader or the highway.
 
-After the intruder has passed, eventually all vehicles become far away from any safety reachable sets.
+After the intruder has passed, eventually all vehicles become far away from any safety BRSs.
 When this occurs, the leader resumes following the highway, and the followers resume following the leader.
@@
         \includegraphics[width=\columnwidth]{fig/in_120}
-        \caption{Vehicles begin avoidance maneuvers as they get near safety reachable set boundaries.}
+        \caption{Vehicles begin avoidance maneuvers as they get near safety BRS boundaries.}
     \end{subfigure}

### 2016-11-09 docs/AIAA 2016 highway platooning/conclusions.tex
finished editing

@@
 To address the important and urgent problem of the traffic management of unmanned aerial vehicles (UAVs), we proposed to have platoons of UAVs traveling on air highways.
-We showed how such an airspace structure leads to much easier safety and liveness analysis.
+We showed how such an airspace structure leads to much easier safety and goal satisfaction analysis.
 We provided simulations which show that by organizing vehicles into platoons, many complex maneuvers can be performed using just a few different backward reachable sets.
@@
 We show how various required platoon functions (merging onto an air highway, changing platoons, etc.) can be implemented using only the Free, Leader, and Follower modes of operation.
-Using HJ reachability, we proposed liveness controllers that guarantee the success of all mode transitions, and wrapped a safety controller around liveness controllers to ensure no collision between the UAVs can occur.
+Using HJ reachability, we proposed goal satisfaction controllers that guarantee the success of all mode transitions, and wrapped a safety controller around goal satisfaction controllers to ensure no collision between the UAVs can occur.
 Under the assumption that faulty vehicles can descend after a pre-specified duration, our safety controller guarantees that no collisions will occur in a single altitude level as long as at most one safety breach occurs for each vehicle in the platoon.

### 2016-11-09 docs/AIAA 2016 highway platooning/high_eikon.tex
Part way through proofreading; currently on page 18, section III-C
finished editing

@@
 \begin{aligned}
-\ocost(\pos^d) &= \min_{\ppath(\cdot)} \ccost(\ppath) \\
-&= \min_{\ppath(\cdot)} \int_{s_0}^{s_1} \cmap(\ppath(s)) ds
+\ocost(\pos^d) &= \min_{\ppath(\cdot), \ppath(s_1)=\pos^d} \ccost(\ppath) \\
+&= \min_{\ppath(\cdot), \ppath(s_1)=\pos^d} \int_{s_0}^{s_1} \cmap(\ppath(s)) ds
 \end{aligned}
@@
 
-It is well known that the solution to the Eikonal equation \eqref{eq:eikonal} precisely computes the function $\ocost(\pos^d)$ given the cost map $\cmap$ \cite{Sethian96,Alton06}.
+It is well known that the \MCnote{viscosity solution} \cite{Crandall84} to the Eikonal equation \eqref{eq:eikonal} precisely computes the function $\ocost(\pos^d)$ given the cost map $\cmap$ \cite{Sethian96,Alton06}.
 Note that a single function characterizes the minimum cost from an origin $\pos^o$ to \textit{any} destination $\pos^d$.

### 2016-11-09 docs/AIAA 2016 highway platooning/high_form.tex
finished editing

@@
 To each highway, we assign a speed of travel $v_\hw$ and specify the direction of travel to be the direction from $\hw(0)$ to $\hw(1)$, denoted using a unit vector $\hwd = \frac{\hw(1) - \hw(0)}{\lVert\hw(1) - \hw(0)\rVert_2}$.
+\MCnote{As we show in Section \ref{sec:platooning}, UAVs use simple controllers to track the highway.}
 
@@
 With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution that allows for real-time recomputation.
+\MCnote{Our solution based on solving the Eikonal equation can be thought of as turning a cost map over a geographic area in continuous space into a discrete graph whose nodes are waypoints joined by edges which are air highways.}
 

### 2016-11-09 docs/AIAA 2016 highway platooning/high_sim.tex
finished editing

@@
 Note that we could have gone further to merge some of the overlapping highways.
-However, the purpose of this section is to illustrate the natural occurrence of air highways from cost-minimizing paths; post-processing of the cost-minimizing paths is not our focus.
+However, the purpose of this section is to illustrate the natural occurrence of air highways from cost-minimizing paths; post-processing of the cost-minimizing paths, \MCnote{which serve as a guide for defining air highways}, is not our focus.
 
@@
 \subsection{Real-Time Highway Location Updates}
-Since \eqref{eq:eikonal} can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost map changes.
+Since \eqref{eq:eikonal} can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost map changes \MCnote{at a particular time}.
 This flexibility can be useful in any situation in which unforeseen circumstances could cause a change in the cost of a particular region of the airspace.

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_form.tex
edited up to reviewer 2: air highways
finished editing

@@
 \noindent where $x$ represents the state, and $u$ represents the control action.
-The techniques we present in this paper do not depend on the dynamics of the vehicles.
+The techniques we present in this paper do not depend on the dynamics of the vehicles, \MCnote{as long as their dynamics are known}.
 However, for concreteness, we assume that the UAVs are quadrotors that fly at a constant altitude under non-faulty circumstances.
@@
 We will denote the $N$ vehicles as $\veh{i}, i=1\ldots,N$.
-We consider a platoon of vehicles to be a group of $M\le N$ vehicles, denoted $\veh{P_1}, \ldots, \veh{P_M}, \{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$, in a single-file formation.
+We consider a platoon of vehicles to be a group of $M$ vehicles ($M\le N$), denoted $\veh{P_1}, \ldots, \veh{P_M}, \{P_j\}_{j=1}^M \subseteq \{i\}_{i=1}^N$, in a single-file formation.
 When necessary, we will use superscripts to denote vehicles of different platoons: $\veh{P_i^j}$ represents the $i$th vehicle in the $j$th platoon.
@@
 The theoretical tool used to provide the safety and goal satisfaction guarantees is reachability.
-The reachable sets we compute will allow each vehicle to perform complex actions such as
+The BRSs we compute will allow each vehicle to perform complex actions such as
 

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_reach.tex
finished editing

@@
 These HJ PDEs and HJ VIs can be solved using well-established numerical methods.
-For this paper, we use the formulation in \cite{Mitchell05}, which shows that the BRS $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value Hamilton-Jacobi-Isaacs (HJI) PDE:
+For this paper, we use the formulation in \cite{Mitchell05}, which shows that the BRS $\mathcal{V}(t)$ can be obtained as the zero sublevel set of the viscosity solution \cite{Crandall84} $V(t,x)$ of the following terminal value HJ PDE:
 
@@
 
-The BRS in this case would be given by the Hamilton-Jacobi-Bellman (HJB) PDE
+The BRS in this case would be given by the HJ PDE
 

### 2016-11-09 docs/AIAA 2016 highway platooning/plat_safety.tex
finished editing

@@
 
-Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons.
-By treating each platoon as a single unit, we can reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.
+Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons \MCnote{when needed}.
+The option of treating each platoon as a single unit can reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.

### 2016-11-09 docs/AIAA 2016 highway platooning/response1/response1.tex
finished editing

@@
 A continuous space is convenient since the cost map is defined on a geographic map, which is a continuous space.
+Effectively the air highway placement method we propose converts a continuous cost map into a graph whose edges are the air highways.
 
@@
 \item \textit{Equation (10) – Some of the symbols in the equation were not defined.}
-\item \textit{What is the difference between the HJB and the HJ equations?}
+\item \textbf{What is the difference between the HJB and the HJ equations?}
+HJ generally refers to either HJB or HJI. The HJB equation is used when the dynamics only involves a control, and the HJI equation is used when the dynamics involve both a control and a disturbance.
 \item \textit{Figure 6 – What is the zero plane and where is it in the picture?}

### 2016-11-10 docs/AIAA 2016 highway platooning/high_form.tex
minor changes to revision

--- 2016-11-09 docs/AIAA 2016 highway platooning/high_form.tex
@@
 To each highway, we assign a speed of travel $v_\hw$ and specify the direction of travel to be the direction from $\hw(0)$ to $\hw(1)$, denoted using a unit vector $\hwd = \frac{\hw(1) - \hw(0)}{\lVert\hw(1) - \hw(0)\rVert_2}$.
+\MCnote{As we will show in Section \ref{sec:platooning}, UAVs use simple controllers to track the highway.}
 
@@
 With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution that allows for real-time recomputation.
+\MCnote{Our solution based on solving the Eikonal equation can be thought of as converting a cost map over a geographic area in continuous space into a discrete graph whose nodes are waypoints joined by edges which are the air highways.}
 
 \MCnote{Note that the primary purpose of this section is to provide a method for the real-time placement of air highways.
-The specifics of coming up with the cost map based on population density, geography, weather forecast information, etc., as well as the criteria for updating the air highway locations, is not discussed.}
+The specifics of determining the cost map based on population density, geography, weather forecast information, etc., as well as the criteria for when air highway locations need to be updated, is beyond the scope of this paper.}
 
-\MCnote{Note that if vehicles in the airspace are far away from each other, it may be reasonable for all vehicles to remain in the ``free'' mode and fly in an unstructured manner.
+\MCnote{In addition, if vehicles in the airspace are far away from each other, it may be reasonable for all vehicles to fly in an unstructured manner.
 As long as multiple-way conflicts do not occur, pairwise collision avoidance maneuvers would be sufficient to ensure safety.
-Unstructured flight is likely to result in more efficient trajectories for each individual vehicle.}
-
-\MCnote{However, whether multiple-way conflicts occur cannot be predicted ahead of time, and are not resolvable when they occur.
+Unstructured flight is likely to result in more efficient trajectories for each individual vehicle.
+However, whether multiple-way conflicts occur cannot be predicted ahead of time, and are not guaranteed to be resolvable when they occur.
 By organizing vehicles into platoons, the likelihood of multiple-way conflicts is vastly reduced.

### 2016-11-10 docs/AIAA 2016 highway platooning/introduction.tex
minor changes to revision

@@
 HJ reachability is a powerful tool because BRS can be used for synthesizing both controllers that steer the system away from a set of unsafe states (``safety controllers'') to guarantee safety, and controllers that steer the system into a set of goal states (``goal satisfaction controllers'') to guarantee goal satisfaction.
-\MCnote{Unlike many formulations of reachability, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of controlled non-linear systems under disturbances}.
+\MCnote{Unlike many formulations of reachability, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of controlled nonlinear systems under disturbances}.
 Furthermore, HJ reachability analysis \MCnote{is complemented by} many numerical tools readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox, Osher02, Sethian96}.
@@
 Once air highways are in place, platoons of UAVs can then fly in fixed formations along the highway to get from origin to destination.
-\MCnote{The air highway structure greatly simplifies safety analysis, while at the same time intuitively allows human participation in airspace management.}
+\MCnote{The air highway structure greatly simplifies safety analysis, while at the same time allows intuitive human participation in unmanned airspace management.}
 
@@
 
-\MCnote{Overall, this paper is not meant to provide an exhaustive solution to the airspace management problem.
+\MCnote{Overall, this paper is not meant to provide an exhaustive solution to the unmanned airspace management problem.
 Instead, this paper illustrates that the computation intractability of HJ reachability can be overcome using an air highway structure with UAVs flying in platoons.

### 2016-11-10 docs/AIAA 2016 highway platooning/plat_form.tex
minor changes to revision

@@
 \MCnote{Such a fail-safe mechanism could be an emergency landing procedure such as those analyzed in \cite{Adler2012,Coombes2014,Idicula2015}.
-Typically, emergency landing involves identifying types of faults, and finding feasible landing locations given the dynamics during the fault.}
+Typically, emergency landing involves identifying the type of fault and finding feasible landing locations given the dynamics during the fault.
+We will omit these details and summarize them into $\td$, the time required to exit the current altitude level.}
 \end{itemize}

### 2016-11-15 docs/AIAA 2016 highway platooning/response1/response1.tex
minor changes to revision
updated talk
updated revision

@@
 \maketitle
-
-Comments and questions from reviewers have been either bolded or italicized.
-The bolded comments and questions have been directly addressed below.
-All comments have been addressed in the paper as much as possible without major changes to the core of the paper.
 
@@
 One primary purpose of the paper is to highlight that air highway placement can be done in real-time given the cost map.
+The text in the paper has been updated to address this comment.
 
@@
 In terms of communicating this information, all vehicles and users could have an interface showing the current highway map.
+The text in the paper has been updated to address this comment.
 
@@
 Whether the vehicles are allowed to be free during their entire flight would be subject to traffic rules to be established by government agencies (or some centralized governing body).
+The text in the paper has been updated to address this comment.
 
@@
 When the number of vehicles increases to a point where all vehicles being free is no longer manageable, each vehicle would need to use the highways, and effectively ``pay'' for a structure that guarantees safety.
+The text in the paper has been updated to address this comment.
 
@@
 
-Strictly speaking there is no maximum. However, practically speaking it is unclear what the best size for a platoon would be on a single highway. Further research would be needed to understand this.
+Strictly speaking there is no maximum.
+However, practically speaking it is unclear what the best size for a platoon would be on a single highway.
+Further research would be needed to understand this.
+The text in the paper has been updated to address this comment.
 
-\item\textit{No future work in Conclusions.  The Conclusions section is only for conclusions that can be drawn directly from the manuscript.}
+\item\textbf{No future work in Conclusions.  The Conclusions section is only for conclusions that can be drawn directly from the manuscript.}
+
+The text in the paper has been updated to address this comment.
 \end{itemize}
@@
 \begin{enumerate}
-\item \textit{Please ensure that the captions of all figures are not longer than two lines.  Additional text can be included in the main body of the pager.}
-\item \textit{Please re-define all acronyms in the Conclusions.}
-\item \textit{The Conclusions section is reserved for conclusions that can be drawn from the body of the paper.  Please delete the last sentence since it is referring to future work.}
-\item \textit{DOI numbers are required for the references whenever available}
-\item \textit{AIAA conference papers need paper numbers}
+\item \textbf{Please ensure that the captions of all figures are not longer than two lines.  Additional text can be included in the main body of the pager.}
+\item \textbf{Please re-define all acronyms in the Conclusions.}
+\item \textbf{The Conclusions section is reserved for conclusions that can be drawn from the body of the paper.  Please delete the last sentence since it is referring to future work.}
+\item \textbf{DOI numbers are required for the references whenever available}
+\item \textbf{AIAA conference papers need paper numbers}
 \end{enumerate}
+The text in the paper has been updated to address these comments.
 
@@
 
-\textit{A well-written paper on a topic of increasing importance.
+\textbf{A well-written paper on a topic of increasing importance.
 The issue of traffic flow management as applied to low-altitude, small UAS is undervalued by many in ATM and aviation.
@@
 
-\textit{Overall the presentation of the paper is clear.
+\textbf{Overall the presentation of the paper is clear.
 However, as a reader, I was left with several (small) open questions.
@@
 \begin{enumerate}
-\item\textit{This work is like platooning research from traditional TFM.
+\item\textbf{This work is like platooning research from traditional TFM.
 The problem with those solutions was typically that through the implementation of platooning, often there was such a loss of efficiency to form the platoon, that it was ultimately not worth while.
 The authors should probably look at some of that previous work for citation rather than relying solely on ground vehicle platooning.}
+
+Platooning and flying on air highways in general can be seen as a cost that the system has to ``pay'' to ensure tractable analysis. This point has been added to the paper.
 
@@
 However, it is difficult to predict whether multiple conflicts would occur, and in addition, unstructured flight can be very unintuitive to monitor.
+This point has been emphasized slightly in the paper.
 
@@
 One assumption implicitly made in this paper is that the mechanism for exiting the altitude range can be abstracted or summarized into just a time-to-exit-altitude-range parameter.
+This point has been clarified in the paper.
 
-\item\textit{A few sentences about the policy implications may help ground the reader in terms of how such a system might find its way in to the airspace in the future.
+\item\textbf{A few sentences about the policy implications may help ground the reader in terms of how such a system might find its way in to the airspace in the future.
 Is this platooning a requirement of operators?
@@
 
-\item\textit{Should your state diagram (Figure 4) have a terminal state of some kind?
+This comment is in general similar to the first comment, and this point has been added to the paper.
+
+\item\textbf{Should your state diagram (Figure 4) have a terminal state of some kind?
 Like a "Closed" state where they just aren't flying anymore?
@@
 Where can the vehicles start out?}
+
+Modified figure caption to say that vehicles begin in the ``Free'' mode initially.
 \end{enumerate}
 
-\textit{Again, I don't think all of these questions need to be answered in detail, but addressing them will strengthen the paper.}
+\textbf{Again, I don't think all of these questions need to be answered in detail, but addressing them will strengthen the paper.}
 
-\textit{The only style point I have, is in that the introduction sounds a bit too "salesman" like.
+\textbf{The only style point I have, is in that the introduction sounds a bit too "salesman" like.
 In the first paragraph, terms like "important" and "human imagination" feel like they may be a tad overplayed.
@@
 
+Agreed. Text has been changed slightly to address this.
+
 \section{Reviewer 2's comments}
 
-\textit{The paper draws inspiration from the Automated Highway Systems (AHS) concept developed at Berkeley in the 90s.
+\textbf{The paper draws inspiration from the Automated Highway Systems (AHS) concept developed at Berkeley in the 90s.
 The paper proposes the introduction of structure, namely Air Highways and platoons, to airspace control, which is bound to be congested in a near future because of the drone revolution.
@@
 
-\textit{The problem is that there is no technical justification (or discussion) for this approach.
+\textbf{The problem is that there is no technical justification (or discussion) for this approach.
 True, that corridors (or Air Highways) make sense, especially in congested areas.
@@
 
+The text in the paper has been modified to address all of these major comments.
+
 \subsection{DETAILED COMMENTS}
@@
 
-\item \textit{“liveness” – Please cite optimal control work on liveness.}
+\item \textbf{“liveness” – Please cite optimal control work on liveness.}
 
@@
 
-\item \textit{''HJ reachability computations are intractable for a large number of vehicles'' – Actually it is not tractable for one single vehicle if we consider dynamics evolving in a high dimension state-space.}
+\item \textbf{''HJ reachability computations are intractable for a large number of vehicles'' – Actually it is not tractable for one single vehicle if we consider dynamics evolving in a high dimension state-space.}
 
@@
 Hopefully this paper can provide a starting point on which future research can be built, and make future research problems more concrete.
+This has been better emphasized in the revised paper.
 \end{itemize}
@@
 
-The paper does not explicitly address the problem of finding common pathways, but the air highway placement method presented here naturally leads to common pathways as seen in figures 2 and 3
+The paper does not explicitly address the problem of finding common pathways, but the air highway placement method presented here naturally leads to common pathways as seen in figures 2 and 3.
+This point has already been stated in the paper
 
@@
 II.A The air highway placement problem
-\item \textit{``... to each air highway we assign a speed of travel'' – shouldn’t this be a control setting? This varies a lot with the type of UAVs.}
-\item \textit{``...air highway locations should ideally be able to be recomputed in real-time when necessary in order to update airspace constraints on-the fly'' – how practical is this under the limitations discussed above?}
+\item \textbf{``... to each air highway we assign a speed of travel'' – shouldn’t this be a control setting? This varies a lot with the type of UAVs.}
+
+The text has been updated to emphasize that details like this are not the focus of the paper.
+
+\item \textbf{``...air highway locations should ideally be able to be recomputed in real-time when necessary in order to update airspace constraints on-the fly'' – how practical is this under the limitations discussed above?}
+
+The changes to the cost map should not be continuously varying in time. This has been clarified in the revision.
+
 \item \textbf{ ``...
@@
 
-\item \textit{Cost function – shouldn’t the cost function depend on the type of UAV?}
+\item \textbf{Cost function – shouldn’t the cost function depend on the type of UAV?}
+
+Perhaps. In this case, perhaps a different set of highways should be created, or somehow different cost maps should be merged together. However this point is out of the scope of the paper.
+
 \end{itemize}
@@
 \begin{itemize}
-\item \textit{``sequence of paths'' – same problem as above for highways}
+\item \textbf{``sequence of paths'' – same problem as above for highways}
 \item \textbf{``It is well known that the solution to the Eikonal equation (5)'' – this statement is misleading.
@@
 
-\item \textit{``Given a single origin point po, the optimal cumulative cost function V (pd) can be computed.
+\item \textbf{``Given a single origin point po, the optimal cumulative cost function V (pd) can be computed.
 Suppose M different destination points.
@@
 In fact any number of M will do since the value function is defined for the whole state space.}
-\item \textit{ Equation (3) – Are there any assumptions on the cost function? If not it may happen that V may not be differentiable. What about the interpretation of equation (5) for this case?}
+\item \textbf{ Equation (3) – Are there any assumptions on the cost function? If not it may happen that V may not be differentiable. What about the interpretation of equation (5) for this case?}
+
+Good point regarding differentiability. The solutions of PDEs in this paper are all viscosity solutions. The text has been changed accordingly with a citation on viscosity solutions added.
 \end{itemize}
@@
 \begin{itemize}
-\item \textit{``Since (5) can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost'' – True, but the results will no longer satisfy the Principle of Optimality which is at the root of the derivation of the Eikonal equation.}
-\item \textit{On the other hand, depending on for instance the time of day, it may be most desirable to fly in different regions of the airspace'' – Again, if the cost varies with time, then the Eikonal equation no longer solves for the value function V.}
+\item \textbf{``Since (5) can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost'' – True, but the results will no longer satisfy the Principle of Optimality which is at the root of the derivation of the Eikonal equation.}
+
+\item \textbf{On the other hand, depending on for instance the time of day, it may be most desirable to fly in different regions of the airspace'' – Again, if the cost varies with time, then the Eikonal equation no longer solves for the value function V.}
 \item \textbf{``We add to the collection of waypoints the first point on the path at which the heading changes by some threshold C, and repeat this process along the entire path.'' – The paths arising from the Eikonal equation can have kinks and jumps in curvature.
@@
 
-As mentioned, post-processing is not the focus of this paper.
+As mentioned, post-processing is not the focus of this paper. The text has been changed to emphasize this.
 \end{itemize}
@@
 
-\item \textit{``...
+\item \textbf{``...
 problem of collision avoidance among N vehicles cannot be tractably solved using traditional dynamic programming approaches because the computation complexity of these approaches scales exponentially with the number ...'' – This needs clarification.
@@
 
-\item \textit{``liveness and safety of the vehicles in a tractable manner'' – liveness and safety are not properly defined.}
-\item \textit{''We consider a platoon of vehicles to be a group of $M \le N$ vehicles, ...'' – This is not clear.}
-\item \textit{''If the vehicle is part of platoon, then it checks safety...” – what it the vehicle is the leader of a platoon? This case is addressed in Figure 5, but not here.}
-\item \textit{``...
+\item \textbf{``liveness and safety of the vehicles in a tractable manner'' – liveness and safety are not properly defined.}
+\item \textbf{''We consider a platoon of vehicles to be a group of $M \le N$ vehicles, ...'' – This is not clear.}
+\item \textbf{''If the vehicle is part of platoon, then it checks safety...” – what it the vehicle is the leader of a platoon? This case is addressed in Figure 5, but not here.}
+\item \textbf{``...
 have a liveness component, which specifies a set of states that the vehicle aims to reach, and a safety component, which specifies a set of states that it must avoid.'' – This is not a definition of liveness.}
@@
 B. Hamilton-Jacobi reachability
-\item \textit{Equation (10) – Some of the symbols in the equation were not defined.}
+\item \textbf{Equation (10) – Some of the symbols in the equation were not defined.}
 \item \textbf{What is the difference between the HJB and the HJ equations?}
-HJ generally refers to either HJB or HJI. The HJB equation is used when the dynamics only involves a control, and the HJI equation is used when the dynamics involve both a control and a disturbance.
-\item \textit{Figure 6 – What is the zero plane and where is it in the picture?}
+HJ generally refers to either HJB or HJI.
+The HJB equation is used when the dynamics only involves a control, and the HJI equation is used when the dynamics involve both a control and a disturbance.
+To avoid confusion, all HJI and HJB PDEs are both now referred to as HJ PDEs.
+
+\item \textbf{Figure 6 – What is the zero plane and where is it in the picture?}
 \end{itemize}
@@
 \begin{itemize}
-\item \textit{``Reachability analysis is useful for constructing controllers ...'' – This does not say much. Please elaborate on it.}
-\item \textit{``The system dynamics with which the reachable set is computed provide additional flexibility when using reachability to construct controller...'' – Not clear.}
+\item \textbf{``Reachability analysis is useful for constructing controllers ...'' – This does not say much. Please elaborate on it.}
+\item \textbf{``The system dynamics with which the reachable set is computed provide additional flexibility when using reachability to construct controller...'' – Not clear.}
+
+Details are in later subsections.
+
 \item \textbf{Aren’t all calculations made much simple because you are in an air highway? Please elaborate on this.}
@@
 
-\item \textit{``liveness controller described in the previous sections when it is not in any danger of collision with other vehicles'' – As before, the concept of liveness has not been introduced before, so it may be difficult to the reader to understand what is going on.}
-\item \textit{``3.
+\item \textbf{``liveness controller described in the previous sections when it is not in any danger of collision with other vehicles'' – As before, the concept of liveness has not been introduced before, so it may be difficult to the reader to understand what is going on.}
+\item \textbf{``3.
 Avoiding collisions'' – What happens when a potential collision is detected and there is no solution to the obstacle avoidance problem?
@@
 \begin{itemize}
-\item \textit{``$\hat d$ is the highway’s direction of travel.'' – The direction of travel is not properly defined.}
+\item \textbf{``$\hat d$ is the highway’s direction of travel.'' – The direction of travel is not properly defined.}
 \end{itemize}
@@
 \begin{itemize}
-\item \textit{The discussion seems to overlook the definition of the information structures for the problem. The same happens with considerations about sensor performance.}
-\item \textit{``Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons.
+\item \textbf{The discussion seems to overlook the definition of the information structures for the problem. The same happens with considerations about sensor performance.}
+\item \textbf{``Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons.
 By treating each platoon as a single unit, we can reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.'' – This seems to be in contradiction with the example with an intruder vehicle.}
+
+When there is only one platoon, it made more sense to not treat it as a single unit in order to show a more interesting behavior.
+The wording of the paper has been changed to say that platoons \textit{can be} treated as single unit \textit{if needed}.
 \end{itemize}
@@
 \begin{itemize}
-\item \textit{What are the information structures for these problems?}
-\item \textit{The maneuvers described in Fig 9 seem to go against our intuition. A more detailed description of what is going on is needed.}
+\item \textbf{What are the information structures for these problems?}
+\item \textbf{The maneuvers described in Fig 9 seem to go against our intuition. A more detailed description of what is going on is needed.}
 \end{itemize}
@@
 \begin{itemize}
-\item \textit{``Many complex maneuvers can be performed using only a few reachability sets.'' – This phrase does not say much.}
+\item \textbf{``Many complex maneuvers can be performed using only a few reachability sets.'' – This phrase does not say much.}
 \end{itemize}

### 2016-11-15 code/platoon/RS_core/Quad4DRelativeLiveness.m
filled in experimental section, removed videos because they are too large

@@ -1,12 +1,12 @@
 function Quad4DRelativeLiveness()
-N = 71;
+N = 41;
 N = N * ones(4,1);
-gMin = [-1; -1; -1; -1];
+gMin = [-1.5; -10; -1; -10];
 gMax = [1; 1; 1; 1];
 
 % Acceleration bounds
-aMax = [3; 3];
-bMax = [3; 3];
+aMax = [-1; 1];
+bMax = [-1; 1];
 
 % Time vector
 dt = 0.01;

### 2016-11-18 docs/AIAA 2016 highway platooning/main.tex
minor changes to revision
added AIAA paper revision
second revision of UTM paper

@@
 \usepackage{cite}
-\newcommand{\MCnote}{\textcolor{red}}
+%\newcommand{\MCnote}[1]{\textcolor{red}{\textbf{#1}}}
+\newcommand{\MCnote}{\textcolor{black}}
 
@@
 
-\author{Mo Chen, Qie Hu, Jaime F. Fisac, Kene Akametalu, Casey Mackin, Claire J. Tomlin}
+\author{Mo Chen\thanks{PhD Candidate, Department of Electrical Engineering and Computer Sciences}, Qie Hu\thanksibid{1}, Jaime F.
+Fisac\thanksibid{1}, Kene Akametalu\thanksibid{1}, Casey Mackin\thanks{PhD Student, Department of Electrical Engineering and Computer Sciences}, Claire J.
+Tomlin\thanks{Professor, Department of Electrical Engineering and Computer Sciences}\\\textit{University of California, Berkeley}}
 \title{\MCnote{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}}
 
-\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations.
+\AIAAabstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations.
 As a result, unmanned aerial systems traffic management is needed to ensure the safety and \MCnote{goal satisfaction} of potentially thousands of UAVs flying simultaneously.
@@
 For a single altitude range, the proposed approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.
-Safety and \MCnote{goal satisfaction} are demonstrated through simulations of three scenarios.}
+We demonstrate the platooning concept through simulations of three representative scenarios.}
 

### 2016-11-18 docs/AIAA 2016 highway platooning/plat_sim.tex
finished editing
second revision of UTM paper

@@
 This occurs at $t=13.9$, where the platoon ``makes room'' for the intruder to pass by to avoid collisions; all vehicles deviate from their intended path, which is to follow the platoon leader or the highway.
+\MCnote{Note that in this case, we have assumed that the platoon does not move as a unit in response to an intruder to show more interesting behavior.}
 
@@
     \end{subfigure}   
-    \caption{A simulation showing how a platoon of four vehicles react to an intruder. \label{fig:in}}
+    \caption{A simulation showing how a platoon of four vehicles reacts to an intruder. \label{fig:in}}
 \end{figure}

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/high_eikon.tex
added final version AIAA

--- 2016-11-09 docs/AIAA 2016 highway platooning/high_eikon.tex
@@
 
-It is well known that the \MCnote{viscosity solution} \cite{Crandall84} to the Eikonal equation \eqref{eq:eikonal} precisely computes the function $\ocost(\pos^d)$ given the cost map $\cmap$ \cite{Sethian96,Alton06}.
+It is well known that the viscosity solution \cite{Crandall84} to the Eikonal equation \eqref{eq:eikonal} precisely computes the function $\ocost(\pos^d)$ given the cost map $\cmap$ \cite{Sethian96,Alton06}.
 Note that a single function characterizes the minimum cost from an origin $\pos^o$ to \textit{any} destination $\pos^d$.

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/high_form.tex
added final version AIAA

--- 2016-11-10 docs/AIAA 2016 highway platooning/high_form.tex
@@
 To each highway, we assign a speed of travel $v_\hw$ and specify the direction of travel to be the direction from $\hw(0)$ to $\hw(1)$, denoted using a unit vector $\hwd = \frac{\hw(1) - \hw(0)}{\lVert\hw(1) - \hw(0)\rVert_2}$.
-\MCnote{As we will show in Section \ref{sec:platooning}, UAVs use simple controllers to track the highway.}
+As we will show in Section \ref{sec:platooning}, UAVs use simple controllers to track the highway.
 
@@
 With this in mind, we now define the air highway placement problem, and propose a simple and fast way to approximate its solution that allows for real-time recomputation.
-\MCnote{Our solution based on solving the Eikonal equation can be thought of as converting a cost map over a geographic area in continuous space into a discrete graph whose nodes are waypoints joined by edges which are the air highways.}
+Our solution based on solving the Eikonal equation can be thought of as converting a cost map over a geographic area in continuous space into a discrete graph whose nodes are waypoints joined by edges which are the air highways.
 
-\MCnote{Note that the primary purpose of this section is to provide a method for the real-time placement of air highways.
-The specifics of determining the cost map based on population density, geography, weather forecast information, etc., as well as the criteria for when air highway locations need to be updated, is beyond the scope of this paper.}
+Note that the primary purpose of this section is to provide a method for the real-time placement of air highways.
+The specifics of determining the cost map based on population density, geography, weather forecast information, etc., as well as the criteria for when air highway locations need to be updated, is beyond the scope of this paper.
 
-\MCnote{In addition, if vehicles in the airspace are far away from each other, it may be reasonable for all vehicles to fly in an unstructured manner.
+In addition, if vehicles in the airspace are far away from each other, it may be reasonable for all vehicles to fly in an unstructured manner.
 As long as multiple-way conflicts do not occur, pairwise collision avoidance maneuvers would be sufficient to ensure safety.
@@
 By organizing vehicles into platoons, the likelihood of multiple-way conflicts is vastly reduced.
-Structured flight is in general less efficient for the individual vehicle, and this loss of efficiency can be thought of as a cost incurred by the vehicles in order ensure higher levels of safety.}
+Structured flight is in general less efficient for the individual vehicle, and this loss of efficiency can be thought of as a cost incurred by the vehicles in order ensure higher levels of safety.
 
-\MCnote{In general, there may be many different levels of abstractions in the airspace.
+In general, there may be many different levels of abstractions in the airspace.
 For larger regions such as cities, air highways may prove beneficial, and for a small region such as a neighborhood, perhaps unstructured flight is sufficiently safe.
-Further research is needed to better understand parameters such as the density of vehicles above which unstructured flight is no longer manageable, and other details like platoon size.}
+Further research is needed to better understand parameters such as the density of vehicles above which unstructured flight is no longer manageable, and other details like platoon size.
 
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{"fig/highway_illustration"}
+	\includegraphics[width=0.95\columnwidth]{"highway_illustration"}
 	\caption{Illustration of the air highway placement procedure.}

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/high_sim.tex
added final version AIAA

--- 2016-07-11 docs/AIAA 2016 highway platooning/high_sim.tex
@@
 	\centering
-	\includegraphics[width=\textwidth]{"fig/airHighway_results"}
-	\caption{Cost-minimizing paths computed by the Fast Marching Method based on the assumed cost map of the San Francisco Bay Area}
+	\includegraphics[width=\columnwidth]{"airHighway_results"}
+	\caption{Cost-minimizing paths computed by the Fast Marching Method based on the assumed cost map of the San Francisco Bay Area.}
 	\label{fig:airHighway_results}
@@
 Note that we could have gone further to merge some of the overlapping highways.
-However, the purpose of this section is to illustrate the natural occurrence of air highways from cost-minimizing paths; post-processing of the cost-minimizing paths is not our focus.
+However, the purpose of this section is to illustrate the natural occurrence of air highways from cost-minimizing paths; post-processing of the cost-minimizing paths, which serve as a guide for defining air highways, is not our focus.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{"fig/airHighway_sparse"}
+	\includegraphics[width=\columnwidth]{"airHighway_sparse"}
 	\caption{Results of conversion from cost-minimizing paths to highway way points.}
@@
 \subsection{Real-Time Highway Location Updates}
-Since \eqref{eq:eikonal} can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost map changes.
+Since \eqref{eq:eikonal} can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost map changes at a particular time.
 This flexibility can be useful in any situation in which unforeseen circumstances could cause a change in the cost of a particular region of the airspace.

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/introduction.tex
added final version AIAA

--- 2016-11-09 docs/AIAA 2016 highway platooning/introduction.tex
@@
 Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, videography, and search and rescue \cite{Kopardekar16}.
-In the future, the use of UAVs \MCnote{is likely to become more and more prevalent.}
+In the future, the use of UAVs is likely to become more and more prevalent.
 
@@
 Optimal control and game theory present powerful tools for providing safety and goal satisfaction guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10, Mitchell05, Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15, Chen14, Chen17, Ding08}.
-These formulations are based on Hamilton-Jacobi (HJ) reachability, which can compute the \MCnote{backward reachable set (BRS)}, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
+These formulations are based on Hamilton-Jacobi (HJ) reachability, which can compute the backward reachable set (BRS), defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states.
 HJ reachability is a powerful tool because BRS can be used for synthesizing both controllers that steer the system away from a set of unsafe states (``safety controllers'') to guarantee safety, and controllers that steer the system into a set of goal states (``goal satisfaction controllers'') to guarantee goal satisfaction.
-\MCnote{Unlike many formulations of reachability, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of controlled non-linear systems under disturbances}.
-Furthermore, HJ reachability analysis \MCnote{is complemented by} many numerical tools readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox, Osher02, Sethian96}.
+Unlike many formulations of reachability, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of controlled nonlinear systems under disturbances.
+Furthermore, HJ reachability analysis is complemented by many numerical tools readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox, Osher02, Sethian96}.
 However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles.
@@
 Once air highways are in place, platoons of UAVs can then fly in fixed formations along the highway to get from origin to destination.
-\MCnote{The air highway structure greatly simplifies safety analysis, while at the same time intuitively allows human participation in airspace management.}
+The air highway structure greatly simplifies safety analysis, while at the same time allows intuitive human participation in unmanned airspace management.
 
@@
 
-Previous analyses of a large number of vehicles typically do not provide safety and \MCnote{goal satisfaction} guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
+Previous analyses of a large number of vehicles typically do not provide safety and goal satisfaction guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles.
 In the second part of this paper, we propose organizing UAVs into platoons, which provides a structure that allows pairwise safety guarantees from HJ reachability to better translate to safety guarantees for the whole platoon.
@@
 Finally, we show several simulations to illustrate the behavior of UAVs in various scenarios.
+
+Overall, this paper is not meant to provide an exhaustive solution to the unmanned airspace management problem.
+Instead, this paper illustrates that the computation intractability of HJ reachability can be overcome using an air highway structure with UAVs flying in platoons.
+In addition, the results are intuitive, which can facilitate human participation in managing the airspace.
+Although many challenges not addressed in this paper still need to be overcome, this paper can provide a starting point for future research in large-scale UASs with safety and goal satisfaction guarantees.

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/main.tex
added final version AIAA

--- 2016-11-18 docs/AIAA 2016 highway platooning/main.tex
@@
-\documentclass[submit]{aiaa-pretty}
+\documentclass[journal]{aiaa-pretty}
 %\documentclass[submit]{AIAA}
@@
 \usepackage{cite}
-%\newcommand{\MCnote}[1]{\textcolor{red}{\textbf{#1}}}
-\newcommand{\MCnote}{\textcolor{black}}
 
@@
 Tomlin\thanks{Professor, Department of Electrical Engineering and Computer Sciences}\\\textit{University of California, Berkeley}}
-\title{\MCnote{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}}
+\title{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}
 
 \AIAAabstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations.
-As a result, unmanned aerial systems traffic management is needed to ensure the safety and \MCnote{goal satisfaction} of potentially thousands of UAVs flying simultaneously.
+As a result, unmanned aerial systems traffic management is needed to ensure the safety and goal satisfaction of potentially thousands of UAVs flying simultaneously.
 Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers is unrestricted.
@@
 Within platoons traveling on air highways, each vehicle is modeled as a hybrid system.
-Using Hamilton-Jacobi reachability, safety and \MCnote{goal satisfaction} are guaranteed for all mode transitions.
+Using Hamilton-Jacobi reachability, safety and goal satisfaction are guaranteed for all mode transitions.
 For a single altitude range, the proposed approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges.

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/plat_controllers.tex
added final version AIAA

--- 2016-11-09 docs/AIAA 2016 highway platooning/plat_controllers.tex
@@
 
-Here, we represent the target set $\mathcal{L}_H$ as the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE that we need to solve.
-Once the HJB PDE is solved, we obtain the BRS $\mathcal V_H(t)$ from the subzero level set of the solution $V_H(t,x)$.
+Here, we represent the target set $\mathcal{L}_H$ as the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJ PDE that we need to solve.
+Once the HJ PDE is solved, we obtain the BRS $\mathcal V_H(t)$ from the subzero level set of the solution $V_H(t,x)$.
 More concretely, $\mathcal{V}_H(T) = \{x: V_H(-T,x)\le 0\}$ is the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.
@@
 
-The target set $\mathcal{L}_P$ is represented by the zero sublevel set of the implicit surface function $l_P(x)$, which specifies the terminal condition of the HJI PDE \eqref{eq:HJIPDE}.
+The target set $\mathcal{L}_P$ is represented by the zero sublevel set of the implicit surface function $l_P(x)$, which specifies the terminal condition of the HJ PDE \eqref{eq:HJIPDE}.
 The zero sublevel set of the solution to \eqref{eq:HJIPDE}, $V_P(-T,x)$, gives us the set of relative states from which a quadrotor can reach the target in the relative coordinates within a duration of $T$.
@@
 
-We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJI PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition.
+We can now define the implicit surface function $l_S(x)$ corresponding to $\mathcal{L}_S$, and solve the HJ PDE \eqref{eq:HJIPDE} using $l_S(x)$ as the terminal condition.
 As before, the zero sublevel set of the solution $V_S(t,x)$ specifies the BRS $\mathcal{V}_S(t)$, which characterizes the states in the augmented relative coordinates, as defined in \eqref{eq:rel_dyn_aug}, from which $Q_i$ \textit{cannot} avoid $\mathcal{L}_S$ for a time period of $t$, if $Q_j$ uses the worst-case control.

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/plat_form.tex
added final version AIAA

--- 2016-11-10 docs/AIAA 2016 highway platooning/plat_form.tex
@@
 Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways.
-\MCnote{The air highway structure along with the UAV platooning concept together enable the use of reachability to analyze safety and goal satisfaction properties.} The structure reduces the likelihood of multiple-way conflicts, and makes pairwise analysis more indicative of the joint safety of all UAVs.
-\MCnote{In addition to reducing complexity, the proposed structure is intuitive, and allows human participation in the monitoring and management of the unmanned airspace.}
+The air highway structure along with the UAV platooning concept together enable the use of reachability to analyze safety and goal satisfaction properties.
+The structure reduces the likelihood of multiple-way conflicts, and makes pairwise analysis more indicative of the joint safety of all UAVs.
+In addition to reducing complexity, the proposed structure is intuitive, and allows human participation in the monitoring and management of the unmanned airspace.
 
@@
 \noindent where $x$ represents the state, and $u$ represents the control action.
-The techniques we present in this paper do not depend on the dynamics of the vehicles, \MCnote{as long as their dynamics are known}.
+The techniques we present in this paper do not depend on the dynamics of the vehicles, as long as their dynamics are known.
 However, for concreteness, we assume that the UAVs are quadrotors that fly at a constant altitude under non-faulty circumstances.
@@
 
-\begin{equation} \label{eq:dyn}
+\begin{equation}
+\label{eq:dyn}
 \begin{aligned}
@@
 
-\MCnote{Such a fail-safe mechanism could be an emergency landing procedure such as those analyzed in \cite{Adler2012,Coombes2014,Idicula2015}.
+Such a fail-safe mechanism could be an emergency landing procedure such as those analyzed in \cite{Adler2012,Coombes2014,Idicula2015}.
 Typically, emergency landing involves identifying the type of fault and finding feasible landing locations given the dynamics during the fault.
-We will omit these details and summarize them into $\td$, the time required to exit the current altitude level.}
+We will omit these details and summarize them into $\td$, the time required to exit the current altitude level.
 \end{itemize}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{"fig/vehicleModes"}
-	\caption{Hybrid modes for vehicles in platoons.}
+	\includegraphics[width=\columnwidth]{"vehicleModes"}
+	\caption{Hybrid modes for vehicles in platoons. Vehicles begin in the ``Free'' mode before they enter the highway.}
 	\label{fig:vehicleModes}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{"fig/vehicleNotation"}
+	\includegraphics[width=\columnwidth]{"vehicleNotation"}
 	\caption{Notation for vehicles in platoons.}
@@
 
-%SHOULD EVASION BE A MODE?
-
 \begin{itemize}
@@
 
-In general, the control strategy of each vehicle has a safety component, which specifies a set of states that it must avoid, and \MCnote{a goal satisfaction component}, which specifies a set of states that the vehicle aims to reach.
+In general, the control strategy of each vehicle has a safety component, which specifies a set of states that it must avoid, and a goal satisfaction component, which specifies a set of states that the vehicle aims to reach.
 Together, the safety and goal satisfaction controllers guarantee the safety and success of a vehicle in the airspace making any desired mode transition.

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/plat_safety.tex
added final version AIAA

--- 2016-11-09 docs/AIAA 2016 highway platooning/plat_safety.tex
@@
 
-Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons \MCnote{when needed}.
+Given that vehicles within a platoon are safe with respect to each other, each platoon can be treated as a single vehicle, and perform collision avoidance with other platoons when needed.
 The option of treating each platoon as a single unit can reduce the number of individual vehicles that need to check for safety against each other, reducing overall computation burden.

### 2016-11-21 docs/AIAA 2016 highway platooning final submission/plat_summary.tex
added final version AIAA

--- 2016-11-09 docs/AIAA 2016 highway platooning/plat_summary.tex
@@
 As long as a vehicle is not in potential danger according to the safety BRSs, it is free to use any other controller.
-All of these other controllers are \MCnote{\textit{goal satisfaction controllers}}, and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.
+All of these other controllers are \textit{goal satisfaction controllers}, and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.
 
@@
 	\centering
-	\includegraphics[width=0.75\textwidth]{"fig/modeControllers"}
+	\includegraphics[width=0.75\columnwidth]{"modeControllers"}
 	\caption{Summary of mode switching controllers. Reachability-based controllers are shown as the blue and green arrows.}

### 2016-11-21 docs/AIAA 2016 highway platooning/fig/RSExample.m

@@ -13,7 +13,8 @@ x = g.xs{1};
 y = g.xs{2};
 R = 4;
 
-figure
+f = figure;
+f.Color = 'w';
 %%
 T = sqrt(x.^2 + y.^2) - R;
 surf(x,y,T, 'facecolor', 'r', 'facealpha', 0.3, 'edgecolor', 'none')
@@ -67,6 +68,8 @@ plot(s+R*cos(t), R*sin(t),  'b-', 'linewidth', 4)
 
 xlabel('x')
 ylabel('y')
-legend('l(x)','Target set', 'Zero plane', 'V(t,x)', 'Reachable set')
+axis equal
+legend('l(x)','Target set', 'Zero plane', 'V(t,x)', 'Reachable set', ...
+  'Location', 'best')
 
 end

### 2017-01-31 docs/AIAA 2016 highway platooning final submission/high_waypoints.tex
updated final submission to better match published version

--- 2016-07-08 docs/AIAA 2016 highway platooning/high_waypoints.tex
@@
 
-There are many different ways to sparsify the close-spaced set of points on each path, and this process will not be our focus.
+There are many different ways to do this, and this process will not be our focus.
 However, for illustrative purposes, we show how this process may be started.
@@
 In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), which may contribute to cluttering the airspace with too many waypoints.
-One way to sparsify the waypoints is to cluster the points.
+To reduce clutter, one could cluster the points.
 Afterwards, each cluster of points can be replaced by a single point located at the centroid of the cluster.

### 2017-01-31 docs/AIAA 2016 highway platooning final submission/introduction.tex
updated final submission to better match published version

@@
 \section{Introduction}
-Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91}; however, recently there has been an immense surge of interest in using UAVs for civil applications.
+Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91, Haulman2003}; however, recently there has been an immense surge of interest in using UAVs for civil applications.
 Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, videography, and search and rescue \cite{Kopardekar16}.

### 2017-01-31 docs/AIAA 2016 highway platooning final submission/main.tex
updated final submission to better match published version

@@
 Fisac\thanksibid{1}, Kene Akametalu\thanksibid{1}, Casey Mackin\thanks{PhD Student, Department of Electrical Engineering and Computer Sciences}, Claire J.
-Tomlin\thanks{Professor, Department of Electrical Engineering and Computer Sciences}\\\textit{University of California, Berkeley}}
-\title{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}
+Tomlin\thanks{Professor, Department of Electrical Engineering and Computer Sciences, Member AIAA}\\\textit{University of California, Berkeley}}
+\title{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Platoons on Air Highways}
 

### 2017-01-31 docs/AIAA 2016 highway platooning final submission/plat_safety.tex
updated final submission to better match published version

@@
 In this case, a ``safety breach" occurs.
-Our synthesis of the safety controller guarantees that between every pair of vehicles $\veh{i},\veh{k}$, as long as $V_S(-t,x_i- x_k)>0$, $\exists u_i$ to keep $\veh{i}$ from colliding with $\veh{k}$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $\veh{k}$.
+Our synthesis of the safety controller guarantees the following: between every pair of vehicles $\veh{i},\veh{k}$, if $V_S(-t,x_i- x_k)>0$, then $\exists u_i$ to keep $\veh{i}$ from colliding with $\veh{k}$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $\veh{k}$.
 Therefore, as long as the number of ``safety breaches" is at most one for $\veh{i}$, $Q_i$ can simply use the optimal control to avoid $\veh{k}$ and avoid collision for the time horizon of $t$.
